### 2018-06-22 reports/paper.tex
First commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is the LaTeX ARTICLE template for RSC journals
%Copyright The Royal Society of Chemistry 2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[twoside,twocolumn,9pt]{article}
\usepackage{extsizes}
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage[version=3]{mhchem}
\usepackage[left=1.5cm, right=1.5cm, top=1.785cm, bottom=2.0cm]{geometry}
\usepackage{balance}
\usepackage{times,mathptmx}
\usepackage{sectsty}
\usepackage{graphicx} 
\usepackage{lastpage}
\usepackage[format=plain,justification=justified,singlelinecheck=false,font={stretch=1.125,small,sf},labelfont=bf,labelsep=space]{caption}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{fnpos}
\usepackage[english]{babel}
\usepackage{amsmath}
\addto{\captionsenglish}{%
  \renewcommand{\refname}{Notes and references}
}
\usepackage{array}
\usepackage{droidsans}
\usepackage{charter}
\usepackage[T1]{fontenc}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage[compact]{titlesec}
\usepackage{hyperref}
%%%Please don't disable any packages in the preamble, as this may cause the template to display incorrectly.%%%

\newcommand*{\citen}[1]{%
	\begingroup
	\romannumeral-`\x % remove space at the beginning of \setcitestyle
	\setcitestyle{numbers}%
	\cite{#1}%
	\endgroup   
}

\usepackage{epstopdf}%This line makes .eps figures into .pdf - please comment out if not required.

\definecolor{cream}{RGB}{222,217,201}

\begin{document}

\pagestyle{fancy}
\thispagestyle{plain}
\fancypagestyle{plain}{

%%%HEADER%%%
\fancyhead[C]{\includegraphics[width=18.5cm]{head_foot/header_bar}}
\fancyhead[L]{\hspace{0cm}\vspace{1.5cm}\includegraphics[height=30pt]{head_foot/journal_name}}
\fancyhead[R]{\hspace{0cm}\vspace{1.7cm}\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}
\renewcommand{\headrulewidth}{0pt}
}
%%%END OF HEADER%%%

%%%PAGE SETUP - Please do not change any commands within this section%%%
\makeFNbottom
\makeatletter
\renewcommand\LARGE{\@setfontsize\LARGE{15pt}{17}}
\renewcommand\Large{\@setfontsize\Large{12pt}{14}}
\renewcommand\large{\@setfontsize\large{10pt}{12}}
\renewcommand\footnotesize{\@setfontsize\footnotesize{7pt}{10}}
\makeatother

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\footnoterule{\vspace*{1pt}% 
\color{cream}\hrule width 3.5in height 0.4pt \color{black}\vspace*{5pt}} 
\setcounter{secnumdepth}{5}

\makeatletter 
\renewcommand\@biblabel[1]{#1}            
\renewcommand\@makefntext[1]% 
{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
\makeatother 
\renewcommand{\figurename}{\small{Fig.}~}
\sectionfont{\sffamily\Large}
\subsectionfont{\normalsize}
\subsubsectionfont{\bf}
\setstretch{1.125} %In particular, please do not alter this line.
\setlength{\skip\footins}{0.8cm}
\setlength{\footnotesep}{0.25cm}
\setlength{\jot}{10pt}
\titlespacing*{\section}{0pt}{4pt}{4pt}
\titlespacing*{\subsection}{0pt}{15pt}{1pt}
%%%END OF PAGE SETUP%%%

%%%FOOTER%%%
\fancyfoot{}
\fancyfoot[LO,RE]{\vspace{-7.1pt}\includegraphics[height=9pt]{head_foot/LF}}
\fancyfoot[CO]{\vspace{-7.1pt}\hspace{13.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[CE]{\vspace{-7.2pt}\hspace{-14.2cm}\includegraphics{head_foot/RF}}
\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt}
\setlength{\arrayrulewidth}{1pt}
\setlength{\columnsep}{6.5mm}
\setlength\bibsep{1pt}
%%%END OF FOOTER%%%

%%%FIGURE SETUP - please do not change any commands within this section%%%
\makeatletter 
\newlength{\figrulesep} 
\setlength{\figrulesep}{0.5\textfloatsep}

\newcommand{\topfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\botfigrule}{\vspace*{-2pt}% 
\noindent{\color{cream}\rule[\figrulesep]{\columnwidth}{1.5pt}} }

\newcommand{\dblfigrule}{\vspace*{-1pt}% 
\noindent{\color{cream}\rule[-\figrulesep]{\textwidth}{1.5pt}} }

\makeatother
%%%END OF FIGURE SETUP%%%

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
\vspace{3cm}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Probabilistic determination of the effect of a deep-euctectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
\vspace{0.3cm} & \vspace{0.3cm} \\

 & \noindent\large{Adrian Sanchez-Fernandez,\textit{$^{ab}$}$^{\dag}$ Andrew R. McCluskey,\textit{$^{ac}$}$^{\dag}$ Karen J. Edler,$^{\ast}$\textit{$^{a}$}$^{\dag}$ Andrew J. Jackson,\textit{$^{bd}$} Richard A. Campbell,\textit{$^{e}$} and Thomas Arnold\textit{$^{abc}$}} \\%Author names go here instead of "Full name", etc.

\includegraphics{head_foot/dates} & \noindent\normalsize{The abstract should be a single paragraph which summarises the content of the article. Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."

\end{tabular}

	\end{@twocolumnfalse} \vspace{0.6cm}

  ]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

%%%FONT SETUP - please do not change any commands within this section
\renewcommand*\rmdefault{bch}\normalfont\upshape
\rmfamily
\section*{}
\vspace{-1cm}

%%%FOOTNOTES%%%

\footnotetext{\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK.}}
\footnotetext{\textit{$^{b}$~European Spallation Source, SE-211 00 Lund, Sweden.}}
\footnotetext{\textit{$^{c}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK.}}
\footnotetext{\textit{$^{d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden.}}
\footnotetext{\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France.}}
\footnotetext{$^{\dag}$~These authors have contributed equally to the work presented here.}
\footnotetext{$^{\ast}$~Corresponding author: k.edler@bath.ac.uk}

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required

\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P. Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}

%%%END OF FOOTNOTES%%%

%%%MAIN TEXT%%%%
\section{Introduction}
Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, amoung others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between the precursors, allowing the mixture to remain liquid at room temperature due to the high-entropy state of the mixture.\cite{Hammond2016, Hammond2017, Araujo2017} Furthermore, through different combinations of the precursors materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}

These solvents have recently shown the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} demonstrating the presense of a solvophobic effect. The behaviour of biomolecules in DES has also seen and increase in interest, due to potential applications towards the preservation of biomolecules by DES, and as environments for enzymatic reactions\cite{Merza2018} additionally, the behaviour and conformation of proteins and enzymes in these solvents have received remarkable interest.\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} Finally, recent investigations have also shown that DES have been shown to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}

The formation of phospholipid monolayers plays a key role in many biological and technological processes. The amphiphilic lipids commonly show a low soluibilty in the one of the two phases, leading to the formation of a stable monolayer at the interface.\cite{Mohwald1990} Phospholipid consist of a charged headgroup, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the lipid-ion interactions on structure, monomer packing and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers in non-aqueous media has not been reported, to the best of the authors' knowledge.

Recent developments in computational resources and software has enabled powerful methodologies to be harnessed by those from non-computer science backgrounds. This has mostly occurred through open-source software projects such as Python and the Jupyter notebooks framework.\cite{vanRossum1995,Kluyver2016} In the area of neutron and X-ray reflectometry data-analysis, this has led to the development of tool such as refnx,\cite{Nelson2018} a Python library for the fitting of layer-based models to reflectometry data. The availiablility of such software enables the use of models that contain chemical-context within theirs structure. Wherein, the chemically-relevant information known about the system is used within the model, such as the constaint that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups.

The use of a Python library for fitting enable powerful probability distribution function sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This library allows for the sampling of a high-dimensionality parameter space, such as that which is relevant to reflectometry fitting to be performed with relative ease. This results in estimatations of the inverse uncertainties associated with each parameter as well as information about the correlations between different parameters within the model.

In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemical-context modelling of X-ray reflectometry measurements. Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air. This allowed the nature of two, chemically distinct, phospholipid headgroups to be understood in this non-aqueous solvent, in addition to the effect of the tail chain length.

\section{Experimental}

\subsection{Materials}
Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) were purchased and used without further purification. The deep eutectic solvent was prepared by mixing the precursors at the appropriate mole ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid was formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.

The water content on the deep eutectic solvent was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to keep track of any effect from the presence of water on our results. Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}

DPPC (> 99 \%), DMPC (> 99 \%), and DMPG (> 99 \%) were supplied by Avanti Polar Lipids and used as received. DLPC (> 99 \%) was supplied by Sigma-Aldrich and used as received. Sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration. After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface. Surface concentration was modified by closing and opening the PTFE barriers of the Langmuir trough (XRR).

\subsection{Methods}
X-ray reflectivity measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$. The data was normalised to the incident beam and background was measured from off-specular reflection and subsequently subtracted. The sample environment consisted of a PTFE Langmuir trough. Samples were equilibrated for at least one hour and preserved under argon atmosphere to minimise the adsorption of water by the subphase. Surface concentration was controlled through opening and closing the barriers of the Langmuir trough and measured using an aluminium Wilhelmy plate. X-ray reflectivity data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG and all measurements were made at 22 $^\circ$C at five different surface concentrations.

\subsection{Data analysis}
The use of reflectometry to analyse the structure of phospholipids on the surface of water has a histroy extending ovoer many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} This has led to some variation in the models used to fit experimental data, shown in Table \ref{tab:water}. Although, there appears to be a general consensus that the molecular volume of the phosphocholine is in the region of 320 \AA$^3$, and as a result this figure is also used as a physical constraint on the layer model when fitting reflectometry data. However, as this work involves the use of a non-aqueous solvent system we believe that the these literature values for the head group molecular volumes may be unreliable. This is due to the charged nature of the zwitterionic and anionic lipid heads having a significant interaction with the solvent in both the neutral water and the charged DES.

\begin{table*}
	\small
	\caption{\ Lipid component volumes extracted from different literature sources. $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTS to differential vibrating tube densimetry}
	\label{tab:water}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllllll}
		\hline 
		Lipid & DPPC & & & & DMPC & & & DMPG \\
		\hline
		Reference & [\citen{Armen1998}] & [\citen{Petrache1997}] & [\citen{Sun1994}] & [\citen{Tardieu1973}] & [\citen{Kucerka2004}] & [\citen{Nagle1978}] & [\citen{Schmidt1985}] & [\citen{Pan2012}] \\
		$V_l$/\AA$^3$ &1216.96 & 1219 & 1148 & 1224 & 1101 & 1061 & 1094 & 1058 \\
		$V_h$/\AA$^3$ & 326.00 & 324 & 319 & 360 & 319 & 344 & & 291 \\
		$V_t$/\AA$^3$ & 890.96 & 895 & 829 & 864 & 782 & 717 & & 767 \\
		Method & MD & MD & WAXS & NB & NB & NB & DVTS & DVTS \\
		T/$^\circ$C & 25 & 50 & 24 & 25 & 30 & 30 & & 30 \\
		\hline
	\end{tabular*}
\end{table*}

To allow for the use of a chemically-relevant model, where the lipid head group molecular volume was allowed to vary, the Python library refnx\cite{Nelson2018} as used. This software allows the inclusion of a custom chemically-sensible model from which the parameters to be fed into the Abel\`{e}s layer-model,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained. This custom model, along with Jupyter notebook showing in full the analysis performed, can be found in the ESI.

This chemical model involves considering the lipids as consisting of head groups and tail groups. The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron), and a molecular volume, $V_h$. The head groups make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, with a same volume fraction of solvent can intercalate into the head group regin, $\phi_h$. While, the tail groups also have a calculated scattering length, $b_t$, and molecular volume, $V_t$, however the thickness of the tail group layer, $d_t$, is found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$, 
\begin{equation}
\label{equ:tl}
d_t = t_t \cos{\theta_t}.
\end{equation}
The air above the monolayer is also able to solvate the tail region with some volume fraction, $\phi_t$. The scattering length density of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows, 
\begin{equation}
\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}\phi_i,
\end{equation}
where $\text{SLD}_{s}$ is the scattering length density of the superphase (air) and the subphase (DES) for the tail and head groups respectively, and $i$ indicates either the tail or head layer. In order to ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was added to the model,
\begin{equation}
d_h = \frac{V_hd_t(1-\phi_t)}{V_t(1-\phi_h)}. 
\end{equation}

This custom model was used to co-refine the two highest surface concentration measurements to determine the molecular volume for the lipid head group, $V_h$, which was allowed to vary within resonable bounds but held constant between the two concentrations. Other parameters that were allowed to very were $\theta_t$, $\phi_t$, $\phi_h$, $\sigma_t$, and $\sigma_h$, while the parameters shown in Table \ref{tab:invariant} were held constant at the values given. The length of the carbon chain was kept constant to the value given by the Tanford equation,\cite{Tanford1980} this is valid due to the condensed nature of the monolayer at this surface pressure resulting in the extending, staggered conformation of the chain being likely.

%Using this custom model, the following parameters where allowed to vary, within resonable bounds; $V_h$, $\theta_t$, $\phi_t$, $\phi_h$, $\sigma_t$, and $\sigma_h$, while those values shown in Table \ref{tab:invariant} were held constant.

\begin{table}[h]
	\small
	\caption{\ The variant parameters within the chemically-sensible model. $^a$Values determined from Armen \emph{et al.}\cite{Armen1998} $^b$Values obtained from the Tanford formula where the carbon chains are assumed to be fully extended.\cite{Tanford1980} $^c$Values extracted from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
	\label{tab:invariant}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ll}
		\hline
		Parameter & Value \\
		\hline
		DP-$b_t$/fm & 6897 \\
		DM-$b_t$/fm & 5985 \\
		DL-$b_t$/fm & 5073 \\
		PC-$b_h$/fm & 4674 \\
		PG-$b_h$/fm & 4731 \\
		DP-$V_t$/\AA$^3$ & 891$^a$ \\
		DM-$V_t$/\AA$^3$ & 779$^a$ \\
		DL-$V_t$/\AA$^3$ & 667$^a$ \\	
		DP-$t_t$/\AA & 21.8$^b$ \\
		DM-$t_t$/\AA & 19.3$^b$ \\
		DL-$t_t$/\AA & 16.7$^b$ \\
		$\text{SLD}_{\text{sup}}$/$\times10^{-6}$\AA$^{-2}$ & 0\\
		$\text{SLD}_{\text{sub}}$/$\times10^{-6}$\AA$^{-2}$ & 10.8$^c$ \\
		\hline
	\end{tabular*}
\end{table}

The fitting of the reflectometry model to the experimental involved transforming the result of the model and the data into $rq^4$ such that the artifact of the Fresnel decay was removed before using the differential evoulation method available to refnx from the scipy library, to find the parameters which gave the best fit to the data. The parameter space for each of these was then probed using the MCMC method available through emcee, this allowed for an estimate of the probability distribution function associated with each parameter. In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.

\section{Results \& Discussion}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
	\caption{The reflectometry profile, scattering length density profile and probability distribution function for each of the three phosphocholine containing lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.}
	\label{fig:lipids}
\end{figure}
The custom model with a variable head molecular volume, was co-refined for the highest two concentrations of all lipids. The resulting reflectometry profiles, associated scattering length density profiles and the probability distribution function (PDF) for the head group molecular volume are shown in Figure \ref{fig:lipids}. Table \ref{tab:liptab} gives details of the other varying parameters for each lipid, these are given with asymmetric error bars which give the 95 \% confidence interval, the full probability distribution plots can be found in the ESI. 
\begin{table*}
	\small
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the phosphocholine reflectometry model. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl}.}
	\label{tab:liptab}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllllll}
		\hline
		 & DLPC & & DMPC & & DPPC & & DMPG & \\
		\hline
		Parameter & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 \\
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle4.txt} & \input{../output/dlpc/angle5.txt} & \input{../output/dmpc/angle4.txt} & \input{../output/dmpc/angle5.txt} & \input{../output/dppc/angle4.txt} & \input{../output/dppc/angle5.txt} & \input{../output/dmpg/angle4.txt} & \input{../output/dmpg/angle5.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dlpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dlpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
		$\phi_t$/$\times10^{-2}$ & \input{../output/dlpc/solt4.txt} & \input{../output/dlpc/solt5.txt} & \input{../output/dmpc/solt4.txt} & \input{../output/dmpc/solt5.txt} & \input{../output/dppc/solt4.txt} & \input{../output/dppc/solt5.txt} & \input{../output/dmpg/solt4.txt} & \input{../output/dmpg/solt5.txt} \\
		$\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh4.txt} & \input{../output/dlpc/solh5.txt} & \input{../output/dmpc/solh4.txt} & \input{../output/dmpc/solh5.txt} & \input{../output/dppc/solh4.txt} & \input{../output/dppc/solh5.txt} & \input{../output/dmpg/solh4.txt} & \input{../output/dmpg/solh5.txt} \\
		$\sigma_t$/\AA & \input{../output/dlpc/rought4.txt} & \input{../output/dlpc/rought5.txt} & \input{../output/dmpc/rought4.txt} & \input{../output/dmpc/rought5.txt} & \input{../output/dppc/rought4.txt} & \input{../output/dppc/rought5.txt} & \input{../output/dmpg/rought4.txt} & \input{../output/dmpg/rought5.txt} \\
		$\sigma_h$/\AA & \input{../output/dlpc/roughh4.txt} & \input{../output/dlpc/roughh5.txt} & \input{../output/dmpc/roughh4.txt} & \input{../output/dmpc/roughh5.txt} & \input{../output/dppc/roughh4.txt} & \input{../output/dppc/roughh5.txt} & \input{../output/dmpg/roughh4.txt} & \input{../output/dmpg/roughh5.txt} \\
		\hline
	\end{tabular*}
\end{table*}

Since the tail chain length is held constant to the value of the Tanford length for a given lipid tail, there is a direct correlation between the thickness of the tail layer and the chain tilt angle from the model. It can be seen from Table \ref{tab:liptab} that as would be expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chains increases. Additionally, it is also observed that the value of the chain tilt either decreases, resulting in a tail thickness increase, or remains constant as the surface concentration increases. This indicates that for DLPC and DPPC these two highest surface concentration measurements where at a similar area per molecule, while the area per molecule slightly decreased between the two measurements for DMPC and DPPC. The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, as would be expected with the head layer becoming more packed and therefore there is less space for solvent.

The thickness of the tail layers in these condensed monolayers appears to agree well with values found for water-analogues for each of the lipids (DMPC: $d_t=15.8$ \AA,\cite{Johnson1991} DPPC: $d_t=16.7$ \AA\cite{Helm1987}). Previous work indicates, although there has been no direct comparison that the phosphatidylglycerol head layer may be thicker than phosphocholine at a water-air interface.\cite{Clifton2012,Johnson1991,Vaknin1991,Lawrie2000} However, the phosphocholine head group appears to be slightly expanded in the DES compared to in water (PPC: $d_h=8.4$ \AA\cite{Helm1987}) resulting in the values for the thicknesses of the head layers being similar between the two head groups.

Figures \ref{fig:lipids}(a-c) shows the PDF determined for the head group volume for each of the four lipids. The three lipids with a phosphocholine head group appear to show some unsystematic variance with values of \input{../output/dlpc/vh.txt} \AA$^{3}$ for DLPC, \input{../output/dmpc/vh.txt} \AA$^{3}$ for DMPC, and \input{../output/dppc/vh.txt} \AA$^{3}$ for DPPC. This is significantly less than the largest estimate of the head volume from literature sources, 360 \AA$^3$,\cite{Tardieu1973} and slightly less than lowest estimate, 319 \AA$^3$.\cite{Sun1994,Kucerka2004} The fact that the choline chloride component of the DES is charged in nature suggests that it has a screening effect on the charged interactions between the zwitterionic phosphocholine head groups reducing the volume that it occupies.

Figure \ref{fig:lipids}(d) contains the PDF for the phosphatidylglycerol head group volume, which was found to be \input{../output/dmpg/vh.txt} \AA$^{3}$. This agrees well with the literature value for this lipid head group of 291 \AA$^{3}$,\cite{Pan2012} indictating that the charged component of the DES solvent has little affect on the volume occupied by the phosphatidylglycerol head group.

It is possible to generalise the difference between the two lipid head groups in terms of the difference in their charges, with the phosphocholine group being zwitterionic in nature while the phosphatidylglycerol is anionic (Figure \ref{fig:heads}). The fact that the phosphatidylglycerol head group appears to show no deviation in volume at the air-DES interface, when compared with the air-water interface, suggests that the interaction resulting in the apparent decrease in volume of the phosphocholine head group is due to the positively-charged nitrogen group interacting with the negatively-charged chlorine component of the DES. The relatively small size of the chloride ion, compared to the choline moiety, means that it is able to intercalate more easily into the lipid head layer allowing for the charge screening to occur.

\begin{figure}
	\centering
	\includegraphics[width=0.30\textwidth]{figures/head_groups}
	\caption{The two lipid head groups compared in this study, where R indicates the carbon tail; (a) phosphatidylglycerol, (b) phosphocholine.}
	\label{fig:heads}
\end{figure}

Previous work has suggested that the DES may provide a segregated environment to better solubilise the phospholipid head groups.\cite{Bryant2016,Bryant2017}. Since both the phosphatidylglycerol and phosphocholine head groups contain a moeity of the DES solvent, it is possible for the choline terminal of the phosphocholine would favour the presence of glycerol, while the glycerol terminal of the phosphatidylglycerol would be favourable solubilised by the choline moeity of the DES. This solvent segregation of the DES may result in the phosphocholine head group being preferentially solubilised due to the greater molar abundence of glycerol in the 1:2 mixture, and hence giving a smaller volume for this head group than found in water.

\section{Conclusions}
The conclusions section should come in this section at the end of the article, before the Conflicts of interest statement.

\section*{Conflicts of interest}
There are no conflicts to declare.

\section*{Acknowledgements}
The authors would like to thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F. A.R.M. is grateful to the university of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149). We also thank Diamond Light Source and Institute Laue-Langevin for the awarded beamtime (SI10546-1 and 9-13-612 respectively).

%%%END OF MAIN TEXT%%%

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

\balance

%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
%\renewcommand\refname{Notes and references}

%%%REFERENCES%%%
\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
\bibliographystyle{rsc} %the RSC's .bst file

\end{document}

### 2018-06-22 src/data/refnx-0.0.15/motofit/SLDcalculatorUI.py

@@ -1,0 +1,170 @@
+# -*- coding: utf-8 -*-
+
+# Form implementation generated from reading ui file 'SLDcalculator.ui'
+#
+# Created: Tue Feb 18 14:22:24 2014
+#      by: pyside-uic 0.2.15 running on PySide 1.2.1
+#
+# WARNING! All changes made in this file will be lost!
+
+from PySide import QtCore, QtGui
+
+
+class Ui_Form(object):
+
+    def setupUi(self, Form):
+        Form.setObjectName("Form")
+        Form.setWindowModality(QtCore.Qt.NonModal)
+        Form.resize(355, 266)
+        self.gridLayout = QtGui.QGridLayout(Form)
+        self.gridLayout.setObjectName("gridLayout")
+        self.chemical_formula = QtGui.QLineEdit(Form)
+        self.chemical_formula.setText("")
+        self.chemical_formula.setObjectName("chemical_formula")
+        self.gridLayout.addWidget(self.chemical_formula, 0, 0, 1, 4)
+        self.use_volume = QtGui.QRadioButton(Form)
+        self.use_volume.setObjectName("use_volume")
+        self.gridLayout.addWidget(self.use_volume, 1, 3, 1, 1)
+        self.label_5 = QtGui.QLabel(Form)
+        self.label_5.setObjectName("label_5")
+        self.gridLayout.addWidget(self.label_5, 2, 0, 1, 3)
+        self.label_6 = QtGui.QLabel(Form)
+        self.label_6.setObjectName("label_6")
+        self.gridLayout.addWidget(self.label_6, 2, 3, 1, 1)
+        self.mass_density = QtGui.QDoubleSpinBox(Form)
+        sizePolicy = QtGui.QSizePolicy(
+            QtGui.QSizePolicy.Expanding,
+            QtGui.QSizePolicy.Fixed)
+        sizePolicy.setHorizontalStretch(0)
+        sizePolicy.setVerticalStretch(0)
+        sizePolicy.setHeightForWidth(
+            self.mass_density.sizePolicy().hasHeightForWidth())
+        self.mass_density.setSizePolicy(sizePolicy)
+        self.mass_density.setDecimals(3)
+        self.mass_density.setSingleStep(0.001)
+        self.mass_density.setProperty("value", 1.107)
+        self.mass_density.setObjectName("mass_density")
+        self.gridLayout.addWidget(self.mass_density, 3, 0, 1, 3)
[…]

### 2018-06-22 src/data/refnx-0.0.15/motofit/aboutUI.py

@@ -1,0 +1,44 @@
+# -*- coding: utf-8 -*-
+
+# Form implementation generated from reading ui file 'about.ui'
+#
+# Created: Thu Jan  8 11:35:49 2015
+#      by: pyside-uic 0.2.15 running on PySide 1.2.2
+#
+# WARNING! All changes made in this file will be lost!
+
+from PySide import QtCore, QtGui
+
+class Ui_Dialog(object):
+    def setupUi(self, Dialog):
+        Dialog.setObjectName("Dialog")
+        Dialog.resize(400, 300)
+        self.formLayout = QtGui.QFormLayout(Dialog)
+        self.formLayout.setFieldGrowthPolicy(QtGui.QFormLayout.FieldsStayAtSizeHint)
+        self.formLayout.setObjectName("formLayout")
+        self.textEdit = QtGui.QTextEdit(Dialog)
+        self.textEdit.setObjectName("textEdit")
+        self.formLayout.setWidget(0, QtGui.QFormLayout.LabelRole, self.textEdit)
+        self.buttonBox = QtGui.QDialogButtonBox(Dialog)
+        self.buttonBox.setOrientation(QtCore.Qt.Horizontal)
+        self.buttonBox.setStandardButtons(QtGui.QDialogButtonBox.Cancel|QtGui.QDialogButtonBox.Ok)
+        self.buttonBox.setObjectName("buttonBox")
+        self.formLayout.setWidget(1, QtGui.QFormLayout.LabelRole, self.buttonBox)
+
+        self.retranslateUi(Dialog)
+        QtCore.QObject.connect(self.buttonBox, QtCore.SIGNAL("accepted()"), Dialog.accept)
+        QtCore.QObject.connect(self.buttonBox, QtCore.SIGNAL("rejected()"), Dialog.reject)
+        QtCore.QMetaObject.connectSlotsByName(Dialog)
+
+    def retranslateUi(self, Dialog):
+        Dialog.setWindowTitle(QtGui.QApplication.translate("Dialog", "About Motofit", None, QtGui.QApplication.UnicodeUTF8))
+        self.textEdit.setHtml(QtGui.QApplication.translate("Dialog", "<!DOCTYPE HTML PUBLIC \"-//W3C//DTD HTML 4.0//EN\" \"http://www.w3.org/TR/REC-html40/strict.dtd\">\n"
+"<html><head><meta name=\"qrichtext\" content=\"1\" /><style type=\"text/css\">\n"
[…]

### 2018-06-22 src/data/refnx-0.0.15/motofit/dataobject.py

@@ -1,0 +1,346 @@
+from __future__ import division
+from PySide import QtGui, QtCore
+import refnx.dataset.reflectdataset as reflectdataset
+import refnx.analysis.reflect as reflect
+import refnx.analysis.fitting as fitting
+import refnx.util.ErrorProp as EP
+import numpy as np
+from copy import deepcopy, copy
+import matplotlib.artist as artist
+import os.path
+import os
+import string
+
+try:
+    import xml.etree.cElementTree as ET
+except ImportError:
+    import xml.etree.ElementTree as ET
+
+
+class DataObject(reflectdataset.ReflectDataset):
+
+    '''
+        defines a dataset
+    '''
+
+    __requiredgraphproperties = {'lw': float,
+                                 'label': str,
+                                 'linestyle': str,
+                                 'fillstyle': str,
+                                 'marker': str,
+                                 'markersize': float,
+                                 'markeredgecolor': str,
+                                 'markerfacecolor': str,
+                                 'zorder': int,
+                                 'color': str,
+                                 'visible': bool}
+
+    def __init__(self, dataTuple=None,
+                 name='theoretical', filename=None):
+        super(DataObject, self).__init__(dataTuple=dataTuple)
+
+        self.name = name
+
+        if filename is not None:
+            with open(filename, 'Ur') as f:
+                self.load(f)
+        else:
+            self.filename = None
+
+        self.fit = None
+        self.residuals = None
+
+        self.chi2 = -1
+        self.sld_profile = None
+
+        self.line2D = None
+        self.line2Dfit = None
+        self.line2Dresiduals = None
+        self.line2Dsld_profile = None
+
+        self.graph_properties = {'line2Dsld_profile_properties': {},
+                                 'line2Dresiduals_properties': {},
+                                 'line2Dfit_properties': {},
+                                 'line2D_properties': {},
+                                 'visible': True}
+
+    def __getstate__(self):
+        self._save_graph_properties()
+        d = copy(self.__dict__)
+        d['line2Dfit'] = None
+        d['line2D'] = None
+        d['line2Dsld_profile'] = None
+        d['line2Dresiduals'] = None
+#        del(d['fit'])
+        return d
+
+    def save_fit(self, filename):
+        if self.fit is not None:
+            with open(filename, 'wb+') as f:
+                np.savetxt(f, np.column_stack((self.x, self.fit)))
+
+    def save(self, f):
+        # this will save it as XML
[…]

### 2018-06-22 src/data/refnx-0.0.15/motofit/globalfitting_GUImodel.py

@@ -1,0 +1,529 @@
+from __future__ import division
+from PySide import QtCore, QtGui
+import refnx.analysis.curvefitter as curvefitter
+from refnx.analysis import CurveFitter, GlobalFitter
+import refnx.analysis.reflect as reflect
+import numpy as np
+from lmfit import Parameters
+import re
+
+
+def is_linked(linkages, dataset, parameter):
+    """
+    Given a set of linkages and a parameter determine whether the parameter
+    is linked, is a master link, and what the master link is.
+
+    Parameters
+    ----------
+    linkages: sequence
+        The linkages for the analysis. 'd1:abc=d2:def' would link parameter
+        `def` of dataset 2 with parameter `abc` of dataset 1.
+    dataset: integer
+        The dataset index the parameter belongs to.
+    parameter: str
+        The parameter name of interest.
+
+    Returns
+    -------
+    (is_linked, is_master, master_link): bool, bool, str
+    """
+    is_linked, is_master, master_link = False, False, ''
+
+    if not len(linkages):
+        return is_linked, is_master, master_link
+
+    for linkage in linkages:
+        d_master, p_master, d_slave, p_slave = linkage_to_CR(linkage)
+
+        if dataset == d_master and p_master == parameter:
+            is_linked = True
+            is_master = True
+
+        if d_slave == dataset and parameter == p_slave:
+            is_linked = True
+            master_link = 'd%d:%s'%(d_master, p_master)
+
+    return is_linked, is_master, master_link
+
+
+def RC_to_parameter(row, col):
+    return 'd%dp%d' % (col, row)
+
+
+def linkage_ref_to_CR(ref):
+    dp_string = 'd([0-9]+):([0-9a-zA-Z_]+)'
+    ref_regex = re.compile(dp_string)
+
+    ref_search = ref_regex.search(ref)
+
+    if ref_regex is not None:
+        vals = ref_search.groups()
+        d_master = int(vals[0])
+        p_master = vals[1]
+
+        return d_master, p_master
+
+    return None
+
+
+def linkage_to_CR(linkage):
+    """
+    Get the dataset and parameter numbers for a linkage
+
+    Parameters
+    ----------
+    linkage: str
+        linkage specified as 'dN:abc=dM:def'
+
+    Returns
+    -------
+    A tuple (N, M, A, B)
+    """
+    dp_string = 'd([0-9]+):([0-9a-zA-Z_]+)'
[…]

### 2018-06-22 src/data/refnx-0.0.15/motofit/graphproperties.py

@@ -1,0 +1,70 @@
+"""
+GraphProperties: storing information about Matplotlib traces
+e.g. colors, linesizes, etc.
+"""
+import matplotlib.artist as artist
+
+_requiredgraphproperties = {'lw': float,
+                             'label': str,
+                             'linestyle': str,
+                             'fillstyle': str,
+                             'marker': str,
+                             'markersize': float,
+                             'markeredgecolor': str,
+                             'markerfacecolor': str,
+                             'zorder': int,
+                             'color': str,
+                             'visible': bool,
+                             'picker': float}
+
+_lines = {'line2D_properties': dict,
+          'line2Dfit_properties': dict,
+          'line2Dsld_profile_properties': dict,
+          'line2Dresiduals_properties': dict}
+
+class GraphProperties(dict):
+    def __init__(self):
+        self['visible'] = True
+
+        #a Matplotlib trace
+        self['line2D'] = None
+        self['line2Dfit'] = None
+        self['line2Dresiduals'] = None
+        self['line2Dsld_profile'] = None
+        self['line2D_properties'] = {}
+        self['line2Dfit_properties'] = {}
+        self['line2Dsld_profile_properties'] = {}
+        self['line2Dresiduals_properties'] = {}
+
+    def __getattr__(self, key):
+        if key in _requiredgraphproperties:
+            return self[key]
+
+    def __getstate__(self):
+        self.save_graph_properties()
+        d = {}
+        for line in _lines:
+            d[line] = self[line]
+        return d
+
+    def save_graph_properties(self):
+        if self.line2D:
+            for key in _requiredgraphproperties:
+                self['line2D_properties'][key] = artist.getp(self.line2D, key)
+
+        if self.line2Dfit:
+            for key in _requiredgraphproperties:
+                self['line2Dfit_properties'][key] = artist.getp(self.line2Dfit,
+                                                                key)
+
+        if self.line2Dresiduals:
+            for key in _requiredgraphproperties:
+                self['line2Dresiduals_properties'][key] = artist.getp(
+                                        self.line2Dresiduals,
+                                        key)
+
+        if self.line2Dsld_profile:
+            for key in _requiredgraphproperties:
+                self['line2Dsld_profile_properties'][key] = artist.getp(
+                                        self.line2Dsld_profile,
+                                        key)

### 2018-06-22 src/data/refnx-0.0.15/motofit/limits_GUImodel.py

@@ -1,0 +1,133 @@
+from __future__ import division
+from PySide import QtCore, QtGui
+import numpy as np
+import refnx.analysis.curvefitter as curvefitter
+
+
+class LimitsModel(QtCore.QAbstractTableModel):
+
+    def __init__(self, params, finite_bounds=False, parent=None):
+        super(LimitsModel, self).__init__(parent)
+        self.params = params
+        self.finite_bounds = finite_bounds
+        self.varys = curvefitter.varys(self.params)
+        self.fitted_params = np.where(self.varys)[0]
+        self.names = curvefitter.names(self.params)
+
+    def columnCount(self, parent=QtCore.QModelIndex()):
+        return 5
+
+    def rowCount(self, parent=QtCore.QModelIndex()):
+        return len(self.params)
+
+    def data(self, index, role=QtCore.Qt.DisplayRole):
+        if not index.isValid():
+            return False
+
+        row = index.row()
+        col = index.column()
+
+        name = self.names[row]
+        param = self.params[name]
+
+        if role == QtCore.Qt.BackgroundRole and col < 2:
+            return QtGui.QBrush(QtCore.Qt.cyan)
+
+        if role == QtCore.Qt.BackgroundRole and (not row in self.fitted_params
+                                                 and col != 4):
+            return QtGui.QBrush(QtCore.Qt.cyan)
+
+        if role == QtCore.Qt.DisplayRole:
+            if col == 0:
+                return name
+            if col == 1:
+                return str(param.value)
+            if col == 2:
+                return str(param.min)
+            if col == 3:
+                return str(param.max)
+            if col == 4:
+                return str(param.expr)
+
+    def headerData(self, section, orientation, role=QtCore.Qt.DisplayRole):
+        """ Set the headers to be displayed. """
+        if role != QtCore.Qt.DisplayRole:
+            return None
+
+        if orientation == QtCore.Qt.Vertical:
+            return ''
+        if orientation == QtCore.Qt.Horizontal:
+            if section == 0:
+                return 'parameter'
+            if section == 1:
+                return 'value'
+            if section == 2:
+                return 'lower limit'
+            if section == 3:
+                return 'upper limit'
+            if section == 4:
+                return 'expr'
+        return None
+
+    def flags(self, index):
+        row = index.row()
+        col = index.column()
+
+        if col == 0 or col == 1:
+            return QtCore.Qt.NoItemFlags
+
[…]

### 2018-06-22 src/data/refnx-0.0.15/motofit/paramsstore_GUImodel.py

@@ -1,0 +1,54 @@
+"""
+Qt Model class for dealing with all the Parameters sets.  It provides data
+for the GUI to display. It deals with GUI requests for loading models as well.
+"""
+
+from __future__ import division
+from PySide import QtCore, QtGui
+import datastore
+import refnx.analysis.reflect as reflect
+import refnx.analysis.curvefitter as curvefitter
+from lmfit import Parameters
+
+class ParamsStoreModel(QtCore.QAbstractListModel):
+
+    def __init__(self, parent=None):
+        super(ParamsStoreModel, self).__init__(parent)
+        self.params_store = datastore.ParametersStore()
+
+    def __iter__(self):
+        for params in self.params_store:
+            yield params
+
+    def __getitem__(self, key):
+        return self.params_store[key]
+
+    def __setitem__(self, key, value):
+        if isinstance(value, Parameters):
+            self.params_store[key] = value
+
+    def rowCount(self, parent=QtCore.QModelIndex()):
+        return len(self.params_store)
+
+    def data(self, index, role=QtCore.Qt.DisplayRole):
+        if role == QtCore.Qt.DisplayRole:
+            return self.params_store.names[index.row()]
+
+    def flags(self, index, filterNormalRef=True):
+        names = self.params_store.names
+        params = self.params_store[names[index.row()]]
+
+        if self.params_store.displayOtherThanReflect:
+            return (QtCore.Qt.ItemIsEnabled |
+                    QtCore.Qt.ItemIsSelectable)
+        else:
+            values = curvefitter.values(params)
+            if reflect.is_proper_abeles_input(values):
+                return (QtCore.Qt.ItemIsEnabled |
+                        QtCore.Qt.ItemIsSelectable)
+            else:
+                return (QtCore.Qt.NoItemFlags)
+
+    def add(self, params, name):
+        self.params_store.add(params, name)
+        self.dataChanged.emit(QtCore.QModelIndex(), QtCore.QModelIndex())

### 2018-06-22 src/data/refnx-0.0.15/refnx/analysis/__init__.py

@@ -1,0 +1,17 @@
+from refnx.analysis.bounds import Interval, PDF, Bounds
+from refnx.analysis.parameter import (Parameter, Parameters, is_parameters,
+                                      is_parameter, possibly_create_parameter)
+from refnx.analysis.objective import (Objective, BaseObjective,
+                                      GlobalObjective, Transform)
+from refnx.analysis.curvefitter import (CurveFitter, MCMCResult, process_chain,
+                                        load_chain)
+from refnx.analysis.model import Model, fitfunc
+
+
+__all__ = [s for s in dir() if not s.startswith('_')]
+
+
+from refnx._lib._testutils import PytestTester
+
+test = PytestTester(__name__)
+del PytestTester

### 2018-06-22 src/data/refnx-0.0.15/refnx/analysis/bounds.py

@@ -1,0 +1,191 @@
+from __future__ import division
+
+from scipy.stats import rv_continuous, uniform
+from scipy.stats._distn_infrastructure import rv_frozen
+from scipy._lib._util import check_random_state
+import numpy as np
+
+
+class Bounds(object):
+    def __init__(self, seed=None):
+        self._random_state = check_random_state(seed)
+
+    def lnprob(self, value):
+        """
+        Calculate the log-likelihood probability of a value with the bounds
+        """
+        raise NotImplementedError
+
+    def valid(self, value):
+        """
+        Checks whether a parameter value is within the support of the
+        distribution. If it isn't then it returns a value that is within the
+        support.
+        """
+        raise NotImplementedError
+
+    def rvs(self, size=1, random_state=None):
+        raise NotImplementedError
+
+
+class PDF(Bounds):
+    def __init__(self, rv, seed=None):
+        super(PDF, self).__init__(seed=seed)
+        # we'll accept any object so long as it has logpdf and rvs methods
+        if hasattr(rv, 'logpdf') and hasattr(rv, 'rvs'):
+            self.rv = rv
+        else:
+            raise ValueError("You must initialise PDF with an object that has"
+                             " logpdf and rvs methods")
+
+    def __repr__(self):
+        return repr(self.rv)
+
+    def lnprob(self, val):
+        """
+        Calculate the log-likelihood probability of a value with the bounds
+        """
+        return self.rv.logpdf(val)
+
+    def valid(self, val):
+        """
+        Checks whether a parameter value is within the support of the
+        distribution. If it isn't then it returns a *random* value that is
+        within the support.
+
+        Parameters
+        ----------
+        val : array-like
+            values to examine
+
+        Returns
+        -------
+        valid : array-like
+            values within the support
+        """
+        _val = np.asfarray(val)
+        valid = np.where(np.isfinite(self.lnprob(_val)),
+                         _val,
+                         self.rv.rvs(size=_val.shape))
+
+        return valid
+
+    def rvs(self, size=1, random_state=None):
+        if random_state is None:
+            random_state = self._random_state
+        return self.rv.rvs(size=size, random_state=random_state)
+
+
+class Interval(Bounds):
+    def __init__(self, lb=-np.inf, ub=np.inf, seed=None):
+        super(Interval, self).__init__(seed=seed)
+        if lb is None:
+            lb = -np.inf
+        if ub is None:
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/analysis/curvefitter.py

@@ -1,0 +1,877 @@
+from __future__ import division
+
+from collections import namedtuple
+import sys
+import re
+import warnings
+import array
+
+import numpy as np
+
+from scipy._lib._util import check_random_state
+from scipy.optimize import minimize, differential_evolution, least_squares
+
+from refnx.analysis import Objective, Interval, PDF, is_parameter
+from refnx._lib import (unique as f_unique, possibly_create_pool,
+                        possibly_open_file, flatten)
+from refnx._lib.util import getargspec
+
+from refnx._lib import emcee
+
+# PTSampler has been forked into a separate package. Try both places
+_HAVE_PTSAMPLER = False
+PTSampler = type(None)
+
+try:
+    from ptemcee.sampler import Sampler as PTSampler
+    _HAVE_PTSAMPLER = True
+except ImportError:
+    warnings.warn("PTSampler (parallel tempering) is not available,"
+                  " please install the ptemcee package", ImportWarning)
+
+MCMCResult = namedtuple('MCMCResult', ['name', 'param', 'stderr', 'chain',
+                                       'median'])
+
+
+def _objective_lnprob(theta, userargs=()):
+    """
+    Calculates the log-posterior probability.
+
+    Parameters
+    ----------
+    theta : sequence
+        Float parameter values (only those being varied)
+    userargs : tuple, optional
+        Extra positional arguments required for user objective function
+
+    Returns
+    -------
+    lnprob : float
+        Log posterior probability
+
+    """
+    # need to use this function because PY27 can't pickle a partial on
+    # an object method
+    objective = userargs
+    return objective.lnprob(theta)
+
+
+def _objective_lnlike(theta, userargs=()):
+    """
+    Calculates the log-likelihood probability.
+
+    Parameters
+    ----------
+    theta : sequence
+        Float parameter values (only those being varied)
+    userargs : tuple, optional
+        Extra positional arguments required for user objective function
+
+    Returns
+    -------
+    lnlike : float
+        Log likelihood probability
+
+    """
+    # need to use this function because PY27 can't pickle a partial on
+    # an object method
+    objective = userargs
+    return objective.lnlike(theta)
+
+
+def _objective_lnprior(theta, userargs=()):
+    """
+    Calculates the log-prior probability.
+
+    Parameters
+    ----------
+    theta : sequence
+        Float parameter values (only those being varied)
+    userargs : tuple, optional
+        Extra positional arguments required for user objective function
+
+    Returns
+    -------
+    lnprior : float
+        Log prior probability
+
+    """
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/analysis/model.py

@@ -1,0 +1,151 @@
+from __future__ import division
+
+from refnx._lib.util import getargspec
+
+
+def fitfunc(f):
+    """
+    A decorator that can be used to say if something is a fitfunc.
+
+    """
+    f.fitfuncwraps = True
+    return f
+
+
+class Model(object):
+    """
+    Calculates a generative model (dependent variable), given parameters
+    and independent variables.
+
+    Parameters
+    ----------
+    parameters : array or refnx.analysis.Parameters
+        Parameters to calculate the model with
+    fitfunc : callable, optional
+        A function that calculates the generative model. Should have the
+        signature ``fitfunc(x, parameters, *fcn_args, **fcn__kwds)`` where `x`
+        is an array-like specifying the independent variables, and
+        `parameters` are the parameters required to calculate the model.
+        `fcn_args` and `fcn_kwds` can be used to supply additional arguments to
+        to `fitfunc`.
+    fcn_args : sequence, optional
+        Supplies extra arguments to `fitfunc`
+    fcn_kwds : dict, optional
+        Supplies keyword arguments to `fitfunc`
+
+    Notes
+    -----
+    It is not necessary to supply `fitfunc` to create a `Model` *iff* you are
+    inheriting `Model` and are also overriding `Model.model`.
+
+    """
+    def __init__(self, parameters, fitfunc=None, fcn_args=(), fcn_kwds=None):
+        self._parameters = parameters
+
+        self._fitfunc = None
+        self._fitfunc_has_xerr = False
+        self.fitfunc = fitfunc
+
+        self.fcn_args = fcn_args
+        self.fcn_kwds = {}
+        if fcn_kwds is not None:
+            self.fcn_kwds = fcn_kwds
+
+    def __call__(self, x, p=None, x_err=None):
+        """
+        Calculates a generative model(dependent variable), given parameters and
+        independent variables.
+
+        Parameters
+        ----------
+        x : array-like
+            Independent variable.
+        p : array-like or refnx.analysis.Parameters
+            Parameters to supply to the generative function.
+        x_err : optional
+            Uncertainty in `x`.
+
+        Returns
+        -------
+        generative : array-like or float
+
+        Notes
+        -----
+        The interpretation of `x`, `p`, and `x_err` is up to the `fitfunc`
+        supplied during construction of this object (or the overridden `model`
+        method of this object).
+
+        """
+        return self.model(x, p=p, x_err=x_err)
+
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/analysis/parameter.py

@@ -1,0 +1,528 @@
+from __future__ import division
+
+import operator
+from types import MethodType
+from six.moves import UserList
+
+
+import numpy as np
+from refnx._lib import flatten, unique as f_unique
+from refnx.analysis import Interval, PDF, Bounds
+
+
+# Functions for making Functors
+def MAKE_BINARY(opfn):
+    return lambda self, other: (_BinaryOp(self, asMagicNumber(other), opfn))
+
+
+def MAKE_RBINARY(opfn):
+    return lambda self, other: (_BinaryOp(asMagicNumber(other), self, opfn))
+
+
+def MAKE_UNARY(opfn):
+    return lambda val: _UnaryOp(val, opfn)
+
+
+def asMagicNumber(x):
+    return x if isinstance(x, BaseParameter) else Constant(x)
+
+
+# a function that takes a function that returns a function
+# MAKE_BINARY = lambda opfn: lambda self, other: (
+#     _BinaryOp(self, asMagicNumber(other), opfn))
+# MAKE_RBINARY = lambda opfn: lambda self, other: (
+#     _BinaryOp(asMagicNumber(other), self, opfn))
+# MAKE_UNARY = lambda opfn: lambda val: _UnaryOp(val, opfn)
+# asMagicNumber = lambda x: x if isinstance(x, BaseParameter) else Constant(x)
+
+# mathematical operations that we might want to use in constraints
+ops = {'sin': np.sin, 'cos': np.cos, 'tan': np.tan, 'arcsin': np.arcsin,
+       'arccos': np.arccos, 'arctan': np.arctan, 'log': np.log,
+       'log10': np.log10, 'exp': np.exp, 'sqrt': np.sqrt, 'sum': np.sum}
+math_ops = {k: MAKE_UNARY(v) for k, v in ops.items()}
+
+
+class Parameters(UserList):
+    """
+    A collection of Parameters
+    """
+    def __init__(self, name=None):
+        super(Parameters, self).__init__()
+        self.name = name
+
+    def __getitem__(self, i):
+        if type(i) is str:
+            try:
+                _names = [param.name for param in self.data]
+                idx = _names.index(i)
+            except ValueError:
+                return None
+            finally:
+                return self.data[idx]
+        else:
+            return self.data[i]
+
+    def __setitem__(self, i, v):
+        # i can be index or string
+        # v has to be Parameters or Parameter
+        if type(i) is str:
+            _names = [param.name for param in self.data]
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/analysis/test/test_bounds.py

@@ -1,0 +1,103 @@
+import pickle
+
+from refnx.analysis import Interval, PDF
+
+import numpy as np
+from numpy.testing import (assert_equal, assert_, assert_almost_equal)
+from scipy.stats import norm, truncnorm
+
+
+class TestBounds(object):
+
+    def setup_method(self):
+        pass
+
+    def test_interval(self):
+        # open interval should have lnprob of 0
+        interval = Interval()
+        assert_equal(interval.lnprob(0), 0)
+
+        # semi closed interval
+        interval.ub = 1000
+        assert_equal(interval.lnprob(0), 0)
+        assert_equal(interval.lnprob(1001), -np.inf)
+
+        # fully closed interval
+        interval.lb = -1000
+        assert_equal(interval.lnprob(-1001), -np.inf)
+        assert_equal(interval.lb, -1000)
+        assert_equal(interval.ub, 1000)
+        assert_equal(interval.lnprob(0), np.log(1 / 2000.))
+
+        # try and set lb higher than ub
+        interval.lb = 1002
+        assert_equal(interval.lb, 1000)
+        assert_equal(interval.ub, 1002)
+
+        # if val is outside closed range then rvs is used
+        vals = interval.valid(np.linspace(990, 1005, 100))
+        assert_(np.max(vals) <= 1002)
+        assert_(np.min(vals) >= 1000)
+        assert_(np.isfinite(interval.lnprob(vals)).all())
+
+        # if bounds are semi-open then val is reflected from lb
+        interval.ub = None
+        interval.lb = 1002
+        x = np.linspace(990, 1001, 10)
+        vals = interval.valid(x)
+        assert_almost_equal(vals, 2 * interval.lb - x)
+        assert_equal(interval.valid(1003), 1003)
+
+        # if bounds are semi-open then val is reflected from ub
+        interval.lb = None
+        interval.ub = 1002
+        x = np.linspace(1003, 1005, 10)
+        vals = interval.valid(x)
+        assert_almost_equal(vals, 2 * interval.ub - x)
+        assert_equal(interval.valid(1001), 1001)
+
+    def test_pdf(self):
+        pdf = PDF(norm)
+
+        # even if it's really far out it's still a valid value
+        assert_equal(pdf.valid(1003), 1003)
+        # logp
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/analysis/test/test_parameter.py

@@ -1,0 +1,224 @@
+import pickle
+
+import numpy as np
+from numpy.testing import (assert_almost_equal, assert_equal, assert_,
+                           assert_allclose)
+from scipy.stats import norm, uniform
+
+from refnx.analysis import (Interval, PDF, Parameter, Parameters,
+                            is_parameters)
+
+
+class TestParameter(object):
+
+    def setup_method(self):
+        pass
+
+    def test_parameter(self):
+        # simple test of constraint
+        x = Parameter(5.)
+        y = Parameter(1.)
+        y.constraint = x * 2.
+        assert_equal(y.value, x.value * 2.)
+
+        # if you've constrained a parameter it shouldn't be varying
+        assert_(y.vary is False)
+
+        # you can't set a constraint on a parameter with an expression that
+        # already involves the parameter
+        from pytest import raises
+        with raises(ValueError):
+            x.constraint = y
+
+        # try a negative value
+        x.value = -1.
+        assert_equal(y.value, -2.)
+
+        # nested constraints
+        z = Parameter(1.)
+        z.constraint = x + y
+        assert_equal(z.value, -3)
+        # check that nested circular constraints aren't allowed
+        with raises(ValueError):
+            x.constraint = z
+
+        # absolute value constraint
+        y.constraint = abs(x)
+        assert_equal(y.value, 1)
+
+        # sin constraint
+        y.constraint = np.sin(x) + 2.
+        assert_equal(y.value, 2. + np.sin(x.value))
+
+    def test_func_attribute(self):
+        # a Parameter object should have math function attributes
+        a = Parameter(1)
+        assert_(hasattr(a, 'sin'))
+
+    def test_remove_constraint(self):
+        x = Parameter(5.)
+        y = Parameter(1.)
+        y.constraint = x * 2.
+        y.constraint = None
+        assert_(y.vary is False)
+        assert_equal(y.value, 10)
+        assert_(y._constraint is None)
+
+    def test_parameter_bounds(self):
+        x = Parameter(4, bounds=Interval(-4, 4))
+        assert_equal(x.lnprob(), uniform.logpdf(0, -4, 8))
+
+        x.bounds = None
+        assert_(isinstance(x._bounds, Interval))
+        assert_equal(x.bounds.lb, -np.inf)
+        assert_equal(x.bounds.ub, np.inf)
+        assert_equal(x.lnprob(), 0)
+
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/dataset/__init__.py

@@ -1,0 +1,11 @@
+from __future__ import division, absolute_import
+
+from refnx.dataset.data1d import Data1D
+from refnx.dataset.reflectdataset import ReflectDataset
+from refnx._lib._testutils import PytestTester
+
+test = PytestTester(__name__)
+del PytestTester
+
+
+__all__ = [s for s in dir() if not s.startswith('_')]

### 2018-06-22 src/data/refnx-0.0.15/refnx/dataset/data1d.py

@@ -1,0 +1,371 @@
+""""
+A basic representation of a 1D dataset
+"""
+from __future__ import division
+
+import os.path
+import re
+
+import numpy as np
+
+from refnx.util.nsplice import get_scaling_in_overlap
+from refnx._lib import possibly_open_file
+
+
+class Data1D(object):
+    r"""
+    A basic representation of a 1D dataset.
+
+    Parameters
+    ----------
+    data : str, file-like or tuple of np.ndarray, optional
+        `data` can be a string or file-like object referring to a File to load
+        the dataset from.
+
+        Alternatively it is a tuple containing the data from which the dataset
+        will be constructed. The tuple should have between 2 and 4 members.
+
+            - data[0] - x
+            - data[1] - y
+            - data[2] - uncertainties on y, y_err
+            - data[3] - uncertainties on x, x_err
+
+        `data` must be at least two long, `x` and `y`.
+        If the tuple is at least 3 long then the third member is `y_err`.
+        If the tuple is 4 long then the fourth member is `x_err`.
+        All arrays must have the same shape.
+
+    Attributes
+    ----------
+    data : tuple of np.ndarray
+        The data, (x, y, y_err, x_err)
+    finite_data : tuple of np.ndarray
+        Data points that are finite
+    x : np.ndarray
+        x data
+    y : np.ndarray
+        y data
+    y_err : np.ndarray
+        uncertainties on the y data
+    x_err : np.ndarray
+        uncertainties on the x data
+    filename : str or None
+        The file the data was read from
+    weighted : bool
+        Whether the y data has uncertainties
+    metadata : dict
+        Information that should be retained with the dataset.
+
+    """
+    def __init__(self, data=None, **kwds):
+        self.filename = None
+        self.name = None
+
+        self.metadata = kwds
+        self.x = np.zeros(0)
+        self.y = np.zeros(0)
+        self.y_err = None
+        self.x_err = None
+        self.weighted = False
+
+        # if it's a file then open and load the file.
+        if hasattr(data, 'read') or type(data) is str:
+            self.load(data)
+        elif data is not None:
+            self.x = np.array(data[0], dtype=float)
+            self.y = np.array(data[1], dtype=float)
+            if len(data) > 2:
+                self.y_err = np.array(data[2], dtype=float)
+                self.weighted = True
+
+            if len(data) > 3:
+                self.x_err = np.array(data[3], dtype=float)
+
+    def __len__(self):
+        """
+        the number of points in the dataset.
+
+        """
+        return self.y.size
+
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/dataset/reflectdataset.py

@@ -1,0 +1,135 @@
+from __future__ import division
+
+import string
+import time
+import re
+# from datetime import datetime
+
+try:
+    import xml.etree.cElementTree as ET
+except ImportError:
+    import xml.etree.ElementTree as ET
+import os.path
+from refnx.dataset import Data1D
+from refnx._lib import possibly_open_file
+
+
+_template_ref_xml = """<?xml version="1.0"?>
+<REFroot xmlns="">
+<REFentry time="$time">
+<Title>$title</Title>
+<User>$user</User>
+<REFsample>
+<ID>$sample</ID>
+</REFsample>
+<REFdata axes="Qz" rank="1" type="POINT" spin="UNPOLARISED" dim="$numpoints">
+<Run filename="$datafilenumber" preset="" size="">
+</Run>
+<R uncertainty="dR">$_ydata</R>
+<Qz uncertainty="dQz" units="1/A">$_xdata</Qz>
+<dR type="SD">$_ydataSD</dR>
+<dQz type="_FWHM" units="1/A">$_xdataSD</dQz>
+</REFdata>
+</REFentry>
+</REFroot>"""
+
+
+class ReflectDataset(Data1D):
+    """
+    A 1D Reflectivity dataset.
+    """
+
+    def __init__(self, data=None, **kwds):
+        """
+        Initialise a reflectivity dataset.
+
+        Parameters
+        ----------
+        data : str, file-like or tuple of np.ndarray, optional
+            `data` can be a string or file-like object referring to a File to
+            load the dataset from.
+
+            Alternatively it is a tuple containing the data from which the
+            dataset will be constructed. The tuple should have between 2 and 4
+            members.
+
+                - data[0] - Q
+                - data[1] - R
+                - data[2] - dR
+                - data[3] - dQ
+
+            `data` must be at least two long, `Q` and `R`.
+            If the tuple is at least 3 long then the third member is `dR`.
+            If the tuple is 4 long then the fourth member is `dQ`.
+            All arrays must have the same shape.
+        """
+        super(ReflectDataset, self).__init__(data=data, **kwds)
+        self.datafilenumber = list()
+        self.sld_profile = None
+
+    def save_xml(self, f, start_time=0):
+        """
+        Saves the reflectivity data to an XML file.
+
+        Parameters
+        ----------
+        f : str or file-like
+            The file to write the spectrum to, or a str that specifies the file
+            name
+        start_time: int, optional
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/dataset/test/test_reflectdataset.py

@@ -1,0 +1,188 @@
+import os.path
+
+import pytest
+
+from refnx.dataset import ReflectDataset, Data1D
+import numpy as np
+from numpy.testing import assert_equal, assert_
+
+
+class TestReflectDataset(object):
+
+    @pytest.fixture(autouse=True)
+    def setup_method(self, tmpdir):
+        self.pth = os.path.dirname(os.path.abspath(__file__))
+
+        data = ReflectDataset()
+
+        x1 = np.linspace(0, 10, 5)
+        y1 = 2 * x1
+        e1 = np.ones_like(x1)
+        dx1 = np.ones_like(x1)
+        data.add_data((x1, y1, e1, dx1))
+        self.data = data
+
+        self.cwd = os.getcwd()
+        self.tmpdir = tmpdir.strpath
+        os.chdir(self.tmpdir)
+
+    def teardown_method(self):
+        os.chdir(self.cwd)
+
+    def test_load(self):
+        # load dataset from XML, via file handle
+        dataset = ReflectDataset()
+        with open(os.path.join(self.pth, 'c_PLP0000708.xml')) as f:
+            dataset.load(f)
+
+        assert_equal(len(dataset), 90)
+        assert_equal(90, np.size(dataset.x))
+
+        # load dataset from XML, via string
+        dataset = ReflectDataset()
+        dataset.load(os.path.join(self.pth, 'c_PLP0000708.xml'))
+
+        assert_equal(len(dataset), 90)
+        assert_equal(90, np.size(dataset.x))
+
+        # load dataset from .dat, via file handle
+        dataset1 = ReflectDataset()
+        with open(os.path.join(self.pth, 'c_PLP0000708.dat')) as f:
+            dataset1.load(f)
+
+        assert_equal(len(dataset1), 90)
+        assert_equal(90, np.size(dataset1.x))
+
+        # load dataset from .dat, via string
+        dataset2 = ReflectDataset()
+        dataset2.load(os.path.join(self.pth, 'c_PLP0000708.dat'))
+
+        assert_equal(len(dataset2), 90)
+        assert_equal(90, np.size(dataset2.x))
+
+    def test_load_dat_with_header(self):
+        # check that the file load works with a header
+        a = ReflectDataset(os.path.join(self.pth, 'c_PLP0000708.dat'))
+        b = ReflectDataset(os.path.join(self.pth, 'c_PLP0000708_header.dat'))
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/__init__.py

@@ -1,0 +1,14 @@
+from refnx.reduce.reduce import PlatypusReduce, reduce_stitch
+from refnx.reduce.platypusnexus import (catalogue, PlatypusNexus,
+                                        number_datafile, basename_datafile,
+                                        datafile_number, Y_PIXEL_SPACING,
+                                        accumulate_HDF_files, Catalogue)
+from refnx.reduce.batchreduction import BatchReducer
+from refnx.reduce.xray import reduce_xrdml
+from refnx._lib._testutils import PytestTester
+
+test = PytestTester(__name__)
+del PytestTester
+
+
+__all__ = [s for s in dir() if not s.startswith('_')]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/batchreduction.py

@@ -1,0 +1,558 @@
+# coding: utf-8
+
+"""
+Batch reduction of reflectometry data based on a spreadsheet
+"""
+
+from __future__ import print_function, division
+
+import collections
+import numpy as np
+import os.path
+import pandas as pd
+import pickle
+import re
+import sys
+import warnings
+
+try:
+    import IPython.display
+    _have_ipython = True
+except ImportError:
+    _have_ipython = False
+
+from refnx.reduce import reduce_stitch
+
+
+ReductionEntryTuple = collections.namedtuple('ReductionEntry',
+                                             ['row',
+                                              'ds',
+                                              'name',
+                                              'fname',
+                                              'entry', ])
+
+
+class ReductionEntry(ReductionEntryTuple):
+
+    def rescale(self, scale_factor, write=True):
+        self.ds.scale(scale_factor)
+        if write:
+            with open(self.fname, 'w') as w:
+                self.ds.save(w)
+
+
+class ReductionCache(list):
+    """
+    Cache for the reduced data to enable look-up by name, run number or row.
+
+    Entries in the cache are ReductionEntry objects.
+
+    Examples
+    --------
+
+    >>> reducer = BatchReducer('reduction.xls', data_folder, rebin_percent)
+    >>> data = reducer()
+
+    Find the filename of a run in the cache by sample name
+
+    >>> data.name('W1234').fname
+
+    Find a run in the cache by run number and plot it
+
+    >>> data = data.run(24623)
+    >>> plt.plot(data[0], data[1])
+
+    Search for data by run name (starting substring or regular expression)
+
+    >>> data.name_startswith('W')
+    >>> plot_data_sets(data.name_search('^W')
+    """
+
+    _default_persistent_cache = "_reduction_cache.pickle"
+
+    def __init__(self, persistent=True):
+        """
+        Create a new reduction cache
+
+        Parameters
+        ----------
+        persistent : bool or str, optional
+            Reduction cache should be stored on disk to allow the reducer to
+            be restarted without having to rereduce the data. If a str is
+            given, it is used as the filename for the persistent cache,
+            otherwise, a default value is used.
+        """
+        super(ReductionCache, self).__init__()
+        self.name_cache = {}
+        self.run_cache = {}
+        self.row_cache = {}
+        self.persistent = persistent
+
+        if self.persistent:
+            self.load_cache()
+
+    def add(self, row, ds, name, fname, entry, update=True):
+        """
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/rebin.py

@@ -1,0 +1,295 @@
+from __future__ import division
+import numpy as np
+
+"""
+Rebins histograms in a piecewise-constant fashion.  Original code based
+on Joshua Hykes code.  However, the error propagation (with the uncertainties
+package) was _very_ slow, so I've extracted the piecewise-constant code and
+modified it.
+"""
+
+"""
+Copyright (c) 2011, Joshua M. Hykes
+All rights reserved.
+
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are met:
+    * Redistributions of source code must retain the above copyright
+      notice, this list of conditions and the following disclaimer.
+    * Redistributions in binary form must reproduce the above copyright
+      notice, this list of conditions and the following disclaimer in the
+      documentation and/or other materials provided with the distribution.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL JOSHUA M. HYKES BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+"""
+
+
+def rebin_along_axis(y1, x1, x2, axis=0, y1_sd=None):
+    """
+    Rebins an N-dimensional array along a given axis, in a piecewise-constant
+    fashion.
+
+    Parameters
+    ----------
+    y1 : array_like
+        The input image
+    x1 : array_like
+        The monotonically increasing/decreasing original bin edges along
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/test/test_batch_reduce.py

@@ -1,0 +1,178 @@
+import os.path
+import os
+import pandas
+import tempfile
+
+from numpy.testing import assert_equal, assert_
+import pytest
+
+from refnx.reduce import BatchReducer
+# also get access to file-scope variables
+import refnx.reduce.batchreduction
+
+
+class TestReduce(object):
+
+    @pytest.fixture(autouse=True)
+    def setup_method(self, tmpdir):
+        path = os.path.dirname(__file__)
+        self.path = path
+
+        self.cwd = os.getcwd()
+
+        self.tmpdir = tmpdir.strpath
+        os.chdir(self.tmpdir)
+        return 0
+
+    def teardown_method(self):
+        os.chdir(self.cwd)
+
+    def test_batch_reduce(self):
+        filename = os.path.join(self.path, "test_batch_reduction.xls")
+        b = BatchReducer(filename, data_folder=self.path, verbose=False,
+                         persistent=False)
+
+        b.reduce(show=False)
+
+    def test_batch_reduce_ipython(self):
+        filename = os.path.join(self.path, "test_batch_reduction.xls")
+
+        refnx.reduce.batchreduction._have_ipython = False
+        b = BatchReducer(filename, data_folder=self.path, verbose=False,
+                         persistent=False)
+        b.reduce(show=False)
+
+        refnx.reduce.batchreduction._have_ipython = True
+        b = BatchReducer(filename, data_folder=self.path, verbose=False,
+                         persistent=False)
+        b.reduce(show=False)
+
+
+class TestReductionCache(object):
+
+    entries = [
+        # row, ds, name, fname, entry
+        [1, None, "Sample A", "a.dat", (1, 2, 3)],
+        [2, None, "Sample B", "b.dat", (11, 12, 13)],
+        [3, None, "Sample C", "c.dat", (21, 22, 23)],
+        # blank row in sheet
+        [5, None, "Sample A1", "a1.dat", (31, 32, 33)],
+        [6, None, "Sample A2", "a2.dat", (41, 42, 43)],
+        [7, None, "Sample D", "d.dat", (51, 52, 53)],
+    ]
+
+    def setup_method(self):
+        self.cache = refnx.reduce.batchreduction.ReductionCache(
+            persistent=False)
+
+        # populate the cache with some fake data to test selector methods
+        for line in self.entries:
+            self._addentry(line)
+
+    def _addentry(self, line, dest=None, **kwargs):
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/test/test_parabolic_motion.py

@@ -1,0 +1,58 @@
+import numpy as np
+from numpy.testing import (assert_almost_equal, assert_)
+from scipy import constants
+import refnx.reduce.parabolic_motion as pm
+
+
+class TestParabolicMotion(object):
+
+    def setup_method(self):
+        pass
+
+    def test_y_deflection(self):
+        # Launch a projectile at 45 degrees at 300 m/s.
+        # It should have a flight time of 43.262894944953523 s
+        # for which the range is 9177.445 m, at which point the
+        # deflection should be 0.
+        deflection = pm.y_deflection(45, 300., 9177.4459168013527)
+        assert_almost_equal(deflection, 0)
+
+    def test_elevation(self):
+        # angle as it passes y = 0 should be -ve of initial trajectory
+        angle = pm.elevation(45., 300., 9177.4459168013527)
+        assert_almost_equal(angle, -45)
+
+    def test_find_trajectory(self):
+        # the angle needs to be 45 degrees for a projectile launched
+        # at 300 m/s with a range of x=9177, y = 0
+        traj = pm.find_trajectory(9177.4459168013527, 0, 300.)
+        assert_almost_equal(traj, 45., 5)
+
+        # Test for theta != 0
+        # Assume parabolic path passes through known peak height.
+        # peak height = v_0y ** 2 / 2 / g
+        # the angle needs to be 45 degrees for a projectile passing
+        # through x = 9177 / 2, arctan(peak_height / 9177 * 2)
+        peak_height = (300 * np.sin(np.radians(45.))) ** 2 / 2. / constants.g
+        assert_almost_equal(peak_height, 2294.3614792003382)
+        theta = np.degrees(np.arctan(peak_height / 9177.4459168013527 * 2.))
+
+        traj = pm.find_trajectory(9177.4459168013527 / 2., theta, 300.)
+        assert_almost_equal(traj, 45., 5)
+
+    def test_parabola_line_intersection_point(self):
+        traj = pm.find_trajectory(3, -0.62, 300.)
+
+        res = pm.parabola_line_intersection_point(3, -0.62, traj, 300, 0)
+        assert_almost_equal(res[3], -0.6293646114131306)
+        assert_almost_equal(res[2], 0)
+        assert_almost_equal(res[1], pm.y_deflection(traj, 300, 3))
+        assert_almost_equal(res[0], 3)
+
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/test/test_platypusnexus.py

@@ -1,0 +1,311 @@
+import os
+import numbers
+import warnings
+
+import pytest
+import numpy as np
+from numpy.testing import (assert_almost_equal, assert_, assert_equal,
+                           assert_array_less, assert_allclose)
+import h5py
+
+import refnx.reduce.platypusnexus as plp
+from refnx.reduce import PlatypusReduce, PlatypusNexus, basename_datafile
+from refnx.reduce.peak_utils import gauss
+from refnx.reduce.platypusnexus import (fore_back_region, EXTENT_MULT,
+                                        PIXEL_OFFSET, create_detector_norm)
+
+
+class TestPlatypusNexus(object):
+
+    @pytest.fixture(autouse=True)
+    def setup_method(self, tmpdir):
+        self.pth = os.path.dirname(os.path.abspath(__file__))
+
+        self.f113 = PlatypusNexus(os.path.join(self.pth,
+                                               'PLP0011613.nx.hdf'))
+        self.f641 = PlatypusNexus(os.path.join(self.pth,
+                                               'PLP0011641.nx.hdf'))
+        self.cwd = os.getcwd()
+
+        self.tmpdir = tmpdir.strpath
+        os.chdir(self.tmpdir)
+        return 0
+
+    def teardown_method(self):
+        os.chdir(self.cwd)
+
+    def test_chod(self):
+        flight_length = self.f113.chod()
+        assert_almost_equal(flight_length[0], 7141.413818359375)
+        assert_almost_equal(flight_length[1], 808)
+
+        flight_length = self.f641.chod(omega=1.8, twotheta=3.6)
+        assert_almost_equal(flight_length[0], 7146.3567785516016)
+        assert_almost_equal(flight_length[1], 808)
+
+    def test_phase_angle(self):
+        # TODO. Add more tests where the phase_angle isn't zero.
+        phase_angle, master_opening = self.f641.phase_angle()
+        assert_almost_equal(phase_angle, 0)
+        assert_almost_equal(master_opening, 1.04719755)
+
+    def test_background_subtract_line(self):
+        # checked each step of the background subtraction with IGOR
+        # so this test background correction should be correct.
+
+        # create some test data
+        xvals = np.linspace(-10, 10, 201)
+        yvals = np.ceil(gauss(xvals, 0, 100, 0, 1) + 2 * xvals + 30)
+
+        # add some reproducible random noise
+        np.random.seed(1)
+        yvals += np.sqrt(yvals) * np.random.randn(yvals.size)
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/test/test_rebin.py

@@ -1,0 +1,239 @@
+"""
+Testing rebin histogram values.
+"""
+
+import numpy as np
+from numpy.random import uniform
+from numpy.testing import (assert_allclose, assert_equal)
+import uncertainties.unumpy as unp
+import refnx.reduce.rebin as rebin
+
+
+class TestRebin(object):
+    def setup_method(self):
+        pass
+
+    # -----------------------------------------------------------------------#
+    #  Tests for piecewise continuous rebinning
+    # -----------------------------------------------------------------------#
+    def test_x2_same_as_x1(self):
+        """
+        x2 same as x1
+        """
+        # old size
+        m = 6
+
+        # new size
+        n = 6
+
+        # bin edges
+        x_old = np.linspace(0., 1., m + 1)
+        x_new = np.linspace(0., 1., n + 1)
+
+        # some arbitrary distribution
+        y_old = 1. + np.sin(x_old[:-1] * np.pi) / np.ediff1d(x_old)
+
+        # rebin
+        y_new = rebin.rebin(x_old, y_old, x_new)
+
+        assert_allclose(y_new, y_old)
+
+    def test_x2_surrounds_x1(self):
+        """
+        x2 range surrounds x1 range
+        """
+        # old size
+        m = 2
+
+        # new size
+        n = 3
+
+        # bin edges
+        x_old = np.linspace(0., 1., m + 1)
+        x_new = np.linspace(-0.1, 1.2, n + 1)
+
+        # some arbitrary distribution
+        y_old = 1. + np.sin(x_old[:-1] * np.pi) / np.ediff1d(x_old)
+
+        # rebin
+        y_new = rebin.rebin(x_old, y_old, x_new)
+
+        # compute answer here to check rebin
+        y_old_ave = y_old / np.ediff1d(x_old)
+        y_new_here = [y_old_ave[0] * (x_new[1] - 0.),
+                      y_old_ave[0] * (x_old[1] - x_new[1]) +
+                      y_old_ave[1] * (x_new[2] - x_old[1]),
+                      y_old_ave[1] * (x_old[-1] - x_new[-2])]
+
+        assert_allclose(y_new, y_new_here)
+        assert_allclose(y_new.sum(), y_old.sum())
+
+    def test_x2_surrounds_x1_2(self):
+        """
+        x2 has some bins that span several x1 bins
+        Also tests uncertainty propagation. Values calculated using
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reduce/xray.py

@@ -1,0 +1,225 @@
+from __future__ import division
+import numpy as np
+import refnx.util.general as general
+import refnx.util.ErrorProp as EP
+import xml.etree.ElementTree as et
+# from refnx.dataset import reflectdataset
+
+# mm
+XRR_BEAMWIDTH_SD = 0.019449
+
+
+def reduce_xrdml(f, bkg=None, scale=1, sample_length=None):
+    """
+    Reduces a Panalytical XRDML file
+
+    Parameters
+    ----------
+    f: file-like object or string
+        The specular reflectivity (XRDML) file of interest
+    bkg: list
+        A list of file-like objects or strings that contain background
+        measurements. The background is assumed to have the same number of
+        points as the specular reflectivity curve.  The backgrounds are
+        averaged and subtracted from the specular reflectivity
+    scale: float
+        The direct beam intensity (cps)
+    sample_length: None or float
+        If None then no footprint correction is done. Otherwise the transverse
+        footprint of the sample (mm).
+
+    Returns
+    -------
+    specular_q, specular_r, specular_dr: np.ndarray
+        The specular reflectivity as a function of momentum transfer, Q.
+    """
+
+    spec = parse_xrdml_file(f)
+
+    reflectivity = spec['intensities'] / spec['count_time']
+    reflectivity_s = np.sqrt(reflectivity) / spec['count_time']
+
+    # do the background subtraction
+    if bkg is not None:
+        bkgds = [parse_xrdml_file(fi) for fi in bkg]
+
+        bkgd_refs = np.r_[[bkgd['intensities'] for bkgd in bkgds]]
+        bkgd_refs_s = np.r_[[np.sqrt(bkgd['intensities']) / bkgd['count_time']
+                             for bkgd in bkgds]]
+        bkgd_refs_var = bkgd_refs_s ** 2
+        weights = 1. / bkgd_refs_var
+        numerator = np.sum(bkgd_refs * weights, axis=0)
+        denominator = np.sum(weights, axis=0)
+
+        total_bkgd = numerator / denominator
+        total_bkgd_s = np.sqrt(1 / denominator)
+
+        reflectivity, reflectivity_s = EP.EPsub(reflectivity,
+                                                reflectivity_s,
+                                                total_bkgd,
+                                                total_bkgd_s)
+
+    # work out the Q values
+    qx, qy, qz = general.q2(spec['omega'],
+                            spec['twotheta'],
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reflect/_interactive_modeller.py

@@ -1,0 +1,1264 @@
+import numpy as np
+import time
+import datetime
+import pickle
+import warnings
+
+import ipywidgets as widgets
+import traitlets
+from traitlets import HasTraits
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from IPython.display import display, clear_output
+
+from refnx.reflect import Slab, ReflectModel
+from refnx.dataset import ReflectDataset
+from refnx.analysis import Objective, CurveFitter, Transform
+from refnx._lib import flatten, possibly_open_file
+
+
+class ReflectModelView(HasTraits):
+    """
+    An ipywidgets viewport of a `refnx.reflect.ReflectModel`.
+
+    Parameters
+    ----------
+    reflect_model: refnx.reflect.ReflectModel
+
+    Notes
+    -----
+    Use the `model_box` property to view/modify the ReflectModel parameters.
+    Use the `limits_box` property to view the limits for the varying
+    parameters.
+    Observe the `view_changed` traitlet to determine when widget values are
+    changed.
+    Observe the `view_redraw` traitlet to determine when a complete redraw
+    of the view is required (because the number of widgets has changed for
+    example).
+
+    """
+
+    # traitlet to say when params were last altered
+    view_changed = traitlets.Float(time.time())
+
+    # traitlet to ask when a redraw of the GUI is requested.
+    # e.g. the number of layers has changed, or there are a
+    # different number of fitted parameters requiring
+    # different limit widgets.
+    view_redraw = traitlets.Float(time.time())
+
+    # number of varying parameters in the model
+    num_varying = traitlets.Int(0)
+
+    def __init__(self, reflect_model):
+        super(ReflectModelView, self).__init__()
+
+        self.model = reflect_model
+        self.structure_view = StructureView(self.model.structure)
+        self.last_selected_param = None
+        self.param_widgets_link = {}
+
+        slab_views = self.structure_view.slab_views
+        slab_views[0].w_thick.disabled = True
+        slab_views[0].c_thick.disabled = True
+        slab_views[0].w_rough.disabled = True
+        slab_views[0].c_rough.disabled = True
+        slab_views[-1].w_thick.disabled = True
+        slab_views[-1].c_thick.disabled = True
+
+        # got to listen to all the slab views
+        for slab_view in slab_views:
+            slab_view.observe(self._on_slab_params_modified,
+                              names=['view_changed'])
+
+        # if you'd like to change the number of layers
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reflect/_reflect.py

@@ -1,0 +1,125 @@
+from __future__ import division, print_function
+import numpy as np
+
+
+"""
+import numpy as np
+q = np.linspace(0.01, 0.5, 1000)
+w = np.array([[0, 2.07, 0, 0],
+              [100, 3.47, 0, 3],
+              [500, -0.5, 0.00001, 3],
+              [0, 6.36, 0, 3]])
+"""
+
+
+def abeles(q, layers, scale=1., bkg=0, threads=0):
+    """
+    Abeles matrix formalism for calculating reflectivity from a stratified
+    medium.
+
+    Parameters
+    ----------
+    layers: np.ndarray
+        coefficients required for the calculation, has shape (2 + N, 4),
+        where N is the number of layers
+        layers[0, 1] - SLD of fronting (/1e-6 Angstrom**-2)
+        layers[0, 2] - iSLD of fronting (/1e-6 Angstrom**-2)
+        layers[N, 0] - thickness of layer N
+        layers[N, 1] - SLD of layer N (/1e-6 Angstrom**-2)
+        layers[N, 2] - iSLD of layer N (/1e-6 Angstrom**-2)
+        layers[N, 3] - roughness between layer N-1/N
+        layers[-1, 1] - SLD of backing (/1e-6 Angstrom**-2)
+        layers[-1, 2] - iSLD of backing (/1e-6 Angstrom**-2)
+        layers[-1, 3] - roughness between backing and last layer
+    q: array_like
+        the q values required for the calculation.
+        Q = 4 * Pi / lambda * sin(omega).
+        Units = Angstrom**-1
+    scale: float
+        Multiply all reflectivities by this value.
+    bkg: float
+        Linear background to be added to all reflectivities
+    threads: int, optional
+        <THIS OPTION IS CURRENTLY IGNORED>
+
+    Returns
+    -------
+    Reflectivity: np.ndarray
+        Calculated reflectivity values for each q value.
+    """
+    qvals = np.asfarray(q)
+    flatq = qvals.ravel()
+
+    nlayers = layers.shape[0] - 2
+    npnts = flatq.size
+
+    kn = np.zeros((npnts, nlayers + 2), np.complex128)
+
+    sld = np.zeros(nlayers + 2, np.complex128)
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reflect/reflect_model.py

@@ -1,0 +1,779 @@
+from __future__ import division
+import abc
+import math
+import numbers
+import warnings
+
+import numpy as np
+import scipy
+from scipy.interpolate import InterpolatedUnivariateSpline
+
+try:
+    from refnx.reflect import _creflect as refcalc
+except ImportError:
+    print('WARNING, Using slow reflectivity calculation')
+    from refnx.reflect import _reflect as refcalc
+from refnx.analysis import (Parameters, Parameter, possibly_create_parameter)
+
+
+# some definitions for resolution smearing
+_FWHM = 2 * np.sqrt(2 * np.log(2.0))
+_INTLIMIT = 3.5
+
+
+class ReflectModel(object):
+    r"""
+    Parameters
+    ----------
+    structure : refnx.reflect.Structure
+        The interfacial structure.
+    scale : float or refnx.analysis.Parameter, optional
+        scale factor. All model values are multiplied by this value before
+        the background is added. This is turned into a Parameter during the
+        construction of this object.
+    bkg : float or refnx.analysis.Parameter, optional
+        linear background added to all model values. This is turned into
+        a Parameter during the construction of this object.
+    name : str, optional
+        Name of the Model
+    dq : float or refnx.analysis.Parameter, optional
+
+        - `dq == 0` then no resolution smearing is employed.
+        - `dq` is a float or refnx.analysis.Parameter
+           a constant dQ/Q resolution smearing is employed.  For 5% resolution
+           smearing supply 5.
+
+        However, if `x_err` is supplied to the `model` method, then that
+        overrides any setting given here. This value is turned into
+        a Parameter during the construction of this object.
+    threads: int, optional
+        Specifies the number of threads for parallel calculation. This
+        option is only applicable if you are using the ``_creflect``
+        module. The option is ignored if using the pure python calculator,
+        ``_reflect``. If `threads == 0` then all available processors are
+        used.
+    quad_order: int, optional
+        the order of the Gaussian quadrature polynomial for doing the
+        resolution smearing. default = 17. Don't choose less than 13. If
+        quad_order == 'ultimate' then adaptive quadrature is used. Adaptive
+        quadrature will always work, but takes a _long_ time (2 or 3 orders
+        of magnitude longer). Fixed quadrature will always take a lot less
+        time. BUT it won't necessarily work across all samples. For
+        example, 13 points may be fine for a thin layer, but will be
+        atrocious at describing a multilayer with bragg peaks.
+
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/reflect/test/test_structure.py

@@ -1,0 +1,117 @@
+import pickle
+
+import numpy as np
+from numpy.testing import (assert_almost_equal, assert_equal, assert_,
+                           assert_allclose, assert_raises)
+
+from refnx.reflect import (SLD, Structure, Spline, Slab)
+from refnx.reflect.structure import _profile_slicer
+from refnx.analysis import Parameter
+
+
+class TestStructure(object):
+
+    def setup_method(self):
+        self.air = SLD(0, name='air')
+        self.sio2 = SLD(3.47, name='sio2')
+        self.d2o = SLD(6.36, name='d2o')
+        self.h2o = SLD(-0.56, name='h2o')
+        self.s = self.air | self.sio2(100, 5) | self.d2o(0, 4)
+
+    def test_structure_construction(self):
+        # structures are constructed by or-ing slabs
+        # test that the slab representation is correct
+        assert_equal(self.s.slabs, np.array([[0, 0, 0, 0, 0],
+                                             [100, 3.47, 0, 5, 0],
+                                             [0, 6.36, 0, 4, 0]]))
+
+        # slabs have solvent penetration
+        self.s.solvent = self.d2o
+        self.s[1] = SLD(3.47 + 1j, name='sio2')(100, 5)
+        self.s[1].vfsolv.value = 0.9
+        sld = 6.36 * 0.9 + 0.1 * 3.47
+        sldi = 1 * 0.1
+        assert_almost_equal(self.s.slabs, np.array([[0, 0, 0, 0, 0],
+                                                    [100, sld, sldi, 5, 0.9],
+                                                    [0, 6.36, 0, 4, 0]]))
+
+    def test_pickle(self):
+        # need to be able to pickle and unpickle structure
+        pkl = pickle.dumps(self.s)
+        unpkl = pickle.loads(pkl)
+        assert_(isinstance(unpkl, Structure))
+        for param in unpkl.parameters.flattened():
+            assert_(isinstance(param, Parameter))
+
+    def test_sld_profile(self):
+        # check that it runs
+        z, sld_profile = self.s.sld_profile()
+
+        z, sld_profile = self.s.sld_profile(np.linspace(-100, 100, 100))
+        assert_equal(min(z), -100)
+        assert_equal(max(z), 100)
+
+    def test_reflectivity(self):
+        q = np.linspace(0.005, 0.3, 200)
+        self.s.reflectivity(q)
+
+    def test_sld_slicer(self):
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/util/ErrorProp.py

@@ -1,0 +1,107 @@
+from __future__ import division
+import numpy as np
+"""
+A simple propagation of uncertainty module.
+# http://en.wikipedia.org/wiki/Propagation_of_uncertainty
+
+For more sophisticated handling of uncertainties use the `uncertainties`
+package.
+"""
+
+
+def EPadd(a, da, b, db, covar=0):
+    """
+    C = A + B
+    """
+    return (a + b), np.sqrt(da**2 + db**2 + 2 * covar)
+
+
+def EPsub(a, da, b, db, covar=0):
+    """
+    C = A - B
+    """
+    return a - b, np.sqrt(da**2 + db**2 - 2 * covar)
+
+
+def EPmul(a, da, b, db, covar=0):
+    """
+    C = A * B
+    """
+    return a * b, np.sqrt((b * da)**2 + (a * db)**2 + 2 * a * b * covar)
+
+
+def EPmulk(a, da, k):
+    """
+    C = A * k
+    """
+    return a * k, np.absolute(da * k)
+
+
+def EPdiv(a, da, b, db, covar=0):
+    """
+    C = A / B
+    """
+    return (a / b,
+            np.sqrt(((da / b)**2 + ((a**2) * (db**2) / (b**4))) -
+                    (2 * covar * a / (b**3))))
+
+
+def EPpow(a, da, b, db, covar=0):
+    """
+    C = A ** B
+    """
+    c = a ** b
+    dc = np.absolute(c) * np.sqrt(((da * b / a)**2) +
+                                  (np.log(a) * db)**2 +
+                                  2 * b * np.log(a) * covar / a)
+    return c, dc
+
+
+def EPpowk(a, da, k, n=1):
+    """
+    C = pow(k, A * n)
+    """
+    return (np.power(k, a * n),
+            np.absolute(np.power(k, a * n) * n * da * np.log(k)))
+
+
+def EPlog(a, da, k=1, n=1):
+    """
+    C = n * log(k * A )
+    """
+    return n * np.log(k * a), np.absolute(n * da / a)
+
+
+def EPlog10(a, da, k=1, n=1):
+    """
+    C = n * log10(k * A)
+    """
+    return n * np.log10(k * a), np.absolute(n * da / (a * np.log(10)))
+
+
+def EPexp(a, da, k=1, n=1):
+    """
+    C = n * exp(k * A)
+    """
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/util/_resolution_kernel.py

@@ -1,0 +1,328 @@
+#!/usr/bin/python
+"""
+Full resolution kernel for a conventional double disc chopper system
+"""
+from __future__ import division
+import numpy as np
+from scipy import stats, integrate, constants, optimize
+
+import refnx.util.general as general
+
+# h / m = 3956
+K = constants.h / constants.m_n * 1.e10
+
+
+"""
+ANGULAR COMPONENTS
+"""
+
+
+class P_Theta(object):
+    def __init__(self, d1, d2, L12=2859.):
+        """
+        Calculates the angular resolution for a two slit collimation
+        system.
+
+        Parameters
+        ----------
+        d1 : float
+            slit 1 opening
+        d2 : float
+            slit 2 opening
+        L12 : float
+            distance between slits
+        """
+
+        alpha = (d1 + d2) / 2. / L12
+        beta = abs(d1 - d2) / 2. / L12
+
+        self.alpha = alpha
+        self.beta = beta
+
+        c = (alpha - beta) / 2 / alpha
+        d = (alpha + beta) / 2 / alpha
+        self.rv = stats.trapz(c, d, -alpha, 2 * alpha)
+        self.width = alpha
+
+    def __call__(self, theta):
+        """
+        Calculates pdf(theta) for the collimation system
+
+        Parameters
+        ----------
+        theta: float
+            quantiles, in radians
+
+        Returns
+        -------
+        pdf: float
+            Probability density function at theta
+        """
+        return self.rv.pdf(theta)
+
+
+def pq_theta(p_theta, theta0, wavelength0, Q):
+    """
+    Angular component of Q resolution for a two slit collimation system
+
+    Parameters
+    ----------
+    p_theta: P_Theta
+        PDF of angular resolution
+    theta0: float
+        nominal angle of incidence, degrees
+    wavelength0: float
+        nominal wavelength
+    Q: float
+        Q value to evaluate PDF at
+
+    Returns
+    -------
+    pdf: float
+        Probability density function of resolution function at Q.
+    """
+    theta = np.radians(general.angle(Q, wavelength0) - theta0)
+    pdf = wavelength0 / 4 / np.pi / np.cos(theta) * p_theta(theta)
+    pdf /= integrate.simps(pdf, x=Q)
+    return pdf
+
+
+"""
+Wavelength components
+"""
+
+
+class P_Wavelength(object):
+    def __init__(self, z0, L, freq, H, xsi=0, R=350, da=0.02):
+        """
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/util/nsplice.py

@@ -1,0 +1,79 @@
+from __future__ import division
+import numpy as np
+
+
+def get_scaling_in_overlap(x0, y0, dy0, x1, y1, dy1):
+    r"""
+    Obtain vertical scaling factor that splices the second dataset onto the
+    first.
+
+    Parameters
+    ----------
+    x0: np.ndarray
+        abscissae for the first dataset
+    y0: np.ndarray
+        y values for the first dataset
+    dy0: np.ndarray
+        dy (standard deviation) values for the first dataset
+    x1: np.ndarray
+        abscissae values for the second dataset
+    y1: np.ndarray
+        y values for the second dataset
+    dy1: np.ndarray
+        dy (standard deviation) values for the second dataset
+
+    Returns
+    -------
+    (scale, dscale, overlap_points): float, float, array-like
+        `scale` and `dscale` are the scaling and uncertainty in scaling factor.
+        They are `np.nan` if the abscissae ranges don't overlap.
+        `overlap_points` indicates the points in the *first* dataset that are
+        in the overlap region.
+    """
+
+    # the datasets should be sorted, but we may not want to sort the data
+    # so make a temporary copy of the data
+    use_dy = (dy1 is not None) and (dy0 is not None)
+
+    sort_arr0 = np.argsort(x0)
+    tx0 = x0[sort_arr0]
+    ty0 = y0[sort_arr0]
+    if dy0 is not None:
+        tdy0 = dy0[sort_arr0]
+    sort_arr1 = np.argsort(x1)
+    tx1 = x1[sort_arr1]
+    ty1 = y1[sort_arr1]
+    if dy1 is not None:
+        tdy1 = dy1[sort_arr1]
+
+    # largest point number of x1 in overlap region
+    num2 = tx1[tx1 < tx0[-1]].size
+
+    if num2 == 0:
+        return np.NaN, np.NaN, np.array([])
+
+    # get scaling factor at each point of second dataset in the overlap region
+    # get the intensity of wave1 at an overlap point
+    newi = np.interp(tx1[:num2], tx0, ty0)
+    w_scalefactor = newi / ty1[:num2]
+
+    if use_dy:
+        newdi = np.interp(tx1[:num2], tx0, tdy0)
+        w_dscalefactor = np.sqrt((newdi / ty1[:num2])**2 +
+                                 ((newi * tdy1[:num2])**2) / ty1[:num2]**4)
+
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/util/quickplot.py

@@ -1,0 +1,31 @@
+import matplotlib.pyplot as plt
+from refnx.dataset import ReflectDataset
+
+
+def ref_plot(datasets):
+    """
+    Quickly plot a lot of datasets
+
+    Parameters
+    ----------
+    datasets : iterable
+        strings or files identifying the datasets to plot
+
+    Returns
+    -------
+    fig : matplotlib.figure.Figure
+        The figure. Use fig.show() to display
+    """
+    fig = plt.figure()
+    ax = fig.add_subplot(111)
+
+    for dataset in datasets:
+        d = ReflectDataset()
+        d.load(dataset)
+        ax.plot(d.x, d.y)
+
+    ax.autoscale(tight=True)
+    ax.set_yscale('log')
+    ax.set_xlabel(u"Q /\u212B **-1")
+    ax.set_ylabel('reflectivity')
+    return fig

### 2018-06-22 src/data/refnx-0.0.15/refnx/util/test/test_ErrorProp.py

@@ -1,0 +1,79 @@
+from __future__ import division
+
+import refnx.util.ErrorProp as EP
+import numpy as np
+import os
+from numpy.testing import assert_equal, assert_array_almost_equal
+
+
+class TestErrorProp(object):
+
+    def setup_method(self):
+        pass
+
+    def test_add(self):
+        c, dc = EP.EPadd(1.1, 0.5, 1.1, 0.5)
+        assert_equal(2.2, c)
+        assert_equal(np.sqrt(0.5), dc)
+
+    def test_sub(self):
+        c, dc = EP.EPsub(1.1, 0.5, 1.1, 0.5)
+        assert_equal(0, c)
+        assert_equal(np.sqrt(0.5), dc)
+
+    def test_mul(self):
+        c, dc = EP.EPmul(1.1, 0.5, 1.1, 0.5)
+        assert_array_almost_equal(1.21, c)
+        assert_equal(np.sqrt(0.605), dc)
+
+        c, dc = EP.EPmul(0, 0.5, 1.1, 0.5)
+        assert_equal(0, c)
+        assert_equal(0.55, dc)
+
+    def test_div(self):
+        c, dc = EP.EPdiv(1.1, 0.5, 1.1, 0.5)
+        assert_array_almost_equal(1, c)
+        assert_array_almost_equal(0.642824346533225, dc)
+
+        c, dc = EP.EPdiv(0, 0.5, 1.1, 0.5)
+        assert_equal(0, c)
+        assert_array_almost_equal(0.45454545454545453, dc)
+
+    def test_pow(self):
+        c, dc = EP.EPpow(1.1, 0.5, 1.1, 0.5)
+        assert_array_almost_equal(1.1105342410545758, c)
+        assert_array_almost_equal(0.5577834505363953, dc)
+
+        c, dc = EP.EPpow(1.1, 0.5, 1.1, 0)
+        assert_array_almost_equal(1.1105342410545758, c)
+        assert_array_almost_equal(0.5552671205272879, dc)
+
+    def test_log(self):
+        c, dc = EP.EPlog(1.1, 0.5)
+        assert_array_almost_equal(0.09531017980432493, c)
+        assert_array_almost_equal(0.45454545454545453, dc)
+
+    def test_log10(self):
+        c, dc = EP.EPlog10(1.1, 0.5)
+        assert_array_almost_equal(0.04139268515822508, c)
+        assert_array_almost_equal(0.19740658268329625, dc)
+
+    def test_exp(self):
[…]

### 2018-06-22 src/data/refnx-0.0.15/refnx/util/test/test_general.py

@@ -1,0 +1,51 @@
+from __future__ import division
+
+import refnx.util.general as general
+import refnx
+import numpy as np
+import os
+from numpy.testing import assert_almost_equal, assert_
+
+
+def test_version():
+    # check that we can retrieve a version string
+    refnx.__version__
+
+
+class TestGeneral(object):
+    def setup_method(self):
+        self.pth = os.path.dirname(os.path.abspath(__file__))
+
+    def test_q(self):
+        q = general.q(1., 2.)
+        assert_almost_equal(q, 0.1096567037)
+
+    def test_q2(self):
+        qx, qy, qz = general.q2(1., 2., 0., 2.)
+        assert_almost_equal(qz, 0.1096567037)
+
+    def test_wavelength_velocity(self):
+        speed = general.wavelength_velocity(20.)
+        assert_almost_equal(speed, 197.8017006541796, 5)
+
+    def test_wavelength(self):
+        wavelength = general.wavelength(0.1096567037, 1.)
+        assert_almost_equal(wavelength, 2.)
+
+    def test_angle(self):
+        angle = general.angle(0.1096567037, 2.)
+        assert_almost_equal(angle, 1.)
+
+    def test_dict_compare(self):
+        c = {'f': np.arange(10)}
+        d = {'f': np.arange(10)}
+
+        assert_(general._dict_compare(c, d))
+
+        d = {'f': np.arange(11)}
+        assert_(not general._dict_compare(c, d))
+
+        d = {'f': 2}
+        assert_(not general._dict_compare(c, d))
+
+        assert_(general._dict_compare({'a': 1}, {'a': 1}))

### 2018-06-22 src/data/refnx-0.0.15/slim/model.py

@@ -1,0 +1,344 @@
+from __future__ import division
+import os.path
+import os
+import logging
+from copy import copy
+
+from PyQt5 import QtCore
+import numpy as np
+
+from refnx._lib import preserve_cwd
+from refnx.dataset import ReflectDataset
+from refnx.reduce import (number_datafile, PlatypusReduce, basename_datafile,
+                          PlatypusNexus)
+
+
+reducer_entry = [('use', False), ('scale', 1.), ('reflect-1', ''),
+                 ('reflect-2', ''), ('reflect-3', ''), ('direct-1', ''),
+                 ('direct-2', ''), ('direct-3', ''), ('flood', '')]
+default_reducer_entry = {re[0]: re[1] for re in reducer_entry}
+
+
+class ReductionState(object):
+    """
+    Reduces multiple reflectometry datafiles. Attributes control how the
+    reduction proceeds.
+    """
+    def __init__(self, manual_beam_finder=None):
+        super(ReductionState, self).__init__()
+
+        # Each entry specifies the scale factor, whether the file is used for
+        # reduction and the reflected and direct beam runs
+        self.reduction_entries = {}
+
+        self.default_reduction_options = {
+            'low_wavelength': (2.5, float),
+            'high_wavelength': (19, float),
+            'rebin_percent': (2., float),
+            'expected_centre': (123., float),
+            'manual_beam_find': (False, bool),
+            'background_subtraction': (True, bool),
+            'monitor_normalisation': (True, bool),
+            'save_offspecular': (True, bool),
+            'save_spectrum': (True, bool),
+            'streamed_reduction': (False, bool)}
+
+        # the time slices for streamed reduction
+        self.stream_start = 0
+        self.stream_end = 3600
+        self.stream_duration = 30
+
+        # where the data, streamed data and output files are located
+        self.data_directory = ''
+        self.streamed_directory = ''
+        self.output_directory = ''
+
+        self.manual_beam_finder = manual_beam_finder
+
+        for attr, val in self.default_reduction_options.items():
+            setattr(self, attr, val[0])
+
+        self.peak_pos = (90, 5)
+
+        self.save_state_path = None
+
+    def __getstate__(self):
+        d = self.__dict__
+        e = copy(d)
+        e.pop('manual_beam_finder')
+        return e
+
+    @preserve_cwd
+    def reducer(self, callback=None):
+        """
+        Reduce all the entries in reduction_entries
+
+        Parameters
+        ----------
+        callback : callable
[…]

### 2018-06-22 src/data/refnx-0.0.15/slim/view.py

@@ -1,0 +1,247 @@
+from __future__ import print_function, division
+import pickle
+import os.path
+import logging
+
+from PyQt5 import QtCore, QtWidgets, uic
+from PyQt5.QtCore import pyqtSlot
+from model import ReductionTableModel, ReductionState
+from refnx.reduce.manual_beam_finder import ManualBeamFinder
+from plot import SlimPlotWindow
+
+
+class SlimWindow(QtWidgets.QMainWindow):
+    """
+    SLIM is an application for reducing neutron reflectometry data
+    """
+    def __init__(self, ui_loc, parent=None):
+        super(SlimWindow, self).__init__(parent)
+        self.ui_loc = ui_loc
+
+        self.ui = uic.loadUi(os.path.join(ui_loc, 'slim.ui'), self)
+
+        self.reduction_options_dialog = uic.loadUi(
+            os.path.join(ui_loc, 'reduction_options.ui'))
+
+        # the manual beam finder instance
+        self.manual_beam_finder = ManualBeamFinder()
+
+        # reduction state contains all the file numbers to be reduced
+        # and all the reduction options information. You could pickle this file
+        # to save the state of the program
+        self._reduction_state = ReductionState(
+            manual_beam_finder=self.manual_beam_finder)
+
+        self.ReductionTable = ReductionTableModel(self.reduction_state,
+                                                  parent=self)
+        self.ui.file_list.setModel(self.ReductionTable)
+
+        # a plot window for displaying datasets
+        self._plot = SlimPlotWindow(self)
+        self.output_directory.textChanged.connect(
+            self._plot.data_directory_changed)
+
+    def reduction_state(self):
+        return self._reduction_state
+
+    def set_state(self, state):
+        """
+        Recreates the GUI from a ReductionState instance
+
+        Parameters
+        ----------
+        state : ReductionState
+        """
+        if not isinstance(state, ReductionState):
+            return
+
+        # restore the directories
+        self.ui.streamed_directory.setText(state.streamed_directory)
+        self.ui.output_directory.setText(state.output_directory)
+        self.ui.data_directory.setText(state.data_directory)
+
+        # restore reduction options dialog
+        rod = self.reduction_options_dialog
+
+        for attr, val in state.default_reduction_options.items():
+            gui_element = getattr(rod, attr)
+            state_element = getattr(state, attr)
+
+            if val[1] is bool:
+                if state_element:
+                    gui_element.setCheckState(QtCore.Qt.Checked)
+                else:
[…]

### 2018-06-22 src/data/refnx-0.0.15/src/_creflect.pyx

@@ -1,0 +1,131 @@
+from __future__ import division, absolute_import
+from multiprocessing import cpu_count
+import numpy as np
+
+cimport numpy as np
+cimport cython
+from cython.view cimport array as cvarray
+
+cdef extern from "refcalc.h":
+    void reflect(int numcoefs, const double *coefP, int npoints, double *yP,
+                 const double *xP)
+    void reflectMT(int numcoefs, const double *coefP, int npoints, double *yP,
+                   const double *xP, int threads)
+
+DTYPE = np.float64
+ctypedef np.float64_t DTYPE_t
+
+
+# figure out CPU count
+NCPU = cpu_count()
+
+
+@cython.boundscheck(False)
+@cython.cdivision(True)
+cpdef np.ndarray abeles(np.ndarray x,
+           np.ndarray[DTYPE_t, ndim=2] w,
+           double scale=1.0, double bkg=0., int threads=0):
+    if w.shape[1] != 4 or w.shape[0] < 2:
+        raise ValueError("Parameters for _creflect must have shape (>2, 4)")
+    if (w.dtype != np.float64 or x.dtype != np.float64):
+        raise ValueError("Parameters for _creflect must be np.float64")
+
+    cdef int nlayers = w.shape[0] - 2
+    cdef int npoints = x.size
+    cdef np.ndarray[DTYPE_t, ndim=1] coefs = np.empty(4 * nlayers + 8,
+                                                      DTYPE)
+    cdef np.ndarray y = np.empty_like(x, DTYPE)
+
+    # we need the abscissae in a contiguous block of memory
+    cdef np.ndarray xtemp = np.ascontiguousarray(x, dtype=DTYPE)
+
+    coefs[0] = nlayers
+    coefs[1] = scale
+    coefs[2:4] = w[0, 1: 3]
+    coefs[4: 6] = w[-1, 1: 3]
+    coefs[6] = bkg
+    coefs[7] = w[-1, 3]
+    if nlayers:
+        coefs[8:] = w.flatten()[4: -4]
+
+    threads = threads or NCPU
+
+    if threads > 1:
+        reflectMT(4*nlayers + 8, <const double*>coefs.data, npoints,
+                  <double*>y.data, <const double*>xtemp.data, threads)
+    else:
[…]

### 2018-06-22 src/data/refnx-0.0.15/src/refcalc.h

@@ -1,0 +1,85 @@
+/*
+    refcalc.h
+
+    *Calculates the specular (Neutron or X-ray) reflectivity from a stratified
+    series of layers.
+    @Copyright, Andrew Nelson 2014.
+ */
+
+
+#ifdef __cplusplus
+extern "C" {
+#endif
+
+/*
+    reflect uses the Abeles matrix method to calculate specular reflectivity.
+    The system is assumed to consist of a series of uniformly dense layers
+    (slabs). The radiation is incident through the fronting medium, leaving
+    through the backing medium.
+
+    Parameters
+    ----------
+
+    numcoefs - the number of parameters held in the coefP array. This should be
+    4 * N + 8 values long, were N is the number of layers.
+
+    coefP - an array holding the parameters.  See below for a more detailed
+    description
+
+    npoints - the number of points in the yP and xP arrays
+
+    yP - this user supplied array is filled by the reflect function.  It must be
+    npoints long
+
+    xP - array containing the Q (momentum transfer) points. It has units Å**-1.
+    The array is npoints long
+
+    threads - specifies the number of parallel threads to use.
+
+
+    Detailed description of the entries in coefP
+    --------------------------------------------
+    coefP[0] - the number of layers. Should be an integer.
+               4 * coefP[0] + 8 == numcoefs
+
+    coefP[1] - scale factor.  The calculated reflectivity is multiplied by this
+    value. i.e. yP = scale * ref + background
+
+    coefP[2] - fronting SLD, real part. (10**-6 Å**-2)
+
+    coefP[3] - fronting SLD, imaginary part. (10**-6 Å**-2)
+
+    coefP[4] - backing SLD, real part. (10**-6 Å**-2)
+
+    coefP[5] - backing SLD, imaginary part. (10**-6 Å**-2)
+
+    coefP[6] - background.  A constant value added to all the reflectivity
+    points.
+
+    coefP[7] - roughness between backing medium and bottom most layer (Å).  If
+    there are no layers, the roughness between the fronting and backing media.
+
+    coefP[4 * M + 8] - thickness of layer M, with M = 0, ... N - 1. (Å)
+
+    coefP[4 * M + 9] - SLD of layer M, real part (10**-6 Å**-2)
+
+    coefP[4 * M + 10] - SLD of layer M, imaginary part (10**-6 Å**-2)
+
+    coefP[4 * M + 11] - roughness between layer M - 1 / M (Å)
[…]

### 2018-06-23 reports/esi.tex
first draft

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\author{Andrew R. McCluskey}
\title{ESI for "Probabilistic determination of the effect of a deep eutectic solvent on the structure of lipid monolayers"}
\begin{document}

\section{Probability distribution functions}

The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids are given in Figures \ref{fig:dlpc4}-\ref{fig:dmpg5}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dlpc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dlpc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dlpc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpg4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpg5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpg5}
\end{figure}

%%%REFERENCES%%%
\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
\bibliographystyle{rsc} %the RSC's .bst file
\end{document}

### 2018-06-23 reports/paper.tex
first draft

@@
 
-\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Probabilistic determination of the effect of a deep-euctectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
+\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Probabilistic determination of the effect of a deep-eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
 \vspace{0.3cm} & \vspace{0.3cm} \\
 
- & \noindent\large{Adrian Sanchez-Fernandez,\textit{$^{ab}$}$^{\dag}$ Andrew R.
+ & \noindent\large{Adrian Sanchez-Fernandez,\textit{$^{ab}$}$^{\dag\P}$ Andrew R.
 McCluskey,\textit{$^{ac}$}$^{\dag}$ Karen J.
-Edler,$^{\ast}$\textit{$^{a}$}$^{\dag}$ Andrew J.
+Edler,\textit{$^{a}$}$^{\ast}$ Andrew J.
 Jackson,\textit{$^{bd}$} Richard A.
@@
 
-\includegraphics{head_foot/dates} & \noindent\normalsize{The abstract should be a single paragraph which summarises the content of the article.
-Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."
+\includegraphics{head_foot/dates} & \noindent\normalsize{Deep eutectic solvents present a novel class of non-aqueous room temperature solvent, with tunable properties and capable of promoting self-assembly of surfactant molecules.
+However, the interactions between the deep eutectic solvent and the surface-active compounds is not well understood.
+In this work, we present the first example of the self-assembly of a phospholipid monolayer at the interface between air and a non-aqueous solvent.
+Furthermore, we use novel, chemically-relevant modelling of reflectometry measurements to show the ability for the deep eutectic solvent to have an interaction with the phosphocholine lipid head group, leading to an apparent reduction in the component volume compared to that observed in water.
+No such reduction was observed for the phosphatidylglycerol head group, indicating that the interaction is ion specific.} \\
 
@@
 \footnotetext{\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France.}}
-\footnotetext{$^{\dag}$~These authors have contributed equally to the work presented here.}
+\footnotetext{\textit{$^{\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}}
 \footnotetext{$^{\ast}$~Corresponding author: k.edler@bath.ac.uk}
@@
 %If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
-\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
+\footnotetext{\dag~Electronic Supplementary Information (ESI) available: A series Jupyter notebooks and Python plotting scripts, allowing for a fully reproducible analysis of all data presented herein as well as figures showing the probability distribution functions for each of the lipid models.
+See DOI: 10.1039/b000000x/}
 %additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
 
-\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
+\footnotetext{$^{\dag}$~These authors have contributed equally to the work presented within.}
+%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
 Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
@@
 \section{Introduction}
-Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, amoung others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between the precursors, allowing the mixture to remain liquid at room temperature due to the high-entropy state of the mixture.\cite{Hammond2016, Hammond2017, Araujo2017} Furthermore, through different combinations of the precursors materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}
+Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, amoung others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between these precursors, allowing the mixture to remain liquid at room temperature due to the high-entropic state of the mixture.\cite{Hammond2016, Hammond2017, Araujo2017} Additionally, through different combinations of the precursors materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}
 
-These solvents have recently shown the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} demonstrating the presense of a solvophobic effect.
-The behaviour of biomolecules in DES has also seen and increase in interest, due to potential applications towards the preservation of biomolecules by DES, and as environments for enzymatic reactions\cite{Merza2018} additionally, the behaviour and conformation of proteins and enzymes in these solvents have received remarkable interest.\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} Finally, recent investigations have also shown that DES have been shown to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
+These solvents have recently shown the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect.
+The behaviour and conformation of biomolecules in DES has seen and increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to potential applications in the preservation of biomolecules, as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES have been shown to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
 
 The formation of phospholipid monolayers plays a key role in many biological and technological processes.
-The amphiphilic lipids commonly show a low soluibilty in the one of the two phases, leading to the formation of a stable monolayer at the interface.\cite{Mohwald1990} Phospholipid consist of a charged headgroup, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the lipid-ion interactions on structure, monomer packing and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers in non-aqueous media has not been reported, to the best of the authors' knowledge.
+Amphiphilic lipids commonly show a low soluibilty in the one of the two phases, leading to the formation of a stable monolayer at the interface.\cite{Mohwald1990} Phospholipids consist of a charged headgroup, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the lipid-ion interactions on structure, monomer packing, and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers in non-aqueous media has not been previously reported, to the best of the authors' knowledge.
 
-Recent developments in computational resources and software has enabled powerful methodologies to be harnessed by those from non-computer science backgrounds.
-This has mostly occurred through open-source software projects such as Python and the Jupyter notebooks framework.\cite{vanRossum1995,Kluyver2016} In the area of neutron and X-ray reflectometry data-analysis, this has led to the development of tool such as refnx,\cite{Nelson2018} a Python library for the fitting of layer-based models to reflectometry data.
-The availiablility of such software enables the use of models that contain chemical-context within theirs structure.
-Wherein, the chemically-relevant information known about the system is used within the model, such as the constaint that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups.
+Recent developments in computational resource and software has enabled powerful methodologies and algorithms to be harnessed by those from non-computer science backgrounds.
+This has mostly occurred through open-source software projects such as the Python language and the Jupyter notebooks framework.\cite{vanRossum1995,Kluyver2016} In the area of neutron and X-ray reflectometry data-analysis, this has led to the development of refnx,\cite{Nelson2018} a Python library for the fitting of layer-based models to reflectometry data.
+refnx enables the use of custom models that contain chemically-relevant information.
+This information includes constaints such as that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups and that the length of the tail chains should be equal to the Tanford length.\cite{Tanford1980}
 
-The use of a Python library for fitting enable powerful probability distribution function sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This library allows for the sampling of a high-dimensionality parameter space, such as that which is relevant to reflectometry fitting to be performed with relative ease.
+The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This method allows for the sampling of a high-dimensionality parameter space, such as that which is relevant to reflectometry fitting, to be performed with relative ease.
 This results in estimatations of the inverse uncertainties associated with each parameter as well as information about the correlations between different parameters within the model.
@@
 Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) were purchased and used without further purification.
-The deep eutectic solvent was prepared by mixing the precursors at the appropriate mole ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid was formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.
+The DES was prepared by mixing the precursors at the appropriate mole ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.
 
-The water content on the deep eutectic solvent was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to keep track of any effect from the presence of water on our results.
+The water content on the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
 Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}
 
-DPPC (> 99 \%), DMPC (> 99 \%), and DMPG (> 99 \%) were supplied by Avanti Polar Lipids and used as received.
-DLPC (> 99 \%) was supplied by Sigma-Aldrich and used as received.
+DPPC (> 99 \%), DMPC (> 99 \%), and DMPG (> 99 \%) were supplied by Avanti Polar Lipids and DLPC (> 99 \%) was supplied by Sigma-Aldrich and all were used as received.
 Sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
 After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
-Surface concentration was modified by closing and opening the PTFE barriers of the Langmuir trough (XRR).
+Surface concentration was modified by closing and opening the PTFE barriers of the Langmuir trough.
 
@@
 X-ray reflectivity measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$.
-The data was normalised to the incident beam and background was measured from off-specular reflection and subsequently subtracted.
+The data was normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
 The sample environment consisted of a PTFE Langmuir trough.
 Samples were equilibrated for at least one hour and preserved under argon atmosphere to minimise the adsorption of water by the subphase.
-Surface concentration was controlled through opening and closing the barriers of the Langmuir trough and measured using an aluminium Wilhelmy plate.
-X-ray reflectivity data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG and all measurements were made at 22 $^\circ$C at five different surface concentrations.
+Surface concentration was controlled through opening and closing the barriers of the Langmuir trough.
+X-ray reflectivity data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG and all measurements were made at 22 $^\circ$C at five different surface concentrations, however full analysis was only performed for the two highest surface concentrations where the monolayer would be in the condensed phase.
 
 \subsection{Data analysis}
-The use of reflectometry to analyse the structure of phospholipids on the surface of water has a histroy extending ovoer many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} This has led to some variation in the models used to fit experimental data, shown in Table \ref{tab:water}.
-Although, there appears to be a general consensus that the molecular volume of the phosphocholine is in the region of 320 \AA$^3$, and as a result this figure is also used as a physical constraint on the layer model when fitting reflectometry data.
-However, as this work involves the use of a non-aqueous solvent system we believe that the these literature values for the head group molecular volumes may be unreliable.
+The use of reflectometry to analyse the structure of phospholipids on the surface of water has a histroy extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} This has led to some variation in the models used to fit experimental data, shown in Table \ref{tab:water}.
+Although, there appears to be a general consensus that the volume of the phosphocholine is in the range from 320 \AA$^3$ to 360 \AA$^3$, and as a result this volume is often used as a physical constraint on the layer model when fitting reflectometry data.
+However, this work involves the use of a non-aqueous solvent system and we believe that the these literature values for the head group volumes may be unreliable in such media.
 This is due to the charged nature of the zwitterionic and anionic lipid heads having a significant interaction with the solvent in both the neutral water and the charged DES.
@@
 
-To allow for the use of a chemically-relevant model, where the lipid head group molecular volume was allowed to vary, the Python library refnx\cite{Nelson2018} as used.
-This software allows the inclusion of a custom chemically-sensible model from which the parameters to be fed into the Abel\`{e}s layer-model,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
+To allow for the use of a chemically-relevant model, where the lipid head group volume was allowed to vary, the Python library refnx\cite{Nelson2018} as used.
+This software allows the inclusion of a custom chemically-relevant model from which the parameters to be fed into the Abel\`{e}s layer-model,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
 This custom model, along with Jupyter notebook showing in full the analysis performed, can be found in the ESI.
 
-This chemical model involves considering the lipids as consisting of head groups and tail groups.
-The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron), and a molecular volume, $V_h$.
-The head groups make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, with a same volume fraction of solvent can intercalate into the head group regin, $\phi_h$.
-While, the tail groups also have a calculated scattering length, $b_t$, and molecular volume, $V_t$, however the thickness of the tail group layer, $d_t$, is found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
+This chemically-relevant model involves considering the lipids as consisting of head groups and tail groups.
+The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron), and a volume, $V_h$.
+These head groups make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
+The tail groups also have a calculated scattering length, $b_t$, and a volume, $V_t$, however the thickness of the tail group layer, $d_t$, is found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
 \begin{equation}
@@
 \end{equation}
-The air above the monolayer is also able to solvate the tail region with some volume fraction, $\phi_t$.
+The air above the monolayer is also able to solvate the tail region by some volume fraction, $\phi_t$.
 The scattering length density of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
@@
 \begin{equation}
+\label{equ:ht}
 d_h = \frac{V_hd_t(1-\phi_t)}{V_t(1-\phi_h)}. 
@@
 
-This custom model was used to co-refine the two highest surface concentration measurements to determine the molecular volume for the lipid head group, $V_h$, which was allowed to vary within resonable bounds but held constant between the two concentrations.
+This custom model was used to co-refine the volume of the lipid head group, $V_h$, for the two highest surface concentration measurements.
 Other parameters that were allowed to very were $\theta_t$, $\phi_t$, $\phi_h$, $\sigma_t$, and $\sigma_h$, while the parameters shown in Table \ref{tab:invariant} were held constant at the values given.
-The length of the carbon chain was kept constant to the value given by the Tanford equation,\cite{Tanford1980} this is valid due to the condensed nature of the monolayer at this surface pressure resulting in the extending, staggered conformation of the chain being likely.
-
-%Using this custom model, the following parameters where allowed to vary, within resonable bounds; $V_h$, $\theta_t$, $\phi_t$, $\phi_h$, $\sigma_t$, and $\sigma_h$, while those values shown in Table \ref{tab:invariant} were held constant.
+The length of the carbon chain was kept constant to the value determined by the Tanford equation,\cite{Tanford1980} this is valid due to the condensed nature of the monolayer at this surface concentration resulting in the extended, staggered conformation of the chain being likely.
 
@@
 
-The fitting of the reflectometry model to the experimental involved transforming the result of the model and the data into $rq^4$ such that the artifact of the Fresnel decay was removed before using the differential evoulation method available to refnx from the scipy library, to find the parameters which gave the best fit to the data.
-The parameter space for each of these was then probed using the MCMC method available through emcee, this allowed for an estimate of the probability distribution function associated with each parameter.
+The fitting of the reflectometry model to the experimental involved transforming the reflectometry calculated from the model and the data into $Rq^4$ such that the artifact of the Fresnel decay was removed, before using the differential evoulation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
+The parameter space was then probed using the MCMC method available through emcee, this allowed for an estimate of the PDF associated with each parameter.
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
@@
 	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
-	\caption{The reflectometry profile, scattering length density profile and probability distribution function for each of the three phosphocholine containing lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.}
+	\caption{The reflectometry profile, scattering length density profile and probability distribution function for each of the three phosphocholine containing lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:lipids}
 \end{figure}
-The custom model with a variable head molecular volume, was co-refined for the highest two concentrations of all lipids.
-The resulting reflectometry profiles, associated scattering length density profiles and the probability distribution function (PDF) for the head group molecular volume are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of the other varying parameters for each lipid, these are given with asymmetric error bars which give the 95 \% confidence interval, the full probability distribution plots can be found in the ESI.
+The custom model was co-refined for the highest two concentrations of all lipids.
+The resulting reflectometry profiles, associated scattering length density profiles and the PDF for the head group volume are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} gives details of all varying parameters for each lipid, these are given with asymmetric error bars which correspond to a 95 \% confidence interval, the full PDF plots can be found in the ESI.
 \begin{table*}
@@
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl}.}
+\ref{equ:tl}.
+The values of $d_h$ were obtained from the appropriate use of Eqn.
+\ref{equ:ht}}
 	\label{tab:liptab}
@@
 
-Since the tail chain length is held constant to the value of the Tanford length for a given lipid tail, there is a direct correlation between the thickness of the tail layer and the chain tilt angle from the model.
 It can be seen from Table \ref{tab:liptab} that as would be expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chains increases.
@@
 This indicates that for DLPC and DPPC these two highest surface concentration measurements where at a similar area per molecule, while the area per molecule slightly decreased between the two measurements for DMPC and DPPC.
-The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, as would be expected with the head layer becoming more packed and therefore there is less space for solvent.
+The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, this would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.
 
-The thickness of the tail layers in these condensed monolayers appears to agree well with values found for water-analogues for each of the lipids (DMPC: $d_t=15.8$ \AA,\cite{Johnson1991} DPPC: $d_t=16.7$ \AA\cite{Helm1987}).
-Previous work indicates, although there has been no direct comparison that the phosphatidylglycerol head layer may be thicker than phosphocholine at a water-air interface.\cite{Clifton2012,Johnson1991,Vaknin1991,Lawrie2000} However, the phosphocholine head group appears to be slightly expanded in the DES compared to in water (PPC: $d_h=8.4$ \AA\cite{Helm1987}) resulting in the values for the thicknesses of the head layers being similar between the two head groups.
+The thickness of the tail layers in these condensed monolayers appears to agree well with values found for water-analogues (DMPC: $d_t=15.8$ \AA,\cite{Johnson1991} DPPC: $d_t=16.7$ \AA\cite{Helm1987}).
+Previous work indicates, although there has been no direct comparison, that the phosphatidylglycerol head layer may be thicker than phosphocholine at a water-air interface.\cite{Clifton2012,Johnson1991,Vaknin1991,Lawrie2000} However, the phosphocholine head group appears to be slightly expanded in the DES compared to in water (DPPC: $d_h=8.4$ \AA\cite{Helm1987}) resulting in the values for the thicknesses of the head layers being similar between the two head groups.
 
-Figures \ref{fig:lipids}(a-c) shows the PDF determined for the head group volume for each of the four lipids.
-The three lipids with a phosphocholine head group appear to show some unsystematic variance with values of \input{../output/dlpc/vh.txt} \AA$^{3}$ for DLPC, \input{../output/dmpc/vh.txt} \AA$^{3}$ for DMPC, and \input{../output/dppc/vh.txt} \AA$^{3}$ for DPPC.
-This is significantly less than the largest estimate of the head volume from literature sources, 360 \AA$^3$,\cite{Tardieu1973} and slightly less than lowest estimate, 319 \AA$^3$.\cite{Sun1994,Kucerka2004} The fact that the choline chloride component of the DES is charged in nature suggests that it has a screening effect on the charged interactions between the zwitterionic phosphocholine head groups reducing the volume that it occupies.
+Figures \ref{fig:lipids}(a-c) show the PDF determined for the head group volume for each of the four lipids.
+The three lipids with a phosphocholine head group appear to show some small unsystematic variation as the tail length is changed, with values of \input{../output/dlpc/vh.txt} \AA$^{3}$ for DLPC, \input{../output/dmpc/vh.txt} \AA$^{3}$ for DMPC, and \input{../output/dppc/vh.txt} \AA$^{3}$ for DPPC.
+This is significantly less than the largest estimate of the head volume from literature sources, 360 \AA$^3$,\cite{Tardieu1973} and slightly less than lowest estimate, 319 \AA$^3$.\cite{Sun1994,Kucerka2004} The fact that the choline chloride component of the DES is charged in nature suggests that it may have a screening effect on the charged interactions between the zwitterionic phosphocholine head groups reducing the volume occupied.
 
@@
 	\includegraphics[width=0.30\textwidth]{figures/head_groups}
-	\caption{The two lipid head groups compared in this study, where R indicates the carbon tail; (a) phosphatidylglycerol, (b) phosphocholine.}
+	\caption{The two lipid head groups compared in this study, where R indicates the carbon tail; (a) phosphatidylglycerol, (b) phosphocholine.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:heads}
@@
 
-Previous work has suggested that the DES may provide a segregated environment to better solubilise the phospholipid head groups.\cite{Bryant2016,Bryant2017}.
-Since both the phosphatidylglycerol and phosphocholine head groups contain a moeity of the DES solvent, it is possible for the choline terminal of the phosphocholine would favour the presence of glycerol, while the glycerol terminal of the phosphatidylglycerol would be favourable solubilised by the choline moeity of the DES.
+Finally, previous work has suggested that the DES may provide a segregated environment to better solubilise phospholipid head groups.\cite{Bryant2016,Bryant2017}.
+Since both the phosphatidylglycerol and phosphocholine head groups contain a moeity of the DES solvent, it is possible for the choline terminal of the phosphocholine would favour the presence of glycerol, while the glycerol terminal of the phosphatidylglycerol would be favourably solubilised by the choline moeity of the DES.
 This solvent segregation of the DES may result in the phosphocholine head group being preferentially solubilised due to the greater molar abundence of glycerol in the 1:2 mixture, and hence giving a smaller volume for this head group than found in water.
@@
 \section{Conclusions}
-The conclusions section should come in this section at the end of the article, before the Conflicts of interest statement.
+Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed to at the air-DES interface, and chemically-relevant modelling was used to analyse X-ray reflectometry measurements quantifying the effect that the non-aqueous solvent on the volume occupied by the head group of each lipid.
+The structure of the tail regions were similar to those previously found at the air-water interface, while there was clear decrease in the volume occupied by the phosphocholine head group.
+This decrease was not also found in the phosphatidylglycerol head group volume.
+
+A possible cause for this volume reduction may be the screening of the positive charge on the ammonium moeity of the phosphocholine, as this is a differential feature of the two lipid head groups.
+It appears that specific ion-ion interactions between the positively charged nitrogen and, most likely, the negatively charged chloride ion results in a modification to the head group charge density in DES compared to that in water.
+It is possible that the change observed to the head groups may be observed structurally, however insufficient instrument resolution did not allow for the precise identification of such changes.
+
+The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-relevant model to be used within the analysis of the X-ray reflectometry measurements.
+Futhermore, this work presents the first, to our knowledge, use of chemically-relevant parameterisation to ce-refine X-ray reflectometry measurements at different surface concentrations.
+
+Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of functional phospholipid monolayers at the air-liquid interface.
+Therefore, choline chloride:glycerol DES constitutes a novel environment where phospholipid membranes may be investigated.
+These possibilities include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
 

### 2018-06-24 reports/paper.tex
fix uncertainties printing

@@
 	\caption{The reflectometry profile, scattering length density profile and probability distribution function for each of the three phosphocholine containing lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+The reflectometry and SLD profiles have been offset in the $y$-axis for clarity.
 Figure files are available under MIT License.\cite{mccluskey_2018}}
@@
 This indicates that for DLPC and DPPC these two highest surface concentration measurements where at a similar area per molecule, while the area per molecule slightly decreased between the two measurements for DMPC and DPPC.
-The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, this would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.
+The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.\cite{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, this would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.
 

### 2018-06-24 notebooks/DMPG/DMPG_all_conc.py

@@ -274,14 +274,14 @@ for i in range(0, flatchain.shape[1]):
     elif 'sol' in lab[i]:
         k = [a[1]*100, (a[1] - a[0])*100, (a[2] - a[1])*100]
         q = '{:.2f}'.format(k[0])
-        w = '{:.2f}'.format(k[1])
-        e = '{:.2f}'.format(k[2])
+        e = '{:.2f}'.format(k[1])
+        w = '{:.2f}'.format(k[2])
         total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     else:
         k = [a[1], a[1] - a[0], a[2] - a[1]]
         q = '{:.2f}'.format(k[0])
-        w = '{:.2f}'.format(k[1])
-        e = '{:.2f}'.format(k[2])
+        e = '{:.2f}'.format(k[1])
+        w = '{:.2f}'.format(k[2])
         total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     total_pearsons.close()
     
@@ -292,8 +292,8 @@ for i in range(0, len(lab2)):
     a = mquantiles(kl[i], prob=[0.025, 0.5, 0.975])
     k = [a[1], a[1] - a[0], a[2] - a[1]]
     q = '{:.2f}'.format(k[0])
-    w = '{:.2f}'.format(k[1])
-    e = '{:.2f}'.format(k[2])
+    e = '{:.2f}'.format(k[1])
+    w = '{:.2f}'.format(k[2])
     total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     total_pearsons.close()
         
@@ -304,8 +304,8 @@ for i in range(0, len(lab2)):
     a = mquantiles(kl[i], prob=[0.025, 0.5, 0.975])
     k = [a[1], a[1] - a[0], a[2] - a[1]]
     q = '{:.2f}'.format(k[0])
-    w = '{:.2f}'.format(k[1])
-    e = '{:.2f}'.format(k[2])
+    e = '{:.2f}'.format(k[1])
+    w = '{:.2f}'.format(k[2])
     total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     total_pearsons.close()
     
[…]

### 2018-06-24 notebooks/DPPC/DPPC_all_conc.py

@@ -274,14 +274,14 @@ for i in range(0, flatchain.shape[1]):
     elif 'sol' in lab[i]:
         k = [a[1]*100, (a[1] - a[0])*100, (a[2] - a[1])*100]
         q = '{:.2f}'.format(k[0])
-        w = '{:.2f}'.format(k[1])
-        e = '{:.2f}'.format(k[2])
+        e = '{:.2f}'.format(k[1])
+        w = '{:.2f}'.format(k[2])
         total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     else:
         k = [a[1], a[1] - a[0], a[2] - a[1]]
         q = '{:.2f}'.format(k[0])
-        w = '{:.2f}'.format(k[1])
-        e = '{:.2f}'.format(k[2])
+        e = '{:.2f}'.format(k[1])
+        w = '{:.2f}'.format(k[2])
         total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     total_pearsons.close()
     
@@ -292,8 +292,8 @@ for i in range(0, len(lab2)):
     a = mquantiles(kl[i], prob=[0.025, 0.5, 0.975])
     k = [a[1], a[1] - a[0], a[2] - a[1]]
     q = '{:.2f}'.format(k[0])
-    w = '{:.2f}'.format(k[1])
-    e = '{:.2f}'.format(k[2])
+    e = '{:.2f}'.format(k[1])
+    w = '{:.2f}'.format(k[2])
     total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     total_pearsons.close()
             
@@ -304,8 +304,8 @@ for i in range(0, len(lab2)):
     a = mquantiles(kl[i], prob=[0.025, 0.5, 0.975])
     k = [a[1], a[1] - a[0], a[2] - a[1]]
     q = '{:.2f}'.format(k[0])
-    w = '{:.2f}'.format(k[1])
-    e = '{:.2f}'.format(k[2])
+    e = '{:.2f}'.format(k[1])
+    w = '{:.2f}'.format(k[2])
     total_pearsons.write('$' + str(q) + '^{+' + str(w) + '}_{-' + str(e) + '}$')
     total_pearsons.close()
     
[…]

### 2018-06-27 reports/esi.tex
Second draft now with neutrons

@@
 
-The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids are given in Figures \ref{fig:dlpc4}-\ref{fig:dmpg5}
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc4}-\ref{fig:dmpg5}.
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpc3_1}-\ref{fig:dppc3_2}.
 \begin{figure}[h]
@@
 	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at the second-highest concentration.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dlpc4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dlpc5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dlpc5}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at the second-highest concentration.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dmpc4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dmpc5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dmpc5}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at the second-highest concentration.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dppc4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dppc5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dppc5}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at the second-highest concentration.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dmpg4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dmpg5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
 	\label{fig:dmpg5}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpc3_neutron_corner1}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC/h-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\label{fig:dmpc3_1}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpc3_neutron_corner2}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC/hd-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\label{fig:dmpc3_2}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dppc3_neutron_corner1}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC/h-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\label{fig:dppc3_1}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dppc3_neutron_corner2}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC/hd-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\label{fig:dppc3_2}
 \end{figure}

### 2018-06-27 reports/paper.tex
Second draft now with neutrons

--- 2018-06-23 reports/paper.tex
@@
 Jackson,\textit{$^{bd}$} Richard A.
-Campbell,\textit{$^{e}$} and Thomas Arnold\textit{$^{abc}$}} \\%Author names go here instead of "Full name", etc.
+Campbell,\textit{$^{e}$} and Thomas Arnold\textit{$^{abcf}$}$^{\ast}$} \\%Author names go here instead of "Full name", etc.
 
 \includegraphics{head_foot/dates} & \noindent\normalsize{Deep eutectic solvents present a novel class of non-aqueous room temperature solvent, with tunable properties and capable of promoting self-assembly of surfactant molecules.
-However, the interactions between the deep eutectic solvent and the surface-active compounds is not well understood.
+However, the solvation model in these systems still challenges the classic understanding of amphiphilicity.
 In this work, we present the first example of the self-assembly of a phospholipid monolayer at the interface between air and a non-aqueous solvent.
@@
 \footnotetext{\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France.}}
+\footnotetext{\textit{$^{f}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK.}}
 \footnotetext{\textit{$^{\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}}
-\footnotetext{$^{\ast}$~Corresponding author: k.edler@bath.ac.uk}
+\footnotetext{$^{\ast}$~Corresponding author: k.edler@bath.ac.uk, tom.arnold@esss.se}
 
@@
 refnx enables the use of custom models that contain chemically-relevant information.
-This information includes constaints such as that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups and that the length of the tail chains should be equal to the Tanford length.\cite{Tanford1980}
+This information includes constaints such as that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups and that the length of the tail chains should not surpass a maximum of the Tanford length for a given chain.\cite{Tanford1980}
 
@@
 
-In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemical-context modelling of X-ray reflectometry measurements.
+In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemical-context modelling of X-ray reflectometry (XRR) measurements.
 Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air.
@@
 \subsection{Materials}
-Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) were purchased and used without further purification.
+Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) d$_9$-choline chloride (99 \%, 98 \% D, CK Isotopes) and d8-glycerol (99 \%, 98 \% D, CK Isotopes)  were purchased and used without further purification.
 The DES was prepared by mixing the precursors at the appropriate mole ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.
+Due to the limited availability of the deuterated precursors, a fully protonated subphase (hDES) and a partially deuterated subphase (hdDES) were prepared and used during the neutron reflectometry (NR) experiment.
+The partiall deuterated subpahse was prepared using the following mixtures of precursors: 1 mole of 0.38 fraction of h-choline chloride/0.62 mole fraction of d-choline chloride; and 2 moles of 0.56 mole fraction of h-glycerol/0.44 mole fraction of d-glycerol.
+The solvent was subsequently prepared follow the procedure discussed above.
 
@@
 DPPC (> 99 \%), DMPC (> 99 \%), and DMPG (> 99 \%) were supplied by Avanti Polar Lipids and DLPC (> 99 \%) was supplied by Sigma-Aldrich and all were used as received.
-Sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
+Deuterated versions of DPPC (d62-DPPC, > 99 \%, deuterated tails-only) and DMPC (d54-DPPC, > 99 \%, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
+These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature.
+
+In the XRR, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
 After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
 Surface concentration was modified by closing and opening the PTFE barriers of the Langmuir trough.
+In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a managageable level) it was not possible to use a Langmuir trough.
+Instead, small Delrin adsorption troughs were used that did not have controlable barriers.
+This resulted in no control over the surface pressure of the measurement and therefore it was not possible to co-refine different NR contrasts.
 
 \subsection{Methods}
-X-ray reflectivity measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$.
+XRR measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$.
 The data was normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
@@
 Surface concentration was controlled through opening and closing the barriers of the Langmuir trough.
-X-ray reflectivity data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG and all measurements were made at 22 $^\circ$C at five different surface concentrations, however full analysis was only performed for the two highest surface concentrations where the monolayer would be in the condensed phase.
+XRR data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG at two surface pressures, 20 mNm$^{-1}$ and 30 mNm$^{-1}$, as measured with an aluminium Wilhelmy plate, all measurements were made at 22 $^\circ$C.
+
+The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Two angle regimes were measured to provide a momentum transfer range from 0.0005 to 0.18 \AA$^{-1}$.
+Small-volume Delrin adsorption troughs were used to support the sample.
+A single surface concentration for each system and contrast was measured.
+Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours) and kept under inert atmosphere.
 
@@
 The use of reflectometry to analyse the structure of phospholipids on the surface of water has a histroy extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} This has led to some variation in the models used to fit experimental data, shown in Table \ref{tab:water}.
-Although, there appears to be a general consensus that the volume of the phosphocholine is in the range from 320 \AA$^3$ to 360 \AA$^3$, and as a result this volume is often used as a physical constraint on the layer model when fitting reflectometry data.
-However, this work involves the use of a non-aqueous solvent system and we believe that the these literature values for the head group volumes may be unreliable in such media.
-This is due to the charged nature of the zwitterionic and anionic lipid heads having a significant interaction with the solvent in both the neutral water and the charged DES.
+Although, there appears to be a general consensus that the component volume of the phosphocholine is in the range from 320 \AA$^3$ to 360 \AA$^3$, and as a result this volume is often used as a physical constraint on the layer model when fitting reflectometry data.
+However, since this work involves a non-aqueous solvent we do not know whether the head group component volumes used in the literature are derived from water-based measurements are appropriate for this work.
+The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with neutral water as compared to the charged DES.\cite{Sanchez-Fernandez2018}
 
@@
 
-To allow for the use of a chemically-relevant model, where the lipid head group volume was allowed to vary, the Python library refnx\cite{Nelson2018} as used.
+To allow for the use of a chemically-relevant model, where the lipid head group component volume was allowed to vary, the Python library refnx\cite{Nelson2018} as used.
 This software allows the inclusion of a custom chemically-relevant model from which the parameters to be fed into the Abel\`{e}s layer-model,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
@@
 This chemically-relevant model involves considering the lipids as consisting of head groups and tail groups.
-The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron), and a volume, $V_h$.
+The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron), and a component volume, $V_h$.
 These head groups make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
-The tail groups also have a calculated scattering length, $b_t$, and a volume, $V_t$, however the thickness of the tail group layer, $d_t$, is found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
+The tail groups also have a calculated scattering length, $b_t$, and a component volume, $V_t$, however the thickness of the tail group layer, $d_t$, is found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
 \begin{equation}
@@
 The air above the monolayer is also able to solvate the tail region by some volume fraction, $\phi_t$.
-The scattering length density of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
+The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
 \begin{equation}
@@
 where $\text{SLD}_{s}$ is the scattering length density of the superphase (air) and the subphase (DES) for the tail and head groups respectively, and $i$ indicates either the tail or head layer.
-In order to ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was added to the model,
+In order to ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was added to the model,\cite{Braun2017}
 \begin{equation}
@@
 
-This custom model was used to co-refine the volume of the lipid head group, $V_h$, for the two highest surface concentration measurements.
-Other parameters that were allowed to very were $\theta_t$, $\phi_t$, $\phi_h$, $\sigma_t$, and $\sigma_h$, while the parameters shown in Table \ref{tab:invariant} were held constant at the values given.
+Initially, this custom model was used to co-refine the component volume of the lipid head group, $V_h$, for the two surface concentration XRR measurements.
+Some parameters were allowed to vary ($\theta_t$, $\phi_t$, $\phi_h$, $\sigma_t$, and $\sigma_h$); while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
 The length of the carbon chain was kept constant to the value determined by the Tanford equation,\cite{Tanford1980} this is valid due to the condensed nature of the monolayer at this surface concentration resulting in the extended, staggered conformation of the chain being likely.
@@
 	\small
-	\caption{\ The variant parameters within the chemically-sensible model.
+	\caption{\ The invariant parameters within the chemically-sensible model.
 $^a$Values determined from Armen \emph{et al.}\cite{Armen1998} $^b$Values obtained from the Tanford formula where the carbon chains are assumed to be fully extended.\cite{Tanford1980} $^c$Values extracted from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
 	\label{tab:invariant}
-	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ll}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}llllll}
 		\hline
-		Parameter & Value \\
+		Component & $b_t$/fm & $b_h$/fm & $V_t$/\AA$^3$ & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
 		\hline
-		DP-$b_t$/fm & 6897 \\
-		DM-$b_t$/fm & 5985 \\
-		DL-$b_t$/fm & 5073 \\
-		PC-$b_h$/fm & 4674 \\
-		PG-$b_h$/fm & 4731 \\
-		DP-$V_t$/\AA$^3$ & 891$^a$ \\
-		DM-$V_t$/\AA$^3$ & 779$^a$ \\
-		DL-$V_t$/\AA$^3$ & 667$^a$ \\	
-		DP-$t_t$/\AA & 21.8$^b$ \\
-		DM-$t_t$/\AA & 19.3$^b$ \\
-		DL-$t_t$/\AA & 16.7$^b$ \\
-		$\text{SLD}_{\text{sup}}$/$\times10^{-6}$\AA$^{-2}$ & 0\\
-		$\text{SLD}_{\text{sub}}$/$\times10^{-6}$\AA$^{-2}$ & 10.8$^c$ \\
+		X-ray & & & & & \\
+		DLPC & 5073 & 4674 & 667$^a$ & 15.5$^b$ & -- \\
+		DMPC & 5985 & 4674 & 779$^a$ & 18.0$^b$ & -- \\
+		DPPC & 6897 & 4674 & 891$^a$ & 20.5$^b$ & -- \\
+		DMPG & 5985 & 4731 & 779$^a$ & 18.0$^b$ & --\\
+		Air & -- & -- & -- & -- & 0\\
+		DES & -- & -- & -- & -- & 10.8$^c$ \\
+		\hline
+		Neutron & & & & & \\
+		d54-DMPC & 5329.8 & 602.7 & 779$^a$ & 18.0$^b$ & -- \\
+		d62-DPPC & 6129.2 & 602.7 & 891$^a$ & 20.5$^b$ & -- \\
+		h-DES & -- & -- & -- & -- & 0.43$^c$  \\
+		hd-DES & -- & -- & -- & -- & 3.15$^c$ \\
 		\hline
@@
 
-The fitting of the reflectometry model to the experimental involved transforming the reflectometry calculated from the model and the data into $Rq^4$ such that the artifact of the Fresnel decay was removed, before using the differential evoulation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
+The determined head group component volumes were then used in the refinement of the custom model against the NR measurements.
+Due to the lack of contrast present between the hydrogenated phosphocholine head group and the solvent, it was necessary to constrain the thickness and roughness of the head layer based on that determined from the highest surface concentration XRR measurement, this allowed the chain tilt angle to be constrained based on the following relationship,
+\begin{equation}
+\label{equ:ct}
+\theta_t = \cos^{-1}\bigg(\frac{V_td_h(1-\phi_h)}{V_ht_t(1-\phi_t)}\bigg),
+\end{equation}
+ensuring that the number density of head groups and pairs of tails is held constant.
+Table \ref{tab:invariant} gives the details of the scattering length and SLDs used as invariant parameters in the custom model, while the tail component volumes and tail chain length were the same as for the XRR.
+
+The refinement of the custom model to the experimental data involved transforming the reflectometry calculated from the model and the data into $Rq^4$ such that the artifact of the Fresnel decay was removed, before using the differential evoulation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
 The parameter space was then probed using the MCMC method available through emcee, this allowed for an estimate of the PDF associated with each parameter.
@@
 \section{Results \& Discussion}
+
+\subsection{Solvent effect on lipid head component volumes}
 
@@
 	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
-	\caption{The reflectometry profile, scattering length density profile and probability distribution function for each of the three phosphocholine containing lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+	\caption{The XRR profile, SLD profile and probability distribution function of the head component volume for each of the four lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+The NR and SLD profiles have been offset in the $y$-axis for clarity.
 Figure files are available under MIT License.\cite{mccluskey_2018}}
@@
 The custom model was co-refined for the highest two concentrations of all lipids.
-The resulting reflectometry profiles, associated scattering length density profiles and the PDF for the head group volume are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of all varying parameters for each lipid, these are given with asymmetric error bars which correspond to a 95 \% confidence interval, the full PDF plots can be found in the ESI.
+The resulting reflectometry profiles, associated SLD profiles and the PDF for the head group component volume are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} gives details of all varying parameters for each lipid, these are given with asymmetric uncertainties that correspond to a 95 \% confidence interval, the full PDF plots can be found in the ESI.
 \begin{table*}
 	\small
-	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the phosphocholine reflectometry model.
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 		\hline
-		 & DLPC & & DMPC & & DPPC & & DMPG & \\
+		Lipid & DLPC & & DMPC & & DPPC & & DMPG & \\
+		Surface Pressure/mNm${-1}$ & 20 & 30 & 20 & 30 & 20 & 30 & 20 & 30 \\
 		\hline
-		Parameter & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 \\
 		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle4.txt} & \input{../output/dlpc/angle5.txt} & \input{../output/dmpc/angle4.txt} & \input{../output/dmpc/angle5.txt} & \input{../output/dppc/angle4.txt} & \input{../output/dppc/angle5.txt} & \input{../output/dmpg/angle4.txt} & \input{../output/dmpg/angle5.txt} \\
@@
 Additionally, it is also observed that the value of the chain tilt either decreases, resulting in a tail thickness increase, or remains constant as the surface concentration increases.
-This indicates that for DLPC and DPPC these two highest surface concentration measurements where at a similar area per molecule, while the area per molecule slightly decreased between the two measurements for DMPC and DPPC.
-The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, this would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.
+This indicates that for DLPC and DPPC these concentrations were in a condensed state, where futher increases in surface concentration had little effect on the monolayer's structure.
+For DMPC and DMPG, however, the area per molecule slightly decreased between the two measurements for DMPC and DPPC.
+The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.\cite{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same.
+This would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.
 
@@
 
-Figures \ref{fig:lipids}(a-c) show the PDF determined for the head group volume for each of the four lipids.
+Figures \ref{fig:lipids}(a-c) show the PDF determined for the head group component volume for each of the four lipids.
 The three lipids with a phosphocholine head group appear to show some small unsystematic variation as the tail length is changed, with values of \input{../output/dlpc/vh.txt} \AA$^{3}$ for DLPC, \input{../output/dmpc/vh.txt} \AA$^{3}$ for DMPC, and \input{../output/dppc/vh.txt} \AA$^{3}$ for DPPC.
-This is significantly less than the largest estimate of the head volume from literature sources, 360 \AA$^3$,\cite{Tardieu1973} and slightly less than lowest estimate, 319 \AA$^3$.\cite{Sun1994,Kucerka2004} The fact that the choline chloride component of the DES is charged in nature suggests that it may have a screening effect on the charged interactions between the zwitterionic phosphocholine head groups reducing the volume occupied.
-
-Figure \ref{fig:lipids}(d) contains the PDF for the phosphatidylglycerol head group volume, which was found to be \input{../output/dmpg/vh.txt} \AA$^{3}$.
-This agrees well with the literature value for this lipid head group of 291 \AA$^{3}$,\cite{Pan2012} indictating that the charged component of the DES solvent has little affect on the volume occupied by the phosphatidylglycerol head group.
-
-It is possible to generalise the difference between the two lipid head groups in terms of the difference in their charges, with the phosphocholine group being zwitterionic in nature while the phosphatidylglycerol is anionic (Figure \ref{fig:heads}).
-The fact that the phosphatidylglycerol head group appears to show no deviation in volume at the air-DES interface, when compared with the air-water interface, suggests that the interaction resulting in the apparent decrease in volume of the phosphocholine head group is due to the positively-charged nitrogen group interacting with the negatively-charged chlorine component of the DES.
-The relatively small size of the chloride ion, compared to the choline moiety, means that it is able to intercalate more easily into the lipid head layer allowing for the charge screening to occur.
+This is significantly less than the largest estimate of the head group component volume from literature sources, 360 \AA$^3$,\cite{Tardieu1973} and slightly less than lowest estimate, 319 \AA$^3$.\cite{Sun1994,Kucerka2004} The fact that the choline chloride component of the DES is charged in nature suggests that it may have a screening effect on the charged interactions between the zwitterionic phosphocholine head groups reducing the volume occupied.
+Figure \ref{fig:lipids}(d) contains the PDF for the phosphatidylglycerol head group component volume, which was found to be \input{../output/dmpg/vh.txt} \AA$^{3}$.
+This value was found to be similar to that in water, 291 \AA$^{3}$,\cite{Pan2012} indictating that the charged nature of the DES has less of an effect on the volume occupied by the phosphatidylglycerol head group.
 
@@
 
-Finally, previous work has suggested that the DES may provide a segregated environment to better solubilise phospholipid head groups.\cite{Bryant2016,Bryant2017}.
-Since both the phosphatidylglycerol and phosphocholine head groups contain a moeity of the DES solvent, it is possible for the choline terminal of the phosphocholine would favour the presence of glycerol, while the glycerol terminal of the phosphatidylglycerol would be favourably solubilised by the choline moeity of the DES.
-This solvent segregation of the DES may result in the phosphocholine head group being preferentially solubilised due to the greater molar abundence of glycerol in the 1:2 mixture, and hence giving a smaller volume for this head group than found in water.
+The variation in the head group component volumes observed my be interpreted in terms of solvation by a charged environment.
+Previous work has suggested that DES may provide segregated environments to enhance the solubility of charged moieties.\cite{Bryant2017,Bryant2016,Sanchez-Fernandez2018} Furthermore, it has also been shown that anionic groups have a certain affinity for the choline cations of the solvent.\cite{Sanchez-Fernandez2016} Since both the phosphatidylglycerol and the phosphocholine headgroup contain a moiety of the DES solvent (Figure \ref{fig:heads}), it is possible for the choline terminal of the phosphocholine to favour the presence of glycerol, while the glycerol terminal of the phosphatidylglycerol would be favourably solubilised by the choline moiety of the DES.
+This solvent segration of the DES may result in the phosphocholine head group being specifically solubilised attending to those affinities.
+Due to the highly ionic environment of the solvent, the electrostatic interactions will be suppressed to some extent and thus the apparent component volume of the head group may be reduced.
+However, this effect needs to be probed at atomistic resolution, which is not available to X-ray and neutron reflectometry.
+
+\subsection{Refinement of neutron reflectometry}
+The custom model was refined individually for each of the 4 NR measurements, two contrasts for each of the two lipids studied.
+The resulting reflectometry profiles and associated SLD profiles are given in Figure \ref{fig:neutron}.
+Table \ref{tab:neutron} gives details of all of the varying parameters for each measurement, again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.36\textwidth]{figures/nDMPC_all_data}
+	\includegraphics[width=0.36\textwidth]{figures/nDPPC_all_data}
+	\caption{The NR and SLD profiles for each of the four lipids, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
+The NR and SLD profiles have been offset in the $y$-axis for clarity.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\label{fig:neutron}
+\end{figure}
+
+The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is accurate for the given system.
+This further indicates that the literature values for the head group component volume found in the literature when solvated with water is not sufficient for modelling this system at the air-DES interface.
+
+\begin{table}
+	\small
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the NR models.
+The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
+\ref{equ:tl}, which in turn was obtained using Eqn.
+\ref{equ:ct}}
+	\label{tab:neutron}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
+		\hline
+		Lipid & DMPC & & DPPC & \\
+		Solvent & h-DES & hd-DES & h-DES & hd-DES \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dmpc/angle3_neutron_n1.txt} & \input{../output/dmpc/angle3_neutron_n2.txt} & \input{../output/dppc/angle3_neutron_n1.txt} & \input{../output/dppc/angle3_neutron_n2.txt} \\
+		$d_t$/\AA & \input{../output/dmpc/tail3_neutron_n1.txt} & \input{../output/dmpc/tail3_neutron_n2.txt} & \input{../output/dppc/tail3_neutron_n1.txt} & \input{../output/dppc/tail3_neutron_n2.txt} \\ 
+		$\phi_t$/$\times10^{-2}$ & \input{../output/dmpc/solt3_neutron_n1.txt} & \input{../output/dmpc/solt3_neutron_n2.txt} & \input{../output/dppc/solt3_neutron_n1.txt} & \input{../output/dppc/solt3_neutron_n2.txt} \\
+		$\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh3_neutron_n1.txt} & \input{../output/dmpc/solh3_neutron_n2.txt} & \input{../output/dppc/solh3_neutron_n1.txt} & \input{../output/dppc/solh3_neutron_n2.txt} \\
+		$\sigma_t$/\AA & \input{../output/dmpc/rought3_neutron_n1.txt} & \input{../output/dmpc/rought3_neutron_n2.txt} & \input{../output/dppc/rought3_neutron_n1.txt} & \input{../output/dppc/rought3_neutron_n2.txt} \\
+		\hline
+	\end{tabular*}
+\end{table}
 
 \section{Conclusions}
-Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed to at the air-DES interface, and chemically-relevant modelling was used to analyse X-ray reflectometry measurements quantifying the effect that the non-aqueous solvent on the volume occupied by the head group of each lipid.
+Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed at the air-DES interface, and chemically-relevant modelling was used to analyse XRR measurements, allowing for the quantification of the effect that the non-aqueous solvent on the volume occupied by the head group of each lipid.
 The structure of the tail regions were similar to those previously found at the air-water interface, while there was clear decrease in the volume occupied by the phosphocholine head group.
 This decrease was not also found in the phosphatidylglycerol head group volume.
+A possible cause for this volume reduction may be the screening of the electrostatic charges between the lipid head groups by the DES.
+This screening may come about through the segregation of the DES, resulting in a specific interaction between the DES and the phosphocholine head.
 
-A possible cause for this volume reduction may be the screening of the positive charge on the ammonium moeity of the phosphocholine, as this is a differential feature of the two lipid head groups.
-It appears that specific ion-ion interactions between the positively charged nitrogen and, most likely, the negatively charged chloride ion results in a modification to the head group charge density in DES compared to that in water.
-It is possible that the change observed to the head groups may be observed structurally, however insufficient instrument resolution did not allow for the precise identification of such changes.
-
-The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-relevant model to be used within the analysis of the X-ray reflectometry measurements.
-Futhermore, this work presents the first, to our knowledge, use of chemically-relevant parameterisation to ce-refine X-ray reflectometry measurements at different surface concentrations.
+The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-relevant model to be used within the analysis of the XRR measurements.
+Futhermore, this work presents the first, to our knowledge, use of chemically-relevant parameterisation to co-refine XRR measurements at different surface concentrations.
 

### 2018-06-27 src/visualization/plotref.py

@@ -1,7 +1,7 @@
 
 # coding: utf-8
 
-# In[5]:
+# In[1]:
 
 
 import matplotlib.pyplot as plt
@@ -57,9 +57,9 @@ def plothist(tohist, gs, label, name):
     ax.set_xticks([a[0], a[1], a[2]])
     ax.set_xticklabels(['{:.1f}'.format(a[0]), '{:.1f}'.format(a[1]), '{:.1f}'.format(a[2])])
 
-mpl.rcParams['axes.labelsize']=24
-mpl.rcParams['xtick.labelsize']=16
-mpl.rcParams['ytick.labelsize']=16
+mpl.rcParams['axes.labelsize']=28
+mpl.rcParams['xtick.labelsize']=20
+mpl.rcParams['ytick.labelsize']=20
 
 l = [1, 10, 100, 1000, 10000]
 fig = plt.figure(figsize=(20, 6))

### 2018-06-27 src/visualization/plotrefn.py

@@ -1,0 +1,82 @@
+
+# coding: utf-8
+
+# In[1]:
+
+
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import seaborn as sns; sns.set('paper', palette='colorblind')
+import numpy as np
+from refnx import analysis
+import sys
+from scipy.stats.mstats import mquantiles
+
+
+# In[ ]:
+
+
+n = len(sys.argv)
+print(sys.argv)
+figures_dir = '/home/arm61/work/writing/articles/lipids_at_airdes/reports/figures/'
+
+
+# In[6]:
+
+
+#plotting reflectometry
+def plotref(data, gs, offset):
+    ax = plt.subplot(gs)
+    ax.errorbar(data[0], data[1] * offset, yerr=data[2] * offset, linestyle='', marker='s', markersize=5, 
+                markeredgecolor='k', markerfacecolor='k', ecolor='k')
+    ax.plot(data[0], data[3] * offset, linewidth=4)
+    for i in range(4, data.shape[0]):
+        ax.plot(data[0], data[i] * offset, color='k', linewidth=2, alpha=0.005)
+    ax.set_ylabel(r'$Rq^4$/Å$^{-4}$')
+    ax.set_yscale('log')
+    ax.set_xlabel(r'$q$/Å$^{-1}$')
+    
+def plotsld(data, gs, offset, label):
+    ax = plt.subplot(gs)
+    z = data[0]
+    true_sld = data[1]
+    ax.plot(z, true_sld + offset, linewidth=4)
+    for i in range(2, data.shape[0]):
+        sld = data[i]
+        ax.plot(z, sld + offset, linewidth=2, alpha=0.05)
+    ax.text(0.80, 0.9, '(' + label + ')', fontsize=30, transform=ax.transAxes)
+    ax.set_xlabel(r'$z$/Å')
+    ax.set_ylabel(r'SLD/$10^{-6}$Å$^{-2}$')
+    return plt
+
+def plothist(tohist, gs, label, name):
+    ax = plt.subplot(gs)
+    a = mquantiles(tohist, prob=[0.025, 0.5, 0.975])
+    ax.hist(tohist, density=True, bins=20)
+    ax.set_ylabel('PDF({}-$V_h$)'.format(name))
+    ax.set_xlabel('{}-$V_h$/Å$^3$'.format(name))
[…]

### 2018-07-09 reports/paper.tex
first full version

@@
 
-\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Probabilistic determination of the effect of a deep-eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
+\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Bayesian determination of the effect of a deep-eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
 \vspace{0.3cm} & \vspace{0.3cm} \\
@@
 This further indicates that the literature values for the head group component volume found in the literature when solvated with water is not sufficient for modelling this system at the air-DES interface.
+Additionall, it is also clear that despite the best effort it was not possible to form condensed phase monolayer of the phospholipid without the force available to a Langmuir trough.
+This is evident from the relatively high volume fractions of air in the tail layer and the high chain tilt angles adopted by the tails.
 

### 2018-07-09 notebooks/DMPG/DMPG_all_conc.py

@@ -26,9 +26,9 @@ import sys
 sys.path.insert(0, '/home/arm61/work/writing/articles/lipids_at_airdes/src/models')
 import mol_vol as mv
 
-data_dir = '/home/arm61/work/writing/articles/lipids_at_airdes/data/processed/DMPG/'
-figures_dir = '/home/arm61/work/writing/articles/lipids_at_airdes/reports/figures/'
-analysis_dir = '/home/arm61/work/writing/articles/lipids_at_airdes/output/'
+data_dir = sys.argv[1] + '/data/processed/DMPG/'
+figures_dir = sys.argv[1] + '/reports/figures/'
+analysis_dir = sys.argv[1] + '/output/'
 
 
 # In[2]:
@@ -237,23 +237,6 @@ printref(4, dataset4, model_dmpg4, global_objective, analysis_dir)
 printref(5, dataset5, model_dmpg5, global_objective, analysis_dir)
 printsld(4, structure_dmpg4, global_objective)
 printsld(5, structure_dmpg5, global_objective)
-
-
-# In[14]:
-
-
-# determine the average pearson r coefficient magnitude 
-from scipy.stats import pearsonr
-
-sumr = np.array([])
-
-for i in range(0, flatchain.shape[1]-1):
-    for j in range(i+1, flatchain.shape[1]):
-        sumr = np.append(sumr, np.abs(pearsonr(flatchain[:, i], flatchain[:, j])[0]))
-        
-total_pearsons = open('{}dmpg_all_pearsons.txt'.format(analysis_dir), 'w')
-total_pearsons.write('pearsons {}'.format(np.average(sumr)))
-total_pearsons.close()
 
 
 # In[16]:

### 2018-07-09 src/visualization/plotcorner.py

@@ -19,7 +19,7 @@ f = sys.argv[1] #'../../output/dlpc_highconc_chain.txt'
 tail_length = float(sys.argv[2]) #1.54 + 1.265 * 12
 vole = float(sys.argv[3]) #667.)
 flatchain = analysis.curvefitter.load_chain(f)
-figures_dir = '/home/arm61/work/writing/articles/lipids_at_airdes/reports/figures/'
+figures_dir = sys.argv[5] + '/reports/figures/'
 lab = sys.argv[4] #'dlpc'
 
 

### 2018-07-23 reports/paper.tex
second draft

--- 2018-06-27 reports/paper.tex
@@
 
-\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Probabilistic determination of the effect of a deep-eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
+\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
 \vspace{0.3cm} & \vspace{0.3cm} \\
 
- & \noindent\large{Adrian Sanchez-Fernandez,\textit{$^{ab}$}$^{\dag\P}$ Andrew R.
-McCluskey,\textit{$^{ac}$}$^{\dag}$ Karen J.
+ & \noindent\large{Andrew R.
+McCluskey,\textit{$^{ac}$}$^{\dag}$ Adrian Sanchez-Fernandez,\textit{$^{ab}$}$^{\dag\P}$ Karen J.
 Edler,\textit{$^{a}$}$^{\ast}$ Andrew J.
 Jackson,\textit{$^{bd}$} Richard A.
-Campbell,\textit{$^{e}$} and Thomas Arnold\textit{$^{abcf}$}$^{\ast}$} \\%Author names go here instead of "Full name", etc.
+Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$} \\%Author names go here instead of "Full name", etc.
 
-\includegraphics{head_foot/dates} & \noindent\normalsize{Deep eutectic solvents present a novel class of non-aqueous room temperature solvent, with tunable properties and capable of promoting self-assembly of surfactant molecules.
+\includegraphics{head_foot/dates} & \noindent\normalsize{Deep eutectic solvents present a novel class of non-aqueous room temperature solvent with tunable properties, that are capable of promoting self-assembly of surfactant molecules.
 However, the solvation model in these systems still challenges the classic understanding of amphiphilicity.
-In this work, we present the first example of the self-assembly of a phospholipid monolayer at the interface between air and a non-aqueous solvent.
-Furthermore, we use novel, chemically-relevant modelling of reflectometry measurements to show the ability for the deep eutectic solvent to have an interaction with the phosphocholine lipid head group, leading to an apparent reduction in the component volume compared to that observed in water.
-No such reduction was observed for the phosphatidylglycerol head group, indicating that the interaction is ion specific.} \\
+In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous solvent.
+Furthermore, we use novel, chemically-consistant Bayesian modelling of reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head group, leading to an apparent increase in the component volume compared to that observed in water.
+No such change was observed for the phosphocholine head group, indicating that the interaction is head group specific.} \\
 
@@
 \footnotetext{\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France.}}
-\footnotetext{\textit{$^{f}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK.}}
+\footnotetext{\textit{$^{f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, M13 9PT, UK.}}
+\footnotetext{\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK.}}
 \footnotetext{\textit{$^{\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}}
@@
 \section{Introduction}
-Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, amoung others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between these precursors, allowing the mixture to remain liquid at room temperature due to the high-entropic state of the mixture.\cite{Hammond2016, Hammond2017, Araujo2017} Additionally, through different combinations of the precursors materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}
+Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, among others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between these precursors, allowing the mixture to remain liquid at room temperature due to its high-entropic state.\cite{Hammond2016, Hammond2017, Araujo2017} Additionally, through different combinations of the precursors materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}
 
 These solvents have recently shown the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect.
-The behaviour and conformation of biomolecules in DES has seen and increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to potential applications in the preservation of biomolecules, as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES have been shown to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
+The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to potential applications in the preservation of biomolecules, as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES have been able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
 
@@
 
-Recent developments in computational resource and software has enabled powerful methodologies and algorithms to be harnessed by those from non-computer science backgrounds.
+Recent developments in computational resource and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
 This has mostly occurred through open-source software projects such as the Python language and the Jupyter notebooks framework.\cite{vanRossum1995,Kluyver2016} In the area of neutron and X-ray reflectometry data-analysis, this has led to the development of refnx,\cite{Nelson2018} a Python library for the fitting of layer-based models to reflectometry data.
-refnx enables the use of custom models that contain chemically-relevant information.
-This information includes constaints such as that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups and that the length of the tail chains should not surpass a maximum of the Tanford length for a given chain.\cite{Tanford1980}
+The refnx library enables the use of custom models that contain chemically-relevant information.
+This information includes constaints such as that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups and that the length of the tail chains should not surpass a maximum of the Tanford length for a given chain.\cite{Tanford1980} This length is an emperically calculated value for the maximum expansion of a series of carbon atoms.
 
-The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This method allows for the sampling of a high-dimensionality parameter space, such as that which is relevant to reflectometry fitting, to be performed with relative ease.
-This results in estimatations of the inverse uncertainties associated with each parameter as well as information about the correlations between different parameters within the model.
+The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This method allows for the Bayesian sampling of a high-dimensionality parameter space, such as that which is relevant to reflectometry fitting, to be performed with relative ease.
+This results in estimations of the inverse uncertainties associated with each parameter as well as information about the correlations between different parameters within the model.
 
-In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemical-context modelling of X-ray reflectometry (XRR) measurements.
+In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemically-consistant modelling of X-ray reflectometry (XRR) measurements.
 Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air.
 This allowed the nature of two, chemically distinct, phospholipid headgroups to be understood in this non-aqueous solvent, in addition to the effect of the tail chain length.
+The analysis was then extended to model complementary neutron reflectometry measurements for two contrasts of DMPC and DPPC at a single surface pressure.
 
@@
 \subsection{Materials}
-Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) d$_9$-choline chloride (99 \%, 98 \% D, CK Isotopes) and d8-glycerol (99 \%, 98 \% D, CK Isotopes)  were purchased and used without further purification.
+Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) d$_9$-choline chloride (99 \%, 98 \% D, CK Isotopes) and d$_8$-glycerol (99 \%, 98 \% D, CK Isotopes)  were purchased and used without further purification.
 The DES was prepared by mixing the precursors at the appropriate mole ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.
 Due to the limited availability of the deuterated precursors, a fully protonated subphase (hDES) and a partially deuterated subphase (hdDES) were prepared and used during the neutron reflectometry (NR) experiment.
-The partiall deuterated subpahse was prepared using the following mixtures of precursors: 1 mole of 0.38 fraction of h-choline chloride/0.62 mole fraction of d-choline chloride; and 2 moles of 0.56 mole fraction of h-glycerol/0.44 mole fraction of d-glycerol.
-The solvent was subsequently prepared follow the procedure discussed above.
+The partially deuterated subphase was prepared using the following mixtures of precursors: 1 mole of 0.38 fraction of h-choline chloride/0.62 mole fraction of d-choline chloride; and 2 moles of 0.56 mole fraction of h-glycerol/0.44 mole fraction of d-glycerol.
+The solvent was subsequently prepared following the procedure discussed above.
 
-The water content on the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
+The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
 Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}
 
-DPPC (> 99 \%), DMPC (> 99 \%), and DMPG (> 99 \%) were supplied by Avanti Polar Lipids and DLPC (> 99 \%) was supplied by Sigma-Aldrich and all were used as received.
-Deuterated versions of DPPC (d62-DPPC, > 99 \%, deuterated tails-only) and DMPC (d54-DPPC, > 99 \%, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
+DPPC (> 99 \%, C$_{16}$ tails), DMPC (> 99 \%, C$_{14}$ tails), and DMPG (> 99 \%, C$_{14}$ tails) were supplied by Avanti Polar Lipids and DLPC (> 99 \%, C$_{12}$ tails) was supplied by Sigma-Aldrich and all were used as received.
+Deuterated versions of DPPC (d$_{62}$-DPPC, > 99 \%, deuterated tails-only) and DMPC (d$_{54}$-DPPC, > 99 \%, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
 These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature.
 
-In the XRR, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
+In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
 After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
-Surface concentration was modified by closing and opening the PTFE barriers of the Langmuir trough.
+Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
 In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a managageable level) it was not possible to use a Langmuir trough.
@@
 XRR measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$.
-The data was normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
-The sample environment consisted of a PTFE Langmuir trough.
-Samples were equilibrated for at least one hour and preserved under argon atmosphere to minimise the adsorption of water by the subphase.
-Surface concentration was controlled through opening and closing the barriers of the Langmuir trough.
-XRR data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG at two surface pressures, 20 mNm$^{-1}$ and 30 mNm$^{-1}$, as measured with an aluminium Wilhelmy plate, all measurements were made at 22 $^\circ$C.
+The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
+Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
+XRR data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG at two surface pressures, 20 mNm$^{-1}$ and 30 mNm$^{-1}$, as measured with an aluminium Wilhelmy plate; all measurements were made at 22 $^\circ$C.
 
-The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Two angle regimes were measured to provide a momentum transfer range from 0.0005 to 0.18 \AA$^{-1}$.
-Small-volume Delrin adsorption troughs were used to support the sample.
+The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Data at two incident angles of 0.62$^\circ$ and 3.8$^\circ$ were measured to provide a momentum transfer range from 0.005 to 0.18 \AA$^{-1}$.
 A single surface concentration for each system and contrast was measured.
-Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours) and kept under inert atmosphere.
+Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours) and kept under an inert atmosphere.
 
 \subsection{Data analysis}
-The use of reflectometry to analyse the structure of phospholipids on the surface of water has a histroy extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} This has led to some variation in the models used to fit experimental data, shown in Table \ref{tab:water}.
-Although, there appears to be a general consensus that the component volume of the phosphocholine is in the range from 320 \AA$^3$ to 360 \AA$^3$, and as a result this volume is often used as a physical constraint on the layer model when fitting reflectometry data.
-However, since this work involves a non-aqueous solvent we do not know whether the head group component volumes used in the literature are derived from water-based measurements are appropriate for this work.
-The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with neutral water as compared to the charged DES.\cite{Sanchez-Fernandez2018}
+The use of reflectometry to analyse the structure of phospholipids on the surface of water has a history extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990,Campbell2018} This has led to some variation in the models used to fit experimental data, shown in Table \ref{tab:water}.
+There appears to be a general consensus that the component volume of the phosphocholine (PC) headgroup is in the range from 320 \AA$^3$ to 360 \AA$^3$ while data from a single source gives the phosphatidylglycerol (PG) headgroup to be 291 \AA$^3$, and as a result these volumes is often used as physical constraints on the layer model when fitting reflectometry data.
+However, since the current work involves a non-aqueous solvent we do not know whether the head group component volumes used in the literature that are derived from water-based measurements will be appropriate for this work.
+The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with neutral water as compared to the charged DES.\cite{Sanchez-Fernandez2018} Further it has been shown that in the liquid condensed phase, which is present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured in the liquid expanded phase.\cite{Campbell2018}
 
@@
 
-To allow for the use of a chemically-relevant model, where the lipid head group component volume was allowed to vary, the Python library refnx\cite{Nelson2018} as used.
-This software allows the inclusion of a custom chemically-relevant model from which the parameters to be fed into the Abel\`{e}s layer-model,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
-This custom model, along with Jupyter notebook showing in full the analysis performed, can be found in the ESI.
+To allow for the use of a chemically-consistant model, where the lipid component volumes were allowed to vary, the Python library refnx\cite{Nelson2018} as used.
+This software allows the inclusion of a custom model from which the parameters to be fed into the Abel\`{e}s model for the reflection of light at a given number of stratified interfaces,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
+This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under an MIT license.\cite{mccluskey_2018}
 
-This chemically-relevant model involves considering the lipids as consisting of head groups and tail groups.
+This chemically-consistent model involves two layers consisting of head groups at the interface with the solvent and tail groups at the interface with the air.
 The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron), and a component volume, $V_h$.
@@
 \end{equation}
-The air above the monolayer is also able to solvate the tail region by some volume fraction, $\phi_t$.
 The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows, 
@@
 \end{equation}
-where $\text{SLD}_{s}$ is the scattering length density of the superphase (air) and the subphase (DES) for the tail and head groups respectively, and $i$ indicates either the tail or head layer.
-In order to ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was added to the model,\cite{Braun2017}
+where $\text{SLD}_{s}$ is the scattering length density of the subphase (DES) for the tail and head groups respectively, and $i$ indicates either the tail or head layer, not that it is assumed that no solvent penetrates into the tail layer, e.g.
+$\phi_t = 0$.
+To ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was added to the model,\cite{Braun2017}
 \begin{equation}
@@
 \end{equation}
+A single value for the interfacial roughness was fitted for all interfaces, as there is only a single lipid molecule type in each monolayer.
 
-Initially, this custom model was used to co-refine the component volume of the lipid head group, $V_h$, for the two surface concentration XRR measurements.
-Some parameters were allowed to vary ($\theta_t$, $\phi_t$, $\phi_h$, $\sigma_t$, and $\sigma_h$); while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
+In the first of two steps, this custom model was used to co-refine the component volume of the lipid head group, $V_h$, and the volume of the tail group, $V_t$, across the two surface concentration XRR measurements.
+The following parameters were allowed to vary; $\theta_t$, $d_h$, $\phi_h$, and $\sigma_{t,h,s}$, independently across the two surface pressurse.
+While others, shown in Table \ref{tab:invariant}, were held constant at the values given.
 The length of the carbon chain was kept constant to the value determined by the Tanford equation,\cite{Tanford1980} this is valid due to the condensed nature of the monolayer at this surface concentration resulting in the extended, staggered conformation of the chain being likely.
+In total for each co-refinement of two XRR measurements, there were ten degrees of freedom in the fitting process.
 
@@
 	\caption{\ The invariant parameters within the chemically-sensible model. 
-$^a$Values determined from Armen \emph{et al.}\cite{Armen1998} $^b$Values obtained from the Tanford formula where the carbon chains are assumed to be fully extended.\cite{Tanford1980} $^c$Values extracted from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
+	$^a$Values obtained from the Tanford formula where the carbon chains are assumed to be fully extended.\cite{Tanford1980} $^b$Values extracted from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
 	\label{tab:invariant}
-	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}llllll}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
 		\hline
-		Component & $b_t$/fm & $b_h$/fm & $V_t$/\AA$^3$ & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
+		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
 		\hline
-		X-ray & & & & & \\
-		DLPC & 5073 & 4674 & 667$^a$ & 15.5$^b$ & -- \\
-		DMPC & 5985 & 4674 & 779$^a$ & 18.0$^b$ & -- \\
-		DPPC & 6897 & 4674 & 891$^a$ & 20.5$^b$ & -- \\
-		DMPG & 5985 & 4731 & 779$^a$ & 18.0$^b$ & --\\
-		Air & -- & -- & -- & -- & 0\\
-		DES & -- & -- & -- & -- & 10.8$^c$ \\
+		X-ray & & & & \\
+		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
+		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
+		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
+		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
+		Air & -- & -- & -- & 0\\
+		DES & -- & -- & -- & 10.8$^b$ \\
 		\hline
-		Neutron & & & & & \\
-		d54-DMPC & 5329.8 & 602.7 & 779$^a$ & 18.0$^b$ & -- \\
-		d62-DPPC & 6129.2 & 602.7 & 891$^a$ & 20.5$^b$ & -- \\
-		h-DES & -- & -- & -- & -- & 0.43$^c$  \\
-		hd-DES & -- & -- & -- & -- & 3.15$^c$ \\
+		Neutron & & & & \\
+		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
+		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
+		h-DES & -- & -- & -- & 0.43$^b$  \\
+		hd-DES & -- & -- & -- & 3.15$^b$ \\
 		\hline
@@
 
-The determined head group component volumes were then used in the refinement of the custom model against the NR measurements.
-Due to the lack of contrast present between the hydrogenated phosphocholine head group and the solvent, it was necessary to constrain the thickness and roughness of the head layer based on that determined from the highest surface concentration XRR measurement, this allowed the chain tilt angle to be constrained based on the following relationship,
+In the second step, the determined head group and tail group component volumes were used in the refinement of the custom model against the NR measurements.
+Due to the lack of contrast present between the hydrogenous PC head group and the solvent, it was necessary to constrain the thickness of the head layer based on that determined from the lowest surface concentration XRR measurement.
+Since the NR measurements did not make use of a Langmuir trough sample environment, the $\phi_t$ parameter was allowed to have non-zero values.
+These values can be rationalised as a reduction of the compression of the tail components.
+To ensure that the number denisty of the head groups and pairs of tail groups was constant, the following constraint was applied to the value of $\phi_t$,
 \begin{equation}
-\label{equ:ct}
-\theta_t = \cos^{-1}\bigg(\frac{V_td_h(1-\phi_h)}{V_ht_t(1-\phi_t)}\bigg),
+\label{equ:phit}
+\phi_t =  1 - \bigg(\frac{d_hV_t(1-\phi_h)}{V_hd_t}\bigg).
 \end{equation}
-ensuring that the number density of head groups and pairs of tails is held constant.
-Table \ref{tab:invariant} gives the details of the scattering length and SLDs used as invariant parameters in the custom model, while the tail component volumes and tail chain length were the same as for the XRR.
+Table \ref{tab:invariant} gives the details of the scattering length and SLDs used as invariant parameters in the custom model, while the tail chain lengths were the same as for the XRR.
 
-The refinement of the custom model to the experimental data involved transforming the reflectometry calculated from the model and the data into $Rq^4$ such that the artifact of the Fresnel decay was removed, before using the differential evoulation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
-The parameter space was then probed using the MCMC method available through emcee, this allowed for an estimate of the PDF associated with each parameter.
+In both cases, the refinement of the custom model to the experimental data involved transforming the reflectometry calculated from the model and the data into $Rq^4$ such that the artifact of the Fresnel decay was removed, before using the differential evoulation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
+The parameter space was then probed in a Bayesian fashion using the MCMC method available through emcee, this allowed for an estimate of the PDF associated with each parameter.
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
@@
 \section{Results \& Discussion}
-
-\subsection{Solvent effect on lipid head component volumes}
-
 \begin{figure}
@@
 	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
-	\caption{The XRR profile, SLD profile and probability distribution function of the head component volume for each of the four lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
-The NR and SLD profiles have been offset in the $y$-axis for clarity.
+	\caption{The XRR profiles, SLD profiles and PDFs of the head component volume for each of the four lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+The XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
 Figure files are available under MIT License.\cite{mccluskey_2018}}
@@
 \end{figure}
-The custom model was co-refined for the highest two concentrations of all lipids.
-The resulting reflectometry profiles, associated SLD profiles and the PDF for the head group component volume are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of all varying parameters for each lipid, these are given with asymmetric uncertainties that correspond to a 95 \% confidence interval, the full PDF plots can be found in the ESI.
+The custom model was co-refined across the two surface pressure measurements for each lipid.
+The resulting XRR profiles, associated SLD profiles and the PDF for the head group component volumes are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} gives details of all varying parameters for each system, these are given with asymmetric uncertainies that correspond to a 95 \% confidence interval of the PDF, the full PDF plots can be found in the ESI.
 \begin{table*}
@@
 		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle4.txt} & \input{../output/dlpc/angle5.txt} & \input{../output/dmpc/angle4.txt} & \input{../output/dmpc/angle5.txt} & \input{../output/dppc/angle4.txt} & \input{../output/dppc/angle5.txt} & \input{../output/dmpg/angle4.txt} & \input{../output/dmpg/angle5.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dlpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
-		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dlpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
-		$\phi_t$/$\times10^{-2}$ & \input{../output/dlpc/solt4.txt} & \input{../output/dlpc/solt5.txt} & \input{../output/dmpc/solt4.txt} & \input{../output/dmpc/solt5.txt} & \input{../output/dppc/solt4.txt} & \input{../output/dppc/solt5.txt} & \input{../output/dmpg/solt4.txt} & \input{../output/dmpg/solt5.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dmpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dmpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
+		$V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} & \input{../output/dmpg/vh.txt} \\
 		$\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh4.txt} & \input{../output/dlpc/solh5.txt} & \input{../output/dmpc/solh4.txt} & \input{../output/dmpc/solh5.txt} & \input{../output/dppc/solh4.txt} & \input{../output/dppc/solh5.txt} & \input{../output/dmpg/solh4.txt} & \input{../output/dmpg/solh5.txt} \\
-		$\sigma_t$/\AA & \input{../output/dlpc/rought4.txt} & \input{../output/dlpc/rought5.txt} & \input{../output/dmpc/rought4.txt} & \input{../output/dmpc/rought5.txt} & \input{../output/dppc/rought4.txt} & \input{../output/dppc/rought5.txt} & \input{../output/dmpg/rought4.txt} & \input{../output/dmpg/rought5.txt} \\
-		$\sigma_h$/\AA & \input{../output/dlpc/roughh4.txt} & \input{../output/dlpc/roughh5.txt} & \input{../output/dmpc/roughh4.txt} & \input{../output/dmpc/roughh5.txt} & \input{../output/dppc/roughh4.txt} & \input{../output/dppc/roughh5.txt} & \input{../output/dmpg/roughh4.txt} & \input{../output/dmpg/roughh5.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough4.txt} & \input{../output/dlpc/rough5.txt} & \input{../output/dmpc/rough4.txt} & \input{../output/dmpc/rough5.txt} & \input{../output/dppc/rough4.txt} & \input{../output/dppc/rough5.txt} & \input{../output/dmpg/rough4.txt} & \input{../output/dmpg/rough5.txt} \\
 		\hline
@@
 \end{table*}
+\subsection{Effect of increasing surface pressure on monolayer thickness}
+The thickness of the head and tail layers in the model, with the tail layer being a function of the chain tilt angle are given in Table \ref{tab:liptab}.
+This shows that as expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
+The thickness of the tail layers in these condensed monolayers appears to agree well with values found for water-analogues (DMPC: $d_t=15.8$ \AA,\cite{Johnson1991} DPPC: $d_t=16.7$ \AA\cite{Helm1987}).
 
-It can be seen from Table \ref{tab:liptab} that as would be expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chains increases.
-Additionally, it is also observed that the value of the chain tilt either decreases, resulting in a tail thickness increase, or remains constant as the surface concentration increases.
-This indicates that for DLPC and DPPC these concentrations were in a condensed state, where futher increases in surface concentration had little effect on the monolayer's structure.
-For DMPC and DMPG, however, the area per molecule slightly decreased between the two measurements for DMPC and DPPC.
-The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.\cite{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same.
-This would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.
+It is also observed that for all lipids, when the surface pressure increases there is an observed increase in the tail layer thickness, resulting from the chain tilt angle descreasing.
+Showing the chains to be more closely aligned with the surface normal as the surface pressure increases.
+The phenomena of the tail thickness increasing with increasing surface pressure has been noted before for DMPC at the air-water interface.\cite{Bayerl1990}
 
-The thickness of the tail layers in these condensed monolayers appears to agree well with values found for water-analogues (DMPC: $d_t=15.8$ \AA,\cite{Johnson1991} DPPC: $d_t=16.7$ \AA\cite{Helm1987}).
-Previous work indicates, although there has been no direct comparison, that the phosphatidylglycerol head layer may be thicker than phosphocholine at a water-air interface.\cite{Clifton2012,Johnson1991,Vaknin1991,Lawrie2000} However, the phosphocholine head group appears to be slightly expanded in the DES compared to in water (DPPC: $d_h=8.4$ \AA\cite{Helm1987}) resulting in the values for the thicknesses of the head layers being similar between the two head groups.
+Alongside the increase in the tail thickness there is also a small decrease in the head layer thickness with increasing surface pressure noted for all lipid.
+Previous work indicates, although there has been no direct comparison, that the PG head layer may be thicker than PC at a water-air interface.\cite{Clifton2012,Johnson1991,Vaknin1991,Lawrie2000} However, this is not observed at the air-DES interface with the PG head layer thickness being similar to that for PC.
 
-Figures \ref{fig:lipids}(a-c) show the PDF determined for the head group component volume for each of the four lipids.
-The three lipids with a phosphocholine head group appear to show some small unsystematic variation as the tail length is changed, with values of \input{../output/dlpc/vh.txt} \AA$^{3}$ for DLPC, \input{../output/dmpc/vh.txt} \AA$^{3}$ for DMPC, and \input{../output/dppc/vh.txt} \AA$^{3}$ for DPPC.
-This is significantly less than the largest estimate of the head group component volume from literature sources, 360 \AA$^3$,\cite{Tardieu1973} and slightly less than lowest estimate, 319 \AA$^3$.\cite{Sun1994,Kucerka2004} The fact that the choline chloride component of the DES is charged in nature suggests that it may have a screening effect on the charged interactions between the zwitterionic phosphocholine head groups reducing the volume occupied.
-Figure \ref{fig:lipids}(d) contains the PDF for the phosphatidylglycerol head group component volume, which was found to be \input{../output/dmpg/vh.txt} \AA$^{3}$.
-This value was found to be similar to that in water, 291 \AA$^{3}$,\cite{Pan2012} indictating that the charged nature of the DES has less of an effect on the volume occupied by the phosphatidylglycerol head group.
+\subsection{Effect of compression on the lipid tail component volumes}
+Using the Langmuir trough sample environment, it was possible to conduct XRR measurements at surface pressures of 20 mNm$^{-1}$ and 30 mNm$^{-1}$.
+These are anticipated to be well into the liquid condensed phase for the lipid tail groups, and therefore it would be anticipated, based on the work of Campbell and co-workers,\cite{Campbell2018} that there would be an observed reduction in the component volume of the tail groups compared to those found in the liquid expanded phase.
+
+It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that the component volumes of the tail groups are reduced in the current XRR measurements compared to those determined previously of systems in the liquid expanded phase.
+The reduction was found to be between 5 to 12 \% for DPPC, between 1 and 10 \% for DMPC and 8 \% for DMPG, depending on the source of the tail component volume in the liquid expanded phase.
+From this we feel that it is clear that the monolayers are indeed in the liquid condensed phase for all of the XRR measurements.
+
+\subsection{Solvent effect on lipid head component volumes}
+Figures \ref{fig:lipids}(a-d) show the PDFs determined for the head group component volume for each of the four lipids.
+The three lipids with the PC head group are consistant with values of $\sim340$ \AA$^3$ irregardless of tail component.
+This agrees well with the values found for the same head group in water, shown in Table \ref{tab:water}.
+Interestingly the component volume for the PG head group is similar to that for the PC head group with a value of \input{../output/dmpg/vh.txt} \AA$^3$, whereas it is considered to be significantly smaller in water.
+This indicates that there is some affect arising from the solvation in DES causing an apparent increase in the PG component volume when compared with water.
 
@@
 
-The variation in the head group component volumes observed my be interpreted in terms of solvation by a charged environment.
-Previous work has suggested that DES may provide segregated environments to enhance the solubility of charged moieties.\cite{Bryant2017,Bryant2016,Sanchez-Fernandez2018} Furthermore, it has also been shown that anionic groups have a certain affinity for the choline cations of the solvent.\cite{Sanchez-Fernandez2016} Since both the phosphatidylglycerol and the phosphocholine headgroup contain a moiety of the DES solvent (Figure \ref{fig:heads}), it is possible for the choline terminal of the phosphocholine to favour the presence of glycerol, while the glycerol terminal of the phosphatidylglycerol would be favourably solubilised by the choline moiety of the DES.
-This solvent segration of the DES may result in the phosphocholine head group being specifically solubilised attending to those affinities.
-Due to the highly ionic environment of the solvent, the electrostatic interactions will be suppressed to some extent and thus the apparent component volume of the head group may be reduced.
-However, this effect needs to be probed at atomistic resolution, which is not available to X-ray and neutron reflectometry.
+Figure \ref{fig:heads} gives the chemical structure for the two head groups investigated in this work.
+The major difference between the two components if the fact PG component is negatively charged whereas the PC component is zwitterionic.
+It has been shown previously that the conformation for the PC component is slightly folded in water,\cite{Gilliams2016} due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
+It would be fair to assume that a similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic carbon atoms and the negatively-charged phosphate group.
+However, clearly such an interaction would be weaker than that observed in the PC component.
+We believe that the observed increase found for the PG component volume in DES when compared with water is due to the unfolding of the component.
+This unfolding is made possible by the charged nature of the solvent providing a greater screening effect for charges in the PG component that are present in water.
+This effect is not observed for PC component due to the greater strength of the folding-charges arising from the formally-charged nature of the ammonium group.
+
+\subsection{Response of interfacial roughness to surface pressure change}
+A single value was fit for the roughness at each of the three intrefaces in the system; solvent-head, head-tail, tail-air, the value for each system is given in Table \ref{tab:liptab}.
+It is clear that there is an increase in the roughness observed for each of the lipid when the surface pressure is increased.
+This is in agreement with previous experimental work investigating the effect of surface pressure on surfactant monolayers at the air-water interface.\cite{Campbell2018,Tikhonov2000}
 
@@
 
-The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is accurate for the given system.
-This further indicates that the literature values for the head group component volume found in the literature when solvated with water is not sufficient for modelling this system at the air-DES interface.
+The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is accurate for the given systems.
+Additionally, it is also clear from the magnitude of the $\phi_t$ parameter that despite the best effort it was not possible to form condensed phase monolayer of the phospholipid without the force available to a Langmuir trough.
+This is evident from the relatively high volume fractions of air in the tail layer and the high chain tilt angles adopted by the tails.
 
@@
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl}, which in turn was obtained using Eqn.
-\ref{equ:ct}}
+\ref{equ:tl}}
 	\label{tab:neutron}
@@
 		\hline
-		Lipid & DMPC & & DPPC & \\
+		Lipid & d$_{54}$-DMPC & & d$_{62}$-DPPC & \\
 		Solvent & h-DES & hd-DES & h-DES & hd-DES \\
@@
 		$\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh3_neutron_n1.txt} & \input{../output/dmpc/solh3_neutron_n2.txt} & \input{../output/dppc/solh3_neutron_n1.txt} & \input{../output/dppc/solh3_neutron_n2.txt} \\
-		$\sigma_t$/\AA & \input{../output/dmpc/rought3_neutron_n1.txt} & \input{../output/dmpc/rought3_neutron_n2.txt} & \input{../output/dppc/rought3_neutron_n1.txt} & \input{../output/dppc/rought3_neutron_n2.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rought3_neutron_n1.txt} & \input{../output/dmpc/rought3_neutron_n2.txt} & \input{../output/dppc/rought3_neutron_n1.txt} & \input{../output/dppc/rought3_neutron_n2.txt} \\
 		\hline
@@
 \section{Conclusions}
-Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed at the air-DES interface, and chemically-relevant modelling was used to analyse XRR measurements, allowing for the quantification of the effect that the non-aqueous solvent on the volume occupied by the head group of each lipid.
-The structure of the tail regions were similar to those previously found at the air-water interface, while there was clear decrease in the volume occupied by the phosphocholine head group.
-This decrease was not also found in the phosphatidylglycerol head group volume.
-A possible cause for this volume reduction may be the screening of the electrostatic charges between the lipid head groups by the DES.
-This screening may come about through the segregation of the DES, resulting in a specific interaction between the DES and the phosphocholine head.
+Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed at the air-DES interface, and chemically-relevant modelling and Bayesian analysis was used to rationalise XRR measurements, allowing for the quantification of the effec that the non-aqueous DES had on their structure.
+The structure of the PC component containing lipids was found to be very similar at the air-DES interface to that at the air-water interface.
+However, the PG component containing lipid was found to have a significantly larger head component volume than observed for the same system in water.
+We propose that this is due to the unfolding of the PG head component arising from the electrostatic screening of the component charges due to the presence of the charged DES solvent.
+This unfolding may not occur for the PC component to the strong interaction arising from the formal charge of the ammonium group.
 
-The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-relevant model to be used within the analysis of the XRR measurements.
-Futhermore, this work presents the first, to our knowledge, use of chemically-relevant parameterisation to co-refine XRR measurements at different surface concentrations.
+The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistant model to be used within the analysis of the XRR and NR measurements.
+Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
 
@@
 is grateful to the university of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-We also thank Diamond Light Source and Institute Laue-Langevin for the awarded beamtime (SI10546-1 and 9-13-612 respectively).
+We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin for the awarded beamtime (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}).
 

### 2018-07-23 notebooks/DLPC/DLPC_all_conc.py

@@ -52,7 +52,7 @@ tail_sl = 5073e-6
 thick_heads = [13.1117, 11.0571]
 tail_length = 1.54 + 1.265 * 11
 chain_tilt = [0.792674, 0.79015]
-vols = [280.497, 891.]
+vols = [400.497, 891.]
 head_tail_rough = 3.3
 tail_air_rough = 5.1
 
@@ -81,14 +81,15 @@ structure_dlpc5 = air(0, 0) | dlpc5 | des(0, 0)
 # In[6]:
 
 
-dlpc4.head_mol_vol.setp(vary=True, bounds=(200., 500.))
-dlpc4.tail_mol_vol.setp(667., vary=False)
+dlpc4.head_mol_vol.setp(348., vary=True, bounds=(72., 472.))
+dlpc4.tail_mol_vol.setp(581., vary=True, bounds=(481, 681))
 dlpc4.tail_length.setp(vary=False)
-dlpc4.cos_rad_chain_tilt.setp(vary=True, bounds=(0.40, 0.96))
-dlpc4.rough_head_tail.setp(vary=True, bounds=(1, 12))
-dlpc4.rough_preceding_mono.setp(vary=True, bounds=(1,12))
-dlpc4.phit.setp(0, vary=True, bounds=(0, 0.1))
-dlpc4.phih.setp(0.312487, vary=True, bounds=(0, 0.9))
+dlpc4.cos_rad_chain_tilt.setp(0.69, vary=True, bounds=(0.59, 0.79))
+dlpc4.rough_head_tail.constraint = dlpc4.solventrough
+dlpc4.rough_preceding_mono.constraint = dlpc4.solventrough
+dlpc4.phit.setp(0, vary=False)
+dlpc4.phih.setp(0.149, vary=True, bounds=(0.049, 0.35))
+dlpc4.solventrough.setp(4.4, vary=True, bounds=(3.4, 5.4))
 dlpc4.solventsld.setp(vary=False)
 dlpc4.solventsldi.setp(vary=False)
 dlpc4.supersld.setp(vary=False)
@@ -97,13 +98,12 @@ dlpc4.thick_heads.constraint = (dlpc4.head_mol_vol * dlpc4.tail_length * dlpc4.c
                                 (1 - dlpc4.phit)) / (dlpc4.tail_mol_vol * (1 - dlpc4.phih))
 structure_dlpc4[-1].rough.setp(vary=False)
 
-dlpc5.tail_mol_vol.setp(667., vary=False)
[…]

### 2018-07-23 notebooks/DMPC/DMPC_all_conc.py

@@ -52,7 +52,7 @@ tail_sl = 5985e-6
 thick_heads = [13.1117, 11.0571]
 tail_length = 1.54 + 1.265 * 13
 chain_tilt = [0.792674, 0.79015]
-vols = [300.497, 891.]
+vols = [290.497, 891.]
 head_tail_rough = 3.3
 tail_air_rough = 5.1
 
@@ -81,14 +81,15 @@ structure_dmpc5 = air(0, 0) | dmpc5 | des(0, 0)
 # In[6]:
 
 
-dmpc4.head_mol_vol.setp(vary=True, bounds=(72., 500.))
-dmpc4.tail_mol_vol.setp(779., vary=False)
+dmpc4.head_mol_vol.setp(vary=True, bounds=(72., 472.))
+dmpc4.tail_mol_vol.setp(779., vary=True, bounds=(600, 1000))
 dmpc4.tail_length.setp(vary=False)
 dmpc4.cos_rad_chain_tilt.setp(vary=True, bounds=(0.56, 0.96))
-dmpc4.rough_head_tail.setp(vary=True, bounds=(1, 12))
-dmpc4.rough_preceding_mono.setp(vary=True, bounds=(1,12))
-dmpc4.phit.setp(0, vary=True, bounds=(0, 0.2))
-dmpc4.phih.setp(0.312487, vary=True, bounds=(0, 0.9))
+dmpc4.rough_head_tail.constraint = dmpc4.solventrough
+dmpc4.rough_preceding_mono.constraint = dmpc4.solventrough
+dmpc4.phit.setp(0, vary=False)
+dmpc4.phih.setp(0, vary=True, bounds=(0.1, 0.9))
+dmpc4.solventrough.setp(vary=True, bounds=(2.5, 12))
 dmpc4.solventsld.setp(vary=False)
 dmpc4.solventsldi.setp(vary=False)
 dmpc4.supersld.setp(vary=False)
@@ -97,13 +98,13 @@ dmpc4.thick_heads.constraint = (dmpc4.head_mol_vol * dmpc4.tail_length * dmpc4.c
                                 (1 - dmpc4.phit)) / (dmpc4.tail_mol_vol * (1 - dmpc4.phih))
 structure_dmpc4[-1].rough.setp(vary=False)
 
-dmpc5.tail_mol_vol.setp(779., vary=False)
-dmpc5.tail_length.setp(vary=False)
+dmpc5.tail_mol_vol.setp(779., vary=True, bounds=(600, 1000))
[…]

### 2018-07-23 notebooks/DPPC/DPPC_neutron_conc3_n1.py

@@ -93,18 +93,19 @@ def get_value(file):
 
 
 dppc3_n1.head_mol_vol.setp(get_value('vh'), vary=False, bounds=(72., 472.))
-dppc3_n1.tail_mol_vol.setp(891., vary=False)
+dppc3_n1.tail_mol_vol.setp(get_value('vt'), vary=False)
 dppc3_n1.tail_length.setp(vary=False)
-dppc3_n1.rough_head_tail.setp(get_value('roughh5'), vary=False, bounds=(0.1, 20))
-dppc3_n1.rough_preceding_mono.setp(get_value('rought5'), vary=True, bounds=(0.1,12))
-dppc3_n1.phit.setp(get_value('solt5')/100, vary=True, bounds=(0, 0.6))
-dppc3_n1.phih.setp(get_value('solh5')/100, vary=True, bounds=(0, 0.9999))
+dppc3_n1.rough_head_tail.constraint = dppc3_n1.solventrough
+dppc3_n1.rough_preceding_mono.constraint = dppc3_n1.solventrough
+dppc3_n1.solventrough.setp(get_value('rough4'), vary=True, bounds=(2.5, 8.))
+dppc3_n1.phih.setp(get_value('solh5')/100, vary=True, bounds=(0.5, 0.9))
 dppc3_n1.solventsld.setp(vary=False)
 dppc3_n1.solventsldi.setp(vary=False)
 dppc3_n1.supersld.setp(vary=False)
 dppc3_n1.supersldi.setp(vary=False)
-dppc3_n1.thick_heads.setp(get_value('head5'), vary=False)
-dppc3_n1.cos_rad_chain_tilt.constraint = (dppc3_n1.tail_mol_vol * (1 - dppc3_n1.phih) * dppc3_n1.thick_heads) / (dppc3_n1.head_mol_vol * dppc3_n1.tail_length * (1 - dppc3_n1.phit))
+dppc3_n1.thick_heads.setp(get_value('head4'), vary=False)
+dppc3_n1.phit.constraint = 1 - ((dppc3_n1.thick_heads * dppc3_n1.tail_mol_vol * (1 - dppc3_n1.phih)) / (dppc3_n1.head_mol_vol * dppc3_n1.cos_rad_chain_tilt * dppc3_n1.tail_length))
+dppc3_n1.cos_rad_chain_tilt.setp(np.cos(np.deg2rad(get_value('angle5'))), vary=True, bounds=(0.5, 0.99))
[…]

### 2018-07-23 src/visualization/plotcorner.py

@@ -33,41 +33,46 @@ mpl.rcParams['axes.labelsize']=22
 mpl.rcParams['xtick.labelsize']=14
 mpl.rcParams['ytick.labelsize']=14
 
-label=['$V_h$/Å$^3$', '$d_h$/Å', 'θ$_t$/°', r'ϕ$_t/\times10^{-2}$', r'ϕ$_h/\times10^{-2}$', 'σ$_t$/Å', 'σ$_h$/Å']
+label=['$V_t$/Å$^3$', '$V_h$/Å$^3$', '$d_h$/Å', 'θ$_t$/°', r'ϕ$_h/\times10^{-2}$', 'σ$_{t,h,s}$/Å']
 
-new_flat = np.zeros((flatchain.shape[0] * flatchain.shape[1], 7))
+new_flat = np.zeros((flatchain.shape[0] * flatchain.shape[1], 6))
 
 new_flat[:, 0] = list(flatchain[:, :, 2].flatten())
-new_flat[:, 2] = list(np.rad2deg(np.arccos(flatchain[:, :, 1].flatten())))
-new_flat[:, 3] = list(flatchain[:, :, 5].flatten() * 100)
-new_flat[:, 4] = list(flatchain[:, :, 6].flatten() * 100)
+new_flat[:, 1] = list(flatchain[:, :, 3].flatten())
+new_flat[:, 3] = list(np.rad2deg(np.arccos(flatchain[:, :, 1].flatten())))
+new_flat[:, 4] = list(flatchain[:, :, 5].flatten() * 100)
 new_flat[:, 5] = list(flatchain[:, :, 4].flatten())
-new_flat[:, 6] = list(flatchain[:, :, 3].flatten())
-new_flat[:, 1] = list((flatchain[:, :, 2].flatten() * tail_length * flatchain[:, :, 1].flatten() * (1 - flatchain[:, :, 5].flatten())))
-new_flat[:, 1] = new_flat[:, 1] / (vole)
-a = 1 - flatchain[:, :, 6].flatten()
-new_flat[:, 1] = new_flat[:, 1] / a
+new_flat[:, 2] = list((flatchain[:, :, 3].flatten() * tail_length * flatchain[:, :, 1].flatten()))
+new_flat[:, 2] = new_flat[:, 2] / (flatchain[:, :, 2].flatten())
+a = 1 - flatchain[:, :, 5].flatten()
+new_flat[:, 2] = new_flat[:, 2] / a
 
 
[…]

### 2018-07-23 src/visualization/plotcornern.py

@@ -46,17 +46,16 @@ mpl.rcParams['axes.labelsize']=22
 mpl.rcParams['xtick.labelsize']=14
 mpl.rcParams['ytick.labelsize']=14
 
-label=['θ$_t$/°', r'ϕ$_t/\times10^{-2}$', r'ϕ$_h/\times10^{-2}$', 'σ$_t$/Å']
+label=['θ$_t$/°', r'ϕ$_t/\times10^{-2}$', r'ϕ$_h/\times10^{-2}$', 'σ$_{t,h,s}$/Å']
 
-new_flat = np.zeros((flatchain.shape[0] * flatchain.shape[1], 4))
-a = (vole * (1 - flatchain[:, :, 3]) * get_value('head5')) 
-b = (get_value('vh') * tail_length * (1 - flatchain[:, :, 2]))
-angle3 = a / b
+print(flatchain.shape)
 
-new_flat[:, 0] = np.rad2deg(np.arccos(angle3.flatten()))
-new_flat[:, 1] = flatchain[:, :, 2].flatten()
-new_flat[:, 2] = flatchain[:, :, 3].flatten()
-new_flat[:, 3] = flatchain[:, :, 1].flatten()
+new_flat = np.zeros((flatchain.shape[0]*flatchain.shape[1], 4))
+
+new_flat[:, 0] = np.rad2deg(np.arccos(flatchain[:, :, 1].flatten()))
+new_flat[:, 1] = (1 - ((get_value('head4') * get_value('vt') * (1 - flatchain[:, :, 3].flatten())) / (get_value('vh') * flatchain[:, :, 1].flatten() * tail_length))) * 100
+new_flat[:, 2] = flatchain[:, :, 3].flatten() * 100
+new_flat[:, 3] = flatchain[:, :, 2].flatten()
 
 
 plt1 = corner.corner(new_flat, max_n_ticks=3, labels=label)

### 2018-07-23 src/visualization/plotref.py

@@ -39,7 +39,7 @@ def plotref(data, gs, offset):
     
 def plotsld(data, gs, offset):
     ax = plt.subplot(gs)
-    z = data[0]
+    z = data[0] - 10
     true_sld = data[1]
     ax.plot(z, true_sld + offset, linewidth=4)
     for i in range(2, data.shape[0]):
@@ -60,8 +60,8 @@ def plothist(tohist, gs, label, name):
     ax.set_xticklabels(['{:.1f}'.format(a[0]), '{:.1f}'.format(a[1]), '{:.1f}'.format(a[2])])
 
 mpl.rcParams['axes.labelsize']=28
-mpl.rcParams['xtick.labelsize']=20
-mpl.rcParams['ytick.labelsize']=20
+mpl.rcParams['xtick.labelsize']=18
+mpl.rcParams['ytick.labelsize']=18
 
 l = [1, 10, 100, 1000, 10000]
 fig = plt.figure(figsize=(20, 6))
@@ -77,7 +77,7 @@ for i in range(1, int(n)-3, 2):
     plotsld(data, gs[0, 1], f)
     f += 5
 j = analysis.curvefitter.load_chain(sys.argv[n-3])
-plothist(j[:, :, 2].flatten(), gs[0, 2], str(sys.argv[n-2]), sys.argv[n-1])
+plothist(j[:, :, 3].flatten(), gs[0, 2], str(sys.argv[n-2]), sys.argv[n-1])
 plt.tight_layout()
 plt.savefig('{}{}_all_data.png'.format(figures_dir, sys.argv[n-1]), dpi=600)
 plt.close()

### 2018-07-23 src/visualization/plotrefn.py

@@ -39,7 +39,7 @@ def plotref(data, gs, offset):
     
 def plotsld(data, gs, offset, label):
     ax = plt.subplot(gs)
-    z = data[0]
+    z = data[0] - 10
     true_sld = data[1]
     ax.plot(z, true_sld + offset, linewidth=4)
     for i in range(2, data.shape[0]):
@@ -60,8 +60,8 @@ def plothist(tohist, gs, label, name):
     ax.set_xticklabels(['{:.1f}'.format(a[0]), '{:.1f}'.format(a[1]), '{:.1f}'.format(a[2])])
 
 mpl.rcParams['axes.labelsize']=28
-mpl.rcParams['xtick.labelsize']=20
-mpl.rcParams['ytick.labelsize']=20
+mpl.rcParams['xtick.labelsize']=18
+mpl.rcParams['ytick.labelsize']=18
 
 l = [1, 10, 100, 1000, 10000]
 fig = plt.figure(figsize=(15, 6))

### 2018-07-24 reports/paper.tex
before Tom meeting

@@
  & \noindent\large{Andrew R.
-McCluskey,\textit{$^{ac}$}$^{\dag}$ Adrian Sanchez-Fernandez,\textit{$^{ab}$}$^{\dag\P}$ Karen J.
-Edler,\textit{$^{a}$}$^{\ast}$ Andrew J.
-Jackson,\textit{$^{bd}$} Richard A.
+McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ Karen J.
+Edler,\textit{$^{a}$}$^{\ast}$ Stephen C.
+Parker,\textit{$^{a}$} Andrew J.
+Jackson,\textit{$^{cd}$} Richard A.
 Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$} \\%Author names go here instead of "Full name", etc.
 
-\includegraphics{head_foot/dates} & \noindent\normalsize{Deep eutectic solvents present a novel class of non-aqueous room temperature solvent with tunable properties, that are capable of promoting self-assembly of surfactant molecules.
+\includegraphics{head_foot/dates} & \noindent\normalsize{Deep eutectic solvents present a novel class of non-aqueous room temperature solvent with tunable properties, that are capable of promoting the self-assembly of surfactant molecules.
 However, the solvation model in these systems still challenges the classic understanding of amphiphilicity.
 In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous solvent.
-Furthermore, we use novel, chemically-consistant Bayesian modelling of reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head group, leading to an apparent increase in the component volume compared to that observed in water.
+Furthermore, we use novel, chemically-consistant Bayesian modelling of X-ray and neutron reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head group, leading to an apparent increase in the component volume compared to that observed in water.
 No such change was observed for the phosphocholine head group, indicating that the interaction is head group specific.} \\
@@
 \footnotetext{\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK.}}
-\footnotetext{\textit{$^{b}$~European Spallation Source, SE-211 00 Lund, Sweden.}}
-\footnotetext{\textit{$^{c}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK.}}
+\footnotetext{\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK.}}
+\footnotetext{\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.}}
 \footnotetext{\textit{$^{d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden.}}
@@
 
-\footnotetext{$^{\dag}$~These authors have contributed equally to the work presented within.}
+\footnotetext{$^{\ddag}$~These authors have contributed equally to the work presented within.}
 %\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
@@
 \section{Introduction}
-Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, among others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between these precursors, allowing the mixture to remain liquid at room temperature due to its high-entropic state.\cite{Hammond2016, Hammond2017, Araujo2017} Additionally, through different combinations of the precursors materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}
+Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, among others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between these precursors, allowing the mixture to remain liquid at room temperature.\cite{Hammond2016, Hammond2017, Araujo2017} Additionally, through different combinations of the precursor materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}
 
-These solvents have recently shown the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect.
-The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to potential applications in the preservation of biomolecules, as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES have been able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
+It has recently been shown that these solvents have the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect.
+The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to potential application in the preservation of biomolecules as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES have been able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
 
-The formation of phospholipid monolayers plays a key role in many biological and technological processes.
-Amphiphilic lipids commonly show a low soluibilty in the one of the two phases, leading to the formation of a stable monolayer at the interface.\cite{Mohwald1990} Phospholipids consist of a charged headgroup, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the lipid-ion interactions on structure, monomer packing, and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers in non-aqueous media has not been previously reported, to the best of the authors' knowledge.
+The formation of phospholipid monolayers at the air/liquid interface also plays a key role in many biological and technological processes.
+The solvent-specific solubility of different components of the phospholipid results in the formation of a stable monolayer of phospholipid at the interface.\cite{Mohwald1990} Phospholipids contain a charged headgroup, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the phospholipid-ion interactions on structure, monomer packing, and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and a non-aqueous media has not been previously reported, to the best of the authors' knowledge.
 
-Recent developments in computational resource and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
-This has mostly occurred through open-source software projects such as the Python language and the Jupyter notebooks framework.\cite{vanRossum1995,Kluyver2016} In the area of neutron and X-ray reflectometry data-analysis, this has led to the development of refnx,\cite{Nelson2018} a Python library for the fitting of layer-based models to reflectometry data.
-The refnx library enables the use of custom models that contain chemically-relevant information.
-This information includes constaints such as that the number density of phospholipid headgroups must be the same as the number density of pairs of phospholipid tailgroups and that the length of the tail chains should not surpass a maximum of the Tanford length for a given chain.\cite{Tanford1980} This length is an emperically calculated value for the maximum expansion of a series of carbon atoms.
+Recent developments in computational resources and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
+This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework.\cite{Kluyver2016} In the area of neutron and X-ray reflectometry data-analysis, the landscape of open-source software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, motofit,\cite{Nelson2006} Aurore,\cite{Gerelli2016} and GenX.\cite{Bjorck2007} The Python library refnx is particularly powerful due to the ability to implement complete custom models which can contain chemically-relevant information.
 
-The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This method allows for the Bayesian sampling of a high-dimensionality parameter space, such as that which is relevant to reflectometry fitting, to be performed with relative ease.
-This results in estimations of the inverse uncertainties associated with each parameter as well as information about the correlations between different parameters within the model.
+The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This is a method for sampling a high-dimensionality parameter space, such as that which is relevant in reflectometry fitting, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously.
+The use of Bayesian inference allows the PDF for each fitting variable to be probed, therefore estimations of the inverse uncertainties associated with each parameter can be found as well as information about the correlations between different variables.
 
@@
 Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) d$_9$-choline chloride (99 \%, 98 \% D, CK Isotopes) and d$_8$-glycerol (99 \%, 98 \% D, CK Isotopes)  were purchased and used without further purification.
-The DES was prepared by mixing the precursors at the appropriate mole ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.
+The DES was prepared by mixing the precursors at the appropriate ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.
 Due to the limited availability of the deuterated precursors, a fully protonated subphase (hDES) and a partially deuterated subphase (hdDES) were prepared and used during the neutron reflectometry (NR) experiment.
@@
 These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature.
+PC indicates the molcule contains a phosphocholine head group, where PG contains a phosphoditylglycerol head group, these are shown in Figure \ref{fig:heads}.
 
-In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
-After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
-Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
-In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a managageable level) it was not possible to use a Langmuir trough.
-Instead, small Delrin adsorption troughs were used that did not have controlable barriers.
-This resulted in no control over the surface pressure of the measurement and therefore it was not possible to co-refine different NR contrasts.
-
-\subsection{Methods}
-XRR measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$.
-The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
-Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
-XRR data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG at two surface pressures, 20 mNm$^{-1}$ and 30 mNm$^{-1}$, as measured with an aluminium Wilhelmy plate; all measurements were made at 22 $^\circ$C.
-
-The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Data at two incident angles of 0.62$^\circ$ and 3.8$^\circ$ were measured to provide a momentum transfer range from 0.005 to 0.18 \AA$^{-1}$.
-A single surface concentration for each system and contrast was measured.
-Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours) and kept under an inert atmosphere.
-
-\subsection{Data analysis}
-The use of reflectometry to analyse the structure of phospholipids on the surface of water has a history extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990,Campbell2018} This has led to some variation in the models used to fit experimental data, shown in Table \ref{tab:water}.
-There appears to be a general consensus that the component volume of the phosphocholine (PC) headgroup is in the range from 320 \AA$^3$ to 360 \AA$^3$ while data from a single source gives the phosphatidylglycerol (PG) headgroup to be 291 \AA$^3$, and as a result these volumes is often used as physical constraints on the layer model when fitting reflectometry data.
-However, since the current work involves a non-aqueous solvent we do not know whether the head group component volumes used in the literature that are derived from water-based measurements will be appropriate for this work.
-The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with neutral water as compared to the charged DES.\cite{Sanchez-Fernandez2018} Further it has been shown that in the liquid condensed phase, which is present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured in the liquid expanded phase.\cite{Campbell2018}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.30\textwidth]{figures/head_groups}
+	\caption{The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol, (b) phosphocholine.
+Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\label{fig:heads}
+\end{figure}
 
@@
 	\caption{\ Lipid component volumes extracted from different literature sources.
-$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTS to differential vibrating tube densimetry}
+$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry}
 	\label{tab:water}
@@
 		$V_t$/\AA$^3$ & 890.96 & 895 & 829 & 864 & 782 & 717 & & 767 \\
-		Method & MD & MD & WAXS & NB & NB & NB & DVTS & DVTS \\
+		Method & MD & MD & WAXS & NB & NB & NB & DVTD & DVTD \\
 		T/$^\circ$C & 25 & 50 & 24 & 25 & 30 & 30 & & 30 \\
@@
 \end{table*}
+In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
+After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
+Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
+In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a managageable level) it was not possible to use a Langmuir trough.
+Instead, small Delrin adsorption troughs were used that did not have controlable barriers.
+This resulted in no control over the surface pressure of the measurement and therefore it was not possible to co-refine NR contrasts.
+
+\subsection{Methods}
+XRR measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$.
+The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
+Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
+XRR data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG at two surface pressures, 20 mNm$^{-1}$ and 30 mNm$^{-1}$, as measured with an aluminium Wilhelmy plate; all measurements were made at 22 $^\circ$C.
+The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
+
+The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Data at two incident angles of 0.62$^\circ$ and 3.8$^\circ$ were measured to provide a momentum transfer range from 0.005 to 0.18 \AA$^{-1}$.
+A single surface concentration for each system and contrast was measured.
+Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours) and kept under an inert atmosphere.
+
+\subsection{Data analysis}
+The use of XRR and NR to analyse the structure of phospholipids on the surface of water has a history extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} The models used in the rationalisation of XRR and NR data have varied significantly in number of layers present, use of interfacial roughness, and parameterisation of physical constraints.
+Frequently these physical constraints include the component volumes of the phospholipid head and tail groups, with values taken from other techniques, such as those shown in Table \ref{tab:water}.
+Additionally, a recent evaluation of the applicability of different models to surfactant and phospholipid monolayers from the NR perspective has been published,\cite{Campbell2018} suggests possible oversights in the modelling of NR data.
+
+In Table \ref{tab:water}, there appears to be a general consensus that the component volume of the phosphocholine (PC) headgroup is in the range from 320 \AA$^3$ to 360 \AA$^3$ while data from a single source give the phosphatidylglycerol (PG) headgroup as 291 \AA$^3$.
+However, we do not know whether the head group component volumes used in the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
+The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES.\cite{Sanchez-Fernandez2018} Further it has been shown that in the liquid condensed phase, which is often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured in the liquid expanded phase,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}
 
 To allow for the use of a chemically-consistant model, where the lipid component volumes were allowed to vary, the Python library refnx\cite{Nelson2018} as used.
-This software allows the inclusion of a custom model from which the parameters to be fed into the Abel\`{e}s model for the reflection of light at a given number of stratified interfaces,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
+This software allows the inclusion of a custom model from which the parameters fed into the Abel\`{e}s model for the reflection of light at a given number of stratified interfaces,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
 This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under an MIT license.\cite{mccluskey_2018}
 
-This chemically-consistent model involves two layers consisting of head groups at the interface with the solvent and tail groups at the interface with the air.
-The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron), and a component volume, $V_h$.
+This chemically-consistent model involves two layers consisting of head groups at the interface with the solvent and tail groups at the interface with the air, and is based on the assumption that at the surface pressures measured the monolayer tail will be in the condensed phase.
+The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron for XRR or the summation of the neutron scattering length for NR), and a component volume, $V_h$.
 These head groups make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
@@
 \end{equation}
-where $\text{SLD}_{s}$ is the scattering length density of the subphase (DES) for the tail and head groups respectively, and $i$ indicates either the tail or head layer, not that it is assumed that no solvent penetrates into the tail layer, e.g.
+where $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer, and it is assumed that the tail layer contains no solvent or air, e.g.
 $\phi_t = 0$.
-To ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was added to the model,\cite{Braun2017}
+To ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was included in the model,\cite{Braun2017}
 \begin{equation}
 \label{equ:ht}
-d_h = \frac{V_hd_t(1-\phi_t)}{V_t(1-\phi_h)}. 
+d_h = \frac{V_hd_t}{V_t(1-\phi_h)}. 
 \end{equation}
 A single value for the interfacial roughness was fitted for all interfaces, as there is only a single lipid molecule type in each monolayer.
+Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
 
-In the first of two steps, this custom model was used to co-refine the component volume of the lipid head group, $V_h$, and the volume of the tail group, $V_t$, across the two surface concentration XRR measurements.
-The following parameters were allowed to vary; $\theta_t$, $d_h$, $\phi_h$, and $\sigma_{t,h,s}$, independently across the two surface pressurse.
-While others, shown in Table \ref{tab:invariant}, were held constant at the values given.
+In the first of two steps, this custom model was used to co-refine the component volume of the lipid head group, $V_h$, and the volume of the tail group, $V_t$, across the XRR measurments at two surface concentrations.
+The following parameters were allowed to vary; $\theta_t$, $d_h$, $\phi_h$, and $\sigma_{t,h,s}$, independently across the two surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
 The length of the carbon chain was kept constant to the value determined by the Tanford equation,\cite{Tanford1980} this is valid due to the condensed nature of the monolayer at this surface concentration resulting in the extended, staggered conformation of the chain being likely.
-In total for each co-refinement of two XRR measurements, there were ten degrees of freedom in the fitting process.
+For each co-refinement of two XRR measurements, there were, in total, eight degrees of freedom in the fitting process.
 
@@
 	\caption{\ The invariant parameters within the chemically-sensible model. 
-	$^a$Values obtained from the Tanford formula where the carbon chains are assumed to be fully extended.\cite{Tanford1980} $^b$Values extracted from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
+	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values extracted from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
 	\label{tab:invariant}
@@
 
-In the second step, the determined head group and tail group component volumes were used in the refinement of the custom model against the NR measurements.
-Due to the lack of contrast present between the hydrogenous PC head group and the solvent, it was necessary to constrain the thickness of the head layer based on that determined from the lowest surface concentration XRR measurement.
-Since the NR measurements did not make use of a Langmuir trough sample environment, the $\phi_t$ parameter was allowed to have non-zero values.
-These values can be rationalised as a reduction of the compression of the tail components.
-To ensure that the number denisty of the head groups and pairs of tail groups was constant, the following constraint was applied to the value of $\phi_t$,
+In the second step, the head group and tail group component volumes determined from XRR were used in the refinement of the custom model against the NR measurements.
+Due to the lack of contrast present between the hydrogenous PC head group and the solvent, it was necessary to also constrain the thickness of the head layer based on that determined from the lowest surface concentration XRR measurement.
+Therefore, a different constraint was required to ensure parity between the numbers of head group and pairs of tail groups,
 \begin{equation}
-\label{equ:phit}
-\phi_t =  1 - \bigg(\frac{d_hV_t(1-\phi_h)}{V_hd_t}\bigg).
+\label{equ:phih}
+\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
 \end{equation}
 Table \ref{tab:invariant} gives the details of the scattering length and SLDs used as invariant parameters in the custom model, while the tail chain lengths were the same as for the XRR.
+The definition of the head and tail component volumes and the head thickness allowed the number of variable parameters to be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$.
 
-In both cases, the refinement of the custom model to the experimental data involved transforming the reflectometry calculated from the model and the data into $Rq^4$ such that the artifact of the Fresnel decay was removed, before using the differential evoulation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
-The parameter space was then probed in a Bayesian fashion using the MCMC method available through emcee, this allowed for an estimate of the PDF associated with each parameter.
+In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
+The parameter space was then probed using the MCMC method available through emcee, which allowed for an estimate of the PDF associated with each parameter.
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
@@
 	\caption{The XRR profiles, SLD profiles and PDFs of the head component volume for each of the four lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
-The XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
+The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
 Figure files are available under MIT License.\cite{mccluskey_2018}}
@@
 \end{figure}
-The custom model was co-refined across the two surface pressure measurements for each lipid.
+The chemically-consistent model was co-refined across the two surface pressure XRR measurements for each lipid.
 The resulting XRR profiles, associated SLD profiles and the PDF for the head group component volumes are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of all varying parameters for each system, these are given with asymmetric uncertainies that correspond to a 95 \% confidence interval of the PDF, the full PDF plots can be found in the ESI.
+Table \ref{tab:liptab} gives details of all varying parameters for each system as well as the details of the $d_t$ and $d_h$ which are determined from Eqns.
+\ref{equ:tl} and \ref{equ:ht} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
 \begin{table*}
@@
 		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle4.txt} & \input{../output/dlpc/angle5.txt} & \input{../output/dmpc/angle4.txt} & \input{../output/dmpc/angle5.txt} & \input{../output/dppc/angle4.txt} & \input{../output/dppc/angle5.txt} & \input{../output/dmpg/angle4.txt} & \input{../output/dmpg/angle5.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dmpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
-		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dmpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
 		$V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} & \input{../output/dmpg/vt.txt} \\
@@
 		\hline
+		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dmpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dmpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
+		\hline
 	\end{tabular*}
@@
 \subsection{Effect of increasing surface pressure on monolayer thickness}
-The thickness of the head and tail layers in the model, with the tail layer being a function of the chain tilt angle are given in Table \ref{tab:liptab}.
+The thickness of the head and tail layers in the model, with the tail layer being a function of the chain tilt angle, are given in Table \ref{tab:liptab}.
 This shows that as expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
-The thickness of the tail layers in these condensed monolayers appears to agree well with values found for water-analogues (DMPC: $d_t=15.8$ \AA,\cite{Johnson1991} DPPC: $d_t=16.7$ \AA\cite{Helm1987}).
+Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail5.txt}\AA$\;$at 30 mN/m in DES compared with $d_t=15.8$ \AA$\;$at 30 mN/m\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail5.txt}\AA$\;$at 30 mN/m in DES compared with $d_t=16.7$ \AA$\;$at 40 mN/m\cite{Helm1987} in water for DPPC.
 
-It is also observed that for all lipids, when the surface pressure increases there is an observed increase in the tail layer thickness, resulting from the chain tilt angle descreasing.
-Showing the chains to be more closely aligned with the surface normal as the surface pressure increases.
-The phenomena of the tail thickness increasing with increasing surface pressure has been noted before for DMPC at the air-water interface.\cite{Bayerl1990}
+It is also observed that for all lipids, when the surface pressure increases, there is an observed increase in the tail layer thickness, resulting from the chain tilt angle descreasing.
+The phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
 
-Alongside the increase in the tail thickness there is also a small decrease in the head layer thickness with increasing surface pressure noted for all lipid.
-Previous work indicates, although there has been no direct comparison, that the PG head layer may be thicker than PC at a water-air interface.\cite{Clifton2012,Johnson1991,Vaknin1991,Lawrie2000} However, this is not observed at the air-DES interface with the PG head layer thickness being similar to that for PC.
+Alongside the increase in the tail thickness there is also a small decrease in the head layer thickness with increasing surface pressure noted for all lipids, which has been observed previously for DPPC in water\cite{Brumm1994}.
+However more recent work has suggested that this is an artifact of the modelling process\cite{Campbell2018} having found an increase in the head thickness with increasing surface pressure.
+Therefore, it is not clear if this decrease is a result of the non-aqueous DES solvent.
 
 \subsection{Effect of compression on the lipid tail component volumes}
-Using the Langmuir trough sample environment, it was possible to conduct XRR measurements at surface pressures of 20 mNm$^{-1}$ and 30 mNm$^{-1}$.
-These are anticipated to be well into the liquid condensed phase for the lipid tail groups, and therefore it would be anticipated, based on the work of Campbell and co-workers,\cite{Campbell2018} that there would be an observed reduction in the component volume of the tail groups compared to those found in the liquid expanded phase.
-
-It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that the component volumes of the tail groups are reduced in the current XRR measurements compared to those determined previously of systems in the liquid expanded phase.
+The surface pressures measured were 20 mNm$^{-1}$ and 30 mNm$^{-1}$, which we have considered to produce the liquid condensed phase for the lipid tail groups, and therefore it would be anticipated, based on the work of Campbell and co-workers,\cite{Campbell2018} that there would be an observed reduction in the component volume of the tail groups compared to those found in the liquid expanded phase.
+It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that the component volumes of the tail groups are indeed also reduced in the current XRR measurements compared to those determined previously of systems in the liquid expanded phase.
 The reduction was found to be between 5 to 12 \% for DPPC, between 1 and 10 \% for DMPC and 8 \% for DMPG, depending on the source of the tail component volume in the liquid expanded phase.
-From this we feel that it is clear that the monolayers are indeed in the liquid condensed phase for all of the XRR measurements.
+This is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} From this we can conclude that it is clear that the monolayers are indeed in the liquid condensed phase for all of the XRR measurements.
 
 \subsection{Solvent effect on lipid head component volumes}
-Figures \ref{fig:lipids}(a-d) show the PDFs determined for the head group component volume for each of the four lipids.
+Figure \ref{fig:lipids} shows the PDFs determined for the head group component volume for each of the four lipids.
 The three lipids with the PC head group are consistant with values of $\sim340$ \AA$^3$ irregardless of tail component.
 This agrees well with the values found for the same head group in water, shown in Table \ref{tab:water}.
-Interestingly the component volume for the PG head group is similar to that for the PC head group with a value of \input{../output/dmpg/vh.txt} \AA$^3$, whereas it is considered to be significantly smaller in water.
+Interestingly the component volume for the PG head group is similar to that for the PC head group with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be significantly smaller in water.
 This indicates that there is some affect arising from the solvation in DES causing an apparent increase in the PG component volume when compared with water.
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.30\textwidth]{figures/head_groups}
-	\caption{The two lipid head groups compared in this study, where R indicates the carbon tail; (a) phosphatidylglycerol, (b) phosphocholine.
-Figure files are available under MIT License.\cite{mccluskey_2018}}
-	\label{fig:heads}
-\end{figure}
+The major difference between the two head group components is the fact PG component is negatively charged whereas the PC component is zwitterionic.
+It has been shown previously that the conformation for the PC component is folded in water,\cite{Gilliams2016} due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
+It would be fair to assume that a similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
+However, clearly such an interaction would be weaker than that observed in the PC component.
+Therefore, we attribute the observed increase found for the PG component volume in DES when compared with water to the unfolding of the component.
+This unfolding is made possible by the charged nature of the solvent providing a greater screening effect for charges in the PG component that are present in water.
+This effect is not observed for PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group.
 
-Figure \ref{fig:heads} gives the chemical structure for the two head groups investigated in this work.
-The major difference between the two components if the fact PG component is negatively charged whereas the PC component is zwitterionic.
-It has been shown previously that the conformation for the PC component is slightly folded in water,\cite{Gilliams2016} due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
-It would be fair to assume that a similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic carbon atoms and the negatively-charged phosphate group.
-However, clearly such an interaction would be weaker than that observed in the PC component.
-We believe that the observed increase found for the PG component volume in DES when compared with water is due to the unfolding of the component.
-This unfolding is made possible by the charged nature of the solvent providing a greater screening effect for charges in the PG component that are present in water.
-This effect is not observed for PC component due to the greater strength of the folding-charges arising from the formally-charged nature of the ammonium group.
-
-\subsection{Response of interfacial roughness to surface pressure change}
-A single value was fit for the roughness at each of the three intrefaces in the system; solvent-head, head-tail, tail-air, the value for each system is given in Table \ref{tab:liptab}.
+%\subsection{Response of interfacial roughness to surface pressure change}
+%A single value was fit for the roughness at each of the three intrefaces in the system; solvent-head, head-tail, tail-air, the value for each system is given in Table \ref{tab:liptab}.
 It is clear that there is an increase in the roughness observed for each of the lipid when the surface pressure is increased.
@@
 \subsection{Refinement of neutron reflectometry}
-The custom model was refined individually for each of the 4 NR measurements, two contrasts for each of the two lipids studied.
-The resulting reflectometry profiles and associated SLD profiles are given in Figure \ref{fig:neutron}.
-Table \ref{tab:neutron} gives details of all of the varying parameters for each measurement, again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
+The custom model was refined individually for each of the 4 NR measurements, two solvent contrasts for each of the two partially deuterated lipids studied.
+The resulting NR profiles and associated SLD profiles are given in Figure \ref{fig:neutron}.
+Table \ref{tab:neutron} gives details of all of the varying parameters for each measurement as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
+\ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
+We remind the reader that while each pair of measurements for the same lipid were intended to create chemically-identical systems, difference in the spread amount may have results in different surface axcess so the data were not co-refined.
+The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is consistant between the pair of measurements for the same system.
+It is clear that the again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
 
@@
 	\caption{The NR and SLD profiles for each of the four lipids, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
-The NR and SLD profiles have been offset in the $y$-axis for clarity.
+The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
 Figure files are available under MIT License.\cite{mccluskey_2018}}
@@
 \end{figure}
-
-The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is accurate for the given systems.
-Additionally, it is also clear from the magnitude of the $\phi_t$ parameter that despite the best effort it was not possible to form condensed phase monolayer of the phospholipid without the force available to a Langmuir trough.
-This is evident from the relatively high volume fractions of air in the tail layer and the high chain tilt angles adopted by the tails.
 
@@
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl}}
+\ref{equ:tl}, and the values of $\phi_h$ were found using Eqn.
+\ref{equ:phih}.}
 	\label{tab:neutron}
@@
 		$\theta_t$/$^\circ$ & \input{../output/dmpc/angle3_neutron_n1.txt} & \input{../output/dmpc/angle3_neutron_n2.txt} & \input{../output/dppc/angle3_neutron_n1.txt} & \input{../output/dppc/angle3_neutron_n2.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rought3_neutron_n1.txt} & \input{../output/dmpc/rought3_neutron_n2.txt} & \input{../output/dppc/rought3_neutron_n1.txt} & \input{../output/dppc/rought3_neutron_n2.txt} \\
+		\hline
 		$d_t$/\AA & \input{../output/dmpc/tail3_neutron_n1.txt} & \input{../output/dmpc/tail3_neutron_n2.txt} & \input{../output/dppc/tail3_neutron_n1.txt} & \input{../output/dppc/tail3_neutron_n2.txt} \\ 
-		$\phi_t$/$\times10^{-2}$ & \input{../output/dmpc/solt3_neutron_n1.txt} & \input{../output/dmpc/solt3_neutron_n2.txt} & \input{../output/dppc/solt3_neutron_n1.txt} & \input{../output/dppc/solt3_neutron_n2.txt} \\
 		$\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh3_neutron_n1.txt} & \input{../output/dmpc/solh3_neutron_n2.txt} & \input{../output/dppc/solh3_neutron_n1.txt} & \input{../output/dppc/solh3_neutron_n2.txt} \\
-		$\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rought3_neutron_n1.txt} & \input{../output/dmpc/rought3_neutron_n2.txt} & \input{../output/dppc/rought3_neutron_n1.txt} & \input{../output/dppc/rought3_neutron_n2.txt} \\
 		\hline
@@
 \section{Conclusions}
-Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed at the air-DES interface, and chemically-relevant modelling and Bayesian analysis was used to rationalise XRR measurements, allowing for the quantification of the effec that the non-aqueous DES had on their structure.
+Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed at the air-DES interface, and chemically-relevant modelling and Bayesian analysis was used to rationalise XRR measurements, allowing for the quantification of the effect that the non-aqueous DES had on their structure.
 The structure of the PC component containing lipids was found to be very similar at the air-DES interface to that at the air-water interface.
 However, the PG component containing lipid was found to have a significantly larger head component volume than observed for the same system in water.
-We propose that this is due to the unfolding of the PG head component arising from the electrostatic screening of the component charges due to the presence of the charged DES solvent.
+We propose that this is due to the unfolding of the PG head component arising from the electrostatic screening of the component charges, due to the presence of the charged DES solvent.
 This unfolding may not occur for the PC component to the strong interaction arising from the formal charge of the ammonium group.
 
-The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistant model to be used within the analysis of the XRR and NR measurements.
+The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
 Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
@@
 \section*{Acknowledgements}
-The authors would like to thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
+The authors thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
 A.R.M.
-is grateful to the university of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin for the awarded beamtime (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}).
+is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
+We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime .
 

### 2018-07-24 notebooks/DMPC/DMPC_neutron_conc3_n1.py

@@ -98,14 +98,14 @@ dmpc3_n1.tail_length.setp(vary=False)
 dmpc3_n1.rough_head_tail.constraint = dmpc3_n1.solventrough
 dmpc3_n1.rough_preceding_mono.constraint = dmpc3_n1.solventrough
 dmpc3_n1.solventrough.setp(get_value('rough4'), vary=True, bounds=(2.5, 8.))
-dmpc3_n1.phih.setp(get_value('solh5')/100, vary=True, bounds=(0.3, 0.9))
+dmpc3_n1.phih.constraint = 1 - (dmpc3_n1.head_mol_vol * dmpc3_n1.tail_length * dmpc3_n1.cos_rad_chain_tilt / (dmpc3_n1.tail_mol_vol * dmpc3_n1.thick_heads))
 dmpc3_n1.solventsld.setp(vary=False)
 dmpc3_n1.solventsldi.setp(vary=False)
 dmpc3_n1.supersld.setp(vary=False)
 dmpc3_n1.supersldi.setp(vary=False)
 dmpc3_n1.thick_heads.setp(get_value('head4'), vary=False)
-dmpc3_n1.phit.constraint = 1 - ((dmpc3_n1.thick_heads * dmpc3_n1.tail_mol_vol * (1 - dmpc3_n1.phih)) / (dmpc3_n1.head_mol_vol * dmpc3_n1.cos_rad_chain_tilt * dmpc3_n1.tail_length))
-dmpc3_n1.cos_rad_chain_tilt.setp(np.cos(np.deg2rad(get_value('angle5'))), vary=True, bounds=(0.5, 0.9))
+dmpc3_n1.phit.setp(0, vary=False)
+dmpc3_n1.cos_rad_chain_tilt.setp(np.cos(np.deg2rad(get_value('angle5'))), vary=True, bounds=(0.01, 0.99))
 structure_dmpc3_n1[-1].rough.setp(vary=False)
 dmpc3_n1.solventsld.setp(solvent_sld[0], vary=False)
 
@@ -201,7 +201,7 @@ printsld("3_n1", structure_dmpc3_n1, objective_n1, choose)
 # In[16]:
 
 
-lab = ['scale3', 'angle3', 'rought3', 'solh3']
+lab = ['scale3', 'angle3', 'rought3']
 
 for i in range(0, flatchain.shape[1]):
     total_pearsons = open('{}dmpc/{}_neutron_n1.txt'.format(analysis_dir, lab[i]), 'w')
[…]

### 2018-08-15 reports/esi.tex
third draft

--- 2018-06-23 reports/esi.tex
@@
 \usepackage{hyperref}
-\author{Andrew R. McCluskey}
-\title{ESI for "Probabilistic determination of the effect of a deep eutectic solvent on the structure of lipid monolayers"}
+\author{Andrew R. McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
+Karen J. Edler,\textit{$^{a}$}$^{\ast}$ Stephen C. Parker,\textit{$^{a}$} Andrew J. Jackson,\textit{$^{cd}$} \\
+Richard A. Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$ \\
+ \\
+\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton} \\
+\textit{Down, Bath, BA2 7AY, UK.} \\
+\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE,} \\
+\textit{UK.} \\
+\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.} \\
+\textit{$^{d}$~Department of Physical Chemistry, Lund University,} \\
+\textit{SE-211 00 Lund, Sweden.} \\
+\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000,} \\
+\textit{Grenoble, France.} \\
+\textit{$^{f}$~Division of Pharmacy and Optometry, University of} \\
+\textit{Manchester, Manchester, M13 9PT, UK.} \\
+\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology} \\
+\textit{Facilities Council, Rutherford Appleton Laboratory, Harwell} \\
+\textit{Oxford, Didcot OX11 0QX, UK.} \\
+\textit{$^{\P}$~Present address: Department of Food Technology, Lund} \\
+\textit{University, SE-211 00 Lund, Sweden}}
+\title{ESI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
+\date{}
 \begin{document}
 
+\maketitle
 \section{Probability distribution functions}
 
-The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids are given in Figures \ref{fig:dlpc4}-\ref{fig:dmpg5}
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc2}-\ref{fig:dmpg5}.
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpcn1}-\ref{fig:dppcn2}.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dlpc2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 20 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dlpc2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dlpc3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 25 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dlpc3}
+\end{figure}
 \begin{figure}[h]
@@
 	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 30 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dlpc4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dlpc5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 35 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dlpc5}
 \end{figure}
-\begin{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpc2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 20 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpc2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpc3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 25 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpc3}
+\end{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 30 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dmpc4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dmpc5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 40 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dmpc5}
 \end{figure}
-\begin{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dppc2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 15 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dppc2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dppc3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 20 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dppc3}
+\end{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 25 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dppc4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dppc5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 30 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dppc5}
 \end{figure}
-\begin{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpg2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 15 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpg2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpg3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 20 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpg3}
+\end{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 25 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dmpg4}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dmpg5_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 30 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dmpg5}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpc20_neutron_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpcn1}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dmpc25_neutron_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 25 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpcn2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dppc15_neutron_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DPPC neutron reflectometry data at 15 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dppcn1}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dppc20_neutron_corner}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dppcn2}
 \end{figure}

### 2018-08-15 reports/paper.tex
third draft

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %This is the LaTeX ARTICLE template for RSC journals
@@
 In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous solvent.
-Furthermore, we use novel, chemically-consistant Bayesian modelling of X-ray and neutron reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head group, leading to an apparent increase in the component volume compared to that observed in water.
-No such change was observed for the phosphocholine head group, indicating that the interaction is head group specific.} \\
+Furthermore, we use novel, chemically-consistant Bayesian modelling of X-ray and neutron reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head component, leading to an apparent increase in the component volume compared to that observed in water.
+No such change was observed for the phosphocholine head component, indicating that the interaction is head component specific.} \\
 
@@
 %If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
-\footnotetext{\dag~Electronic Supplementary Information (ESI) available: A series Jupyter notebooks and Python plotting scripts, allowing for a fully reproducible analysis of all data presented herein as well as figures showing the probability distribution functions for each of the lipid models.
-See DOI: 10.1039/b000000x/}
+\footnotetext{\dag~Electronic Supplementary Information (ESI) available: All datasets, figure file and analysis/plotting scripts, allowing for a fully reproducible analysis of all work presented herein.
+See DOI: 10.6084/m9.figshare.6661784}
 %additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
@@
 The formation of phospholipid monolayers at the air/liquid interface also plays a key role in many biological and technological processes.
-The solvent-specific solubility of different components of the phospholipid results in the formation of a stable monolayer of phospholipid at the interface.\cite{Mohwald1990} Phospholipids contain a charged headgroup, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the phospholipid-ion interactions on structure, monomer packing, and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and a non-aqueous media has not been previously reported, to the best of the authors' knowledge.
+The solvent-specific solubility of different components of the phospholipid results in the formation of a stable monolayer of phospholipid at the interface.\cite{Mohwald1990} Phospholipids contain a charged head, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the phospholipid-ion interactions on structure, monomer packing, and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and a non-aqueous media has not been previously reported, to the best of the authors' knowledge.
 
@@
 Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air.
-This allowed the nature of two, chemically distinct, phospholipid headgroups to be understood in this non-aqueous solvent, in addition to the effect of the tail chain length.
+This allowed the nature of two, chemically distinct, phospholipid head components to be understood in this non-aqueous solvent, in addition to the effect of the tail chain length.
 The analysis was then extended to model complementary neutron reflectometry measurements for two contrasts of DMPC and DPPC at a single surface pressure.
@@
 These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature.
-PC indicates the molcule contains a phosphocholine head group, where PG contains a phosphoditylglycerol head group, these are shown in Figure \ref{fig:heads}.
+PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphoditylglycerol head component, these are shown in Figure \ref{fig:heads}.
 
@@
 	\includegraphics[width=0.30\textwidth]{figures/head_groups}
-	\caption{The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol, (b) phosphocholine.
-Figure files are available under MIT License.\cite{mccluskey_2018}}
+	\caption{The two lipid classes with different head components compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol, (b) phosphocholine.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:heads}
@@
 	\caption{\ Lipid component volumes extracted from different literature sources.
-$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry}
+$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry.
+$^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
 	\label{tab:water}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllllll}
+	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llllllllll}
 		\hline
-		Lipid & DPPC & & & & DMPC & & & DMPG \\
+    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
     \hline
-		Reference & [\citen{Armen1998}] & [\citen{Petrache1997}] & [\citen{Sun1994}] & [\citen{Tardieu1973}] & [\citen{Kucerka2004}] & [\citen{Nagle1978}] & [\citen{Schmidt1985}] & [\citen{Pan2012}] \\
-		$V_l$/\AA$^3$ &1216.96 & 1219 & 1148 & 1224 & 1101 & 1061 & 1094 & 1058 \\
-		$V_h$/\AA$^3$ & 326.00 & 324 & 319 & 360 & 319 & 344 & & 291 \\
-		$V_t$/\AA$^3$ & 890.96 & 895 & 829 & 864 & 782 & 717 & & 767 \\
-		Method & MD & MD & WAXS & NB & NB & NB & DVTD & DVTD \\
-		T/$^\circ$C & 25 & 50 & 24 & 25 & 30 & 30 & & 30 \\
+    Reference & [\citen{Armen1998}] & [\citen{Sun1994}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Pan2012}] & [\citen{Kucerka2012}] \\
     \hline
+    $V_l$/\AA$^3$ & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1£$ & $1155.4\pm30.0£$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
+    $V_t$/\AA$^3$ & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0£$ & $815.9\pm15.5£$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
+    $V_h$/\AA$^3$ & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
+    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
+    T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
 	\end{tabular*}
@@
 Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
-XRR data were collected for each of the lipids, DMPC, DPPC, DLPC and DMPG at two surface pressures, 20 mNm$^{-1}$ and 30 mNm$^{-1}$, as measured with an aluminium Wilhelmy plate; all measurements were made at 22 $^\circ$C.
+XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and 35 mNm$^{-1}$, DMPC: 20, 25, 30, and 40 mNm$^{-1}$, DPPC: 15, 20, 25, and 30 mNm$^{-1}$, DMPG: 15, 20, 25, and 30 mNm$^{-1}$), as measured with an aluminium Wilhelmy plate; all measurements were conducted at 22 $^\circ$C.
 The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
@@
 The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Data at two incident angles of 0.62$^\circ$ and 3.8$^\circ$ were measured to provide a momentum transfer range from 0.005 to 0.18 \AA$^{-1}$.
-A single surface concentration for each system and contrast was measured.
-Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours) and kept under an inert atmosphere.
+Two surface pressures for each system and contrast was measured (DMPC: 20 and 25 mNm$^{-1}$, DPPC: 15 and 20 mNm$^{-1}$).
+Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours), kept under an inert atmosphere, and all measurements were conducted at 22 $^\circ$C.
 
@@
 The use of XRR and NR to analyse the structure of phospholipids on the surface of water has a history extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} The models used in the rationalisation of XRR and NR data have varied significantly in number of layers present, use of interfacial roughness, and parameterisation of physical constraints.
-Frequently these physical constraints include the component volumes of the phospholipid head and tail groups, with values taken from other techniques, such as those shown in Table \ref{tab:water}.
+Frequently these physical constraints include the component volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}.
 Additionally, a recent evaluation of the applicability of different models to surfactant and phospholipid monolayers from the NR perspective has been published,\cite{Campbell2018} suggests possible oversights in the modelling of NR data.
 
-In Table \ref{tab:water}, there appears to be a general consensus that the component volume of the phosphocholine (PC) headgroup is in the range from 320 \AA$^3$ to 360 \AA$^3$ while data from a single source give the phosphatidylglycerol (PG) headgroup as 291 \AA$^3$.
-However, we do not know whether the head group component volumes used in the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
-The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES.\cite{Sanchez-Fernandez2018} Further it has been shown that in the liquid condensed phase, which is often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured in the liquid expanded phase,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}
+In Table \ref{tab:water}, there appears to be a general consensus that the component volume of the phosphocholine (PC) head is in the range from 320-360 \AA$^3$ while the phosphatidylglycerol (PG) head is in the range 289-291 \AA$^3$.
+However, we do not know whether the head component volumes used in the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
+The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES.\cite{Sanchez-Fernandez2018} Furthermore, it has been shown that in the liquid expanded and condensed phases, which are often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured from other techniques,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}
 
@@
 This software allows the inclusion of a custom model from which the parameters fed into the Abel\`{e}s model for the reflection of light at a given number of stratified interfaces,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
-This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under an MIT license.\cite{mccluskey_2018}
+This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under CC-BY.\cite{mccluskey_2018}
 
-This chemically-consistent model involves two layers consisting of head groups at the interface with the solvent and tail groups at the interface with the air, and is based on the assumption that at the surface pressures measured the monolayer tail will be in the condensed phase.
-The head groups have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head group multiplied by the classical radius of the electron for XRR or the summation of the neutron scattering length for NR), and a component volume, $V_h$.
-These head groups make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
-The tail groups also have a calculated scattering length, $b_t$, and a component volume, $V_t$, however the thickness of the tail group layer, $d_t$, is found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
+This chemically-consistent model involves two layers; the head layer at the interface with the solvent and tail layer at the interface with the air.
+The head components have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head component multiplied by the classical radius of the electron for XRR or the summation of the neutron scattering lengths for NR), and a component volume, $V_h$.
+These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
+The tail components also have a calculated scattering length, $b_t$, and a component volume, $V_t$.
+In this work, the thickness of the tail layer, $d_t$, was found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
+%
 \begin{equation}
@@
 \end{equation}
+%
+The was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g.
+it cannot be thicker than the maximum extended length of the lipid tail.
 The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
+%
 \begin{equation}
-\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}\phi_i,
+\text{SLD}_i = \frac{b_i}{V_i}(\phi_i) + \text{SLD}_{s}(1-\phi_i),
 \end{equation}
-where $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer, and it is assumed that the tail layer contains no solvent or air, e.g.
+%
+where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains either solvent nor air, e.g.
 $\phi_t = 0$.
-To ensure that the number density of head groups and pairs of tail groups is the same, the following constraint was included in the model,\cite{Braun2017}
+To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
+%
 \begin{equation}
-\label{equ:ht}
-d_h = \frac{V_hd_t}{V_t(1-\phi_h)}. 
+\label{equ:phih}
+\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
 \end{equation}
-A single value for the interfacial roughness was fitted for all interfaces, as there is only a single lipid molecule type in each monolayer.
+%
+Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all interfaces, as there is only a single lipid molecule type in each monolayer.
 Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
 
-In the first of two steps, this custom model was used to co-refine the component volume of the lipid head group, $V_h$, and the volume of the tail group, $V_t$, across the XRR measurments at two surface concentrations.
-The following parameters were allowed to vary; $\theta_t$, $d_h$, $\phi_h$, and $\sigma_{t,h,s}$, independently across the two surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
-The length of the carbon chain was kept constant to the value determined by the Tanford equation,\cite{Tanford1980} this is valid due to the condensed nature of the monolayer at this surface concentration resulting in the extended, staggered conformation of the chain being likely.
-For each co-refinement of two XRR measurements, there were, in total, eight degrees of freedom in the fitting process.
+In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across the XRR measurments at four surface concentrations.
+The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, this based on the understanding that the increasing surface pressure should not significantly influence the head layer thickness.
+The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
+The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} due to the nature of the monolayer at the surface pressures resulting in the extended, staggered conformation of the chain being likely.
+For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
 
+%
 \begin{table}[h]
 	\small
-	\caption{\ The invariant parameters within the chemically-sensible model. 
-	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values extracted from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
+	\caption{\ The invariant parameters within the chemically-consistent model.
+	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
 	\label{tab:invariant}
@@
 \end{table}
-
-In the second step, the head group and tail group component volumes determined from XRR were used in the refinement of the custom model against the NR measurements.
-Due to the lack of contrast present between the hydrogenous PC head group and the solvent, it was necessary to also constrain the thickness of the head layer based on that determined from the lowest surface concentration XRR measurement.
-Therefore, a different constraint was required to ensure parity between the numbers of head group and pairs of tail groups,
-\begin{equation}
-\label{equ:phih}
-\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
-\end{equation}
-Table \ref{tab:invariant} gives the details of the scattering length and SLDs used as invariant parameters in the custom model, while the tail chain lengths were the same as for the XRR.
-The definition of the head and tail component volumes and the head thickness allowed the number of variable parameters to be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$.
+%
+In the second step, the head and tail component volumes, and head layer thickness determined from XRR were used in the refinement of the custom model against the NR measurements.
+Table \ref{tab:invariant} gives the details of the scattering lengths and SLDs used as invariant parameters in the custom model, while the tail chain lengths were the same as for the XRR.
+The definition of the head and tail component volumes, and the head thickness allowed the number of variable parameters to be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.
 
 In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
-The parameter space was then probed using the MCMC method available through emcee, which allowed for an estimate of the PDF associated with each parameter.
+The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the PDF associated with each parameter.
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
+The use of MCMC sampling allowed for the Bayesian inference of the probability density function for each of the variables and their respective interactions (shown in detail in the ESI).
+This allowed asymmetric confidence intervals to be found for each of the variable parameters.
+However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, e.g.
+they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.
 
-\section{Results \& Discussion}
+%
 \begin{figure}
@@
 	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
-	\caption{The XRR profiles, SLD profiles and PDFs of the head component volume for each of the four lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
 The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
-Figure files are available under MIT License.\cite{mccluskey_2018}}
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:lipids}
 \end{figure}
-The chemically-consistent model was co-refined across the two surface pressure XRR measurements for each lipid.
-The resulting XRR profiles, associated SLD profiles and the PDF for the head group component volumes are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of all varying parameters for each system as well as the details of the $d_t$ and $d_h$ which are determined from Eqns.
-\ref{equ:tl} and \ref{equ:ht} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
-\begin{table*}
+%
+\section{Results \& Discussion}
+The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
+The resulting XRR profiles, associated SLD profiles are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} gives details of all varying parameters for each lipid at the highest surface pressure measured, as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
+\ref{equ:tl} and \ref{equ:phih} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
+%
+\begin{table}
 	\small
-	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models.
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl}.
-The values of $d_h$ were obtained from the appropriate use of Eqn.
-\ref{equ:ht}}
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn.
+\ref{equ:phih}}
 	\label{tab:liptab}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllllll}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
 		\hline
-		Lipid & DLPC & & DMPC & & DPPC & & DMPG & \\
-		Surface Pressure/mNm${-1}$ & 20 & 30 & 20 & 30 & 20 & 30 & 20 & 30 \\
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
 		\hline
-		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle4.txt} & \input{../output/dlpc/angle5.txt} & \input{../output/dmpc/angle4.txt} & \input{../output/dmpc/angle5.txt} & \input{../output/dppc/angle4.txt} & \input{../output/dppc/angle5.txt} & \input{../output/dmpg/angle4.txt} & \input{../output/dmpg/angle5.txt} \\
-		$V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} & \input{../output/dmpg/vt.txt} \\
-		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} & \input{../output/dmpg/vh.txt} \\
-		$\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh4.txt} & \input{../output/dlpc/solh5.txt} & \input{../output/dmpc/solh4.txt} & \input{../output/dmpc/solh5.txt} & \input{../output/dppc/solh4.txt} & \input{../output/dppc/solh5.txt} & \input{../output/dmpg/solh4.txt} & \input{../output/dmpg/solh5.txt} \\
-		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough4.txt} & \input{../output/dlpc/rough5.txt} & \input{../output/dmpc/rough4.txt} & \input{../output/dmpc/rough5.txt} & \input{../output/dppc/rough4.txt} & \input{../output/dppc/rough5.txt} & \input{../output/dmpg/rough4.txt} & \input{../output/dmpg/rough5.txt} \\
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
     \hline
-		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dmpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
-		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dmpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
 		\hline
 	\end{tabular*}
-\end{table*}
-\subsection{Effect of increasing surface pressure on monolayer thickness}
-The thickness of the head and tail layers in the model, with the tail layer being a function of the chain tilt angle, are given in Table \ref{tab:liptab}.
-This shows that as expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
-Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail5.txt}\AA$\;$at 30 mN/m in DES compared with $d_t=15.8$ \AA$\;$at 30 mN/m\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail5.txt}\AA$\;$at 30 mN/m in DES compared with $d_t=16.7$ \AA$\;$at 40 mN/m\cite{Helm1987} in water for DPPC.
+\end{table}
+%
 
-It is also observed that for all lipids, when the surface pressure increases, there is an observed increase in the tail layer thickness, resulting from the chain tilt angle descreasing.
-The phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
+\subsection{Effect of compression on monolayer thickness}
+Table \ref{tab:liptab} gives the best-fit values for each lipid at the highest surface pressure measured.
+From this, we can see that, as expected and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
+Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$ \AA\ at 30 mN/m\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=16.7$ \AA\ at 40 mN/m\cite{Helm1987} in water for DPPC.
 
-Alongside the increase in the tail thickness there is also a small decrease in the head layer thickness with increasing surface pressure noted for all lipids, which has been observed previously for DPPC in water\cite{Brumm1994}.
-However more recent work has suggested that this is an artifact of the modelling process\cite{Campbell2018} having found an increase in the head thickness with increasing surface pressure.
-Therefore, it is not clear if this decrease is a result of the non-aqueous DES solvent.
+%
+\begin{figure}
+	\centering
+	\includegraphics[width=0.48\textwidth]{figures/DLPC_other_data}
+	\includegraphics[width=0.48\textwidth]{figures/DMPC_other_data}
+	\includegraphics[width=0.48\textwidth]{figures/DPPC_other_data}
+	\includegraphics[width=0.48\textwidth]{figures/DMPG_other_data}
+	\caption{The PDFs of the head component volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:lipresults}
+\end{figure}
+%
+The variation of the tail layer thickness in the models, found from $\theta_t$ using Eqn \ref{equ:tl}, with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
+It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateuing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC the plateu can be assumed to be at higher pressures than those studied.
+This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
+
+\subsection{Effect of compression on solvent concentration}
+In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increase there is a corresponding decrease in the percentage solvent present in the lipid head layer.
+This can be rationalised by considering when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.
+A similar effect has been observed when increasing the surface pressure from 11 mNm$^{-1}$ to 31 mNm$^{-1)}$ for a DMPC/DMPG monolayer at the air-water interface.\cite{Bayerl1990}
 
 \subsection{Effect of compression on the lipid tail component volumes}
-The surface pressures measured were 20 mNm$^{-1}$ and 30 mNm$^{-1}$, which we have considered to produce the liquid condensed phase for the lipid tail groups, and therefore it would be anticipated, based on the work of Campbell and co-workers,\cite{Campbell2018} that there would be an observed reduction in the component volume of the tail groups compared to those found in the liquid expanded phase.
-It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that the component volumes of the tail groups are indeed also reduced in the current XRR measurements compared to those determined previously of systems in the liquid expanded phase.
-The reduction was found to be between 5 to 12 \% for DPPC, between 1 and 10 \% for DMPC and 8 \% for DMPG, depending on the source of the tail component volume in the liquid expanded phase.
-This is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} From this we can conclude that it is clear that the monolayers are indeed in the liquid condensed phase for all of the XRR measurements.
+It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails is significantly lower in the current measurements than found previously, by other techniques.
+It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
+However, this reduction observed has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elavated surface pressure.
+In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.
+
+In this work, a single tail component volume was fitted to each lipid for all four surface pressures that were measured.
+This is based on the assumption that at all four surface pressures, the lipids adopt the same phase and therefore any variation in the structure with surface pressure would manifest as a change in the tail thickness, via the chain tilt angle.
+It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail component volumes are also reduced in the current XRR measurements compared to those determined previously.
+The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} However, DMPG presented a small increase in the tail volume, although this may be due to comparison with a previous measurement at a lower temperature.
 
 \subsection{Solvent effect on lipid head component volumes}
-Figure \ref{fig:lipids} shows the PDFs determined for the head group component volume for each of the four lipids.
-The three lipids with the PC head group are consistant with values of $\sim340$ \AA$^3$ irregardless of tail component.
-This agrees well with the values found for the same head group in water, shown in Table \ref{tab:water}.
-Interestingly the component volume for the PG head group is similar to that for the PC head group with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be significantly smaller in water.
-This indicates that there is some affect arising from the solvation in DES causing an apparent increase in the PG component volume when compared with water.
+Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids.
+The three lipids with the PC head component are consistant with values of $\sim330$ \AA$^3$, irregardless of tail component.
+This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
+Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be smaller in water when compared with either DMPG using differential vibrating tube densimetry\cite{Pan2012} or POPG using molecular dynamics simulations.\cite{Kucerka2012} This indicates that there may be some affect arising from the solvation in DES causing an apparent increase in the PG component volume when compared with water.
 
-The major difference between the two head group components is the fact PG component is negatively charged whereas the PC component is zwitterionic.
+The major difference between the two head components is the fact PG component is negatively charged whereas the PC component is zwitterionic.
 It has been shown previously that the conformation for the PC component is folded in water,\cite{Gilliams2016} due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
-It would be fair to assume that a similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
-However, clearly such an interaction would be weaker than that observed in the PC component.
-Therefore, we attribute the observed increase found for the PG component volume in DES when compared with water to the unfolding of the component.
-This unfolding is made possible by the charged nature of the solvent providing a greater screening effect for charges in the PG component that are present in water.
-This effect is not observed for PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group.
-
-%\subsection{Response of interfacial roughness to surface pressure change}
-%A single value was fit for the roughness at each of the three intrefaces in the system; solvent-head, head-tail, tail-air, the value for each system is given in Table \ref{tab:liptab}.
-It is clear that there is an increase in the roughness observed for each of the lipid when the surface pressure is increased.
-This is in agreement with previous experimental work investigating the effect of surface pressure on surfactant monolayers at the air-water interface.\cite{Campbell2018,Tikhonov2000}
+A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
+However, such an interaction would be weaker than that observed in the PC component.
+Therefore, this observed increase found for the PG component volume in DES when compared with water may be due to the unfolding of the PG head.
+This unfolding would be made possible by the charged nature of the solvent providing a greater screening effect for the PG head than are present in water.
+This effect may not be observed for the PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group.
+It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
+Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements,\cite{Clifton2012} which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head component may be occuring as a result of interaction with the DES.
 
 \subsection{Refinement of neutron reflectometry}
-The custom model was refined individually for each of the 4 NR measurements, two solvent contrasts for each of the two partially deuterated lipids studied.
-The resulting NR profiles and associated SLD profiles are given in Figure \ref{fig:neutron}.
-Table \ref{tab:neutron} gives details of all of the varying parameters for each measurement as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
+The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure.
+The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}.
+Table \ref{tab:neutron} gives details of the varying parameters at each surface pressure as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
 \ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
-We remind the reader that while each pair of measurements for the same lipid were intended to create chemically-identical systems, difference in the spread amount may have results in different surface axcess so the data were not co-refined.
-The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is consistant between the pair of measurements for the same system.
-It is clear that the again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
 
+The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head component volume is consistant between the pair of measurements for the same system.
+It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
+Futhermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components is also observed in the NR models.
+%
 \begin{figure}
 	\centering
-	\includegraphics[width=0.36\textwidth]{figures/nDMPC_all_data}
-	\includegraphics[width=0.36\textwidth]{figures/nDPPC_all_data}
-	\caption{The NR and SLD profiles for each of the four lipids, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
+	\includegraphics[width=0.48\textwidth]{figures/nDMPC20_all_data}
+	\includegraphics[width=0.48\textwidth]{figures/nDPPC20_all_data}
+	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
 The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
-Figure files are available under MIT License.\cite{mccluskey_2018}}
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:neutron}
 \end{figure}
-
+%
 \begin{table}
 	\small
-	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the NR models.
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 		Lipid & d$_{54}$-DMPC & & d$_{62}$-DPPC & \\
-		Solvent & h-DES & hd-DES & h-DES & hd-DES \\
+    SP/mNm$^{-1}$ & 20 & 25 & 15 & 20 \\
 		\hline
-		$\theta_t$/$^\circ$ & \input{../output/dmpc/angle3_neutron_n1.txt} & \input{../output/dmpc/angle3_neutron_n2.txt} & \input{../output/dppc/angle3_neutron_n1.txt} & \input{../output/dppc/angle3_neutron_n2.txt} \\
-		$\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rought3_neutron_n1.txt} & \input{../output/dmpc/rought3_neutron_n2.txt} & \input{../output/dppc/rought3_neutron_n1.txt} & \input{../output/dppc/rought3_neutron_n2.txt} \\
+		$\theta_t$/$^\circ$ & \input{../output/dmpc/angle20_neutron.txt} & \input{../output/dmpc/angle25_neutron.txt} & \input{../output/dppc/angle15_neutron.txt} & \input{../output/dppc/angle20_neutron.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rough20_neutron.txt} & \input{../output/dmpc/rough25_neutron.txt} & \input{../output/dppc/rough15_neutron.txt} & \input{../output/dppc/rough20_neutron.txt} \\
     \hline
-		$d_t$/\AA & \input{../output/dmpc/tail3_neutron_n1.txt} & \input{../output/dmpc/tail3_neutron_n2.txt} & \input{../output/dppc/tail3_neutron_n1.txt} & \input{../output/dppc/tail3_neutron_n2.txt} \\ 
-		$\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh3_neutron_n1.txt} & \input{../output/dmpc/solh3_neutron_n2.txt} & \input{../output/dppc/solh3_neutron_n1.txt} & \input{../output/dppc/solh3_neutron_n2.txt} \\
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} & \input{../output/dmpc/solh25_neutron.txt} & \input{../output/dppc/solh15_neutron.txt} & \input{../output/dppc/solh20_neutron.txt} \\
+		$d_t$/\AA & \input{../output/dmpc/tail20_neutron.txt} & \input{../output/dmpc/tail25_neutron.txt} & \input{../output/dppc/tail15_neutron.txt} & \input{../output/dppc/tail20_neutron.txt} \\
 		\hline
@@
 \end{table}
+%
 
@@
 The structure of the PC component containing lipids was found to be very similar at the air-DES interface to that at the air-water interface.
-However, the PG component containing lipid was found to have a significantly larger head component volume than observed for the same system in water.
+However, the PG component containing lipid was found to have a larger head component volume than observed for the same system in water.
 We propose that this is due to the unfolding of the PG head component arising from the electrostatic screening of the component charges, due to the presence of the charged DES solvent.
@@
 
-The ability to determine the head group volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
+The ability to determine the head component volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
 Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.

### 2018-08-15 notebooks/DMPC/DMPC_all_conc.py

@@ -1,304 +1,0 @@
-
-# coding: utf-8
-
-# In[1]:
-
-
-# Standard libraries to import
-from __future__ import division
-import numpy as np 
-import matplotlib.pyplot as plt
-#from matplotlib import rcParams, rc
-import seaborn as sns; sns.set('paper', palette='colorblind')
-import matplotlib as mpl
-from matplotlib import gridspec
-from scipy.stats import pearsonr
-from scipy.stats.mstats import mquantiles
-
-# The refnx library, and associated classes
-import refnx
-from refnx.reflect import structure, ReflectModel, SLD
-from refnx.dataset import ReflectDataset
-from refnx.analysis import Transform, CurveFitter, Objective, GlobalObjective, Parameter
-
-# The custom class to constain the monolayer model. 
-import sys
-sys.path.insert(0, '/home/arm61/work/writing/articles/lipids_at_airdes/src/models')
-import mol_vol as mv
-
-data_dir = sys.argv[1] + '/data/processed/DMPC/'
-figures_dir = sys.argv[1] + '/reports/figures/'
-analysis_dir = sys.argv[1] + '/output/'
-
-
-# In[2]:
-
-
-# Reading datasets into refnx format
-dataset4 = ReflectDataset('{}DMPC_Xray_conc4.dat'.format(data_dir))
-dataset5 = ReflectDataset('{}DMPC_Xray_conc5.dat'.format(data_dir))
-
-
-# In[3]:
-
-
-# Scattering length of the lipid head group 
-# (found from summing the electrons in the head group 
-# and multiplying by the classical radius of an electron)
-head_sl = 4674e-6
-# Scattering length of the lipid tail group 
-tail_sl = 5985e-6
-# Some initial values for the head and tail thicknesses & APM
-thick_heads = [13.1117, 11.0571]
-tail_length = 1.54 + 1.265 * 13
-chain_tilt = [0.792674, 0.79015]
-vols = [290.497, 891.]
-head_tail_rough = 3.3
-tail_air_rough = 5.1
-
-
-# In[4]:
-
-
-# set up the chemical context system
-dmpc4 = mv.VolMono(head_sl, thick_heads[0], tail_sl, tail_length, chain_tilt[0], vols, 
[…]

### 2018-08-15 notebooks/DMPC/DMPC_neutron_conc3_n1.py

@@ -1,255 +1,0 @@
-
-# coding: utf-8
-
-# In[1]:
-
-
-# Standard libraries to import
-from __future__ import division
-import numpy as np 
-import matplotlib.pyplot as plt
-#from matplotlib import rcParams, rc
-import seaborn as sns; sns.set('paper', palette='colorblind')
-import matplotlib as mpl
-from matplotlib import gridspec
-from scipy.stats import pearsonr
-from scipy.stats.mstats import mquantiles
-
-# The refnx library, and associated classes
-import refnx
-from refnx.reflect import structure, ReflectModel, SLD#
-from refnx.dataset import ReflectDataset
-from refnx.analysis import Transform, CurveFitter, Objective, GlobalObjective, Parameter
-
-# The custom class to constain the monolayer model. 
-import sys
-sys.path.insert(0, '/home/arm61/work/writing/articles/lipids_at_airdes/src/models')
-import mol_vol as mv
-
-data_dir = sys.argv[1] + '/data/processed/DMPC/'
-figures_dir = sys.argv[1] + '/reports/figures/'
-analysis_dir = sys.argv[1] + '/output/'
-
-
-# In[2]:
-
-
-# Reading datasets into refnx format
-dataset3_n1 = ReflectDataset('{}DMPC_Neutron_conc2_dDMPC_hDES.mft'.format(data_dir))
-
-
-# In[3]:
-
-
-# Scattering length of the lipid head group 
-# (found from summing the electrons in the head group 
-# and multiplying by the classical radius of an electron)
-head_sl = [602.7e-6, 602.7e-6]
-# Scattering length of the lipid tail group",
-tail_sl = [5329.76e-6, 5329.76e-6]
-# Solvent SLD from ref [3]
-solvent_sld = [0.43, 3.15]
-# SLD of air",
-super_sld = [0, 0]
-# Some initial values for the head and tail thicknesses & APM
-thick_heads = [13.1117, 11.0571]
-tail_length = 1.54 + 1.265 * 13
-chain_tilt = [0.792674, 0.79015]
-vols = [200.497, 891.]
-head_tail_rough = 3.3
-tail_air_rough = 5.1
-
-
-# In[4]:
-
-
-# set up the chemical context system
[…]

### 2018-08-15 notebooks/DPPC/DPPC_neutron_conc3_n1.py

@@ -1,262 +1,0 @@
-
-# coding: utf-8
-
-# In[1]:
-
-
-# Standard libraries to import
-from __future__ import division
-import numpy as np 
-import matplotlib.pyplot as plt
-#from matplotlib import rcParams, rc
-import seaborn as sns; sns.set('paper', palette='colorblind')
-import matplotlib as mpl
-from matplotlib import gridspec
-from scipy.stats import pearsonr
-from scipy.stats.mstats import mquantiles
-
-# The refnx library, and associated classes
-import refnx
-from refnx.reflect import structure, ReflectModel, SLD#
-from refnx.dataset import ReflectDataset
-from refnx.analysis import Transform, CurveFitter, Objective, GlobalObjective, Parameter
-
-# The custom class to constain the monolayer model. 
-import sys
-sys.path.insert(0, '/home/arm61/work/writing/articles/lipids_at_airdes/src/models')
-import mol_vol as mv
-
-data_dir = sys.argv[1] + '/data/processed/DPPC/'
-figures_dir = sys.argv[1] + '/reports/figures/'
-analysis_dir = sys.argv[1] + '/output/'
-
-
-# In[2]:
-
-
-# Reading datasets into refnx format
-dataset3_n1 = ReflectDataset('{}DPPC_Neutron_conc3_dDPPC_hDES.mft'.format(data_dir))
-
-
-# In[3]:
-
-
-# Scattering length of the lipid head group 
-# (found from summing the electrons in the head group 
-# and multiplying by the classical radius of an electron)
-head_sl = [602.7e-6, 602.7e-6]
-# Scattering length of the lipid tail group",
-tail_sl = [6129.2e-6, 6129.2e-6]
-# Solvent SLD from ref [3]
-solvent_sld = [0.43, 3.15]
-# SLD of air",
-super_sld = [0, 0]
-# Some initial values for the head and tail thicknesses & APM
-thick_heads = [13.1117, 11.0571]
-tail_length = 1.54 + 1.265 * 15
-chain_tilt = [0.792674, 0.79015]
-vols = [200.497, 891.]
-head_tail_rough = 3.3
-tail_air_rough = 5.1
-
-
-# In[4]:
-
-
-# set up the chemical context system
[…]

### 2018-08-15 notebooks/lipid_nr.py

@@ -1,0 +1,273 @@
+
+# coding: utf-8
+
+# In[ ]:
+
+
+# Standard libraries to import
+from __future__ import division
+import numpy as np 
+import scipy
+from scipy.stats.mstats import mquantiles
+
+# The refnx library, and associated classes
+import refnx
+from refnx.reflect import structure, ReflectModel, SLD#
+from refnx.dataset import ReflectDataset
+from refnx.analysis import Transform, CurveFitter, Objective, GlobalObjective, Parameter
+
+# The custom class to constain the monolayer model. 
+import sys
+sys.path.insert(0, '../src/models')
+import mol_vol as mv
+sys.path.insert(0, '../src/tools')
+import helper
+
+lipid = sys.argv[1]
+length = int(sys.argv[2])
+sp = sys.argv[3]
+
+data_dir = '../data/processed/{}/'.format(lipid)
+figures_dir = '../reports/figures/'
+analysis_dir = '../output/'
+
+
+# In[ ]:
+
+
+refnx.version.full_version, scipy.version.version
+
+
+# In[ ]:
+
+
+# Reading datasets into refnx format
+dataset_1 = ReflectDataset('{}nr_h_sp_{}.dat'.format(data_dir, sp))
+dataset_2 = ReflectDataset('{}nr_hd_sp_{}.dat'.format(data_dir, sp))
+
+
+# In[ ]:
+
+
+head = {'C': 10, 'H': 18, 'O': 8, 'N': 1, 'P': 1}
+tail = {'C': length * 2, 'D': length * 4 + 2}
+
+head_sl = mv.get_scattering_length(head, neutron=True)
+tail_sl = mv.get_scattering_length(tail, neutron=True)
+
+solvent_sld = [0.43, 3.15]
+super_sld = [0, 0]
+thick_heads = 13.1117
+tail_length = 1.54 + 1.265 * length
+chain_tilt = 0.792674
+vols = [200.497, 891.]
+
+
+# In[ ]:
+
+
+lipid_1 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+                      reverse_monolayer=True, name='{}_1'.format(lipid))
+lipid_2 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+                      reverse_monolayer=True, name='{}_2'.format(lipid))
+
+
+# In[ ]:
+
+
[…]

### 2018-08-15 src/data/refnx-0.0.15/benchmarks/run.py

@@ -1,70 +1,0 @@
-#!/usr/bin/env python
-"""
-run.py [options] ASV_COMMAND..
-
-Convenience wrapper around the ``asv`` command; just sets environment
-variables and chdirs to the correct place etc.
-
-"""
-from __future__ import division, absolute_import, print_function
-
-import os
-import sys
-import subprocess
-import json
-import shutil
-import argparse
-import sysconfig
-import errno
-
-
-EXTRA_PATH = ['']
-
-
-def main():
-    class ASVHelpAction(argparse.Action):
-        nargs = 0
-        def __call__(self, parser, namespace, values, option_string=None):
-            sys.exit(run_asv(['--help']))
-
-    p = argparse.ArgumentParser(usage=__doc__.strip())
-    p.add_argument('--help-asv', nargs=0, action=ASVHelpAction,
-        help="""show ASV help""")
-    p.add_argument('asv_command', nargs=argparse.REMAINDER)
-    args = p.parse_args()
-
-    sys.exit(run_asv(args.asv_command))
-
-
-def run_asv(args):
-    cwd = os.path.abspath(os.path.dirname(__file__))
-
-    repo_dir = os.path.join(cwd, 'refnx')
-
-    cmd = ['asv'] + list(args)
-    env = dict(os.environ)
-
-    # Inject ccache/f90cache paths
-    if sys.platform.startswith('linux'):
-        env['PATH'] = os.pathsep.join(EXTRA_PATH + env.get('PATH', '').split(os.pathsep))
-
-    # Check refnx version if in dev mode; otherwise clone and setup results
-    # repository
-    if args and (args[0] == 'dev' or '--python=same' in args):
-        import refnx
-        print("Running benchmarks for refnx version %s at %s" % (refnx.__version__, refnx.__file__))
-
-    # Run
-    try:
-        return subprocess.call(cmd, env=env, cwd=cwd)
-    except OSError as err:
-        if err.errno == errno.ENOENT:
-            print("Error when running '%s': %s\n" % (" ".join(cmd), str(err),))
-            print("You need to install Airspeed Velocity https://spacetelescope.github.io/asv/")
-            print("to run refnx benchmarks")
-            return 1
-        raise
-
-
-if __name__ == "__main__":
-    sys.exit(main())

### 2018-08-15 src/data/refnx-0.0.15/doc/conf.py

@@ -1,309 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-#
-# refnx documentation build configuration file, created by
-# sphinx-quickstart on Fri Oct 23 10:21:57 2015.
-#
-# This file is execfile()d with the current directory set to its
-# containing dir.
-#
-# Note that not all possible configuration values are present in this
-# autogenerated file.
-#
-# All configuration values have a default; values that are commented out
-# serve to show the default.
-
-import sys
-import os
-import shlex
-import re
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-#sys.path.insert(0, os.path.abspath('.'))
-
-# -- General configuration ------------------------------------------------
-
-# If your documentation needs a minimal Sphinx version, state it here.
-#needs_sphinx = '1.0'
-
-# Add any Sphinx extension module names here, as strings. They can be
-# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
-# ones.
-extensions = [
-    'sphinx.ext.autodoc',
-    'sphinx.ext.intersphinx',
-    'sphinx.ext.mathjax',
-    'sphinx.ext.viewcode',
-    'sphinx.ext.autosummary',
-    'sphinx.ext.napoleon'
-]
-
-# Add any paths that contain templates here, relative to this directory.
-templates_path = ['_templates']
-
-# The suffix(es) of source filenames.
-# You can specify multiple suffix as a list of string:
-# source_suffix = ['.rst', '.md']
-source_suffix = '.rst'
-
-# The encoding of source files.
-#source_encoding = 'utf-8-sig'
-
-# The master toctree document.
-master_doc = 'index'
-
-# General information about the project.
-project = 'refnx'
-copyright = '2015-2017, Andrew Nelson'
-author = 'Andrew Nelson'
-
-# The version info for the project you're documenting, acts as replacement for
-# |version| and |release|, also used in various other places throughout the
-# built documents.
-import refnx
-
-# The short X.Y version.
-version = re.sub(r'\.dev-.*$', r'.dev', refnx.__version__)
-# The full version, including alpha/beta/rc tags.
-release = refnx.__version__
-
-intersphinx_mapping = {'py': ('http://docs.python.org/3', None),
-                       'numpy': ('https://docs.scipy.org/doc/numpy/', None),
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/_lib/_testutils.py

@@ -1,60 +1,0 @@
-"""
-Generic test utilities.
-AMENDED FROM scipy version Aug17
-"""
-
-from __future__ import division, print_function, absolute_import
-
-import os
-import re
-import sys
-
-
-__all__ = ['PytestTester']
-
-
-class PytestTester(object):
-    """
-    Pytest test runner entry point.
-    """
-
-    def __init__(self, module_name):
-        self.module_name = module_name
-
-    def __call__(self, label="fast", verbose=1, extra_argv=None,
-                 doctests=False, coverage=False, tests=None):
-        import pytest
-
-        module = sys.modules[self.module_name]
-        module_path = os.path.abspath(module.__path__[0])
-
-        pytest_args = ['-l']
-
-        if doctests:
-            raise ValueError("Doctests not supported")
-
-        if extra_argv:
-            pytest_args += list(extra_argv)
-
-        if verbose and int(verbose) > 1:
-            pytest_args += ["-" + "v" * (int(verbose) - 1)]
-
-        if coverage:
-            pytest_args += ["--cov=" + module_path]
-
-        if label == "fast":
-            pytest_args += ["-m", "not slow"]
-        elif label != "full":
-            pytest_args += ["-m", label]
-
-        if tests is None:
-            tests = [self.module_name]
-
-        pytest_args += ['--pyargs'] + list(tests)
-
-        try:
-            code = pytest.main(pytest_args)
-        except SystemExit as exc:
-            code = exc.code
-
-        return (code == 0)

### 2018-08-15 src/data/refnx-0.0.15/refnx/_lib/emcee/moves/de.py

@@ -1,51 +1,0 @@
-# -*- coding: utf-8 -*-
-
-from __future__ import division, print_function
-
-import numpy as np
-from .red_blue import RedBlueMove
-
-__all__ = ["DEMove"]
-
-
-class DEMove(RedBlueMove):
-    """A proposal using differential evolution.
-
-    This `Differential evolution proposal
-    <http://www.stat.columbia.edu/~gelman/stuff_for_blog/cajo.pdf>`_ is
-    implemented following `Nelson et al. (2013)
-    <http://arxiv.org/abs/1311.5229>`_.
-
-    Args:
-        sigma (float): The standard deviation of the Gaussian used to stretch
-            the proposal vector.
-        gamma0 (Optional[float]): The mean stretch factor for the proposal
-            vector. By default, it is :math:`2.38 / \sqrt{2\,\mathrm{ndim}}`
-            as recommended by the two references.
-
-    """
-    def __init__(self, sigma, gamma0=None, **kwargs):
-        self.sigma = sigma
-        self.gamma0 = gamma0
-        kwargs["nsplits"] = 3
-        super(DEMove, self).__init__(**kwargs)
-
-    def setup(self, coords):
-        self.g0 = self.gamma0
-        if self.g0 is None:
-            # Pure MAGIC:
-            ndim = coords.shape[1]
-            self.g0 = 2.38 / np.sqrt(2 * ndim)
-
-    def get_proposal(self, s, c, random):
-        Ns = len(s)
-        Nc = list(map(len, c))
-        ndim = s.shape[1]
-        q = np.empty((Ns, ndim), dtype=np.float64)
-        f = random.randn(Ns)
-        for i in range(Ns):
-            w = np.array([c[j][random.randint(Nc[j])] for j in range(2)])
-            random.shuffle(w)
-            g = np.diff(w, axis=0) * (1 + self.g0 * f[i])
-            q[i] = s[i] + g
-        return q, np.zeros(Ns, dtype=np.float64)

### 2018-08-15 src/data/refnx-0.0.15/refnx/_lib/emcee/moves/move.py

@@ -1,47 +1,0 @@
-# -*- coding: utf-8 -*-
-
-from __future__ import division, print_function
-
-import numpy as np
-
-__all__ = ["Move"]
-
-
-class Move(object):
-
-    def update(self,
-               coords, log_probs, blobs,
-               new_coords, new_log_probs, new_blobs,
-               accepted, subset=None):
-        """Update a given subset of the ensemble with an accepted proposal
-
-        Args:
-            coords: The original ensemble coordinates.
-            log_probs: The original log probabilities of the walkers.
-            blobs: The original blobs.
-            new_coords: The proposed coordinates.
-            new_log_probs: The proposed log probabilities.
-            new_blobs: The proposed blobs.
-            accepted: A vector of booleans indicating which walkers were
-                accepted.
-            subset (Optional): A boolean mask indicating which walkers were
-                included in the subset. This can be used, for example, when
-                updating only the primary ensemble in a :class:`RedBlueMove`.
-
-        """
-        if subset is None:
-            subset = np.ones(len(coords), dtype=bool)
-        m1 = subset & accepted
-        m2 = accepted[subset]
-        coords[m1] = new_coords[m2]
-        log_probs[m1] = new_log_probs[m2]
-
-        if new_blobs is not None:
-            if blobs is None:
-                raise ValueError(
-                    "If you start sampling with a given lnprob, "
-                    "you also need to provide the current list of "
-                    "blobs at that position.")
-            blobs[m1] = new_blobs[m2]
-
-        return coords, log_probs, blobs

### 2018-08-15 src/data/refnx-0.0.15/refnx/_lib/emcee/pbar.py

@@ -1,47 +1,0 @@
-# -*- coding: utf-8 -*-
-
-from __future__ import division, print_function
-
-__all__ = ["get_progress_bar"]
-
-import logging
-
-try:
-    from tqdm import tqdm
-except ImportError:
-    tqdm = None
-
-
-class _NoOpPBar(object):
-    """This class implements the progress bar interface but does nothing"""
-    def __init__(self):
-        pass
-
-    def __enter__(self, *args, **kwargs):
-        return self
-
-    def __exit__(self, *args, **kwargs):
-        pass
-
-    def update(self, count):
-        pass
-
-
-def get_progress_bar(display, total):
-    """Get a progress bar interface with given properties
-
-    If the tqdm library is not installed, this will always return a "progress
-    bar" that does nothing.
-
-    Args:
-        display (bool): Should the bar actually show the progress?
-        total (int): The total size of the progress bar.
-
-    """
-    if not display:
-        return _NoOpPBar()
-    if tqdm is None:
-        logging.warn("You must install the tqdm library to use progress "
-                     "indicators with emcee")
-        return _NoOpPBar()
-    return tqdm(total=total)

### 2018-08-15 src/data/refnx-0.0.15/refnx/_lib/util.py

@@ -1,272 +1,0 @@
-from __future__ import print_function
-
-import warnings as _warnings
-import os as _os
-import sys as _sys
-import functools
-from tempfile import mkdtemp
-import collections
-from contextlib import contextmanager
-try:
-    from inspect import getfullargspec as _getargspecf
-except ImportError:
-    # on 2.7
-    from inspect import getargspec as _getargspecf
-
-
-from refnx._lib.emcee.interruptible_pool import InterruptiblePool
-
-
-def preserve_cwd(function):
-    """
-    Ensures that the original working directory is kept when exiting a function
-
-    Parameters
-    ----------
-    function : callable
-
-    """
-    @functools.wraps(function)
-    def decorator(*args, **kwargs):
-        cwd = _os.getcwd()
-        try:
-            return function(*args, **kwargs)
-        finally:
-            _os.chdir(cwd)
-    return decorator
-
-
-class TemporaryDirectory(object):
-    """Create and return a temporary directory.  This has the same
-    behavior as mkdtemp but can be used as a context manager.  For
-    example:
-
-        with TemporaryDirectory() as tmpdir:
-            ...
-
-    Upon exiting the context, the directory and everything contained
-    in it are removed.
-    """
-
-    def __init__(self, suffix="", prefix="tmp", dir=None):
-        self._closed = False
-        # Handle mkdtemp raising an exception
-        self.name = None
-        self.name = mkdtemp(suffix, prefix, dir)
-
-    def __repr__(self):
-        return "<{} {!r}>".format(self.__class__.__name__, self.name)
-
-    def __enter__(self):
-        return self.name
-
-    def cleanup(self, _warn=False):
-        if self.name and not self._closed:
-            try:
-                self._rmtree(self.name)
-            except (TypeError, AttributeError) as ex:
-                # Issue #10188: Emit a warning on stderr
-                # if the directory could not be cleaned
-                # up due to missing globals
-                if "None" not in str(ex):
-                    raise
-                print("ERROR: {!r} while cleaning up {!r}".format(ex, self,),
-                      file=_sys.stderr)
-                return
-            self._closed = True
-            if _warn:
-                # ResourceWarning
-                self._warn("ResourceWarning: Implicitly cleaning"
-                           " up {!r}".format(self))
-
-    def __exit__(self, exc, value, tb):
-        self.cleanup()
-
-    def __del__(self):
-        # Issue a ResourceWarning if implicit cleanup needed
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/analysis/test/test_bounds.py

@@ -1,103 +1,0 @@
-import pickle
-
-from refnx.analysis import Interval, PDF
-
-import numpy as np
-from numpy.testing import (assert_equal, assert_, assert_almost_equal)
-from scipy.stats import norm, truncnorm
-
-
-class TestBounds(object):
-
-    def setup_method(self):
-        pass
-
-    def test_interval(self):
-        # open interval should have lnprob of 0
-        interval = Interval()
-        assert_equal(interval.lnprob(0), 0)
-
-        # semi closed interval
-        interval.ub = 1000
-        assert_equal(interval.lnprob(0), 0)
-        assert_equal(interval.lnprob(1001), -np.inf)
-
-        # fully closed interval
-        interval.lb = -1000
-        assert_equal(interval.lnprob(-1001), -np.inf)
-        assert_equal(interval.lb, -1000)
-        assert_equal(interval.ub, 1000)
-        assert_equal(interval.lnprob(0), np.log(1 / 2000.))
-
-        # try and set lb higher than ub
-        interval.lb = 1002
-        assert_equal(interval.lb, 1000)
-        assert_equal(interval.ub, 1002)
-
-        # if val is outside closed range then rvs is used
-        vals = interval.valid(np.linspace(990, 1005, 100))
-        assert_(np.max(vals) <= 1002)
-        assert_(np.min(vals) >= 1000)
-        assert_(np.isfinite(interval.lnprob(vals)).all())
-
-        # if bounds are semi-open then val is reflected from lb
-        interval.ub = None
-        interval.lb = 1002
-        x = np.linspace(990, 1001, 10)
-        vals = interval.valid(x)
-        assert_almost_equal(vals, 2 * interval.lb - x)
-        assert_equal(interval.valid(1003), 1003)
-
-        # if bounds are semi-open then val is reflected from ub
-        interval.lb = None
-        interval.ub = 1002
-        x = np.linspace(1003, 1005, 10)
-        vals = interval.valid(x)
-        assert_almost_equal(vals, 2 * interval.ub - x)
-        assert_equal(interval.valid(1001), 1001)
-
-    def test_pdf(self):
-        pdf = PDF(norm)
-
-        # even if it's really far out it's still a valid value
-        assert_equal(pdf.valid(1003), 1003)
-        # logp
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/analysis/test/test_globalfitting.py

@@ -1,154 +1,0 @@
-"""
-Test co-refinement of datasets by fitting 3 neutron reflectivity datasets. The
-overall construction of the models can be done in a few different ways.
-"""
-from __future__ import print_function, division
-import os.path
-
-import numpy as np
-from numpy.testing import (assert_, assert_equal, assert_almost_equal,
-                           assert_allclose)
-
-from refnx.analysis import (CurveFitter, Objective, GlobalObjective, Transform)
-from refnx.dataset import ReflectDataset
-from refnx.reflect import (Slab, SLD, ReflectModel)
-
-SEED = 1
-
-
-class TestGlobalFitting(object):
-
-    def setup_method(self):
-        self.pth = os.path.dirname(os.path.abspath(__file__))
-
-        self.si = SLD(2.07, name='Si')
-        self.sio2 = SLD(3.47, name='SiO2')
-        self.d2o = SLD(6.36, name='d2o')
-        self.h2o = SLD(-0.56, name='h2o')
-        self.cm3 = SLD(3.5, name='cm3')
-        self.polymer = SLD(2, name='polymer')
-
-        self.sio2_l = self.sio2(40, 3)
-        self.polymer_l = self.polymer(200, 3)
-
-        self.structure = (self.si | self.sio2_l | self.polymer_l |
-                          self.d2o(0, 3))
-
-        fname = os.path.join(self.pth, 'c_PLP0011859_q.txt')
-
-        self.dataset = ReflectDataset(fname)
-        self.model = ReflectModel(self.structure, bkg=2e-7)
-        self.objective = Objective(self.model,
-                                   self.dataset,
-                                   use_weights=False,
-                                   transform=Transform('logY'))
-        self.global_objective = GlobalObjective([self.objective])
-
-    def test_residuals_length(self):
-        # the residuals should be the same length as the data
-        residuals = self.global_objective.residuals()
-        assert_equal(residuals.size, len(self.dataset))
-
-    def test_globalfitting(self):
-        # smoke test for can the global fitting run?
-        # also tests that global fitting gives same output as
-        # normal fitting (for a single dataset)
-        self.model.scale.setp(vary=True, bounds=(0.1, 2))
-        self.model.bkg.setp(vary=True, bounds=(1e-10, 8e-6))
-        self.structure[-1].rough.setp(vary=True, bounds=(0.2, 6))
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/analysis/test/test_model.py

@@ -1,66 +1,0 @@
-import pickle
-
-import numpy as np
-from numpy.testing import (assert_almost_equal, assert_equal, assert_,
-                           assert_allclose, assert_raises)
-
-from refnx.analysis import Parameter, Model
-
-
-def line(x, params, *args, **kwds):
-    p_arr = np.array(params)
-    return p_arr[0] + x * p_arr[1]
-
-
-def line2(x, p):
-    return p['c'].value + p['m'].value * x
-
-
-def line3(x, params, x_err=None):
-    pass
-
-
-class TestModel(object):
-
-    def setup_method(self):
-        pass
-
-    def test_evaluation(self):
-        c = Parameter(1.0, name='c')
-        m = Parameter(2.0, name='m')
-        p = c | m
-
-        fit_model = Model(p, fitfunc=line)
-        x = np.linspace(0, 100., 20)
-        y = 2. * x + 1.
-
-        # different ways of getting the model instance to evaluate
-        assert_equal(fit_model.model(x, p), y)
-        assert_equal(fit_model(x, p), y)
-        assert_equal(fit_model.model(x), y)
-        assert_equal(fit_model(x), y)
-
-        # can we pickle the model object
-        pkl = pickle.dumps(fit_model)
-        unpkl = pickle.loads(pkl)
-        assert_equal(unpkl(x), y)
-
-        # you should be able to use a lambda
-        fit_model = Model(p, fitfunc=line2)
-        assert_equal(fit_model(x, p), y)
-
-        # and swap the order of parameters - retrieve by key
-        p = m | c
-        fit_model = Model(p, fitfunc=line2)
-        assert_equal(fit_model(x, p), y)
-
-    def test_xerr(self):
-        c = Parameter(1.0, name='c')
-        m = Parameter(2.0, name='m')
-        p = c | m
-
-        fit_model = Model(p, fitfunc=line3)
-        assert_(fit_model._fitfunc_has_xerr is True)
-
-        fit_model = Model(p, fitfunc=line2)
-        assert_(fit_model._fitfunc_has_xerr is False)

### 2018-08-15 src/data/refnx-0.0.15/refnx/analysis/test/test_parameter.py

@@ -1,224 +1,0 @@
-import pickle
-
-import numpy as np
-from numpy.testing import (assert_almost_equal, assert_equal, assert_,
-                           assert_allclose)
-from scipy.stats import norm, uniform
-
-from refnx.analysis import (Interval, PDF, Parameter, Parameters,
-                            is_parameters)
-
-
-class TestParameter(object):
-
-    def setup_method(self):
-        pass
-
-    def test_parameter(self):
-        # simple test of constraint
-        x = Parameter(5.)
-        y = Parameter(1.)
-        y.constraint = x * 2.
-        assert_equal(y.value, x.value * 2.)
-
-        # if you've constrained a parameter it shouldn't be varying
-        assert_(y.vary is False)
-
-        # you can't set a constraint on a parameter with an expression that
-        # already involves the parameter
-        from pytest import raises
-        with raises(ValueError):
-            x.constraint = y
-
-        # try a negative value
-        x.value = -1.
-        assert_equal(y.value, -2.)
-
-        # nested constraints
-        z = Parameter(1.)
-        z.constraint = x + y
-        assert_equal(z.value, -3)
-        # check that nested circular constraints aren't allowed
-        with raises(ValueError):
-            x.constraint = z
-
-        # absolute value constraint
-        y.constraint = abs(x)
-        assert_equal(y.value, 1)
-
-        # sin constraint
-        y.constraint = np.sin(x) + 2.
-        assert_equal(y.value, 2. + np.sin(x.value))
-
-    def test_func_attribute(self):
-        # a Parameter object should have math function attributes
-        a = Parameter(1)
-        assert_(hasattr(a, 'sin'))
-
-    def test_remove_constraint(self):
-        x = Parameter(5.)
-        y = Parameter(1.)
-        y.constraint = x * 2.
-        y.constraint = None
-        assert_(y.vary is False)
-        assert_equal(y.value, 10)
-        assert_(y._constraint is None)
-
-    def test_parameter_bounds(self):
-        x = Parameter(4, bounds=Interval(-4, 4))
-        assert_equal(x.lnprob(), uniform.logpdf(0, -4, 8))
-
-        x.bounds = None
-        assert_(isinstance(x._bounds, Interval))
-        assert_equal(x.bounds.lb, -np.inf)
-        assert_equal(x.bounds.ub, np.inf)
-        assert_equal(x.lnprob(), 0)
-
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/dataset/__init__.py

@@ -1,11 +1,0 @@
-from __future__ import division, absolute_import
-
-from refnx.dataset.data1d import Data1D
-from refnx.dataset.reflectdataset import ReflectDataset
-from refnx._lib._testutils import PytestTester
-
-test = PytestTester(__name__)
-del PytestTester
-
-
-__all__ = [s for s in dir() if not s.startswith('_')]

### 2018-08-15 src/data/refnx-0.0.15/refnx/dataset/test/test_reflectdataset.py

@@ -1,188 +1,0 @@
-import os.path
-
-import pytest
-
-from refnx.dataset import ReflectDataset, Data1D
-import numpy as np
-from numpy.testing import assert_equal, assert_
-
-
-class TestReflectDataset(object):
-
-    @pytest.fixture(autouse=True)
-    def setup_method(self, tmpdir):
-        self.pth = os.path.dirname(os.path.abspath(__file__))
-
-        data = ReflectDataset()
-
-        x1 = np.linspace(0, 10, 5)
-        y1 = 2 * x1
-        e1 = np.ones_like(x1)
-        dx1 = np.ones_like(x1)
-        data.add_data((x1, y1, e1, dx1))
-        self.data = data
-
-        self.cwd = os.getcwd()
-        self.tmpdir = tmpdir.strpath
-        os.chdir(self.tmpdir)
-
-    def teardown_method(self):
-        os.chdir(self.cwd)
-
-    def test_load(self):
-        # load dataset from XML, via file handle
-        dataset = ReflectDataset()
-        with open(os.path.join(self.pth, 'c_PLP0000708.xml')) as f:
-            dataset.load(f)
-
-        assert_equal(len(dataset), 90)
-        assert_equal(90, np.size(dataset.x))
-
-        # load dataset from XML, via string
-        dataset = ReflectDataset()
-        dataset.load(os.path.join(self.pth, 'c_PLP0000708.xml'))
-
-        assert_equal(len(dataset), 90)
-        assert_equal(90, np.size(dataset.x))
-
-        # load dataset from .dat, via file handle
-        dataset1 = ReflectDataset()
-        with open(os.path.join(self.pth, 'c_PLP0000708.dat')) as f:
-            dataset1.load(f)
-
-        assert_equal(len(dataset1), 90)
-        assert_equal(90, np.size(dataset1.x))
-
-        # load dataset from .dat, via string
-        dataset2 = ReflectDataset()
-        dataset2.load(os.path.join(self.pth, 'c_PLP0000708.dat'))
-
-        assert_equal(len(dataset2), 90)
-        assert_equal(90, np.size(dataset2.x))
-
-    def test_load_dat_with_header(self):
-        # check that the file load works with a header
-        a = ReflectDataset(os.path.join(self.pth, 'c_PLP0000708.dat'))
-        b = ReflectDataset(os.path.join(self.pth, 'c_PLP0000708_header.dat'))
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/__init__.py

@@ -1,14 +1,0 @@
-from refnx.reduce.reduce import PlatypusReduce, reduce_stitch
-from refnx.reduce.platypusnexus import (catalogue, PlatypusNexus,
-                                        number_datafile, basename_datafile,
-                                        datafile_number, Y_PIXEL_SPACING,
-                                        accumulate_HDF_files, Catalogue)
-from refnx.reduce.batchreduction import BatchReducer
-from refnx.reduce.xray import reduce_xrdml
-from refnx._lib._testutils import PytestTester
-
-test = PytestTester(__name__)
-del PytestTester
-
-
-__all__ = [s for s in dir() if not s.startswith('_')]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/platypusnexus.py

@@ -1,1971 +1,0 @@
-from __future__ import division, absolute_import
-import io
-import os
-import os.path
-import argparse
-import re
-import shutil
-from time import gmtime, strftime
-import string
-import warnings
-from contextlib import contextmanager
-
-from scipy.optimize import leastsq, curve_fit
-from scipy.stats import t
-import pandas as pd
-import numpy as np
-import h5py
-
-from refnx.reduce.peak_utils import peak_finder, centroid
-import refnx.util.general as general
-from refnx.util.general import resolution_double_chopper, _dict_compare
-import refnx.util.ErrorProp as EP
-from refnx.reduce.parabolic_motion import find_trajectory, y_deflection
-from refnx.reduce.event import (events, process_event_stream,
-                                framebins_to_frames)
-from refnx.reduce.rebin import rebin, rebin_along_axis
-from refnx._lib import possibly_open_file
-
-
-# detector y pixel spacing in mm per pixel
-Y_PIXEL_SPACING = 1.177
-
-disc_openings = (60., 10., 25., 60.)
-O_C1d, O_C2d, O_C3d, O_C4d = disc_openings
-O_C1, O_C2, O_C3, O_C4 = np.radians(disc_openings)
-
-DISCRADIUS = 350.
-EXTENT_MULT = 2
-PIXEL_OFFSET = 1
-
-spectrum_template = """<?xml version="1.0"?>
-<REFroot xmlns="">
-<REFentry time="$time">
-<Title>$title</Title>
-<REFdata axes="lambda" rank="1" type="POINT"\
- spin="UNPOLARISED" dim="$n_spectra">
-<Run filename="$runnumber"/>
-<R uncertainty="dR">$r</R>
-<lambda uncertainty="dlambda" units="1/A">$lmda</lambda>
-<dR type="SD">$dr</dR>
-<dlambda type="_FWHM" units="1/A">$dlmda</dlambda>
-</REFdata>
-</REFentry>
-</REFroot>"""
-
-
-def catalogue(start, stop, data_folder=None):
-    """
-    Extract interesting information from Platypus NeXUS files.
-
-    Parameters
-    ----------
-    start : int
-        start cataloguing from this run number.
-    stop : int
-        stop cataloguing at this run number
-    data_folder : str, optional
-        path specifying location of NeXUS files
-
-    Returns
-    -------
-    catalog : pd.DataFrame
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/reduce.py

@@ -1,608 +1,0 @@
-from __future__ import division, absolute_import
-
-import string
-from copy import deepcopy
-import os.path
-from time import gmtime, strftime
-
-import numpy as np
-from refnx.reduce.platypusnexus import (PlatypusNexus, ReflectNexus,
-                                        number_datafile,
-                                        Y_PIXEL_SPACING, basename_datafile)
-from refnx.util import ErrorProp as EP
-import refnx.util.general as general
-from refnx.reduce.parabolic_motion import (parabola_line_intersection_point,
-                                           find_trajectory)
-from refnx.dataset import ReflectDataset
-from refnx._lib import possibly_open_file
-
-
-_template_ref_xml = """<?xml version="1.0"?>
-<REFroot xmlns="">
-<REFentry time="$time">
-<Title>$title</Title>
-<User>$user</User>
-<REFsample>
-<ID>$sample</ID>
-</REFsample>
-<REFdata axes="Qz:Qy" rank="2" type="POINT" \
-spin="UNPOLARISED" dim="$_numpointsz:$_numpointsy">
-<Run filename="$_rnumber" preset="" size="">
-</Run>
-<R uncertainty="dR">$_r</R>
-<Qz uncertainty="dQz" units="1/A">$_qz</Qz>
-<dR type="SD">$_dr</dR>
-<Qy type="_FWHM" units="1/A">$_qy</Qy>
-</REFdata>
-</REFentry>
-</REFroot>"""
-
-
-class ReflectReduce(object):
-    def __init__(self, direct, prefix, data_folder=None):
-
-        self.data_folder = os.path.curdir
-        if data_folder is not None:
-            self.data_folder = data_folder
-
-        if prefix == 'PLP':
-            self.reflect_klass = PlatypusNexus
-        else:
-            raise ValueError("Instrument prefix not known. Must be one of"
-                             " ['PLP']")
-        if isinstance(direct, ReflectNexus):
-            self.direct_beam = direct
-        elif type(direct) is str:
-            direct = os.path.join(self.data_folder, direct)
-            self.direct_beam = self.reflect_klass(direct)
-        else:
-            self.direct_beam = self.reflect_klass(direct)
-
-        self.prefix = prefix
-
-    def __call__(self, reflect, scale=1, save=True, **kwds):
-        return self.reduce(reflect, scale=scale, save=save, **kwds)
-
-    def reduce(self, reflect, scale=1., save=True, **kwds):
-        """
-        Reduction of a single dataset.
-
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/test/test_event.py

@@ -1,140 +1,0 @@
-import os
-import numpy as np
-from numpy.testing import assert_equal
-import refnx.reduce.event as event
-from refnx.reduce.event import events
-from refnx.reduce import PlatypusNexus
-
-try:
-    import refnx.reduce._cevent as _cevent
-except ImportError:
-    HAVE_CEVENTS = False
-else:
-    HAVE_CEVENTS = True
-
-
-class TestEvent(object):
-
-    @classmethod
-    def setup_class(cls):
-        path = os.path.dirname(os.path.realpath(__file__))
-        cls.event_file_path = os.path.join(path,
-                                           'DAQ_2012-01-19T15-45-52',
-                                           'DATASET_0',
-                                           'EOS.bin')
-
-        with open(cls.event_file_path, 'rb') as f:
-            if HAVE_CEVENTS:
-                event_list, fpos = _cevent._cevents(f)
-            else:
-                event_list, fpos = event._events(f)
-
-        cls.event_list = event_list
-        cls.fpos = fpos
-        cls.f, cls.t, cls.y, cls.x = event_list
-
-    def setup_method(self):
-        path = os.path.dirname(os.path.realpath(__file__))
-        self.path = path
-
-    def test_events_smoke(self):
-        # check that the event.events function works
-        events(self.event_file_path)
-
-    def test_num_events(self):
-        assert_equal(1056618, self.x.size)
-
-    def test_max_frames(self):
-        # test reading only a certain number of frames
-        # also use this test to compare pure python read of events
-        with open(self.event_file_path, 'rb') as g:
-            event_list, fpos = event._events(g, max_frames=10)
-
-        f, t, y, x = event_list
-        max_f = np.max(f)
-        assert_equal(9, max_f)
-
-        if HAVE_CEVENTS:
-            with open(self.event_file_path, 'rb') as g:
-                event_list, fpos = _cevent._cevents(g, max_frames=10)
-                cyf, cyt, cyy, cyx = event_list
-
-            max_f = np.max(cyf)
-            assert_equal(9, max_f)
-
-            assert_equal(cyf, f)
-            assert_equal(cyt, t)
-            assert_equal(cyy, y)
-            assert_equal(cyx, x)
-
-    def test_event_same_as_detector(self):
-        # the detector file should be the same as the event file
-        orig_file = PlatypusNexus(os.path.join(self.path,
-                                               'PLP0011613.nx.hdf'))
-        orig_det = orig_file.cat.detector
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/test/test_parabolic_motion.py

@@ -1,58 +1,0 @@
-import numpy as np
-from numpy.testing import (assert_almost_equal, assert_)
-from scipy import constants
-import refnx.reduce.parabolic_motion as pm
-
-
-class TestParabolicMotion(object):
-
-    def setup_method(self):
-        pass
-
-    def test_y_deflection(self):
-        # Launch a projectile at 45 degrees at 300 m/s.
-        # It should have a flight time of 43.262894944953523 s
-        # for which the range is 9177.445 m, at which point the
-        # deflection should be 0.
-        deflection = pm.y_deflection(45, 300., 9177.4459168013527)
-        assert_almost_equal(deflection, 0)
-
-    def test_elevation(self):
-        # angle as it passes y = 0 should be -ve of initial trajectory
-        angle = pm.elevation(45., 300., 9177.4459168013527)
-        assert_almost_equal(angle, -45)
-
-    def test_find_trajectory(self):
-        # the angle needs to be 45 degrees for a projectile launched
-        # at 300 m/s with a range of x=9177, y = 0
-        traj = pm.find_trajectory(9177.4459168013527, 0, 300.)
-        assert_almost_equal(traj, 45., 5)
-
-        # Test for theta != 0
-        # Assume parabolic path passes through known peak height.
-        # peak height = v_0y ** 2 / 2 / g
-        # the angle needs to be 45 degrees for a projectile passing
-        # through x = 9177 / 2, arctan(peak_height / 9177 * 2)
-        peak_height = (300 * np.sin(np.radians(45.))) ** 2 / 2. / constants.g
-        assert_almost_equal(peak_height, 2294.3614792003382)
-        theta = np.degrees(np.arctan(peak_height / 9177.4459168013527 * 2.))
-
-        traj = pm.find_trajectory(9177.4459168013527 / 2., theta, 300.)
-        assert_almost_equal(traj, 45., 5)
-
-    def test_parabola_line_intersection_point(self):
-        traj = pm.find_trajectory(3, -0.62, 300.)
-
-        res = pm.parabola_line_intersection_point(3, -0.62, traj, 300, 0)
-        assert_almost_equal(res[3], -0.6293646114131306)
-        assert_almost_equal(res[2], 0)
-        assert_almost_equal(res[1], pm.y_deflection(traj, 300, 3))
-        assert_almost_equal(res[0], 3)
-
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/test/test_platypusnexus.py

@@ -1,311 +1,0 @@
-import os
-import numbers
-import warnings
-
-import pytest
-import numpy as np
-from numpy.testing import (assert_almost_equal, assert_, assert_equal,
-                           assert_array_less, assert_allclose)
-import h5py
-
-import refnx.reduce.platypusnexus as plp
-from refnx.reduce import PlatypusReduce, PlatypusNexus, basename_datafile
-from refnx.reduce.peak_utils import gauss
-from refnx.reduce.platypusnexus import (fore_back_region, EXTENT_MULT,
-                                        PIXEL_OFFSET, create_detector_norm)
-
-
-class TestPlatypusNexus(object):
-
-    @pytest.fixture(autouse=True)
-    def setup_method(self, tmpdir):
-        self.pth = os.path.dirname(os.path.abspath(__file__))
-
-        self.f113 = PlatypusNexus(os.path.join(self.pth,
-                                               'PLP0011613.nx.hdf'))
-        self.f641 = PlatypusNexus(os.path.join(self.pth,
-                                               'PLP0011641.nx.hdf'))
-        self.cwd = os.getcwd()
-
-        self.tmpdir = tmpdir.strpath
-        os.chdir(self.tmpdir)
-        return 0
-
-    def teardown_method(self):
-        os.chdir(self.cwd)
-
-    def test_chod(self):
-        flight_length = self.f113.chod()
-        assert_almost_equal(flight_length[0], 7141.413818359375)
-        assert_almost_equal(flight_length[1], 808)
-
-        flight_length = self.f641.chod(omega=1.8, twotheta=3.6)
-        assert_almost_equal(flight_length[0], 7146.3567785516016)
-        assert_almost_equal(flight_length[1], 808)
-
-    def test_phase_angle(self):
-        # TODO. Add more tests where the phase_angle isn't zero.
-        phase_angle, master_opening = self.f641.phase_angle()
-        assert_almost_equal(phase_angle, 0)
-        assert_almost_equal(master_opening, 1.04719755)
-
-    def test_background_subtract_line(self):
-        # checked each step of the background subtraction with IGOR
-        # so this test background correction should be correct.
-
-        # create some test data
-        xvals = np.linspace(-10, 10, 201)
-        yvals = np.ceil(gauss(xvals, 0, 100, 0, 1) + 2 * xvals + 30)
-
-        # add some reproducible random noise
-        np.random.seed(1)
-        yvals += np.sqrt(yvals) * np.random.randn(yvals.size)
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/test/test_rebin.py

@@ -1,239 +1,0 @@
-"""
-Testing rebin histogram values.
-"""
-
-import numpy as np
-from numpy.random import uniform
-from numpy.testing import (assert_allclose, assert_equal)
-import uncertainties.unumpy as unp
-import refnx.reduce.rebin as rebin
-
-
-class TestRebin(object):
-    def setup_method(self):
-        pass
-
-    # -----------------------------------------------------------------------#
-    #  Tests for piecewise continuous rebinning
-    # -----------------------------------------------------------------------#
-    def test_x2_same_as_x1(self):
-        """
-        x2 same as x1
-        """
-        # old size
-        m = 6
-
-        # new size
-        n = 6
-
-        # bin edges
-        x_old = np.linspace(0., 1., m + 1)
-        x_new = np.linspace(0., 1., n + 1)
-
-        # some arbitrary distribution
-        y_old = 1. + np.sin(x_old[:-1] * np.pi) / np.ediff1d(x_old)
-
-        # rebin
-        y_new = rebin.rebin(x_old, y_old, x_new)
-
-        assert_allclose(y_new, y_old)
-
-    def test_x2_surrounds_x1(self):
-        """
-        x2 range surrounds x1 range
-        """
-        # old size
-        m = 2
-
-        # new size
-        n = 3
-
-        # bin edges
-        x_old = np.linspace(0., 1., m + 1)
-        x_new = np.linspace(-0.1, 1.2, n + 1)
-
-        # some arbitrary distribution
-        y_old = 1. + np.sin(x_old[:-1] * np.pi) / np.ediff1d(x_old)
-
-        # rebin
-        y_new = rebin.rebin(x_old, y_old, x_new)
-
-        # compute answer here to check rebin
-        y_old_ave = y_old / np.ediff1d(x_old)
-        y_new_here = [y_old_ave[0] * (x_new[1] - 0.),
-                      y_old_ave[0] * (x_old[1] - x_new[1]) +
-                      y_old_ave[1] * (x_new[2] - x_old[1]),
-                      y_old_ave[1] * (x_old[-1] - x_new[-2])]
-
-        assert_allclose(y_new, y_new_here)
-        assert_allclose(y_new.sum(), y_old.sum())
-
-    def test_x2_surrounds_x1_2(self):
-        """
-        x2 has some bins that span several x1 bins
-        Also tests uncertainty propagation. Values calculated using
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reduce/xray.py

@@ -1,225 +1,0 @@
-from __future__ import division
-import numpy as np
-import refnx.util.general as general
-import refnx.util.ErrorProp as EP
-import xml.etree.ElementTree as et
-# from refnx.dataset import reflectdataset
-
-# mm
-XRR_BEAMWIDTH_SD = 0.019449
-
-
-def reduce_xrdml(f, bkg=None, scale=1, sample_length=None):
-    """
-    Reduces a Panalytical XRDML file
-
-    Parameters
-    ----------
-    f: file-like object or string
-        The specular reflectivity (XRDML) file of interest
-    bkg: list
-        A list of file-like objects or strings that contain background
-        measurements. The background is assumed to have the same number of
-        points as the specular reflectivity curve.  The backgrounds are
-        averaged and subtracted from the specular reflectivity
-    scale: float
-        The direct beam intensity (cps)
-    sample_length: None or float
-        If None then no footprint correction is done. Otherwise the transverse
-        footprint of the sample (mm).
-
-    Returns
-    -------
-    specular_q, specular_r, specular_dr: np.ndarray
-        The specular reflectivity as a function of momentum transfer, Q.
-    """
-
-    spec = parse_xrdml_file(f)
-
-    reflectivity = spec['intensities'] / spec['count_time']
-    reflectivity_s = np.sqrt(reflectivity) / spec['count_time']
-
-    # do the background subtraction
-    if bkg is not None:
-        bkgds = [parse_xrdml_file(fi) for fi in bkg]
-
-        bkgd_refs = np.r_[[bkgd['intensities'] for bkgd in bkgds]]
-        bkgd_refs_s = np.r_[[np.sqrt(bkgd['intensities']) / bkgd['count_time']
-                             for bkgd in bkgds]]
-        bkgd_refs_var = bkgd_refs_s ** 2
-        weights = 1. / bkgd_refs_var
-        numerator = np.sum(bkgd_refs * weights, axis=0)
-        denominator = np.sum(weights, axis=0)
-
-        total_bkgd = numerator / denominator
-        total_bkgd_s = np.sqrt(1 / denominator)
-
-        reflectivity, reflectivity_s = EP.EPsub(reflectivity,
-                                                reflectivity_s,
-                                                total_bkgd,
-                                                total_bkgd_s)
-
-    # work out the Q values
-    qx, qy, qz = general.q2(spec['omega'],
-                            spec['twotheta'],
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reflect/spline.py

@@ -1,195 +1,0 @@
-from __future__ import division
-import numpy as np
-
-from scipy.interpolate import PchipInterpolator as Pchip
-
-from refnx.reflect import Structure, Component
-from refnx.analysis import (Parameter, Parameters,
-                            possibly_create_parameter)
-
-
-EPS = np.finfo(float).eps
-
-
-class Spline(Component):
-    """
-    Freeform modelling of the real part of an SLD profile using spline
-    interpolation.
-    """
-
-    def __init__(self, extent, vs, dz, left, right, solvent, name='',
-                 interpolator=Pchip, zgrad=True, microslab_max_thickness=1):
-        """
-        Parameters
-        ----------
-        extent : float or Parameter
-            Total extent of spline region
-        vs : Sequence of float/Parameter
-            the real part of the SLD values of each of the knots.
-        dz : Sequence of float/Parameter
-            the lateral offset between successive knots.
-        left : refnx.reflect.Component
-            The Component to the left of this Spline region.
-        right : refnx.reflect.Component
-            The Component to the right of this Spline region.
-        solvent : refnx.reflect.SLD
-            An SLD instance representing the solvent
-        name : str
-            Name of component
-        interpolator : scipy.interpolate Univariate Interpolator, optional
-            Which scipy.interpolate Univariate Interpolator to use.
-        zgrad : bool, optional
-            If true then extra control knots are placed outside this spline
-            with the same SLD as the materials on the left and right. With a
-            monotonic interpolator this guarantees that the gradient is zero
-            at either end of the interval.
-        microslab_max_thickness : float
-            Maximum size of the microslabs approximating the spline.
-
-        Notes
-        -----
-        This spline component only generates the real part of the SLD (thereby
-        assuming that the imaginary part is negligible).
-        The sequence dz are the lateral offsets of the knots normalised to a
-        unit interval [0, 1]. The reason for using lateral offsets is
-        so that the knots are monotonically increasing in location. When each
-        dz offset is turned into a Parameter it is given bounds in [0, 1].
-        Thus with an extent of 500, and dz = [0.1, 0.2, 0.2], the knots will be
-        at [0, 50, 150, 250, 500]. Notice that there are two extra knots for
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/reflect/test/gsmear.py

@@ -1,36 +1,0 @@
-from __future__ import division
-import numpy as np
-from scipy.signal import fftconvolve
-from scipy.interpolate import interp1d
-from refnx.reflect import reflectivity
-
-
-def res(qq, layer, resolution=5):
-    resolution /= 100
-    gaussnum = 51
-    gaussgpoint = (gaussnum - 1) / 2
-
-    def gauss(x, s):
-        return 1. / s / np.sqrt(2 * np.pi) * np.exp(-0.5 * x**2 / s / s)
-
-    lowQ = np.min(qq)
-    highQ = np.max(qq)
-    if lowQ <= 0:
-        lowQ = 1e-6
-
-    start = np.log10(lowQ) - 6 * resolution / 2.35482
-    finish = np.log10(highQ * (1 + 6 * resolution / 2.35482))
-    interpnum = np.round(np.abs(1 * (np.abs(start - finish)) /
-                                (1.7 * resolution / 2.35482 / gaussgpoint)))
-    xtemp = np.linspace(start, finish, int(interpnum))
-
-    gauss_x = np.linspace(-1.7 * resolution, 1.7 * resolution, gaussnum)
-    gauss_y = gauss(gauss_x, resolution / (2 * np.sqrt(2 * np.log(2))))
-
-    rvals = reflectivity(np.power(10, xtemp), layer)
-    smeared_rvals = fftconvolve(rvals, gauss_y, mode='same')
-    interpolator = interp1d(np.power(10, xtemp), smeared_rvals)
-
-    smeared_output = interpolator(qq)
-    smeared_output /= np.sum(gauss_y)
-    return smeared_output

### 2018-08-15 src/data/refnx-0.0.15/refnx/reflect/test/test_structure.py

@@ -1,117 +1,0 @@
-import pickle
-
-import numpy as np
-from numpy.testing import (assert_almost_equal, assert_equal, assert_,
-                           assert_allclose, assert_raises)
-
-from refnx.reflect import (SLD, Structure, Spline, Slab)
-from refnx.reflect.structure import _profile_slicer
-from refnx.analysis import Parameter
-
-
-class TestStructure(object):
-
-    def setup_method(self):
-        self.air = SLD(0, name='air')
-        self.sio2 = SLD(3.47, name='sio2')
-        self.d2o = SLD(6.36, name='d2o')
-        self.h2o = SLD(-0.56, name='h2o')
-        self.s = self.air | self.sio2(100, 5) | self.d2o(0, 4)
-
-    def test_structure_construction(self):
-        # structures are constructed by or-ing slabs
-        # test that the slab representation is correct
-        assert_equal(self.s.slabs, np.array([[0, 0, 0, 0, 0],
-                                             [100, 3.47, 0, 5, 0],
-                                             [0, 6.36, 0, 4, 0]]))
-
-        # slabs have solvent penetration
-        self.s.solvent = self.d2o
-        self.s[1] = SLD(3.47 + 1j, name='sio2')(100, 5)
-        self.s[1].vfsolv.value = 0.9
-        sld = 6.36 * 0.9 + 0.1 * 3.47
-        sldi = 1 * 0.1
-        assert_almost_equal(self.s.slabs, np.array([[0, 0, 0, 0, 0],
-                                                    [100, sld, sldi, 5, 0.9],
-                                                    [0, 6.36, 0, 4, 0]]))
-
-    def test_pickle(self):
-        # need to be able to pickle and unpickle structure
-        pkl = pickle.dumps(self.s)
-        unpkl = pickle.loads(pkl)
-        assert_(isinstance(unpkl, Structure))
-        for param in unpkl.parameters.flattened():
-            assert_(isinstance(param, Parameter))
-
-    def test_sld_profile(self):
-        # check that it runs
-        z, sld_profile = self.s.sld_profile()
-
-        z, sld_profile = self.s.sld_profile(np.linspace(-100, 100, 100))
-        assert_equal(min(z), -100)
-        assert_equal(max(z), 100)
-
-    def test_reflectivity(self):
-        q = np.linspace(0.005, 0.3, 200)
-        self.s.reflectivity(q)
-
-    def test_sld_slicer(self):
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/util/general.py

@@ -1,701 +1,0 @@
-#!/usr/bin/python
-"""
-Functions for various calculations related to reflectometry
-"""
-from __future__ import division
-
-import numpy as np
-from scipy import stats, integrate, constants, optimize
-
-# h / m = 3956
-K = constants.h / constants.m_n * 1.e10
-
-
-def div(d1, d2, L12=2859):
-    """
-    Calculate the angular resolution for a set of collimation conditions
-
-    Parameters
-    ----------
-    d1 : float
-        slit 1 opening
-    d2 : float
-        slit 2 opening
-    L12 : float
-        distance between slits
-
-    Returns
-    -------
-    dtheta, alpha, beta
-        dtheta is the FWHM of the Gaussian approximation to the trapezoidal
-        resolution function
-        alpha is the angular divergence of the penumbra
-        beta is the angular divergence of the umbra
-
-    When calculating dtheta / theta values for resolution, then dtheta is the
-    value you need to use.
-    See equations 11-14 in [1]_.
-
-    .. [1] de Haan, V.-O.; de Blois, J.; van der Ende, P.; Fredrikze, H.;
-    van der Graaf, A.; Schipper, M.; van Well, A. A. & J., v. d. Z. ROG, the
-    neutron reflectometer at IRI Delft Nuclear Instruments and Methods in
-    Physics Research A, 1995, 362, 434-453
-    """
-    divergence = 0.68 * 0.68 * (d1 ** 2 + d2 ** 2) / (L12 ** 2)
-    alpha = (d1 + d2) / 2. / L12
-    beta = abs(d1 - d2) / 2. / L12
-    return np.degrees(np.sqrt(divergence)), np.degrees(alpha), np.degrees(beta)
-
-
-def q(angle, wavelength):
-    """
-    Calculate Q given angle of incidence and wavelength
-
-    Parameters
-    ----------
-    angle: float
-        angle of incidence (degrees)
-    wavelength: float
-        wavelength of radiation (Angstrom)
-
-    Returns
-    -------
-    Q: float
-        Momentum transfer (A**-1)
-    """
-    return 4 * np.pi * np.sin(np.radians(angle)) / wavelength
-
-
-def q2(omega, twotheta, phi, wavelength):
-    """
-    convert angles and wavelength (lambda) to Q vector.
-
-    Parameters
-    ----------
-    omega: float
-        angle of incidence of beam (in xy plane)
-    twotheta: float
-        angle between direct beam and projected reflected beam onto yz plane
-    phi: float
[…]

### 2018-08-15 src/data/refnx-0.0.15/refnx/util/test/test_ErrorProp.py

@@ -1,79 +1,0 @@
-from __future__ import division
-
-import refnx.util.ErrorProp as EP
-import numpy as np
-import os
-from numpy.testing import assert_equal, assert_array_almost_equal
-
-
-class TestErrorProp(object):
-
-    def setup_method(self):
-        pass
-
-    def test_add(self):
-        c, dc = EP.EPadd(1.1, 0.5, 1.1, 0.5)
-        assert_equal(2.2, c)
-        assert_equal(np.sqrt(0.5), dc)
-
-    def test_sub(self):
-        c, dc = EP.EPsub(1.1, 0.5, 1.1, 0.5)
-        assert_equal(0, c)
-        assert_equal(np.sqrt(0.5), dc)
-
-    def test_mul(self):
-        c, dc = EP.EPmul(1.1, 0.5, 1.1, 0.5)
-        assert_array_almost_equal(1.21, c)
-        assert_equal(np.sqrt(0.605), dc)
-
-        c, dc = EP.EPmul(0, 0.5, 1.1, 0.5)
-        assert_equal(0, c)
-        assert_equal(0.55, dc)
-
-    def test_div(self):
-        c, dc = EP.EPdiv(1.1, 0.5, 1.1, 0.5)
-        assert_array_almost_equal(1, c)
-        assert_array_almost_equal(0.642824346533225, dc)
-
-        c, dc = EP.EPdiv(0, 0.5, 1.1, 0.5)
-        assert_equal(0, c)
-        assert_array_almost_equal(0.45454545454545453, dc)
-
-    def test_pow(self):
-        c, dc = EP.EPpow(1.1, 0.5, 1.1, 0.5)
-        assert_array_almost_equal(1.1105342410545758, c)
-        assert_array_almost_equal(0.5577834505363953, dc)
-
-        c, dc = EP.EPpow(1.1, 0.5, 1.1, 0)
-        assert_array_almost_equal(1.1105342410545758, c)
-        assert_array_almost_equal(0.5552671205272879, dc)
-
-    def test_log(self):
-        c, dc = EP.EPlog(1.1, 0.5)
-        assert_array_almost_equal(0.09531017980432493, c)
-        assert_array_almost_equal(0.45454545454545453, dc)
-
-    def test_log10(self):
-        c, dc = EP.EPlog10(1.1, 0.5)
-        assert_array_almost_equal(0.04139268515822508, c)
-        assert_array_almost_equal(0.19740658268329625, dc)
-
-    def test_exp(self):
[…]

### 2018-08-15 src/data/refnx-0.0.15/slim/model.py

@@ -1,344 +1,0 @@
-from __future__ import division
-import os.path
-import os
-import logging
-from copy import copy
-
-from PyQt5 import QtCore
-import numpy as np
-
-from refnx._lib import preserve_cwd
-from refnx.dataset import ReflectDataset
-from refnx.reduce import (number_datafile, PlatypusReduce, basename_datafile,
-                          PlatypusNexus)
-
-
-reducer_entry = [('use', False), ('scale', 1.), ('reflect-1', ''),
-                 ('reflect-2', ''), ('reflect-3', ''), ('direct-1', ''),
-                 ('direct-2', ''), ('direct-3', ''), ('flood', '')]
-default_reducer_entry = {re[0]: re[1] for re in reducer_entry}
-
-
-class ReductionState(object):
-    """
-    Reduces multiple reflectometry datafiles. Attributes control how the
-    reduction proceeds.
-    """
-    def __init__(self, manual_beam_finder=None):
-        super(ReductionState, self).__init__()
-
-        # Each entry specifies the scale factor, whether the file is used for
-        # reduction and the reflected and direct beam runs
-        self.reduction_entries = {}
-
-        self.default_reduction_options = {
-            'low_wavelength': (2.5, float),
-            'high_wavelength': (19, float),
-            'rebin_percent': (2., float),
-            'expected_centre': (123., float),
-            'manual_beam_find': (False, bool),
-            'background_subtraction': (True, bool),
-            'monitor_normalisation': (True, bool),
-            'save_offspecular': (True, bool),
-            'save_spectrum': (True, bool),
-            'streamed_reduction': (False, bool)}
-
-        # the time slices for streamed reduction
-        self.stream_start = 0
-        self.stream_end = 3600
-        self.stream_duration = 30
-
-        # where the data, streamed data and output files are located
-        self.data_directory = ''
-        self.streamed_directory = ''
-        self.output_directory = ''
-
-        self.manual_beam_finder = manual_beam_finder
-
-        for attr, val in self.default_reduction_options.items():
-            setattr(self, attr, val[0])
-
-        self.peak_pos = (90, 5)
-
-        self.save_state_path = None
-
-    def __getstate__(self):
-        d = self.__dict__
-        e = copy(d)
-        e.pop('manual_beam_finder')
-        return e
-
-    @preserve_cwd
-    def reducer(self, callback=None):
-        """
-        Reduce all the entries in reduction_entries
-
-        Parameters
-        ----------
-        callback : callable
[…]

### 2018-08-15 src/data/refnx-0.0.15/src/refcalc.cpp

@@ -1,408 +1,0 @@
-/*
-    refcalc.h
-
-    *Calculates the specular (Neutron or X-ray) reflectivity from a stratified
-    series of layers.
-    @Copyright, Andrew Nelson 2014.
- */
-
-#include "refcalc.h"
-#include <math.h>
-#include "MyComplex.h"
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <cstdio>
-
-#ifdef _WIN32
-    #include <windows.h>
-    #include <process.h>
-#endif
-#if defined (__unix__) || (defined (__APPLE__) && defined (__MACH__))
-    #include <unistd.h>
-    #include <pthread.h>
-    #define HAVE_PTHREAD_H
-#endif
-
-#ifdef _OPENMP
-   #include <omp.h>
-#endif
-
-#define NUM_CPUS 4
-#define PI 3.141592653589793
-
-using namespace MyComplexNumber;
-
-#ifdef __cplusplus
-extern "C" {
-#endif
-
-
-void* malloc2d(int ii, int jj, int sz){
-    void** p;
-    size_t sz_ptr_array;
-    size_t sz_elt_array;
-    size_t sz_allocation;
-    long i = 0;
-    char *c = NULL;
-
-    sz_ptr_array = ii * sizeof(void*);
-    sz_elt_array = jj * sz;
-    sz_allocation = sz_ptr_array + ii * sz_elt_array;
-
-    p = (void**) malloc(sz_allocation);
-    if (p == NULL)
-        return p;
-    memset(p, 0, sz_allocation);
-
-    c = ((char*) p) + sz_ptr_array;
-    for (i = 0; i < ii; ++i)
-    {
-        //*(p+i) = (void*) ((long)p + sz_ptr_array + i * sz_elt_array);
-        p[i] = (void*) (c + i * sz_elt_array);
-    }
-    return p;
-}
-
-
-void AbelesCalc_ImagAll(int numcoefs,
-                        const double *coefP,
-                        int npoints,
-                        double *yP,
-                        const double *xP,
-                        int workers){
-        int j;
-        double scale, bkg;
-        double num = 0, den = 0, answer = 0;
-
-        MyComplex super;
-        MyComplex sub;
-        MyComplex oneC = MyComplex(1, 0);
-        MyComplex MRtotal[2][2];
-        MyComplex MI[2][2];
-        MyComplex temp2[2][2];
-        MyComplex qq2;
[…]

### 2018-08-15 src/data/refnx-0.0.15/src/refcalc.h

@@ -1,85 +1,0 @@
-/*
-    refcalc.h
-
-    *Calculates the specular (Neutron or X-ray) reflectivity from a stratified
-    series of layers.
-    @Copyright, Andrew Nelson 2014.
- */
-
-
-#ifdef __cplusplus
-extern "C" {
-#endif
-
-/*
-    reflect uses the Abeles matrix method to calculate specular reflectivity.
-    The system is assumed to consist of a series of uniformly dense layers
-    (slabs). The radiation is incident through the fronting medium, leaving
-    through the backing medium.
-
-    Parameters
-    ----------
-
-    numcoefs - the number of parameters held in the coefP array. This should be
-    4 * N + 8 values long, were N is the number of layers.
-
-    coefP - an array holding the parameters.  See below for a more detailed
-    description
-
-    npoints - the number of points in the yP and xP arrays
-
-    yP - this user supplied array is filled by the reflect function.  It must be
-    npoints long
-
-    xP - array containing the Q (momentum transfer) points. It has units Å**-1.
-    The array is npoints long
-
-    threads - specifies the number of parallel threads to use.
-
-
-    Detailed description of the entries in coefP
-    --------------------------------------------
-    coefP[0] - the number of layers. Should be an integer.
-               4 * coefP[0] + 8 == numcoefs
-
-    coefP[1] - scale factor.  The calculated reflectivity is multiplied by this
-    value. i.e. yP = scale * ref + background
-
-    coefP[2] - fronting SLD, real part. (10**-6 Å**-2)
-
-    coefP[3] - fronting SLD, imaginary part. (10**-6 Å**-2)
-
-    coefP[4] - backing SLD, real part. (10**-6 Å**-2)
-
-    coefP[5] - backing SLD, imaginary part. (10**-6 Å**-2)
-
-    coefP[6] - background.  A constant value added to all the reflectivity
-    points.
-
-    coefP[7] - roughness between backing medium and bottom most layer (Å).  If
-    there are no layers, the roughness between the fronting and backing media.
-
-    coefP[4 * M + 8] - thickness of layer M, with M = 0, ... N - 1. (Å)
-
-    coefP[4 * M + 9] - SLD of layer M, real part (10**-6 Å**-2)
-
-    coefP[4 * M + 10] - SLD of layer M, imaginary part (10**-6 Å**-2)
-
-    coefP[4 * M + 11] - roughness between layer M - 1 / M (Å)
-*/
[…]

### 2018-08-15 src/tools/helper.py

@@ -1,0 +1,7 @@
+import numpy as np
+
+def data_cutoff(dataset, cutoff):
+    dataset.y = dataset.y[:np.argmax(dataset.x>cutoff)]
+    dataset.y_err = dataset.y_err[:np.argmax(dataset.x>cutoff)]
+    dataset.x = dataset.x[:np.argmax(dataset.x>cutoff)]
+    return dataset

### 2018-08-15 src/visualization/plotcorner-new.py

@@ -1,0 +1,92 @@
+
+# coding: utf-8
+
+# In[4]:
+
+
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import seaborn as sns; sns.set('paper', palette='colorblind')
+import numpy as np
+from refnx import analysis
+import sys
+
+
+# In[5]:
+
+
+f = sys.argv[1] #'../../output/dlpc_highconc_chain.txt'
+tail_length = float(sys.argv[2]) #1.54 + 1.265 * 12
+vole = float(sys.argv[3]) #667.)
+flatchain = analysis.curvefitter.load_chain(f)
+figures_dir = sys.argv[5] + '/reports/figures/'
+lab = sys.argv[4] #'dlpc'
+
+
+# In[6]:
+
+
+# plotting pdfs
+import corner
+
+mpl.rcParams['axes.labelsize']=22
+mpl.rcParams['xtick.labelsize']=14
+mpl.rcParams['ytick.labelsize']=14
+
+
+label=['$V_t$/Å$^3$', '$V_h$/Å$^3$', '$d_h$/Å', 'θ$_t$/°', r'ϕ$_h/\times10^{-2}$', 'σ$_{t,h,s}$/Å']
+
+new_flat = np.zeros((flatchain.shape[0] * flatchain.shape[1], 6))
+
+new_flat[:, 0] = list(flatchain[:, :, 3].flatten())
+new_flat[:, 1] = list(flatchain[:, :, 4].flatten())
+new_flat[:, 3] = list(np.rad2deg(np.arccos(flatchain[:, :, 2].flatten())))
+tail3 = flatchain[:, :, 2].flatten() * tail_length
+solh3 = 1 - (flatchain[:, :, 4].flatten() / flatchain[:, :, 3].flatten()) * (tail3 / flatchain[:, :, 1].flatten())
+new_flat[:, 4] = list(solh3 * 100)
+new_flat[:, 5] = list(flatchain[:, :, 5].flatten())
+new_flat[:, 2] = list(flatchain[:, :, 1].flatten())
+
+plt1 = corner.corner(new_flat, max_n_ticks=3, labels=label)
+plt.savefig('{}{}3_all_corner.png'.format(figures_dir, lab), dpi=600)
+plt.close()
+
+new_flat = np.zeros((flatchain.shape[0] * flatchain.shape[1], 6))
+
+new_flat[:, 0] = list(flatchain[:, :, 3].flatten())
[…]

### 2018-08-15 src/visualization/plotcorner.py

@@ -16,11 +16,10 @@ import sys
 
 
 f = sys.argv[1] #'../../output/dlpc_highconc_chain.txt'
-tail_length = float(sys.argv[2]) #1.54 + 1.265 * 12
-vole = float(sys.argv[3]) #667.)
+tail_length = 1.54 + 1.265 * int(sys.argv[2])
 flatchain = analysis.curvefitter.load_chain(f)
-figures_dir = sys.argv[5] + '/reports/figures/'
-lab = sys.argv[4] #'dlpc'
+figures_dir = '../../reports/figures/'
+lab = sys.argv[3] #'dlpc'
 
 
 # In[6]:
@@ -32,41 +31,69 @@ import corner
 mpl.rcParams['axes.labelsize']=22
 mpl.rcParams['xtick.labelsize']=14
 mpl.rcParams['ytick.labelsize']=14
+mpl.rcParams['axes.linewidth'] = 1
+mpl.rcParams['axes.edgecolor'] = 'k'
+
 
 label=['$V_t$/Å$^3$', '$V_h$/Å$^3$', '$d_h$/Å', 'θ$_t$/°', r'ϕ$_h/\times10^{-2}$', 'σ$_{t,h,s}$/Å']
 
 new_flat = np.zeros((flatchain.shape[0] * flatchain.shape[1], 6))
 
-new_flat[:, 0] = list(flatchain[:, :, 2].flatten())
-new_flat[:, 1] = list(flatchain[:, :, 3].flatten())
-new_flat[:, 3] = list(np.rad2deg(np.arccos(flatchain[:, :, 1].flatten())))
-new_flat[:, 4] = list(flatchain[:, :, 5].flatten() * 100)
-new_flat[:, 5] = list(flatchain[:, :, 4].flatten())
-new_flat[:, 2] = list((flatchain[:, :, 3].flatten() * tail_length * flatchain[:, :, 1].flatten()))
-new_flat[:, 2] = new_flat[:, 2] / (flatchain[:, :, 2].flatten())
-a = 1 - flatchain[:, :, 5].flatten()
-new_flat[:, 2] = new_flat[:, 2] / a
-
+new_flat[:, 0] = list(flatchain[:, :, 3].flatten())
+new_flat[:, 1] = list(flatchain[:, :, 4].flatten())
+new_flat[:, 3] = list(np.rad2deg(np.arccos(flatchain[:, :, 2].flatten())))
[…]

### 2018-08-15 src/visualization/plotrefn.py

@@ -45,7 +45,7 @@ def plotsld(data, gs, offset, label):
     for i in range(2, data.shape[0]):
         sld = data[i]
         ax.plot(z, sld + offset, linewidth=2, alpha=0.05)
-    ax.text(0.80, 0.9, '(' + label + ')', fontsize=30, transform=ax.transAxes)
+    ax.text(0.81, 0.90, '(' + label + ')', fontsize=44, transform=ax.transAxes)
     ax.set_xlabel(r'$z$/Å')
     ax.set_ylabel(r'SLD/$10^{-6}$Å$^{-2}$')
     return plt
@@ -59,12 +59,20 @@ def plothist(tohist, gs, label, name):
     ax.set_xticks([a[0], a[1], a[2]])
     ax.set_xticklabels(['{:.1f}'.format(a[0]), '{:.1f}'.format(a[1]), '{:.1f}'.format(a[2])])
 
-mpl.rcParams['axes.labelsize']=28
-mpl.rcParams['xtick.labelsize']=18
-mpl.rcParams['ytick.labelsize']=18
+mpl.rcParams['axes.labelsize']=44
+mpl.rcParams['xtick.labelsize']=32
+mpl.rcParams['ytick.labelsize']=32
+mpl.rcParams['grid.linestyle'] = ''
+mpl.rcParams['axes.grid'] = True
+mpl.rcParams['axes.facecolor'] = 'w'
+mpl.rcParams['axes.linewidth'] = 1
+mpl.rcParams['axes.edgecolor'] = 'k'
+mpl.rcParams['xtick.bottom'] = True
+mpl.rcParams['ytick.left'] = True
+
 
 l = [1, 10, 100, 1000, 10000]
-fig = plt.figure(figsize=(15, 6))
+fig = plt.figure(figsize=(20, 7.5))
 gs = mpl.gridspec.GridSpec(1, 2, width_ratios=[2, 1]) 
 k = 0
 for i in range(0, int(n)-4, 2):
@@ -77,7 +85,7 @@ for i in range(1, int(n)-3, 2):
     plotsld(data, gs[0, 1], f, sys.argv[n-2])
     f += 5
 plt.tight_layout()
-plt.savefig('{}{}_all_data.png'.format(figures_dir, sys.argv[n-1]), dpi=600)
+plt.savefig('{}{}_all_data.pdf'.format(figures_dir, sys.argv[n-1]))
 plt.close()
 #plt.show()
 

### 2018-08-16 reports/paper.tex
fix some typos

@@
 \begin{equation}
-\text{SLD}_i = \frac{b_i}{V_i}(\phi_i) + \text{SLD}_{s}(1-\phi_i),
+\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}(\phi_i),
 \end{equation}
@@
 \subsection{Effect of compression on solvent concentration}
-In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increase there is a corresponding decrease in the percentage solvent present in the lipid head layer.
+In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer.
 This can be rationalised by considering when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.

### 2018-08-29 reports/esi.tex
nearly at the sending to people stage

@@
 \usepackage{hyperref}
+\usepackage{siunitx}
 \author{Andrew R. McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
@@
 \maketitle
+\section{Grazing incident X-ray diffraction (GIXD)}
+GIXD was measured for DPPC and DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius} (and \SI{7}{\celsius} for DMPC), and are shown in Figures \ref{fig:dppcgixd}-\ref{fig:dmpcgixd7}.
+All figures contain an artifact from the X-ray beam interacting with the Teflon of the Langmuir trough.
+However, in figures \ref{fig:dppcgixd} and \ref{fig:dmpcgixd7} it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid phase at all surface pressures measured.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/206041}
+	\caption{The GIXD pattern for DPPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, the axes at in units of \si{\per\angstrom}.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dppcgixd}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/206151}
+	\caption{The GIXD pattern for DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, the axes at in units of \si{\per\angstrom}.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpcgixd}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/206161}
+	\caption{The GIXD pattern for DMPC at \SI{30}{\milli\newton\per\meter} at \SI{7}{\celsius}, the axes at in units of \si{\per\angstrom}.
+Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\label{fig:dmpcgixd7}
+\end{figure}
 \section{Probability distribution functions}

### 2018-08-29 reports/paper.tex
nearly at the sending to people stage

@@
-%%\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %This is the LaTeX ARTICLE template for RSC journals
@@
 Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
-In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a managageable level) it was not possible to use a Langmuir trough.
+In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
 Instead, small Delrin adsorption troughs were used that did not have controlable barriers.
-This resulted in no control over the surface pressure of the measurement and therefore it was not possible to co-refine NR contrasts.
+So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.
 
@@
 
-To allow for the use of a chemically-consistant model, where the lipid component volumes were allowed to vary, the Python library refnx\cite{Nelson2018} as used.
-This software allows the inclusion of a custom model from which the parameters fed into the Abel\`{e}s model for the reflection of light at a given number of stratified interfaces,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained.
+In this work we would therefore like to use a model that does not assume the molecular volume while remaining physical meaningful.
+To do this we have allowed the lipid component volumes to vary while constraining the overall system to be self-consistent across multiple different measurements.
+To do this we have used the Python library refnx\cite{Nelson2018}.
+This software allows the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s reflectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}).
 This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under CC-BY.\cite{mccluskey_2018}
 
-This chemically-consistent model involves two layers; the head layer at the interface with the solvent and tail layer at the interface with the air.
-The head components have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head component multiplied by the classical radius of the electron for XRR or the summation of the neutron scattering lengths for NR), and a component volume, $V_h$.
+Our chemically-consistent model is made up of two layers to define the lipid monolayer; the head layer at the interface with the solvent and tail layer at the interface with the air.
+The head components have a calculated scattering length, $b_h$, (found as a summation of the X-ray or neutron atomic scattering lengths), and a component volume, $V_h$.
 These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
-The tail components also have a calculated scattering length, $b_t$, and a component volume, $V_t$.
-In this work, the thickness of the tail layer, $d_t$, was found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
+The tail components also have a calculated scattering length, $b_t$, roughness, $\sigma_t$, and a component volume, $V_t$.
+We have defined the thickness of the tail layer, $d_t$, in terms of the maximum (all-trans) length of the carbon tail, $t_t$, and the angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
 %
@@
 %
-The was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g.
+This was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g.
 it cannot be thicker than the maximum extended length of the lipid tail.
@@
 %
-where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains either solvent nor air, e.g.
+where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains neither solvent nor air, e.g.
 $\phi_t = 0$.
@@
 %
-Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all interfaces, as there is only a single lipid molecule type in each monolayer.
+Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
+$\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
 Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
 
-In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across the XRR measurments at four surface concentrations.
-The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, this based on the understanding that the increasing surface pressure should not significantly influence the head layer thickness.
+In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations.
+The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, an assumption that is based on our belief that increasing surface pressure should not significantly influence the head layer thickness.
 The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
-The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} due to the nature of the monolayer at the surface pressures resulting in the extended, staggered conformation of the chain being likely.
+The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} since this is the maximum chain length possible and the most likely conformation at the surface pressures studied.
 For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
+Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.
 
@@
 %
-In the second step, the head and tail component volumes, and head layer thickness determined from XRR were used in the refinement of the custom model against the NR measurements.
-Table \ref{tab:invariant} gives the details of the scattering lengths and SLDs used as invariant parameters in the custom model, while the tail chain lengths were the same as for the XRR.
-The definition of the head and tail component volumes, and the head thickness allowed the number of variable parameters to be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.
+In the second step, the head and tail component volumes, and head layer thickness determined from XRR were fixed for the refinement of the custom model against the NR measurements.
+This approach means that the number of variable parameters to fir the NR data can be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.
+Table \ref{tab:invariant} also gives the details of the scattering lengths and SLDs used as invariant parameters for the NR fitting.
 
@@
 This allowed asymmetric confidence intervals to be found for each of the variable parameters.
-However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, e.g.
+However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e.
 they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.
@@
 \ref{equ:tl} and \ref{equ:phih} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
+
+The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure.
+The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}.
+Table \ref{tab:neutron} gives details of the varying parameters at each surface pressure as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
+\ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
 %
@@
 \subsection{Effect of compression on the lipid tail component volumes}
-It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails is significantly lower in the current measurements than found previously, by other techniques.
+It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
 It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
-However, this reduction observed has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elavated surface pressure.
+However, this reduction observed has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elevated surface pressure.
 In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.
@@
 In this work, a single tail component volume was fitted to each lipid for all four surface pressures that were measured.
-This is based on the assumption that at all four surface pressures, the lipids adopt the same phase and therefore any variation in the structure with surface pressure would manifest as a change in the tail thickness, via the chain tilt angle.
+This is based on the assumption, that at all four surface pressures, the lipids adopt the same phase (as discussed in the ESI) and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the chain tilt angle.
 It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail component volumes are also reduced in the current XRR measurements compared to those determined previously.
-The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} However, DMPG presented a small increase in the tail volume, although this may be due to comparison with a previous measurement at a lower temperature.
+The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
+Notably our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
 
@@
 Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids.
-The three lipids with the PC head component are consistant with values of $\sim330$ \AA$^3$, irregardless of tail component.
+The three lipids with the PC head component are consistent with values of $\sim330$ \AA$^3$, regardless of tail component.
 This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
@@
 It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements,\cite{Clifton2012} which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head component may be occuring as a result of interaction with the DES.
+Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements,\cite{Clifton2012} which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
 
 \subsection{Refinement of neutron reflectometry}
-The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure.
-The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}.
-Table \ref{tab:neutron} gives details of the varying parameters at each surface pressure as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
-\ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
-
 The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head component volume is consistant between the pair of measurements for the same system.
 It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
-Futhermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components is also observed in the NR models.
+Futhermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components are consistant with that found in the NR models.
 %
@@
 \section{Conclusions}
-Stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed at the air-DES interface, and chemically-relevant modelling and Bayesian analysis was used to rationalise XRR measurements, allowing for the quantification of the effect that the non-aqueous DES had on their structure.
-The structure of the PC component containing lipids was found to be very similar at the air-DES interface to that at the air-water interface.
-However, the PG component containing lipid was found to have a larger head component volume than observed for the same system in water.
-We propose that this is due to the unfolding of the PG head component arising from the electrostatic screening of the component charges, due to the presence of the charged DES solvent.
-This unfolding may not occur for the PC component to the strong interaction arising from the formal charge of the ammonium group.
+
+For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a non-aqueous liquid surface.
+Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of functional phospholipid monolayers at the air-liquid interface.
+
+A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
+This has the important implication that DES therefore offer the possibility of performing studies of model membranes in the absence of water.
+Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
+However, the fact that the PG component containing lipid did show a significant difference; having a larger head component volume than observed for the same system in water.
+This that the transfer of lipids to a DES is not just a simple substitution of the subphase.
+In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the charged solvent.
 
@@
 Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
-
-Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of functional phospholipid monolayers at the air-liquid interface.
-Therefore, choline chloride:glycerol DES constitutes a novel environment where phospholipid membranes may be investigated.
-These possibilities include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
 

### 2018-08-29 src/visualization/plotref.py

@@ -90,9 +90,7 @@ def plothist(tohist, gs, name):
     ax.set_ylabel('PDF({}-$V_h$)'.format(name))
     ax.set_xlabel('{}-$V_h$/Å$^3$'.format(name))
     ax.set_xticks([a[0], a[1], a[2]])
-    #ax.set_ylim([0, 15000])
     ax.set_xlim([np.min(tohist)-0.01, np.max(tohist)+0.01])
-    #ax.set_yticks([])
     ax.set_xticklabels(['{:.1f}'.format(a[0]), '{:.1f}'.format(a[1]), '{:.1f}'.format(a[2])])
 
 def plotgraph(gs, sp, tails, sols, n1, n2, p1, p2, x1, x2, label):

### 2018-08-31 reports/apssamp.tex
added the prl version

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 %aps,
 prl,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[detect-all]{siunitx}
\usepackage{hyperref}% add hypertext capabilities
\usepackage{xr}
\externaldocument{esi2}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Bayesian determination of the effect of a deep euctectic solvent on the structure of lipid monolayers}% Force line breaks with \\%

\author{Andrew R. McCluskey}
  \thanks{These authors have contributed equally to the work presented within}
  \altaffiliation[Also at ]{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}

\author{Adrian Sanchez-Fernandez}
  \thanks{These authors have contributed equally to the work presented within}
  \altaffiliation[Also at ]{European Spallation Source, SE-211 00 Lund, Sweden}
  \altaffiliation[Present address ]{Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}
\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}

\author{Karen J. Edler}
\email{k.edler@bath.ac.uk}
\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}

\author{Stephen C. Parker}
\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}

\author{Andrew J. Jackson}
  \altaffiliation[Also at ]{Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}

\author{Richard A. Campbell}
  \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France}
\affiliation{Division of Pharmacy and Optometry, University of Manchester, Manchester, UK}

\author{Thomas Arnold}
\email{tom.arnold@esss.se}
  \altaffiliation[Also at ]{ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 OQX, UK; Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK; Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
  Deep eutectic solvents present a novel class of non-aqueous room temperature solvent with tunable properties, that are capable of promoting the self-assembly of surfactant molecules. However, the solvation model in these systems still challenges the classic understanding of amphiphilicity. In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous solvent. Furthermore, we use novel, chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leading to an apparent increase in the volume compared to that observed in water. No such change was observed for the phosphocholine head, indicating that the interaction is head specific.
\begin{description}
\item[Usage]
Electronic Supplementary Information (ESI) available: All datasets, figure file and analysis/plotting scripts, allowing for a fully reproducible analysis of all work presented herein. See DOI: 10.6084/m9.figshare.6661784.
\end{description}
\end{abstract}

\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

Deep eutectic solvents (DES) are a green, sustainable solvent system obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013}.
An extensive hydrogen bonding network is present, allowing the mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
Furthermore, recently DES have indicated the presence of a solvophobic effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer conformations\cite{Sapir2016}.

Phospholipid monolayer formation at the air/liquid interface plays a key role in many biological and technological processes, where the solvent-specific solubility of different components of the phospholipid enables a stable monolayer to form at the interface\cite{Mohwald1990}.
Investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and a non-aqueous media has not been previously reported, to the best of the authors' knowledge.

This work presents the first investigation of the structure of four phospholipid monolayers at the air-DES interface, as determined by chemically-consistent modelling of X-ray reflectometry (XRR) measurements.
Evaluting the interaction of two, chemically distinct, phospholipid heads with this non-aqueous solvent, in addition to the effect of the tail chain length. The analysis was then extended to model complementary neutron reflectometry measurements for two contrasts of DMPC and DPPC at a single surface pressure.

Recent developments in computational resources and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework\cite{Kluyver2016}.
In the area of neutron and X-ray reflectometry data-analysis, the landscape of open-source software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, motofit\cite{Nelson2006}, Aurore\cite{Gerelli2016}, and GenX\cite{Bjorck2007}.

The use of a Python library, such as refnx, enables the implementation custom models that contain chemically-relevant information as well as the application of probability distribution function (PDF) sampling techniques.
The Python library emcee\cite{Foreman-Mackey2013} offers refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method\cite{Goodman2010}.
This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously\cite{Sivia2006}.
Bayesian inference gives an understanding of the PDF for the fitted parameters and therefore estimations of their inverse uncertainties and inter-parameter correlations.

%
\begin{figure}[b]
\includegraphics[width=0.3\textwidth]{figures/head_groups}
\caption{\label{fig:heads} The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC). Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
\end{figure}
%
We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of measurements at different surface concentration.
The model was applied to the study of four phospholipids monolayers by X-ray reflectometry (XRR), namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface.
Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
Instead these parameters, along with the thickness of the phospholipid head layer, $d_h$, were allowed to vary for each lipid.
However, their values were constained to be self-consistent for a single lipid over multiple measurements at different surface pressures.

This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \numrange{320}{360} \AA$^3$, while the phosphatidylglycerol (PG) head is \numrange{289}{291} \AA$^3$ (Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
Furthermore, the effect of pressure, which is not necessarily present for the tail volume values in Table \ref{tab:water}, has been shown to compress the lipid tail volume\cite{Marsh2010,Small1984}, and the need to account for this hydrocarbon compaction according to their phase in the modelling of NR data has recently been demonstrated\cite{Campbell2018}.
%
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.45\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.45\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.45\textwidth]{figures/DMPG_all_data}
	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up. The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity. Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
	\label{fig:lipids}
\end{figure}
%

The custom model for each lipid, fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}, while Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a 95 \% confidence interval, of the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, and the interfacial roughness, $\sigma$ which were free to vary independent of surface pressure, and the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$, for each a single value was fitted for each lipid across all surface pressures.
%
\begin{table}
	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih}. Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
  \begin{ruledtabular}
	\begin{tabular}{ccccc}
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
		$\sigma$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
	\end{tabular}
  \end{ruledtabular}
\end{table}
%

In keeping this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
Furthermore, the thickness of the tail layers agress well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$ \AA\ at 30 mN/m\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=16.7$ \AA\ at 40 mN/m\cite{Helm1987} in water for DPPC.

Figure \ref{fig:lipresults} shows the tail layer thickness increasing with surface pressure, before plateuing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC the plateu can be assumed to be at higher pressures than those studied.
This phenomenon has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
%
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{figures/DLPC_other_data}
	\includegraphics[width=0.45\textwidth]{figures/DMPC_other_data}
	\includegraphics[width=0.45\textwidth]{figures/DPPC_other_data}
	\includegraphics[width=0.45\textwidth]{figures/DMPG_other_data}
	\caption{The PDFs of the head volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl}. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:lipresults}
\end{figure}
%

In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent, $\phi_h$, present in the lipid head layer.
This can be rationalised by considering when the surface pressure is increased, the free volume available between the lipid heads reduces forcing the solvent out of the lipid head layer and into the bulk.
A similar effect has been observed when increasing the surface pressure from 11 mNm$^{-1}$ to 31 mNm$^{-1)}$ for a DMPC/DMPG monolayer at the air-water interface\cite{Bayerl1990}.

When comparing Tables \ref{tab:water} and \ref{tab:liptab} it is clear that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
Such a reduction has been shown previously\cite{Campbell2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
In that work, the optimal value of the tail volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.

In this work, a single tail volume was fitted to each lipid for all four surface pressures that were measured.
This is based on the assumption, that at all four surface pressures, the lipids adopt the same phase (as discussed Section \ref{sec:gixd}) and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the tail tilt angle.
It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail volumes are reduced in the current XRR measurements compared to those determined previously.
The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers\cite{Small1984}. DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
Notably our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.

Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of the four lipids.
The three lipids with the PC head are consistent with values of $\sim330$ \AA$^3$, regardless of tail.
This agrees well with the values found for the same head in water (Table \ref{tab:water}).
Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be smaller in water when measured by either DMPG using differential vibrating tube densimetry\cite{Pan2012} ($291.0$ \AA$^3$) or POPG using molecular dynamics simulations\cite{Kucerka2012} ($289$ \AA$^3$).
This indicates that there may be some effect arising from the solvation in DES causing an apparent increase in the PG head volume when compared with water.

The major difference between the two heads is the fact PG head is negatively charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
It has been shown previously that, due to the electrostic interaction, the conformation of the PC head is folded in water\cite{Gilliams2016}.
A similar structure may occur for the PG head, with a weaker interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
Therefore, the observed increase found for the PG volume in DES when compared with water may be due to the unfolding of the PG head, where the solvent is capable of providing a greater screening effect to the PG head than that present in water.
This may not be observed for the PC head due to the greater strength of the folding interaction arising from the formally-charged nature of the ammonium group.
It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer. Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head.

The determined volumes for the head and tails, and the thickness of the head layers, for DMPC and DPPC were then used as constraints in the co-refinement of the custom model against two contrasts NR data (Figure \ref{fig:neutron}). In these analysis the only two varying parameters were the tail tilt angle, $\theta_t$, and the interfacial roughness, $\sigma$
The quality of agreement with the NR measurements indicates that the values found for the head and tail volumes air consistent between the pair of measurements for the same system.
It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the head and tail volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
Futhermore, the trends present with varying surface pressure in the XRR models are consistent with that found in the NR models.
%
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{figures/nDMPC20_all_data}
	\includegraphics[width=0.45\textwidth]{figures/nDPPC20_all_data}
	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC. The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity. Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
	\label{fig:neutron}
\end{figure}
%
%
\begin{table}
	\caption{\label{tab:neutron} he best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl}, and the values of $\phi_h$ were found using Eqn. \ref{equ:phih}. Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
  \begin{ruledtabular}
	\begin{tabular}{ccccc}
    Lipid & d$_{54}$-DMPC & & d$_{62}$-DPPC & \\
    SP/mNm$^{-1}$ & 20 & 25 & 15 & 20 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dmpc/angle20_neutron.txt} & \input{../output/dmpc/angle25_neutron.txt} & \input{../output/dppc/angle15_neutron.txt} & \input{../output/dppc/angle20_neutron.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rough20_neutron.txt} & \input{../output/dmpc/rough25_neutron.txt} & \input{../output/dppc/rough15_neutron.txt} & \input{../output/dppc/rough20_neutron.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} & \input{../output/dmpc/solh25_neutron.txt} & \input{../output/dppc/solh15_neutron.txt} & \input{../output/dppc/solh20_neutron.txt} \\
		$d_t$/\AA & \input{../output/dmpc/tail20_neutron.txt} & \input{../output/dmpc/tail25_neutron.txt} & \input{../output/dppc/tail15_neutron.txt} & \input{../output/dppc/tail20_neutron.txt} \\
	\end{tabular}
  \end{ruledtabular}
\end{table}
%

For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a non-aqueous liquid surface.
Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of functional phospholipid monolayers at the air-liquid interface.

A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
This has the important implication that DES therefore offers the possibility of performing studies of model membranes in the absence of water.
Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
However, the fact remains that the PG head containing lipid did show a significant difference; having a larger head volume than observed for the same system in water.
This shows that the transfer of lipids to a DES is not just a simple substitution of the subphase. In this specific case we have proposed an explanation based on unfolding of the PG head that is enabled by electrostatic screening of the head charges by the charged solvent.

The ability to determine the head volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistent model within the analysis of the XRR and NR measurements.
Futhermore, this work presents the first, to our knowledge, use of chemically-consistent parameterisation to co-refine XRR measurements at different surface concentrations.

\begin{acknowledgments}
The authors thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F. A.R.M. is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149). We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
\end{acknowledgments}

\bibliography{rsc}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2018-08-31 reports/esi2.tex
added the prl version

--- 2018-08-29 reports/esi.tex
@@
 \usepackage{hyperref}
-\usepackage{siunitx}
+\usepackage[detect-all]{siunitx}
+\usepackage{xr}
+\externaldocument{apssamp}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\thetable}{S\Roman{table}}
 \author{Andrew R. McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
@@
 \maketitle
+
+\section{Materials}
+Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) d$_9$-choline chloride (99 \%, 98 \% D, CK Isotopes) and d$_8$-glycerol (99 \%, 98 \% D, CK Isotopes)  were purchased and used without further purification.
+The DES was prepared by mixing the precursors at the appropriate ratio, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at \SI{40}{\celsius} and subsequently stored under a dry atmosphere.
+Due to the limited availability of the deuterated precursors, a fully protonated subphase (hDES) and a partially deuterated subphase (hdDES) were prepared and used during the neutron reflectometry (NR) experiment.
+The partially deuterated subphase was prepared using the following mixtures of precursors: \SI{1}{\mole} of 0.38 mole-fraction of h-choline chloride/0.62 mole-fraction of d-choline chloride; and \SI{2}{\mole} of 0.56 mole-fraction of h-glycerol/0.44 mole-fraction of d-glycerol.
+The solvent was subsequently prepared following the procedure discussed above.
+
+The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
+Those measurements showed that the water content of the solvent was kept below \SI{0.3}{wt\percent} during all the experimental procedures presented here, which we assume to be negligible and have little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}
+
+DPPC (\SI{>99}{\percent}, C$_{16}$ tails), DMPC (\SI{>99}{\percent}, C$_{14}$ tails), and DMPG (\SI{>99}{\percent}, C$_{14}$ tails) were supplied by Avanti Polar Lipids and DLPC (\SI{>99}{\percent}, C$_{12}$ tails) was supplied by Sigma-Aldrich and all were used as received.
+Deuterated versions of DPPC (d$_{62}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) and DMPC (d$_{54}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
+These phospholipids were dissolved in chloroform (\SI{0.5}{\milli\gram\per\milli\liter}) at room temperature.
+PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphoditylglycerol head component, these are shown in Figure \ref{fig:heads}.
+
+In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
+After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
+Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
+In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
+Instead, small Delrin adsorption troughs were used that did not have controlable barriers.
+So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.
+
+\section{Methods}
+XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\eV} photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\AA^{-1}}.
+The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
+Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
+XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius}.
+The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
+
+The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Data at two incident angles of \SI{0.62}{\degree} and \SI{3.8}{\degree} were measured to provide a momentum transfer range from \SIrange{0.005}{0.18}{\AA^{-1}}.
+Two surface pressures for each system and contrast was measured (DMPC: 20 and \SI{25}{\milli\newton\meter^{-1}}, DPPC: 15 and \SI{20}{\milli\newton\meter^{-1}}).
+Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours), kept under an inert atmosphere, and all measurements were conducted at \SI{22}{\celsius}.
+
+\section{Literature values for head and tail volumes}
+\begin{table}
+	\caption{\ Lipid component volumes extracted from different literature sources.
+$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry.
+$^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
+  \centering
+	\label{tab:water}
+	\begin{tabular}{llllllllll}
+		\hline
+    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
+    \hline
+    Reference & [\cite{Armen1998}] & [\cite{Sun1994}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Pan2012}] & [\cite{Kucerka2012}] \\
+    \hline
+    $V_l$/\si{\angstrom^3} & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1$ & $1155.4\pm30.0$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
+    $V_t$/\si{\angstrom^3} & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0$ & $815.9\pm15.5$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
+    $V_h$/\si{\angstrom^3} & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
+    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
+    T/\si{\celsius} & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
+	\end{tabular}
+\end{table}
+
+\section{Chemically-consistant model}
+Our chemically-consistent model is made up of two layers to define the lipid monolayer; the head layer at the interface with the solvent and tail layer at the interface with the air.
+The head components have a calculated scattering length, $b_h$, (found as a summation of the X-ray or neutron atomic scattering lengths), and a component volume, $V_h$.
+These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
+The tail components also have a calculated scattering length, $b_t$, roughness, $\sigma_t$, and a component volume, $V_t$.
+We have defined the thickness of the tail layer, $d_t$, in terms of the maximum (all-trans) length of the carbon tail, $t_t$, and the angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
+%
+\begin{equation}
+\label{equ:tl}
+d_t = t_t \cos{\theta_t}.
+\end{equation}
+%
+This was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g.
+it cannot be thicker than the maximum extended length of the lipid tail.
+The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
+%
+\begin{equation}
+\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}(\phi_i),
+\end{equation}
+%
+where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains neither solvent nor air, e.g.
+$\phi_t = 0$.
+To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
+%
+\begin{equation}
+\label{equ:phih}
+\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
+\end{equation}
+%
+Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
+$\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
+Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
+
+%
+\begin{table}[h]
+	\small
+	\caption{\ The invariant parameters within the chemically-consistent model.
+	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
+	\label{tab:invariant}
+  \centering
+	\begin{tabular}{ccccc}
+		\hline
+		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
+		\hline
+		X-ray & & & & \\
+		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
+		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
+		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
+		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
+		Air & -- & -- & -- & 0\\
+		DES & -- & -- & -- & 10.8$^b$ \\
+		\hline
+		Neutron & & & & \\
+		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
+		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
+		h-DES & -- & -- & -- & 0.43$^b$  \\
+		hd-DES & -- & -- & -- & 3.15$^b$ \\
+		\hline
+	\end{tabular}
+\end{table}
+%
+
 \section{Grazing incident X-ray diffraction (GIXD)}
+\label{sec:gixd}
 GIXD was measured for DPPC and DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius} (and \SI{7}{\celsius} for DMPC), and are shown in Figures \ref{fig:dppcgixd}-\ref{fig:dmpcgixd7}.
@@
 \end{figure}
+
 \section{Probability distribution functions}

### 2018-08-31 reports/paper.tex
added the prl version

@@
 
-The formation of phospholipid monolayers at the air/liquid interface also plays a key role in many biological and technological processes.
+The formation of phospholipid monolayers at the air/liquid interface plays a key role in many biological and technological processes.
 The solvent-specific solubility of different components of the phospholipid results in the formation of a stable monolayer of phospholipid at the interface.\cite{Mohwald1990} Phospholipids contain a charged head, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the phospholipid-ion interactions on structure, monomer packing, and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and a non-aqueous media has not been previously reported, to the best of the authors' knowledge.
@@
 is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime .
+We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
 

### 2018-08-31 reports/apssamp.tex
slight rearrange

@@
 We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of measurements at different surface concentration.
-The model was applied to the study of four phospholipids monolayers by X-ray reflectometry (XRR), namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface.
+The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by X-ray reflectometry (XRR).
 Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.

### 2018-08-31 reports/apssamp.tex
changing plot colors

@@
 
-\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
 %\keywords{Suggested keywords}%Use showkeys class option if keyword
@@
 	\includegraphics[width=0.45\textwidth]{figures/DMPG_other_data}
-	\caption{The PDFs of the head volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+	\caption{The PDFs of the head volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (yellow circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 	\includegraphics[width=0.45\textwidth]{figures/nDPPC20_all_data}
-	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
+	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in yellow; (a) DMPC, (b) DPPC.
 The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
@@
 	\begin{tabular}{ccccc}
-    Lipid & d$_{54}$-DMPC & & d$_{62}$-DPPC & \\
+    Lipid & \multicolumn{2}{c}{d$_{54}$-DMPC} & \multicolumn{2}{c}{d$_{62}$-DPPC} \\
     SP/mNm$^{-1}$ & 20 & 25 & 15 & 20 \\

### 2018-08-31 reports/apssamp.tex
change all to siunitx

@@
 \item[Usage]
-Electronic Supplementary Information (ESI) available: All datasets, figure file and analysis/plotting scripts, allowing for a fully reproducible analysis of all work presented herein.
+Electronic Supplementary Information (ESI) available: All datasets, figure files and analysis/plotting scripts, allowing for a fully reproducible analysis of all work presented herein.
 See DOI: 10.6084/m9.figshare.6661784.
@@
 
-This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \numrange{320}{360} \AA$^3$, while the phosphatidylglycerol (PG) head is \numrange{289}{291} \AA$^3$ (Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
+This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
 Furthermore, the effect of pressure, which is not necessarily present for the tail volume values in Table \ref{tab:water}, has been shown to compress the lipid tail volume\cite{Marsh2010,Small1984}, and the need to account for this hydrocarbon compaction according to their phase in the modelling of NR data has recently been demonstrated\cite{Campbell2018}.
@@
 	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
-The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
+The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.
 Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
@@
 
-The custom model for each lipid, fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}, while Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a 95 \% confidence interval, of the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, and the interfacial roughness, $\sigma$ which were free to vary independent of surface pressure, and the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$, for each a single value was fitted for each lipid across all surface pressures.
+The custom model for each lipid, fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}, while Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, of the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, and the interfacial roughness, $\sigma$ which were free to vary independent of surface pressure, and the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$, for each a single value was fitted for each lipid across all surface pressures.
 %
@@
 		Lipid & DLPC & DMPC & DPPC & DMPG \\
-    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
+    SP/\si{\milli\newton\per\meter} & 35 & 40 & 30 & 30 \\
 		\hline
-		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
-		$\sigma$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
+		$\theta_t$/\si{\degree} & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
+		$\sigma$/\si{\angstrom} & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
     \hline
-    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
-		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
-		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
     \hline
     $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
+		$d_t$/\si{\angstrom} & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
 	\end{tabular}
@@
 In keeping this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
-Furthermore, the thickness of the tail layers agress well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$ \AA\ at 30 mN/m\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=16.7$ \AA\ at 40 mN/m\cite{Helm1987} in water for DPPC.
+Furthermore, the thickness of the tail layers agress well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
 
-Figure \ref{fig:lipresults} shows the tail layer thickness increasing with surface pressure, before plateuing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC the plateu can be assumed to be at higher pressures than those studied.
+Figure \ref{fig:lipresults} shows the tail layer thickness increasing with surface pressure, before plateuing; for DPPC this occurs at \SI{20}{\milli\newton\per\meter}, DMPC at \SI{30}{\milli\newton\per\meter} and for DMPG and DLPC the plateu can be assumed to be at higher pressures than those studied.
 This phenomenon has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
@@
 This can be rationalised by considering when the surface pressure is increased, the free volume available between the lipid heads reduces forcing the solvent out of the lipid head layer and into the bulk.
-A similar effect has been observed when increasing the surface pressure from 11 mNm$^{-1}$ to 31 mNm$^{-1)}$ for a DMPC/DMPG monolayer at the air-water interface\cite{Bayerl1990}.
+A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface\cite{Bayerl1990}.
 
@@
 Such a reduction has been shown previously\cite{Campbell2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
-In that work, the optimal value of the tail volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.
+In that work, the optimal value of the tail volume for DPPC was found to be \SI{772}{\cubic\angstrom} at a surface pressure of \SI{35}{\milli\newton\per\meter}, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work at surface pressures of 15, 20, 25, and \SI{30}{\milli\newton\per\meter}.
 
@@
 It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail volumes are reduced in the current XRR measurements compared to those determined previously.
-The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers\cite{Small1984}.
+The reduction was found to be \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
 DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
@@
 Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of the four lipids.
-The three lipids with the PC head are consistent with values of $\sim330$ \AA$^3$, regardless of tail.
+The three lipids with the PC head are consistent with values of around \SI{330}{\cubic\angstrom}, regardless of hydrocarbon tail.
 This agrees well with the values found for the same head in water (Table \ref{tab:water}).
-Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be smaller in water when measured by either DMPG using differential vibrating tube densimetry\cite{Pan2012} ($291.0$ \AA$^3$) or POPG using molecular dynamics simulations\cite{Kucerka2012} ($289$ \AA$^3$).
+Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, whereas it is considered to be smaller in water when measured by either DMPG using differential vibrating tube densimetry\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG using molecular dynamics simulations\cite{Kucerka2012} (\SI{289}{\cubic\angstrom}).
 This indicates that there may be some effect arising from the solvation in DES causing an apparent increase in the PG head volume when compared with water.
@@
 It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head.
+Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
 
 The determined volumes for the head and tails, and the thickness of the head layers, for DMPC and DPPC were then used as constraints in the co-refinement of the custom model against two contrasts NR data (Figure \ref{fig:neutron}).
-In these analysis the only two varying parameters were the tail tilt angle, $\theta_t$, and the interfacial roughness, $\sigma$
+In these analysis the only two varying parameters were the tail tilt angle, $\theta_t$, and the interfacial roughness, $\sigma$.
 The quality of agreement with the NR measurements indicates that the values found for the head and tail volumes air consistent between the pair of measurements for the same system.
@@
 	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in yellow; (a) DMPC, (b) DPPC.
-The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
+The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.
 Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}

### 2018-08-31 reports/apssamp.tex
a bit more cleaning

@@
 Evaluting the interaction of two, chemically distinct, phospholipid heads with this non-aqueous solvent, in addition to the effect of the tail chain length.
-The analysis was then extended to model complementary neutron reflectometry measurements for two contrasts of DMPC and DPPC at a single surface pressure.
+The analysis was then extended to model complementary neutron reflectometry (NR) measurements for two contrasts of DMPC and DPPC at a single surface pressure.
 
@@
 This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework\cite{Kluyver2016}.
-In the area of neutron and X-ray reflectometry data-analysis, the landscape of open-source software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, motofit\cite{Nelson2006}, Aurore\cite{Gerelli2016}, and GenX\cite{Bjorck2007}.
+In the area of NR and XRR data-analysis, the landscape of open-source software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Aurore\cite{Gerelli2016}, and GenX\cite{Bjorck2007}.
 
@@
 %
-We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of measurements at different surface concentration.
-The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by X-ray reflectometry (XRR).
+We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of XRR and NR measurements at different surface concentration.
+The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by XRR.
 Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
@@
 
-This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
+This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (seee Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
 Furthermore, the effect of pressure, which is not necessarily present for the tail volume values in Table \ref{tab:water}, has been shown to compress the lipid tail volume\cite{Marsh2010,Small1984}, and the need to account for this hydrocarbon compaction according to their phase in the modelling of NR data has recently been demonstrated\cite{Campbell2018}.
@@
 It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
+Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from NR measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
 

### 2018-09-05 reports/paper.tex
after most of karens comments

@@
 It has recently been shown that these solvents have the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect.
-The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to potential application in the preservation of biomolecules as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES have been able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
+The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to the potential application of DES as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES are able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
 
@@
 The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This is a method for sampling a high-dimensionality parameter space, such as that which is relevant in reflectometry fitting, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously.
-The use of Bayesian inference allows the PDF for each fitting variable to be probed, therefore estimations of the inverse uncertainties associated with each parameter can be found as well as information about the correlations between different variables.
+The use of Bayesian inference allows the PDF for each fitting variable to be probed, therefore estimations of the inverse uncertainties associated with each parameter can be found, as well as information about the correlations between different variables.
 
@@
 The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
-Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}
+Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have to little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}
 
@@
 These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature.
-PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphoditylglycerol head component, these are shown in Figure \ref{fig:heads}.
+PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphatidylglycerol head component, these are shown in Figure \ref{fig:heads}.
 
@@
 	\label{tab:water}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llllllllll}
-		\hline
+	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l|lll|ll|ll|l|l}
+		%\hline
     Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
@@
     T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
+    %\hline
 	\end{tabular*}
@@
 In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
-Instead, small Delrin adsorption troughs were used that did not have controlable barriers.
+Instead, small Delrin adsorption troughs were used that did not have controllable barriers.
 So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.
@@
 Frequently these physical constraints include the component volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}.
-Additionally, a recent evaluation of the applicability of different models to surfactant and phospholipid monolayers from the NR perspective has been published,\cite{Campbell2018} suggests possible oversights in the modelling of NR data.
+Additionally, a recent evaluation of the applicability of different models to surfactant and phospholipid monolayers from the NR perspective has been published,\cite{Campbell2018} that suggests possible oversights in the modelling of NR data.
 
@@
 However, we do not know whether the head component volumes used in the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
-The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES.\cite{Sanchez-Fernandez2018} Furthermore, it has been shown that in the liquid expanded and condensed phases, which are often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured from other techniques,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}
+The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES components.\cite{Sanchez-Fernandez2018} Furthermore, it has been shown that in the liquid expanded and condensed phases, which are often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured from other techniques,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}
 
@@
 The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
-The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} since this is the maximum chain length possible and the most likely conformation at the surface pressures studied.
-For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
+The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} since this is the maximum chain length possible and the most likely conformation at the surface pressures studied.\cite{Hollinshead2009} For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
 Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.
@@
 In the second step, the head and tail component volumes, and head layer thickness determined from XRR were fixed for the refinement of the custom model against the NR measurements.
-This approach means that the number of variable parameters to fir the NR data can be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.
+This approach means that the number of variable parameters to fit the NR data can be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.
 Table \ref{tab:invariant} also gives the details of the scattering lengths and SLDs used as invariant parameters for the NR fitting.
@@
 In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
-The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the PDF associated with each parameter.
+The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
-The use of MCMC sampling allowed for the Bayesian inference of the probability density function for each of the variables and their respective interactions (shown in detail in the ESI).
+The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions (shown in detail in the ESI).
 This allowed asymmetric confidence intervals to be found for each of the variable parameters.
@@
 The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
-The resulting XRR profiles, associated SLD profiles are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of all varying parameters for each lipid at the highest surface pressure measured, as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
-\ref{equ:tl} and \ref{equ:phih} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
+The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} gives details of all varied parameters for each lipid at the highest surface pressure measured, as well as the details of $d_t$ and $\phi_h$ which are determined from Eqns.
+\ref{equ:tl} and \ref{equ:phih} respectively.
+Each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
 
@@
 The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}.
-Table \ref{tab:neutron} gives details of the varying parameters at each surface pressure as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns.
-\ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
+Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $d_t$ and $\phi_h$, again determined from Eqns.
+\ref{equ:tl} and \ref{equ:phih}.
+These are, once again, given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
 %
@@
 	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
-The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
 \ref{equ:phih}}
@@
 %
-The variation of the tail layer thickness in the models, found from $\theta_t$ using Eqn \ref{equ:tl}, with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
-It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateuing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC the plateu can be assumed to be at higher pressures than those studied.
+The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
+It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateauing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC can be assumed to be at higher pressures than those studied.
 This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
@@
 In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer.
-This can be rationalised by considering when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.
+This can be rationalised by considering that when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.
 A similar effect has been observed when increasing the surface pressure from 11 mNm$^{-1}$ to 31 mNm$^{-1)}$ for a DMPC/DMPG monolayer at the air-water interface.\cite{Bayerl1990}
@@
 It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
-However, this reduction observed has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elevated surface pressure.
+However, this reduction has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elevated surface pressure.
 In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.
@@
 The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
-Notably our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
+Notably this value is similar to that found in this work for DMPC, which has the same tail structure and suggests that our results are at least self-consistent.
 
@@
 Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids.
-The three lipids with the PC head component are consistent with values of $\sim330$ \AA$^3$, regardless of tail component.
+The three lipids with the PC head component are consistent, giving values of $\sim330$ \AA$^3$, regardless of tail component.
 This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
-Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be smaller in water when compared with either DMPG using differential vibrating tube densimetry\cite{Pan2012} or POPG using molecular dynamics simulations.\cite{Kucerka2012} This indicates that there may be some affect arising from the solvation in DES causing an apparent increase in the PG component volume when compared with water.
+Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$.
+The PG head component volume in water, from either DMPG using differential vibrating tube densimetry\cite{Pan2012} or POPG using molecular dynamics simulations,\cite{Kucerka2012} is noticeably smaller.
+This indicates that there may be some effect arising from the solvation in choline cloride:glycerol causing an apparent increase in the PG component volume when compared with water.
 
@@
 The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head component volume is consistant between the pair of measurements for the same system.
-It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
+It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust enough to be used in the modelling of NR data.
 Futhermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components are consistant with that found in the NR models.
@@
 For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a non-aqueous liquid surface.
-Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of functional phospholipid monolayers at the air-liquid interface.
+Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of phospholipid monolayers at the air-liquid interface.
 
@@
 Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
-However, the fact that the PG component containing lipid did show a significant difference; having a larger head component volume than observed for the same system in water.
-This that the transfer of lipids to a DES is not just a simple substitution of the subphase.
-In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the charged solvent.
+However, the PG component did show a significant difference; having a larger head component volume than observed for the same system in water.
+This suggests that the transfer of lipids to a DES is not just a simple substitution of the subphase.
+In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the partially charged solvent.
 
-The ability to determine the head component volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
+The ability to determine the head component volume was facilitated by access to easy to use, open-source software that allowed for the straightforward use of a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
 Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
@@
 is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
+We also thank Diamond Light Source (Experiment Number: SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
 

### 2018-09-05 src/visualization/plotref.py

@@ -58,25 +58,25 @@ for i in range(0, len(sps)):
 
 
 #plotting reflectometry
-def plotref(data, gs, offset):
+def plotref(data, gs, offset, col):
     ax = plt.subplot(gs)
     ax.errorbar(data[0], data[1] * offset, yerr=data[2] * offset, linestyle='', marker='s', markersize=7, 
                 markeredgecolor='k', markerfacecolor='k', ecolor='k')
-    ax.plot(data[0], data[3] * offset, linewidth=4)
+    ax.plot(data[0], data[3] * offset, linewidth=4, color=col)
     for i in range(4, data.shape[0]):
-        ax.plot(data[0], data[i] * offset, color='k', linewidth=2, alpha=0.005)
+        ax.plot(data[0], data[i] * offset, color=col, linewidth=2, alpha=0.005)
     ax.set_ylabel(r'$Rq^4$/Å$^{-4}$')
     ax.set_yscale('log')
     ax.set_xlabel(r'$q$/Å$^{-1}$')
     
-def plotsld(data, gs, offset, label):
+def plotsld(data, gs, offset, label, col):
     ax = plt.subplot(gs)
     z = data[0] - 10
     true_sld = data[1]
-    ax.plot(z, true_sld + offset, linewidth=4)
+    ax.plot(z, true_sld + offset, linewidth=4, color=col)
     for i in range(2, data.shape[0]):
         sld = data[i]
-        ax.plot(z, sld + offset, color='k', linewidth=2, alpha=0.005)
+        ax.plot(z, sld + offset, color=col, linewidth=2, alpha=0.005)
     ax.set_xlabel(r'$z$/Å')
     ax.set_ylabel(r'SLD/$10^{-6}$Å$^{-2}$')
     ax.text(0.80, 0.05, '(' + label + ')', fontsize=44, transform=ax.transAxes)
@@ -115,8 +115,8 @@ def plotgraph(gs, sp, tails, sols, n1, n2, p1, p2, x1, x2, label):
     #make_patch_spines_invisible(par2)
     # Second, show the right spine.
     #par2.spines["right"].set_visible(True)
-    p11, = host.plot(sp, tails, c='#0173B2', marker='s', ls='', ms=15)
-    p21, = par1.plot(sp, sols, c='#029E73', marker='o', ls='', ms=15)
[…]

### 2018-09-05 reports/paper.tex
cleaning everything up

@@
 	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l|lll|ll|ll|l|l}
-		%\hline
+		\hline
     Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
@@
     T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
-    %\hline
+    \hline
 	\end{tabular*}
@@
 In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations.
-The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, an assumption that is based on our belief that increasing surface pressure should not significantly influence the head layer thickness.
+In keeping with the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the head thickness was fitted for each lipid across all surface pressures, as the thickness of the head layer was considered to be dependent on molecular dimensions only.
 The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
-	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
-	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
-	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
+	\includegraphics[width=0.45\textwidth]{figures/dlpc_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dmpc_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dppc_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
 	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{figures/DLPC_other_data}
-	\includegraphics[width=0.48\textwidth]{figures/DMPC_other_data}
-	\includegraphics[width=0.48\textwidth]{figures/DPPC_other_data}
-	\includegraphics[width=0.48\textwidth]{figures/DMPG_other_data}
+	\includegraphics[width=0.45\textwidth]{figures/dlpc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dmpc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dppc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
 	\caption{The PDFs of the head component volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{figures/nDMPC20_all_data}
-	\includegraphics[width=0.48\textwidth]{figures/nDPPC20_all_data}
+	\includegraphics[width=0.45\textwidth]{figures/nDMPC20_all_data}
+	\includegraphics[width=0.45\textwidth]{figures/nDPPC20_all_data}
 	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
@@
 	\label{tab:neutron}
-	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}l|ll|ll}
 		\hline

### 2018-09-06 reports/apssamp.tex
cleaning everything up
Following adrians comments

@@
 Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
-Furthermore, recently DES have indicated the presence of a solvophobic effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer conformations\cite{Sapir2016}.
+Furthermore, recently DES have indicated the presence of a solvophobic effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer conformations\cite{Sapir2016} and protein conformation\cite{Sanchez-Fernandez2017}.
 
@@
 This work presents the first investigation of the structure of four phospholipid monolayers at the air-DES interface, as determined by chemically-consistent modelling of X-ray reflectometry (XRR) measurements.
-Evaluting the interaction of two, chemically distinct, phospholipid heads with this non-aqueous solvent, in addition to the effect of the tail chain length.
+Evaluating the interaction of two, chemically distinct, phospholipid heads with this non-aqueous solvent, in addition to the effect of the tail chain length.
 The analysis was then extended to model complementary neutron reflectometry (NR) measurements for two contrasts of DMPC and DPPC at a single surface pressure.
@@
 \includegraphics[width=0.3\textwidth]{figures/head_groups}
-\caption{\label{fig:heads} The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
+\caption{\label{fig:heads} The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
 \end{figure}
@@
 
-This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (seee Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
-Furthermore, the effect of pressure, which is not necessarily present for the tail volume values in Table \ref{tab:water}, has been shown to compress the lipid tail volume\cite{Marsh2010,Small1984}, and the need to account for this hydrocarbon compaction according to their phase in the modelling of NR data has recently been demonstrated\cite{Campbell2018}.
+This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (see Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
+Furthermore, the effect of pressure, which is not necessarily accounted for the in the literature, has been shown to compress the lipid tail volume\cite{Marsh2010,Small1984}, and the need to account for this hydrocarbon compaction according to their phase in the modelling of NR data has recently been demonstrated\cite{Campbell2018}.
 %
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/DLPC_all_data}
-	\includegraphics[width=0.45\textwidth]{figures/DMPC_all_data}
-	\includegraphics[width=0.45\textwidth]{figures/DPPC_all_data}
-	\includegraphics[width=0.45\textwidth]{figures/DMPG_all_data}
+	\includegraphics[width=0.45\textwidth]{figures/dlpc_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dmpc_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dppc_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
 	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
-The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
+The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:lipids}
@@
 
-The custom model for each lipid, fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}, while Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, of the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, and the interfacial roughness, $\sigma$ which were free to vary independent of surface pressure, and the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$, for each a single value was fitted for each lipid across all surface pressures.
+The custom model for each lipid, fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, and the interfacial roughness, $\sigma$, which were free to vary independent of surface pressure.
+In addition to the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$, for which a single value was fitted for each lipid across all surface pressures.
 %
@@
 \ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn.
-\ref{equ:phih}.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
+\ref{equ:phih}.}
   \begin{ruledtabular}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/DLPC_other_data}
-	\includegraphics[width=0.45\textwidth]{figures/DMPC_other_data}
-	\includegraphics[width=0.45\textwidth]{figures/DPPC_other_data}
-	\includegraphics[width=0.45\textwidth]{figures/DMPG_other_data}
+	\includegraphics[width=0.45\textwidth]{figures/dlpc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dmpc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dppc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
 	\caption{The PDFs of the head volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (yellow circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl}.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+\ref{equ:tl}.}
 	\label{fig:lipresults}
@@
 In this work, a single tail volume was fitted to each lipid for all four surface pressures that were measured.
-This is based on the assumption, that at all four surface pressures, the lipids adopt the same phase (as discussed Section \ref{sec:gixd}) and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the tail tilt angle.
+This is based on the assumption, that at all four surface pressures, the lipids adopt the same liquid expanded phase (as discussed Section \ref{sec:gixd}) and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the tail tilt angle.
 It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail volumes are reduced in the current XRR measurements compared to those determined previously.
@@
 The major difference between the two heads is the fact PG head is negatively charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
-It has been shown previously that, due to the electrostic interaction, the conformation of the PC head is folded in water\cite{Gilliams2016}.
+It has been shown previously that, due to the electrostatic interaction, the conformation of the PC head is folded in water\cite{Gilliams2016}.
 A similar structure may occur for the PG head, with a weaker interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
@@
 Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from NR measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
+Previously, the presence of short range, electrostatic interactions has been noted to impact the solution structure adopted by zwitterionic surfactants in choline chloride:glycerol\cite{Sanchez-Fernandez2018}.
 
@@
 In these analysis the only two varying parameters were the tail tilt angle, $\theta_t$, and the interfacial roughness, $\sigma$.
-The quality of agreement with the NR measurements indicates that the values found for the head and tail volumes air consistent between the pair of measurements for the same system.
+The quality of agreement with the NR measurements indicates that the values found for the head and tail volumes are consistent between the pair of measurements for the same system.
 It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the head and tail volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/nDMPC20_all_data}
-	\includegraphics[width=0.45\textwidth]{figures/nDPPC20_all_data}
+	\includegraphics[width=0.45\textwidth]{figures/dmpc_20n_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
 	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in yellow; (a) DMPC, (b) DPPC.
-The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
+The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:neutron}
@@
 \ref{equ:tl}, and the values of $\phi_h$ were found using Eqn.
-\ref{equ:phih}.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY\cite{mccluskey_2018}.}
+\ref{equ:phih}.}
   \begin{ruledtabular}

### 2018-09-06 reports/esi.tex
Following adrians comments

@@
 \end{figure}
+
+\section{XRR parameters at each surface pressure}
+
+%
+\begin{table}
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second highest surface pressure (SP) measured.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+\ref{equ:phih}}
+	\label{tab:liptab1}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
+		\hline
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 30 & 30 & 25 & 25 \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle30.txt} & \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle25.txt} & \input{../output/dmpg/angle25.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough25.txt} & \input{../output/dmpg/rough25.txt} \\
+    \hline
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh25.txt} & \input{../output/dmpg/solh25.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail25.txt} & \input{../output/dmpg/tail25.txt} \\
+		\hline
+	\end{tabular*}
+\end{table}
+%
+%
+\begin{table}
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second lowest surface pressure (SP) measured.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+\ref{equ:phih}}
+	\label{tab:liptab2}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
+		\hline
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 25 & 25 & 20 & 20 \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle25.txt} & \input{../output/dmpc/angle25.txt} & \input{../output/dppc/angle20.txt} & \input{../output/dmpg/angle20.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough25.txt} & \input{../output/dmpc/rough25.txt} & \input{../output/dppc/rough20.txt} & \input{../output/dmpg/rough20.txt} \\
+    \hline
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh25.txt} & \input{../output/dmpc/solh25.txt} & \input{../output/dppc/solh20.txt} & \input{../output/dmpg/solh20.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail25.txt} & \input{../output/dmpc/tail25.txt} & \input{../output/dppc/tail20.txt} & \input{../output/dmpg/tail20.txt} \\
+		\hline
+	\end{tabular*}
+\end{table}
+%
+%
+\begin{table}
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the lowest surface pressure (SP) measured.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+\ref{equ:phih}}
+	\label{tab:liptab3}
+	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
+		\hline
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 20 & 20 & 15 & 15 \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle20.txt} & \input{../output/dmpc/angle20.txt} & \input{../output/dppc/angle15.txt} & \input{../output/dmpg/angle15.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough20.txt} & \input{../output/dmpc/rough20.txt} & \input{../output/dppc/rough15.txt} & \input{../output/dmpg/rough15.txt} \\
+    \hline
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh20.txt} & \input{../output/dmpc/solh20.txt} & \input{../output/dppc/solh15.txt} & \input{../output/dmpg/solh15.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail20.txt} & \input{../output/dmpc/tail20.txt} & \input{../output/dppc/tail15.txt} & \input{../output/dmpg/tail15.txt} \\
+		\hline
+	\end{tabular*}
+\end{table}
+%
+
 \section{Probability distribution functions}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dlpc2_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dlpc1_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 20 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dlpc3_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dlpc2_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 25 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dlpc3_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 30 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dlpc5_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 35 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc20_neutron_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc_20n_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc25_neutron_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc_25n_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 25 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc15_neutron_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dppc_15n_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DPPC neutron reflectometry data at 15 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc20_neutron_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dppc_20n_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.

### 2018-09-06 reports/paper.tex
Following adrians comments

@@
 	\includegraphics[width=0.30\textwidth]{figures/head_groups}
-	\caption{The two lipid classes with different head components compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol, (b) phosphocholine.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The two lipid classes with different head components compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol, (b) phosphocholine.}
 	\label{fig:heads}
@@
 This software allows the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s reflectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}).
-This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under CC-BY.\cite{mccluskey_2018}
+This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under CC-BY.\cite{mccluskey_2018c}
 
@@
 	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
-The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.}
 	\label{fig:lipids}
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
-	\caption{The PDFs of the head component volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The PDFs of the head component volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.}
 	\label{fig:lipresults}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/nDMPC20_all_data}
-	\includegraphics[width=0.45\textwidth]{figures/nDPPC20_all_data}
+	\includegraphics[width=0.45\textwidth]{figures/dmpc_20n_ref_sld}
+	\includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
 	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
-The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.}
 	\label{fig:neutron}

### 2018-09-06 notebooks/lipid_nr.py

@@ -1,6 +1,12 @@
 
 # coding: utf-8
 
+# # Neutron reflectometry analysis
+# 
+# This is a custom Python analysis notebook for analysing XRR data using the class `VolMono`, as defined in `src/models/mol_vol.py`, and the refnx [1] package. 
+# 
+# It is first necessary to import the necessary modules for the analysis.
+
 # In[ ]:
 
 
@@ -23,20 +29,43 @@ import mol_vol as mv
 sys.path.insert(0, '../src/tools')
 import helper
 
+
+# When running the `Makefile` in the top directory of this ESI, a this notebook is converted to a Python script and running for four different lipids, each at four surface pressures. The necessary variables are assigned here. 
+
+# In[ ]:
+
+
 lipid = sys.argv[1]
 length = int(sys.argv[2])
 sp = sys.argv[3]
+
+
+# Here we assign the directories that contain the data, as well as where the figures and analysis outputs should be stored. If you directory structure does not match that in the GitHub repository these should be adapted. 
+
+# In[ ]:
+
 
 data_dir = '../data/processed/{}/'.format(lipid)
 figures_dir = '../reports/figures/'
 analysis_dir = '../output/'
 
 
+# In order for the analysis to be exactly reproducible the same package versions must be used. The conda packaging manager, and pip, can be used to ensure this is the case. The versions of refnx and scipy used original are:
+# 
+# ```
+# refnx.version.full_version = 0.0.17
+# scipy.version.version = 1.1.0
+# ```
+
 # In[ ]:
 
 
 refnx.version.full_version, scipy.version.version
 
+
+# ## Setup of the analysis
+# 
+# The experimental datafiles are then read in.
 
 # In[ ]:
 
@@ -45,6 +74,8 @@ refnx.version.full_version, scipy.version.version
 dataset_1 = ReflectDataset('{}nr_h_sp_{}.dat'.format(data_dir, sp))
 dataset_2 = ReflectDataset('{}nr_hd_sp_{}.dat'.format(data_dir, sp))
 
+
+# The scattering lengths for the head and tail components are defined.
 
 # In[ ]:
 
[…]

### 2018-09-07 reports/apssamp.tex
made b&w and esi finished

@@
 
-\author{Andrew R. McCluskey}
+\author{A.~R.~McCluskey}
   \thanks{These authors have contributed equally to the work presented within}
@@
 
-\author{Adrian Sanchez-Fernandez}
+\author{A.~Sanchez-Fernandez}
   \thanks{These authors have contributed equally to the work presented within}
@@
 
-\author{Karen J. Edler}
+\author{K.~J.~Edler}
 \email{k.edler@bath.ac.uk}
@@
 
-\author{Stephen C. Parker}
+\author{S.~C.~Parker}
 \affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
 
-\author{Andrew J. Jackson}
+\author{A.~J.~Jackson}
   \altaffiliation[Also at ]{Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden}
@@
 
-\author{Richard A. Campbell}
+\author{R.~A.~Campbell}
   \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France}
@@
 
-\author{Thomas Arnold}
+\author{T.~Arnold}
 \email{tom.arnold@esss.se}
@@
 We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of XRR and NR measurements at different surface concentration.
-The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by XRR.
+The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by XRR at a series of different surface pressures, between \SIrange{15}{40}{\milli\newton\per\meter}.
 Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
-	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
+	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; see legend above each plot.
 The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
-	\caption{The PDFs of the head volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (yellow circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+	\caption{The PDFs of the head volume (left) and variation of $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 	\includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
-	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in yellow; (a) DMPC, (b) DPPC.
+	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$ for two contrasts (see legend above each plot); (a) DMPC, (b) DPPC.
 The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}

### 2018-09-07 reports/esi2.tex
made b&w and esi finished

@@
 \externaldocument{apssamp}
+\usepackage{rotating}
 \renewcommand{\thefigure}{S\arabic{figure}}
@@
 \renewcommand{\thetable}{S\Roman{table}}
-\author{Andrew R. McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
-Karen J. Edler,\textit{$^{a}$}$^{\ast}$ Stephen C. Parker,\textit{$^{a}$} Andrew J. Jackson,\textit{$^{cd}$} \\
-Richard A. Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$ \\
+\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
+K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} \\
+R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold\textit{$^{abcg}$}$^{\ast}$ \\
  \\
@@
 \textit{University, SE-211 00 Lund, Sweden}}
-\title{ESI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
+\title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
 \date{}
@@
 \section{Literature values for head and tail volumes}
-\begin{table}
+Table \ref{tab:water} gives a variety of literature values for the component volumes of the lipids investigated in this work.
+\begin{sidewaystable}
+  \centering
 	\caption{\ Lipid component volumes extracted from different literature sources.
@@
 	\label{tab:water}
-	\begin{tabular}{llllllllll}
-		\hline
+	\begin{tabular}{l|lll|ll|ll|l|l}
     Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
@@
 	\end{tabular}
-\end{table}
+\end{sidewaystable}
 
@@
 \begin{table}[h]
-	\small
+  \centering
 	\caption{\ The invariant parameters within the chemically-consistent model.
@@
 	\label{tab:invariant}
-  \centering
-	\begin{tabular}{ccccc}
-		\hline
+	\begin{tabular}{c|c|c|c|c}
 		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
@@
 		hd-DES & -- & -- & -- & 3.15$^b$ \\
-		\hline
 	\end{tabular}
 \end{table}
+%
+
+\section{XRR parameters at each surface pressure}
+Tables \ref{tab:liptab1}-\ref{tab:liptab3} gives the best fit values for the custom model that was fitted to each surface pressure, for each lipid.
+These values were used for comparison to assess the effect of the choline chloride:glycerol on the lipid.
+%
+\begin{table}
+  \centering
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second highest surface pressure (SP) measured.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+\ref{equ:phih}}
+	\label{tab:liptab1}
+	\begin{tabular}{l|l|l|l|l}
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 30 & 30 & 25 & 25 \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle30.txt} & \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle25.txt} & \input{../output/dmpg/angle25.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough25.txt} & \input{../output/dmpg/rough25.txt} \\
+    \hline
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh25.txt} & \input{../output/dmpg/solh25.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail25.txt} & \input{../output/dmpg/tail25.txt} \\
+	\end{tabular}
+\end{table}
+%
+%
+\begin{table}
+  \centering
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second lowest surface pressure (SP) measured.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+\ref{equ:phih}}
+	\label{tab:liptab2}
+	\begin{tabular}{l|l|l|l|l}
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 25 & 25 & 20 & 20 \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle25.txt} & \input{../output/dmpc/angle25.txt} & \input{../output/dppc/angle20.txt} & \input{../output/dmpg/angle20.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough25.txt} & \input{../output/dmpc/rough25.txt} & \input{../output/dppc/rough20.txt} & \input{../output/dmpg/rough20.txt} \\
+    \hline
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh25.txt} & \input{../output/dmpc/solh25.txt} & \input{../output/dppc/solh20.txt} & \input{../output/dmpg/solh20.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail25.txt} & \input{../output/dmpc/tail25.txt} & \input{../output/dppc/tail20.txt} & \input{../output/dmpg/tail20.txt} \\
+	\end{tabular}
+\end{table}
+%
+%
+\begin{table}
+  \centering
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the lowest surface pressure (SP) measured.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+\ref{equ:phih}}
+	\label{tab:liptab3}
+	\begin{tabular}{l|l|l|l|l}
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 20 & 20 & 15 & 15 \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle20.txt} & \input{../output/dmpc/angle20.txt} & \input{../output/dppc/angle15.txt} & \input{../output/dmpg/angle15.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough20.txt} & \input{../output/dmpc/rough20.txt} & \input{../output/dppc/rough15.txt} & \input{../output/dmpg/rough15.txt} \\
+    \hline
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh20.txt} & \input{../output/dmpc/solh20.txt} & \input{../output/dppc/solh15.txt} & \input{../output/dmpg/solh15.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail20.txt} & \input{../output/dmpc/tail20.txt} & \input{../output/dppc/tail15.txt} & \input{../output/dmpg/tail15.txt} \\
+	\end{tabular}
+\end{table}
+%
+
+\section{Neutron reflectometry and SLD profiles}
+Figure \ref{fig:neutron} shows the neutron reflectomery and scattering length density profiles for DMPC at \SI{25}{\milli\newton\per\meter} (two contrasts) and DPPC at \SI{15}{\milli\newton\per\meter} (two contrasts).
+%
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\textwidth]{figures/dmpc_25n_ref_sld}
+	\includegraphics[width=0.9\textwidth]{figures/dppc_15n_ref_sld}
+	\caption{The NR and SLD profiles at a surface pressure of (a) 25 mNm$^{-1}$ for two contrasts of DMPC, and (b) 15 mNm$^{-1}$ for two contrasts of DPPC.
+The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
+	\label{fig:neutron}
+\end{figure}
 %
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc2_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc1_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 20 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc3_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc2_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 25 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc3_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 30 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc5_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 40 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc2_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dppc1_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 15 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc3_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dppc2_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 20 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dppc3_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 25 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc5_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 30 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg2_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpg1_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 15 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg3_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpg2_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 20 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpg3_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 25 mNm$^{-1}$.
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg5_all_corner}
+	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
 	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 30 mNm$^{-1}$.

### 2018-09-07 reports/paper_prl.tex
adding the preprint (amoung other stuff)@

--- 2018-09-07 reports/apssamp.tex
@@
 \item[Usage]
-Electronic Supplementary Information (ESI) available: All datasets, figure files and analysis/plotting scripts, allowing for a fully reproducible analysis of all work presented herein.
-See DOI: 10.6084/m9.figshare.6661784.
+Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and figure files, allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: **some doi**) under an MIT license.
+Reduced experimental datasets are available at \url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
 \end{description}
@@
 is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-We also thank Diamond Light Source (SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
+We also thank Diamond Light Source (Experiment number SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
 \end{acknowledgments}

### 2018-09-07 reports/paper_rsc.tex
adding the preprint (amoung other stuff)@

--- 2018-09-06 reports/paper.tex
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
-	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
+	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; 15, 20, 25, 30, 35, 40 mNm$^{-1}$ (coloured blue, yellow, green, orange, pink, and brown respectively).
 The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.}

### 2018-09-07 reports/preprint.tex
adding the preprint (amoung other stuff)@

--- 2018-09-07 reports/paper_prl.tex
@@
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.1 distribution.
-%   Version 4.1r of REVTeX, August 2010
-%
-%   Copyright (c) 2009, 2010 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
-\documentclass[%
- reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose,
-%preprint,
-%showpacs,preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- %aps,
- prl,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
+\documentclass[twocolumn,a4paper]{paper}
+\usepackage{graphicx}
+\usepackage{siunitx}
+\usepackage[super,sort&compress,comma]{natbib}
+\usepackage{hyperref}
+\usepackage{xr}
+\externaldocument{esi}
 
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-\usepackage[detect-all]{siunitx}
-\usepackage{hyperref}% add hypertext capabilities
-\usepackage{xr}
-\externaldocument{esi2}
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
+\title{Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers}
+\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ \\
+S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold \textit{$^{abcg}$}$^{\ast}$}
 
-%\usepackage[showframe,%Uncomment any one of the following lines to test
-%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
-%%text={7in,10in},centering,
-%%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
-%%height=10in,a5paper,hmargin={3cm,0.8in},
-%]{geometry}
+\institution{${a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK. \\
+${b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK. \\
+${c}$~European Spallation Source, SE-211 00 Lund, Sweden. \\
+${d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden. \\
+${e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France. \\
+${f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, \\
+\indent M13 9PT, UK. \\
+${g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, \\
+Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK. \\
+${\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 \\
+Lund, Sweden. \\
+$\ddag$~These authors have contributed equally to the work presented within. \\
+$\ast$~k.edler@bath.ac.uk; tom.arnold@esss.se}
+
+\date{\today}
 
@@
 
-\preprint{APS/123-QED}
-
-\title{Bayesian determination of the effect of a deep euctectic solvent on the structure of lipid monolayers}% Force line breaks with \\%
-
-\author{A.~R.~McCluskey}
-  \thanks{These authors have contributed equally to the work presented within}
-  \altaffiliation[Also at ]{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
-
-\author{A.~Sanchez-Fernandez}
-  \thanks{These authors have contributed equally to the work presented within}
-  \altaffiliation[Also at ]{European Spallation Source, SE-211 00 Lund, Sweden}
-  \altaffiliation[Present address ]{Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
-
-\author{K.~J.~Edler}
-\email{k.edler@bath.ac.uk}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
-
-\author{S.~C.~Parker}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
-
-\author{A.~J.~Jackson}
-  \altaffiliation[Also at ]{Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden}
-\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
-
-\author{R.~A.~Campbell}
-  \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France}
-\affiliation{Division of Pharmacy and Optometry, University of Manchester, Manchester, UK}
-
-\author{T.~Arnold}
-\email{tom.arnold@esss.se}
-  \altaffiliation[Also at ]{ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 OQX, UK; Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK; Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
-\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
+\maketitle
 
@@
 \end{abstract}
-
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-\maketitle
-
-%\tableofcontents
 
@@
 %
-\begin{figure}[b]
+\begin{figure}
 \includegraphics[width=0.3\textwidth]{figures/head_groups}
@@
 %
-\begin{table}
+\begin{table*}
+  \centering
 	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
@@
 \ref{equ:phih}.}
-  \begin{ruledtabular}
 	\begin{tabular}{ccccc}
@@
 	\end{tabular}
-  \end{ruledtabular}
-\end{table}
+\end{table*}
 %
@@
 %
-\begin{table}
+\begin{table*}
+  \centering
 	\caption{\label{tab:neutron} he best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
@@
 
-\begin{acknowledgments}
 The authors thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
@@
 We also thank Diamond Light Source (Experiment number SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
-\end{acknowledgments}
 
 \bibliography{rsc}% Produces the bibliography via BibTeX.
-
+\bibliographystyle{rsc}
 \end{document}
-%
-% ****** End of file apssamp.tex ******

### 2018-09-07 notebooks/lipid_xrr.py

@@ -53,7 +53,7 @@ label = sys.argv[7]
 
 
 # Relative directory locations
-data_dir = '../data/processed/{}/'.format(lipid)
+data_dir = '../data/processed/{}_'.format(lipid)
 figures_dir = '../reports/figures/'
 analysis_dir = '../output/'
 

### 2018-09-07 reports/preprint.tex
small changes

@@
 \usepackage{xr}
-\externaldocument{esi}
+\externaldocument{si}
 
@@
 \begin{figure}
+\centering
 \includegraphics[width=0.3\textwidth]{figures/head_groups}
-\caption{\label{fig:heads} The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
+\caption{\label{fig:heads}\small The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
 \end{figure}
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
-	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; see legend above each plot.
+	\caption{\small The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; see legend above each plot.
 The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
@@
   \centering
-	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
+	\caption{\label{tab:liptab}\small  The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
-	\caption{The PDFs of the head volume (left) and variation of $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+	\caption{\small The PDFs of the head volume (left) and variation of $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 	\includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
-	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$ for two contrasts (see legend above each plot); (a) DMPC, (b) DPPC.
+	\caption{\small The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$ for two contrasts (see legend above each plot); (a) DMPC, (b) DPPC.
 The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
@@
   \centering
-	\caption{\label{tab:neutron} he best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
+	\caption{\label{tab:neutron}\small The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.

### 2018-09-10 reports/preprint.tex
cleaning the SI a bit

@@
 ${f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, \\
-\indent M13 9PT, UK. \\
+M13 9PT, UK. \\
 ${g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, \\
@@
 It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from NR measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
+Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from NR measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
 Previously, the presence of short range, electrostatic interactions has been noted to impact the solution structure adopted by zwitterionic surfactants in choline chloride:glycerol\cite{Sanchez-Fernandez2018}.
@@
 
+\setlength{\bibsep}{1pt}
 \bibliography{rsc}% Produces the bibliography via BibTeX.

### 2018-09-10 reports/si.tex
Getting only the preprint on git@
cleaning the SI a bit

--- 2018-09-07 reports/esi2.tex
@@
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,a4paper]{paper}
 \usepackage[latin1]{inputenc}
@@
 \usepackage{rotating}
+\usepackage[margin=2cm]{geometry}
 \renewcommand{\thefigure}{S\arabic{figure}}
@@
 \renewcommand{\thetable}{S\Roman{table}}
-\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
-K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} \\
-R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold\textit{$^{abcg}$}$^{\ast}$ \\
- \\
-\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton} \\
-\textit{Down, Bath, BA2 7AY, UK.} \\
-\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE,} \\
-\textit{UK.} \\
-\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.} \\
-\textit{$^{d}$~Department of Physical Chemistry, Lund University,} \\
-\textit{SE-211 00 Lund, Sweden.} \\
-\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000,} \\
-\textit{Grenoble, France.} \\
-\textit{$^{f}$~Division of Pharmacy and Optometry, University of} \\
-\textit{Manchester, Manchester, M13 9PT, UK.} \\
-\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology} \\
-\textit{Facilities Council, Rutherford Appleton Laboratory, Harwell} \\
-\textit{Oxford, Didcot OX11 0QX, UK.} \\
-\textit{$^{\P}$~Present address: Department of Food Technology, Lund} \\
-\textit{University, SE-211 00 Lund, Sweden}}
 \title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
-\date{}
+\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ \\
+S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold \textit{$^{abcg}$}$^{\ast}$}
+
+\institution{${a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, \\
+BA2 7AY, UK. \\
+${b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK. \\
+${c}$~European Spallation Source, SE-211 00 Lund, Sweden. \\
+${d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden. \\
+${e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France. \\
+${f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, \\
+M13 9PT, UK. \\
+${g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, \\
+Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK. \\
+${\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 \\
+Lund, Sweden. \\
+$\ddag$~These authors have contributed equally to the work presented within. \\
+$\ast$~k.edler@bath.ac.uk; tom.arnold@esss.se}
+
+\date{\today}
+
 \begin{document}

### 2018-09-27 reports/si.tex
After richards final comments

@@
 
-The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Data at two incident angles of \SI{0.62}{\degree} and \SI{3.8}{\degree} were measured to provide a momentum transfer range from \SIrange{0.005}{0.18}{\AA^{-1}}.
-Two surface pressures for each system and contrast was measured (DMPC: 20 and \SI{25}{\milli\newton\meter^{-1}}, DPPC: 15 and \SI{20}{\milli\newton\meter^{-1}}).
+The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Measurements at two incident angles of \SI{0.62}{\degree} and \SI{3.8}{\degree} were carried out to provide reduced data with a momentum transfer range from \SIrange{0.005}{0.25}{\AA^{-1}}.
+Two surface pressures for each system and contrast were measured (DMPC: 20 and \SI{25}{\milli\newton\meter^{-1}}, DPPC: 15 and \SI{20}{\milli\newton\meter^{-1}}).
 Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours), kept under an inert atmosphere, and all measurements were conducted at \SI{22}{\celsius}.
@@
 $\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
-Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
+Therefore, the capillary wave roughness at the air-DES interface is carried equally through the layers.
 
@@
 All figures contain an artifact from the X-ray beam interacting with the Teflon of the Langmuir trough.
-However, in figures \ref{fig:dppcgixd} and \ref{fig:dmpcgixd7} it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid phase at all surface pressures measured.
+However, in figures \ref{fig:dppcgixd} and \ref{fig:dmpcgixd7} it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid condensed phase at all surface pressures measured.
 \begin{figure}[h]

### 2018-09-27 reports/preprint.tex
update preprint

@@
 
-In this work, a single tail volume was fitted to each lipid for all four surface pressures that were measured.
-This is based on the assumption, that at all four surface pressures, the lipids adopt the same liquid expanded phase (as discussed Section \ref{sec:gixd}) and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the tail tilt angle.
+Due to the poor wetting properties of the DES, it was not possible to collect surface isotherm measurements.
+However, grazing incidence X-ray diffraction was collected for DMPC and DPPC at \SI{30}{\milli\newton\per\meter}, indicating that the lipids had adopted the liquid condensed phase (see Section \ref{sec:gixd}).
+This is the same phase behaviour as is observed in water \cite{Phillips1968} and by considering that there will be little interaction between the lipid tails and the DES it is unlikely that a significant change in the phase behaviour \cite{Nagle1976}.
+The means that at all four surface pressures, as is the case on water, the lipids would adopt the same liquid condensed phase and any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the tail tilt angle.
+This allowed a single tail volume to be fitted for each lipid at all four surface pressures that were measured.
 It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail volumes are reduced in the current XRR measurements compared to those determined previously.
@@
 It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from NR measurements\cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
+Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and \SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at \SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements, which it slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
 Previously, the presence of short range, electrostatic interactions has been noted to impact the solution structure adopted by zwitterionic surfactants in choline chloride:glycerol\cite{Sanchez-Fernandez2018}.

### 2018-10-01 reports/preprint.tex
After tom's clean up job

@@
 In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous solvent.
-  Furthermore, we use novel, chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leading to an apparent increase in the volume compared to that observed in water.
-  No such change was observed for the phosphocholine head, indicating that the interaction is head specific.
+We use novel, chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
+However, the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leads to an apparent increase in its volume compared to that observed in water.
+No such change was observed for the phosphocholine head, indicating that such interactions are head, and therefore solvent, specific.
 \begin{description}
@@
 
-Deep eutectic solvents (DES) are a green, sustainable solvent system obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013}.
-An extensive hydrogen bonding network is present, allowing the mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
+Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013}.
+The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
 Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
-Furthermore, recently DES have indicated the presence of a solvophobic effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer conformations\cite{Sapir2016} and protein conformation\cite{Sanchez-Fernandez2017}.
+Recently DES have also been shown to exhibit a "solvophobic" effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein conformations\cite{Sanchez-Fernandez2017}.
 
-Phospholipid monolayer formation at the air/liquid interface plays a key role in many biological and technological processes, where the solvent-specific solubility of different components of the phospholipid enables a stable monolayer to form at the interface\cite{Mohwald1990}.
-Investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
-Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and a non-aqueous media has not been previously reported, to the best of the authors' knowledge.
+Phospholipid monolayers at the air/water interface have been widely studied as simplistic models for biological membranes.
+As such, they have been used to gain insight into many biological processes that are technologically and medically relevant.
+For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
+However, the native environment for lipids in-vivo is far from a simple aqueous solution.
+In fact, it has been suggested\cite{Choi2011,Hammond2017} that DES effectively form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, particularly assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
+Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and any non-aqueous media has not been previously reported, to the best of the authors' knowledge.
 
-This work presents the first investigation of the structure of four phospholipid monolayers at the air-DES interface, as determined by chemically-consistent modelling of X-ray reflectometry (XRR) measurements.
-Evaluating the interaction of two, chemically distinct, phospholipid heads with this non-aqueous solvent, in addition to the effect of the tail chain length.
-The analysis was then extended to model complementary neutron reflectometry (NR) measurements for two contrasts of DMPC and DPPC at a single surface pressure.
+This work presents the first investigation of the structure of phospholipid monolayers at an air-DES interface.
+We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
 
@@
 This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework\cite{Kluyver2016}.
-In the area of NR and XRR data-analysis, the landscape of open-source software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Aurore\cite{Gerelli2016}, and GenX\cite{Bjorck2007}.
+In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Rascal\cite{HughesRascal} Aurore\cite{Gerelli2016}, and GenX\cite{Bjorck2007}.
 
@@
 %
-We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of XRR and NR measurements at different surface concentration.
+We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of reflectometry measurements at different surface concentration.
 The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by XRR at a series of different surface pressures, between \SIrange{15}{40}{\milli\newton\per\meter}.
@@
 
-This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (see Table \ref{tab:water}), as it not clear if the presence of the DES would affect the head volume due to electrostatic interactions, which may differ from those between the head and water.
-Furthermore, the effect of pressure, which is not necessarily accounted for the in the literature, has been shown to compress the lipid tail volume\cite{Marsh2010,Small1984}, and the need to account for this hydrocarbon compaction according to their phase in the modelling of NR data has recently been demonstrated\cite{Campbell2018}.
+This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (see Table \ref{tab:water}), since the DES may affect the head volume, because of differing electrostatic interactions compared to water.
+Furthermore, it is known that, on water, increased surface pressure and associated liquid-expanded to liquid-condensed (LE-LC) phase transitions lead to a compression of the lipid tail volume\cite{Marsh2010,Small1984}.
+It has been shown recently that such hydrocarbon compaction should be included when modelling reflectometry data\cite{Campbell2018}, something that has not necessarily been accounted for the in the literature.
+
 %
@@
 
-The custom model for each lipid, fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, and the interfacial roughness, $\sigma$, which were free to vary independent of surface pressure.
-In addition to the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$, for which a single value was fitted for each lipid across all surface pressures.
+The custom model for each lipid, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
+In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure.
+The other parameters, $V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface pressures measured for each lipid.
+
 %
@@
 In keeping this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
-Furthermore, the thickness of the tail layers agress well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
+Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
+In all cases the surface roughness was found to be relatively high when compared to water.
+However this should be considered in the context that the absolute surface tension of the DES is less than water with a corresponding higher surface roughness\cite{Arnold2015}.
 
@@
 This phenomenon has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
+
 %
@@
 
-Due to the poor wetting properties of the DES, it was not possible to collect surface isotherm measurements.
-However, grazing incidence X-ray diffraction was collected for DMPC and DPPC at \SI{30}{\milli\newton\per\meter}, indicating that the lipids had adopted the liquid condensed phase (see Section \ref{sec:gixd}).
-This is the same phase behaviour as is observed in water \cite{Phillips1968} and by considering that there will be little interaction between the lipid tails and the DES it is unlikely that a significant change in the phase behaviour \cite{Nagle1976}.
-The means that at all four surface pressures, as is the case on water, the lipids would adopt the same liquid condensed phase and any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the tail tilt angle.
+While we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the poor wetting properties of the DES.
+This inconsistency means that we cannot be confident in the phase of the lipids based on the surface pressure alone.
+Instead we have used grazing incidence X-ray diffraction to confirm the phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
+Thus DPPC was found to be in the LC phase at room temperature while DMPC was in the LE phase at room temperature and the LC phase at 7C (see Section \ref{sec:gixd}).
+This is essentially the same phase behaviour as is observed in water \cite{Phillips1968} and by considering that there is little interaction between the lipid tails and the DES we believe that it is unlikely that there is a significant change in the phase behaviour in these systems\cite{Nagle1976}.
+We therefore assume that for all four surface pressures, as is the case on water, the lipids adopt the same phase for all surface pressures measured and any variation in the structure would manifest only as a change in the tail thickness, via the tail tilt angle.
 This allowed a single tail volume to be fitted for each lipid at all four surface pressures that were measured.
+
 It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail volumes are reduced in the current XRR measurements compared to those determined previously.
@@
 Futhermore, the trends present with varying surface pressure in the XRR models are consistent with that found in the NR models.
+
 %
@@
 Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
-However, the fact remains that the PG head containing lipid did show a significant difference; having a larger head volume than observed for the same system in water.
+However, the fact remains that the PG lipid did show a significant difference; having a larger head volume than observed for the same system in water.
 This shows that the transfer of lipids to a DES is not just a simple substitution of the subphase.
@@
 \setlength{\bibsep}{1pt}
-\bibliography{rsc}% Produces the bibliography via BibTeX.
+\bibliography{bibi}% Produces the bibliography via BibTeX.
 \bibliographystyle{rsc}

### 2018-10-08 reports/preprint.tex
add nelson acknowledgement
changing acknowledgment wording
add more references

@@
 
-Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013}.
+Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013,Jiang2018}.
 The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
 Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
-Recently DES have also been shown to exhibit a "solvophobic" effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein conformations\cite{Sanchez-Fernandez2017}.
+Recently DES have also been shown to exhibit a "solvophobic" effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein conformations\cite{Sanchez-Fernandez2017}.
 
@@
 
+\section*{Acknowledgments}
+
+The authors thank Andrew Nelson for his help with the refnx software.
+A.R.M. is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
 The authors thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
-A.R.M.
-is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
 We also thank Diamond Light Source (Experiment number SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.

### 2018-10-08 reports/preprint.tex
more references

@@
 Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013,Jiang2018}.
-The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
+The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017,Faraone2018}.
 Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.

### 2018-10-09 reports/preprint.tex
First set of edits/typos

@@
 The custom model for each lipid, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tile angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
+Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tilt angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
 In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure.
@@
 
-In keeping this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
+In keeping with this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
 Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
-In all cases the surface roughness was found to be relatively high when compared to water.
+In all cases the surface roughness was found to be higher than in water.
 However this should be considered in the context that the absolute surface tension of the DES is less than water with a corresponding higher surface roughness\cite{Arnold2015}.
@@
 In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent, $\phi_h$, present in the lipid head layer.
-This can be rationalised by considering when the surface pressure is increased, the free volume available between the lipid heads reduces forcing the solvent out of the lipid head layer and into the bulk.
+This can be rationalised by considering when the surface pressure is increased, the free volume available between the lipid heads reduces, forcing the solvent out of the lipid head layer and into the bulk.
 A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface\cite{Bayerl1990}.

### 2018-10-09 reports/preprint.tex
Another edit

@@
 As such, they have been used to gain insight into many biological processes that are technologically and medically relevant.
-For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
+Investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
 However, the native environment for lipids in-vivo is far from a simple aqueous solution.

### 2018-10-09 reports/preprint.tex
Typo
Edit

@@
 Instead these parameters, along with the thickness of the phospholipid head layer, $d_h$, were allowed to vary for each lipid.
-However, their values were constained to be self-consistent for a single lipid over multiple measurements at different surface pressures.
+However, their values were constrained to be self-consistent for a single lipid over multiple measurements at different surface pressures.
 
@@
 
-In keeping with this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
+In keeping with previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
 Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.

### 2018-10-09 reports/preprint.tex
Comment on lipid tail volume comparison
resolved the issue of repeating myself

@@
 In that work, the optimal value of the tail volume for DPPC was found to be \SI{772}{\cubic\angstrom} at a surface pressure of \SI{35}{\milli\newton\per\meter}, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work at surface pressures of 15, 20, 25, and \SI{30}{\milli\newton\per\meter}.
+The reduction was found to be \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
+DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
+However, our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
 
@@
 This allowed a single tail volume to be fitted for each lipid at all four surface pressures that were measured.
-
-It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail volumes are reduced in the current XRR measurements compared to those determined previously.
-The reduction was found to be \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
-DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
-Notably our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
 

### 2018-10-10 reports/preprint.tex

@@
 DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
-However, our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
+However, this value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
 

### 2018-10-11 reports/si.tex
After tom's clean up job
update gixd image

@@
 \label{sec:gixd}
-GIXD was measured for DPPC and DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius} (and \SI{7}{\celsius} for DMPC), and are shown in Figures \ref{fig:dppcgixd}-\ref{fig:dmpcgixd7}.
+GIXD was measured for DPPC and DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius} (and \SI{7}{\celsius} for DMPC), and are shown in Figure \ref{fig:dppcgixd}.
 All figures contain an artifact from the X-ray beam interacting with the Teflon of the Langmuir trough.
@@
 	\includegraphics[width=0.50\textwidth]{figures/206041}
-	\caption{The GIXD pattern for DPPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, the axes at in units of \si{\per\angstrom}.
+	\caption{The GIXD pattern for (a) DPPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, (b) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, and (c) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{7}{\celsius}.
 Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
 	\label{fig:dppcgixd}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.50\textwidth]{figures/206151}
-	\caption{The GIXD pattern for DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, the axes at in units of \si{\per\angstrom}.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
-	\label{fig:dmpcgixd}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.50\textwidth]{figures/206161}
-	\caption{The GIXD pattern for DMPC at \SI{30}{\milli\newton\per\meter} at \SI{7}{\celsius}, the axes at in units of \si{\per\angstrom}.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
-	\label{fig:dmpcgixd7}
 \end{figure}
@@
 %%%REFERENCES%%%
-\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
+\bibliography{bibi} %You need to replace "rsc" on this line with the name of your .bib file
 \bibliographystyle{rsc} %the RSC's .bst file

### 2018-10-13 reports/si.tex
clean up the references and change the gixd figure

@@
 \usepackage{amssymb}
+\usepackage{float}
 \usepackage{graphicx}
@@
 %
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 However, in figures \ref{fig:dppcgixd} and \ref{fig:dmpcgixd7} it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid condensed phase at all surface pressures measured.
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/206041}
-	\caption{The GIXD pattern for (a) DPPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, (b) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, and (c) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{7}{\celsius}.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\includegraphics[width=0.50\textwidth]{figures/gixd}
+	\caption{The GIXD pattern for (a) DPPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, (b) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, and (c) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{7}{\celsius}.}
 	\label{fig:dppcgixd}
@@
 The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpcn1}-\ref{fig:dppcn2}.
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dlpc1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 20 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 20 mNm$^{-1}$.}
 	\label{fig:dlpc2}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dlpc2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 25 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 25 mNm$^{-1}$.}
 	\label{fig:dlpc3}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dlpc3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 30 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 30 mNm$^{-1}$.}
 	\label{fig:dlpc4}
 \end{figure}
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 35 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 35 mNm$^{-1}$.}
 	\label{fig:dlpc5}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 20 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 20 mNm$^{-1}$.}
 	\label{fig:dmpc2}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 25 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 25 mNm$^{-1}$.}
 	\label{fig:dmpc3}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 30 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 30 mNm$^{-1}$.}
 	\label{fig:dmpc4}
 \end{figure}
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 40 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 40 mNm$^{-1}$.}
 	\label{fig:dmpc5}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dppc1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 15 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 15 mNm$^{-1}$.}
 	\label{fig:dppc2}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dppc2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 20 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 20 mNm$^{-1}$.}
 	\label{fig:dppc3}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dppc3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 25 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 25 mNm$^{-1}$.}
 	\label{fig:dppc4}
 \end{figure}
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 30 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 30 mNm$^{-1}$.}
 	\label{fig:dppc5}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpg1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 15 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 15 mNm$^{-1}$.}
 	\label{fig:dmpg2}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpg2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 20 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 20 mNm$^{-1}$. }
 	\label{fig:dmpg3}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpg3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 25 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 25 mNm$^{-1}$.}
 	\label{fig:dmpg4}
 \end{figure}
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 30 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 30 mNm$^{-1}$.}
 	\label{fig:dmpg5}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc_20n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.}
 	\label{fig:dmpcn1}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc_25n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 25 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 25 mNm$^{-1}$.}
 	\label{fig:dmpcn2}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dppc_15n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DPPC neutron reflectometry data at 15 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DPPC neutron reflectometry data at 15 mNm$^{-1}$.}
 	\label{fig:dppcn1}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dppc_20n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.
-Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
+	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.}
 	\label{fig:dppcn2}

### 2018-10-16 reports/si.tex
fixing

@@
 \usepackage{xr}
-\externaldocument{apssamp}
+\externaldocument{preprint}
 \usepackage{rotating}
@@
 All figures contain an artifact from the X-ray beam interacting with the Teflon of the Langmuir trough.
-However, in figures \ref{fig:dppcgixd} and \ref{fig:dmpcgixd7} it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid condensed phase at all surface pressures measured.
+However, in figures \ref{fig:dppcgixd}a and \ref{fig:dppcgixd}c it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid condensed phase at all surface pressures measured.
 \begin{figure}[H]

### 2018-10-16 reports/si.tex
tom's new si and fix name in bib

@@
 In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
-After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
-Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
+After the evaporation of the chloroform, it is assumed that the resulting system is a liquid subphase with a monolayer of phospholipid at the interface.
+The surface concentration was modified by closing and opening the barriers of a Langmuir trough (Nima Custom model: 20cm x 40cm with a total volume of approximately 450 ml).
 In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
-Instead, small Delrin adsorption troughs were used that did not have controlable barriers.
+Instead, small Delrin adsorption troughs (5 x 6 cm with a volume of less than 15 ml) were used that did not have controllable barriers.
+In this case a volume of the lipid-chloroform solution, calculated to give the equivalent surface area per molecule, was spread onto the surface.
 So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.
@@
 \section{Methods}
-XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\eV} photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\AA^{-1}}.
-The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
+XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\eV} photon energy using the double-crystal-deflector\cite{Arnold2012} and a Pilatus 100k detector.
+The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\AA^{-1}}.
+The data were normalised with respect to the incident beam and the background was measured from off-specular region-of-interest and subsequently subtracted.
 Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
-XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius}.
-The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
+XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius} under a Helium atmosphere.
+The aluminium Wilhelmy plate was used over a traditional paper plate because the DES was found to wet Aluminium but not paper, and therefore allowed more reproducible surface pressure measurements.
+It is noted that the known phase transitions of DMPC and DMPG are 24 and \SI{23}{\celsius} respectively, which is very close to our measurement temperature.
+For the sake of our assumptions during analysis it is therefore important that we were able to to determine which phase (LE or LC) the molecules are in.
+This was done directly using Grazing incident X-ray diffraction (see below).
 
@@
 \section{Literature values for head and tail volumes}
-Table \ref{tab:water} gives a variety of literature values for the component volumes of the lipids investigated in this work.
-\begin{sidewaystable}
-  \centering
-	\caption{\ Lipid component volumes extracted from different literature sources.
-$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry.
-$^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
-  \centering
-	\label{tab:water}
-	\begin{tabular}{l|lll|ll|ll|l|l}
-    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
-    \hline
-    Reference & [\cite{Armen1998}] & [\cite{Sun1994}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Pan2012}] & [\cite{Kucerka2012}] \\
-    \hline
-    $V_l$/\si{\angstrom^3} & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1$ & $1155.4\pm30.0$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
-    $V_t$/\si{\angstrom^3} & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0$ & $815.9\pm15.5$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
-    $V_h$/\si{\angstrom^3} & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
-    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
-    T/\si{\celsius} & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
-	\end{tabular}
-\end{sidewaystable}
+The range of volumes used for phospholipid heads and tails are somewhat inconsistent in the literature.
+There is a general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (see Table \ref{tab:water}).
+Tail volumes are also quite variable and, as discussed in the main text, the compaction in chain volumes on a phase transition is often not accounted for\cite{Campbell2018}.
+We are interested in comparing the volumes of the lipid components on a non-aqueous liquid.
+To allow this comparison, table \ref{tab:water} gives a variety of literature values for the component volumes of the lipids investigated in this work.
 
@@
 %
-where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains neither solvent nor air, e.g.
+where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains neither solvent nor air, i.e.
 $\phi_t = 0$.
@@
 Therefore, the capillary wave roughness at the air-DES interface is carried equally through the layers.
+As described in the main text, further constraints were applied to the fitting by co-refining the data across different surface pressures and assuming that the tail volume was constant.
+This is based on our assumption that there is no phase transition in the monolayer over the surface pressures measured.
+Thus we have assumed that DPPC is in the LC phase, while DMPC, DMPG and DLPC are all in the LE phase at the measurement temperature.
+
+\section{XRR parameters at each surface pressure}
+Tables \ref{tab:liptab1}-\ref{tab:liptab3} give the best fit values for the custom model that were fitted to each surface pressure, for each lipid.
+These values were used for comparison to assess the effect of the choline chloride:glycerol on the lipid.
+
+\section{Neutron reflectometry and SLD profiles}
+Figure \ref{fig:neutron} shows the neutron reflectomery and scattering length density profiles for DMPC at \SI{25}{\milli\newton\per\meter} (two contrasts) and DPPC at \SI{15}{\milli\newton\per\meter} (two contrasts).
+
+\section{Grazing incident X-ray diffraction (GIXD)}
+\label{sec:gixd}
+We have already indicated that the surface pressure was measured using an Aluminium Wilhelmy plate because the standard paper plates did not wet properly.
+This method did allow us to measure Langmuir isotherms, but these were inconsistent and as such, not a reliable method for determining the phase of the lipid monolayers.
+Instead we were able to measure GIXD for DPPC and DMPC over a range of different surface pressures and temperatures and representative data from these measurements are shown in Figure \ref{fig:gixd} for \SI{30}{\milli\newton\per\meter} and \SI{22}{\celsius} (and \SI{7}{\celsius} for DMPC).
+Unfortunately, despite our best efforts, the quality of GIXD data obtained was not entirely satisfactory.
+All of data contains a weak artefact which we believe is due to scattering from the Teflon trough, which is probably due to the relatively low meniscus of the DES (due to its low surface tension compared to water).
+In addition we cannot see the expected (1,1) peak observed for these lipids on water.
+It is unclear whether this is because these peaks are absent or too weak to be measured.
+Nonetheless, figure \ref{fig:gixd} shows clear diffraction peaks (which we assume to be the (2, 0)) for DPPC at \SI{22}{\celsius} and for DMPC at \SI{7}{\celsius}.
+These peaks are also visible at lower surface pressures (data not shown).
+The presence of any diffraction feature indicates the presence of an LC phase at these temperatures.
+Importantly there is no such peak observed for DMPC at \SI{22}{\celsius} (see \ref{fig:gixd}), indicating that DMPC is in the LE phase at this temperature.
+The position of the (2,0) peak, approx \SI{1.48}{\AA^{-1}}, is similar to that found under the same conditions in water.\cite{Watkins2009}
+We therefore assume that the phase behaviour on the DES is similar to that observed on water and that the phases observed at \SI{30}{\milli\newton\per\meter} are the same at the other surface pressures measured with XRR and NR.
+While we have no direct evidence, we have extended this assumption to DLPC and DMPG since there is no reason to believe that the phases of these molecules should be different from that observed for DMPC.
+
+\section{Probability distribution functions}
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc2}-\ref{fig:dmpg5}.
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpcn1}-\ref{fig:dppcn2}.
+
+\section{Tables and Figures}
+
+\begin{sidewaystable}
+  \centering
+	\caption{\ Lipid component volumes extracted from different literature sources.
+$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry.
+$^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
+  \centering
+	\label{tab:water}
+	\begin{tabular}{l|lll|ll|ll|l|l}
+    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
+    \hline
+    Reference & [\cite{Armen1998}] & [\cite{Sun1994}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Pan2012}] & [\cite{Kucerka2012}] \\
+    \hline
+    $V_l$/\si{\angstrom^3} & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1$ & $1155.4\pm30.0$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
+    $V_t$/\si{\angstrom^3} & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0$ & $815.9\pm15.5$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
+    $V_h$/\si{\angstrom^3} & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
+    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
+    T/\si{\celsius} & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
+	\end{tabular}
+\end{sidewaystable}
 
@@
 
-\section{XRR parameters at each surface pressure}
-Tables \ref{tab:liptab1}-\ref{tab:liptab3} gives the best fit values for the custom model that was fitted to each surface pressure, for each lipid.
-These values were used for comparison to assess the effect of the choline chloride:glycerol on the lipid.
 %
@@
 
-\section{Neutron reflectometry and SLD profiles}
-Figure \ref{fig:neutron} shows the neutron reflectomery and scattering length density profiles for DMPC at \SI{25}{\milli\newton\per\meter} (two contrasts) and DPPC at \SI{15}{\milli\newton\per\meter} (two contrasts).
-%
 \begin{figure}[H]
@@
 \end{figure}
-%
 
-\section{Grazing incident X-ray diffraction (GIXD)}
-\label{sec:gixd}
-GIXD was measured for DPPC and DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius} (and \SI{7}{\celsius} for DMPC), and are shown in Figure \ref{fig:dppcgixd}.
-All figures contain an artifact from the X-ray beam interacting with the Teflon of the Langmuir trough.
-However, in figures \ref{fig:dppcgixd}a and \ref{fig:dppcgixd}c it is possible to identify a (2, 0) diffraction peak that indicates the presence of a similar structure to that found under the same conditions in water.\cite{Watkins2009} Based on this information we believe that, similar to water, the phase of the lipid tails is likely to be in the liquid condensed phase at all surface pressures measured.
 \begin{figure}[H]
@@
 
-\section{Probability distribution functions}
-
-The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc2}-\ref{fig:dmpg5}.
-The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpcn1}-\ref{fig:dppcn2}.
 \begin{figure}[H]

### 2018-10-16 reports/preprint.tex
after tom edits

--- 2018-10-09 reports/preprint.tex
@@
 \begin{abstract}
-Deep eutectic solvents present a novel class of non-aqueous room temperature solvent with tunable properties, that are capable of promoting the self-assembly of surfactant molecules.
-However, the solvation model in these systems still challenges the classic understanding of amphiphilicity.
-In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous solvent.
-We use novel, chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
+In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous liquid.
+Deep eutectic solvents are a novel class of environmentally friendly non-aqueous room temperature liquids with tunable properties, that have wide ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
+We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
 However, the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leads to an apparent increase in its volume compared to that observed in water.
 No such change was observed for the phosphocholine head, indicating that such interactions are head, and therefore solvent, specific.
+This has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
 \begin{description}
@@
 
-Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013,Jiang2018}.
-The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017,Faraone2018}.
+Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013}.
+The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
 Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
@@
 As such, they have been used to gain insight into many biological processes that are technologically and medically relevant.
-Investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
+For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
 However, the native environment for lipids in-vivo is far from a simple aqueous solution.
-In fact, it has been suggested\cite{Choi2011,Hammond2017} that DES effectively form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, particularly assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
-Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and any non-aqueous media has not been previously reported, to the best of the authors' knowledge.
+In fact, it has been suggested\cite{Dai2013,Hammond2017} that DES effectively form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
 
-This work presents the first investigation of the structure of phospholipid monolayers at an air-DES interface.
+This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any non-aqueous media, to the best of the authors' knowledge).
 We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
@@
 %
-We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of reflectometry measurements at different surface concentration.
-The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by XRR at a series of different surface pressures, between \SIrange{15}{40}{\milli\newton\per\meter}.
-Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
-Instead these parameters, along with the thickness of the phospholipid head layer, $d_h$, were allowed to vary for each lipid.
-However, their values were constrained to be self-consistent for a single lipid over multiple measurements at different surface pressures.
-
-This model was required, despite the general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (see Table \ref{tab:water}), since the DES may affect the head volume, because of differing electrostatic interactions compared to water.
-Furthermore, it is known that, on water, increased surface pressure and associated liquid-expanded to liquid-condensed (LE-LC) phase transitions lead to a compression of the lipid tail volume\cite{Marsh2010,Small1984}.
-It has been shown recently that such hydrocarbon compaction should be included when modelling reflectometry data\cite{Campbell2018}, something that has not necessarily been accounted for the in the literature.
+We report on measurements of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-DES (1:2 choline choride:glycerol) interface.
+In contrast to many previous studies\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed a chemically-consistent model (detail in the ESI) that allows for the co-refinement of reflectometry measurements at different surface pressure and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
+Instead these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG and DLPC.
+This model was required because we cannot assume that the electrostatic interactions between lipid head and the solvent are the same in the DES and in water.
+This may therefore influence the effective head volume which means we cannot rely on the literature values (see ESI) derived from measurements on or in water.
+Furthermore, it is known that, on water, increased surface pressure and associated LE-LC phase transitions lead to a compression of the lipid tail volume\cite{Marsh2010,Small1984} and this compaction has not necessarily been accounted for in the literature\cite{Campbell2018}.
+Our approach avoids this issue by making no assumption about the molecular volumes and only considering surface pressures that we believe to be in the same phase.
 
@@
 
-The custom model for each lipid, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data, and the associated SLD profiles are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} presents the mean value, and asymmetric uncertainies that correspond to a \SI{95}{\percent} confidence interval, for the PDF for each of the varying parameters; the tail tilt angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
+Our model has more variables than we can uniquely fit with limited data.
+In reflectometry the usual approach to this problem is to collect more equivalent dataset with varying deuteration (NR). For reasons of cost and practicality this was not possible in this work.
+The other approach is to constrain the model so that the number of fitted variables are reduced, and is the approach taken here.
+To do this we add the constraint that a single tail volume can be used for all surface pressures.
+To justify this we need to be sure that the lipids remain in the same phase.
+On water this is can be demonstrated with a Langmuir isotherm.
+However, while we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the poor wetting properties of the DES.
+This inconsistency means that we cannot be confident in the phase of the lipids based on the surface pressure alone.
+Instead we have used grazing incidence X-ray diffraction to confirm the phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
+DPPC was found to be in the LC phase and DMPC in the LE phase at room temperature for the surface pressures measured (see Section \ref{sec:gixd}).
+We assume that DMPG and DLPC are also in the LE phase since there is no reason to believe that the phase behaviour in these systems differs significantly from DMPC at the same temperature.
+
+The model, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data.
+The associated SLD profiles are shown in Figure \ref{fig:lipids} while table \ref{tab:liptab} presents the results of the PDF for each of the varying parameters; the tail tilt angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
 In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure.
@@
   \centering
-	\caption{\label{tab:liptab}\small The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
+	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 
-In keeping with previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
-Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
-In all cases the surface roughness was found to be higher than in water.
-However this should be considered in the context that the absolute surface tension of the DES is less than water with a corresponding higher surface roughness\cite{Arnold2015}.
+For each lipid, the tail layer thickness, $d_t$, increases with chain length and in general agrees with the literature for monolayers on water\cite{Mohwald1990,Vaknin1991}:
+For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
+In all cases the surface roughness was found to be relatively high compared to water. This is expected because the absolute surface tension of the DES is less than water\cite{Arnold2015}.
 
-Figure \ref{fig:lipresults} shows the tail layer thickness increasing with surface pressure, before plateuing; for DPPC this occurs at \SI{20}{\milli\newton\per\meter}, DMPC at \SI{30}{\milli\newton\per\meter} and for DMPG and DLPC the plateu can be assumed to be at higher pressures than those studied.
+Figure \ref{fig:lipresults} shows the tail layer thickness variation with surface pressure.
+For DPPC and DMPC a plateau in thickness is reached at \SI{25}{\milli\newton\per\meter} and \SI{30}{\milli\newton\per\meter} respectively.
+Presumably a similar plateau would be seen for DMPG and DLPC at higher pressures.
 This phenomenon has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
@@
 
-In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent, $\phi_h$, present in the lipid head layer.
-This can be rationalised by considering when the surface pressure is increased, the free volume available between the lipid heads reduces, forcing the solvent out of the lipid head layer and into the bulk.
-A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface\cite{Bayerl1990}.
+Figure \ref{fig:lipresults} also shows that for all four lipids there is a decrease in head solvation, $\phi_h$, with surface pressure.
+This is because an increase in the surface pressure means a reduction in the free volume available between the lipid heads, which in turn forces solvent molecules out of the layer, an effect that has also been observed on water\cite{Bayerl1990}.
 
-When comparing Tables \ref{tab:water} and \ref{tab:liptab} it is clear that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
-It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
-Such a reduction has been shown previously\cite{Campbell2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
-In that work, the optimal value of the tail volume for DPPC was found to be \SI{772}{\cubic\angstrom} at a surface pressure of \SI{35}{\milli\newton\per\meter}, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work at surface pressures of 15, 20, 25, and \SI{30}{\milli\newton\per\meter}.
-The reduction was found to be \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
-DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
-However, our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
-
-While we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the poor wetting properties of the DES.
-This inconsistency means that we cannot be confident in the phase of the lipids based on the surface pressure alone.
-Instead we have used grazing incidence X-ray diffraction to confirm the phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
-Thus DPPC was found to be in the LC phase at room temperature while DMPC was in the LE phase at room temperature and the LC phase at 7C (see Section \ref{sec:gixd}).
-This is essentially the same phase behaviour as is observed in water \cite{Phillips1968} and by considering that there is little interaction between the lipid tails and the DES we believe that it is unlikely that there is a significant change in the phase behaviour in these systems\cite{Nagle1976}.
-We therefore assume that for all four surface pressures, as is the case on water, the lipids adopt the same phase for all surface pressures measured and any variation in the structure would manifest only as a change in the tail thickness, via the tail tilt angle.
-This allowed a single tail volume to be fitted for each lipid at all four surface pressures that were measured.
+Our fits suggest lower lipid tail volumes than previous measurements using other techniques (compare Tables \ref{tab:water} and \ref{tab:liptab}).
+It is unlikely that this is a result of the DES subphase since the tails do not directly interact with the solvent.
+However this may be related to the compaction of the monolayer at elevated surface pressures.
+The optimal value of the tail volume for DPPC in the LC phase\cite{Campbell2018} was found to be \SI{772}{\cubic\angstrom} at \SI{35}{\milli\newton\per\meter}, which agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work.
+Similarly the tail volume for DMPS in the LE phase\cite{Campbell2018}, \SI{714}{\cubic\angstrom} at \SI{10}{\milli\newton\per\meter}, broadly agrees with the values for DMPC (\input{../output/dmpc/vt.txt}\si{\cubic\angstrom}) and DMPG (\input{../output/dmpg/vt.txt}\si{\cubic\angstrom}) in this work.
+The literature value\cite{Pan2012} quoted for DMPG (at a lower temperature) is also similar to our result (but slightly smaller).
+We find that the reduction is \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
+In general our results are at least self-consistent while comparisons to the literature are favourable.
 
@@
 
+Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of the four lipids.
+The three lipids with the PC head are consistent with values of around \SI{330}{\cubic\angstrom}, regardless of hydrocarbon tail.
+This agrees well with the values found for the same head in water (Table \ref{tab:water}).
+Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, which is significantly larger than values quoted in the literature for DMPG\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG\cite{Kucerka2012} (\SI{289}{\cubic\angstrom}).
+This suggests that there may be some effect arising from the solvation in DES.
+
 The major difference between the two heads is the fact PG head is negatively charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
-It has been shown previously that, due to the electrostatic interaction, the conformation of the PC head is folded in water\cite{Gilliams2016}.
-A similar structure may occur for the PG head, with a weaker interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
-Therefore, the observed increase found for the PG volume in DES when compared with water may be due to the unfolding of the PG head, where the solvent is capable of providing a greater screening effect to the PG head than that present in water.
-This may not be observed for the PC head due to the greater strength of the folding interaction arising from the formally-charged nature of the ammonium group.
-It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and \SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at \SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements, which it slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head.
-Previously, the presence of short range, electrostatic interactions has been noted to impact the solution structure adopted by zwitterionic surfactants in choline chloride:glycerol\cite{Sanchez-Fernandez2018}.
+It has been shown previously that the PC head is folded in water\cite{Gilliams2016}, while the presence of strong electrostatic interactions in DES is known to effect the structure of surfactants micelles\cite{Sanchez-Fernandez2018}.
+If we infer a similar folded structure for the PG head driven by a weaker interaction between the alcohol and phosphate groups, then we may explain the observed increase in volume to be due to unfolding of the PG head because we expect that the DES provides a greater charge screening effect than water.
+If so then we would also expect an increase in the thickness of the head layer in DES.
+This does seem to be the case: The PG head layer thickness was found to be \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and \SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at \SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements.
+For the PC head the stronger folding interaction, due to the formal charge on the ammonium group, means that no unfolding effect is observed.
 
-The determined volumes for the head and tails, and the thickness of the head layers, for DMPC and DPPC were then used as constraints in the co-refinement of the custom model against two contrasts NR data (Figure \ref{fig:neutron}).
-In these analysis the only two varying parameters were the tail tilt angle, $\theta_t$, and the interfacial roughness, $\sigma$.
-The quality of agreement with the NR measurements indicates that the values found for the head and tail volumes are consistent between the pair of measurements for the same system.
-It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the head and tail volumes determined from XRR measurements are robust-enough to be used in the modelling of NR data.
-Futhermore, the trends present with varying surface pressure in the XRR models are consistent with that found in the NR models.
+The volumes determined for the head and tails, and the thickness of the head layers, for DMPC and DPPC were used to constrain the fitting of corresponding NR data (Figure \ref{fig:neutron}).
+This leaves only two variables, $\theta_t$ and $\sigma$ to fit this data.
+The agreement is good and a confirmation that the volumes derived from XRR are consistent with the NR data.
+Furthermore, the observed trends with surface pressure are also consistent which adds some confidence in our conclusions.
 
@@
   \centering
-	\caption{\label{tab:neutron}\small The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
+	\caption{\label{tab:neutron} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
-This has the important implication that DES therefore offers the possibility of performing studies of model membranes in the absence of water.
+This has the important implication that DES therefore offer the possibility of performing studies of model membranes in the absence of water.
 Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
@@
 The ability to determine the head volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistent model within the analysis of the XRR and NR measurements.
-Futhermore, this work presents the first, to our knowledge, use of chemically-consistent parameterisation to co-refine XRR measurements at different surface concentrations.
+Furthermore, this work presents the first, to our knowledge, use of chemically-consistent parameterisation to co-refine XRR measurements at different surface concentrations.
 
@@
 A.R.M. is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-The authors thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
+Thanks also to the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
 We also thank Diamond Light Source (Experiment number SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.

### 2018-10-16 reports/si.tex
after tom edits

@@
 \usepackage{xr}
-\externaldocument{preprint}
+\externaldocument{apssamp}
 \usepackage{rotating}
@@
 These phospholipids were dissolved in chloroform (\SI{0.5}{\milli\gram\per\milli\liter}) at room temperature.
-PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphoditylglycerol head component, these are shown in Figure \ref{fig:heads}.
+PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphoditylglycerol head component, these are shown in Figure 1.
 

### 2018-10-16 reports/preprint.tex
after adrians comments

@@
 However, the native environment for lipids in-vivo is far from a simple aqueous solution.
-In fact, it has been suggested\cite{Dai2013,Hammond2017} that DES effectively form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
+In fact, it has been suggested\cite{Dai2013,Hammond2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
 
@@
 On water this is can be demonstrated with a Langmuir isotherm.
-However, while we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the poor wetting properties of the DES.
+However, while we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the high viscosity of the DES.
 This inconsistency means that we cannot be confident in the phase of the lipids based on the surface pressure alone.

### 2018-10-16 reports/preprint.tex
make arm corresponding author

@@
 \title{Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers}
-\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ \\
+\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag\ast}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$} \\
 S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold \textit{$^{abcg}$}$^{\ast}$}
@@
 $\ddag$~These authors have contributed equally to the work presented within. \\
-$\ast$~k.edler@bath.ac.uk; tom.arnold@esss.se}
+$\ast$~a.r.mccluskey@bath.ac.uk; tom.arnold@esss.se}
 

### 2018-10-17 reports/preprint.tex
after toms changes

@@
 For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
-In all cases the surface roughness was found to be relatively high compared to water. This is expected because the absolute surface tension of the DES is less than water\cite{Arnold2015}.
+In all cases the surface roughness was found to be relatively high compared to water.
+This is expected because the absolute surface tension of the DES is less than water, while a previous XRR measurement of pure choline chloride:glycerol suggests a roughness of 3.3\si{\angstrom}\cite{Arnold2015}, significantly higher than the capillary wave roughness of water of about 2.8\si{\angstrom}.
 

### 2018-10-17 reports/si.tex
after toms changes

@@
 Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
-XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius} under a Helium atmosphere.
-The aluminium Wilhelmy plate was used over a traditional paper plate because the DES was found to wet Aluminium but not paper, and therefore allowed more reproducible surface pressure measurements.
+XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an Aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius} under a Helium atmosphere.
+The Aluminium Wilhelmy plate was used over a traditional paper plate because the DES was found to wet Aluminium but not paper, and therefore allowed more reproducible surface pressure measurements.
 It is noted that the known phase transitions of DMPC and DMPG are 24 and \SI{23}{\celsius} respectively, which is very close to our measurement temperature.

### 2018-10-17 reports/preprint.tex
fix reference for des roughness

--- 2018-10-16 reports/preprint.tex
@@
 For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
-In all cases the surface roughness was found to be relatively high compared to water. This is expected because the absolute surface tension of the DES is less than water\cite{Arnold2015}.
+In all cases the surface roughness was found to be relatively high compared to water.
+This is expected because the absolute surface tension of the DES is less than water, while a previous XRR measurement of pure choline chloride:glycerol suggests a roughness of 3.3\si{\angstrom}\cite{Sanchez-Fernandez2016}, significantly higher than the capillary wave roughness of water of about 2.8\si{\angstrom}.
 

### 2018-10-17 reports/si.tex
all of tom's final comments

@@
 We are interested in comparing the volumes of the lipid components on a non-aqueous liquid.
-To allow this comparison, table \ref{tab:water} gives a variety of literature values for the component volumes of the lipids investigated in this work.
+To allow this comparison, Table \ref{tab:water} gives a variety of literature values for the component volumes of the lipids investigated in this work.
 
@@
 It is unclear whether this is because these peaks are absent or too weak to be measured.
-Nonetheless, figure \ref{fig:gixd} shows clear diffraction peaks (which we assume to be the (2, 0)) for DPPC at \SI{22}{\celsius} and for DMPC at \SI{7}{\celsius}.
+Nonetheless, Figure \ref{fig:gixd} shows clear diffraction peaks (which we assume to be the (2, 0)) for DPPC at \SI{22}{\celsius} and for DMPC at \SI{7}{\celsius}.
 These peaks are also visible at lower surface pressures (data not shown).
@@
 	\caption{The GIXD pattern for (a) DPPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, (b) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{22}{\celsius}, and (c) DMPC at \SI{30}{\milli\newton\per\meter} at \SI{7}{\celsius}.}
-	\label{fig:dppcgixd}
+	\label{fig:gixd}
 \end{figure}

### 2018-10-17 reports/preprint.tex
after adrians final comments

@@
   \centering
-	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
+	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the \SI{30}{\milli\newton\per\meter}.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 		Lipid & DLPC & DMPC & DPPC & DMPG \\
-    SP/\si{\milli\newton\per\meter} & 35 & 40 & 30 & 30 \\
 		\hline
-		$\theta_t$/\si{\degree} & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
-		$\sigma$/\si{\angstrom} & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
+		$\theta_t$/\si{\degree} & \input{../output/dlpc/angle30.txt} & \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
+		$\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
     \hline
@@
     \hline
-    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
-		$d_t$/\si{\angstrom} & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
+		$d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
 	\end{tabular}
@@
 This agrees well with the values found for the same head in water (Table \ref{tab:water}).
-Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, whereas it is considered to be smaller in water when measured by either DMPG using differential vibrating tube densimetry\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG using molecular dynamics simulations\cite{Kucerka2012} (\SI{289}{\cubic\angstrom}).
-This indicates that there may be some effect arising from the solvation in DES causing an apparent increase in the PG head volume when compared with water.
-
-Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of the four lipids.
-The three lipids with the PC head are consistent with values of around \SI{330}{\cubic\angstrom}, regardless of hydrocarbon tail.
-This agrees well with the values found for the same head in water (Table \ref{tab:water}).
 Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, which is significantly larger than values quoted in the literature for DMPG\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG\cite{Kucerka2012} (\SI{289}{\cubic\angstrom}).
@@
 If so then we would also expect an increase in the thickness of the head layer in DES.
-This does seem to be the case: The PG head layer thickness was found to be \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and \SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at \SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements.
+This does seem to be the case: The PG head layer thickness was found to be \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and \SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at \SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements at the air-water interface.
 For the PC head the stronger folding interaction, due to the formal charge on the ammonium group, means that no unfolding effect is observed.

### 2018-10-17 reports/si.tex
add highest sp table

@@
 
+%
+\begin{table}
+  \centering
+	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
+The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+\ref{equ:phih}}
+	\label{tab:liptab1}
+	\begin{tabular}{l|l|l|l|l}
+		Lipid & DLPC & DMPC & DPPC & DMPG \\
+    SP/mNm$^{-1}$ & 30 & 30 & 25 & 25 \\
+		\hline
+		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
+		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
+    \hline
+    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    \hline
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
+		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
+	\end{tabular}
+\end{table}
+%
 %

### 2018-10-17 reports/si.tex
short discussion of the correlations

@@
 
+These incidate the correlations present between the fitted parameters of the chemically-consistant model.
+Particularly noteworthy is the positive correlation between the head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$, which shows a clear interaction between these two variables.
+This can be rationalised as the smoothing of the interface between the head and the solvent, blurring the values of each variable.
+Additionally, it is noted that the correlations present are more substantial for the smaller lipid (particularly DLPC), this is due to the reduced structure presented for such a short tailed lipid and the fact that the length of the tail is closer to the value of the surface roughness for DES (\SI{3.3}{\angstrom}\cite{Sanchez-Fernandez2016}).
+
 \section{Tables and Figures}
@@
 %
-
 %

### 2018-10-17 reports/si.tex
short discussion of the correlations

@@
 
-These incidate the correlations present between the fitted parameters of the chemically-consistant model.
-Particularly noteworthy is the positive correlation between the head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$, which shows a clear interaction between these two variables.
-This can be rationalised as the smoothing of the interface between the head and the solvent, blurring the values of each variable.
+These two-dimensional PDFs give information about the correlations between the parameters fitted to the chemically-consistent model.
+The less circular in nature the 2-D PDF is, the greater the correlation present between the respective variables.
+Particularly noteworthy is the substantial positive correlation between the head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$, across all lipids.
+This interaction can be rationalised as being the result of the SLD of the solvent and the head layer (including some fraction of solvent) being similar.
+Such a correlation is unavoidable without considering many neutron contrasts of the lipid and solvent due to the solvophilic nature of the lipid heads.
 Additionally, it is noted that the correlations present are more substantial for the smaller lipid (particularly DLPC), this is due to the reduced structure presented for such a short tailed lipid and the fact that the length of the tail is closer to the value of the surface roughness for DES (\SI{3.3}{\angstrom}\cite{Sanchez-Fernandez2016}).

### 2018-10-17 reports/paper.tex
change preprint to paper

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%This is the LaTeX ARTICLE template for RSC journals
-%Copyright The Royal Society of Chemistry 2016
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ****** Start of file apssamp.tex ******
+%
+%   This file is part of the APS files in the REVTeX 4.1 distribution.
+%   Version 4.1r of REVTeX, August 2010
+%
+%   Copyright (c) 2009, 2010 The American Physical Society.
+%
+%   See the REVTeX 4 README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.1
+%
+% See the REVTeX 4 README file
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex apssamp.tex
+%  2)  bibtex apssamp
+%  3)  latex apssamp.tex
+%  4)  latex apssamp.tex
+%
+\documentclass[%
+ reprint,
+%superscriptaddress,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose,
+%preprint,
+%showpacs,preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+ amsmath,amssymb,
+ %aps,
+ prl,
+%pra,
+%prb,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-1}
 
-\documentclass[twoside,twocolumn,9pt]{article}
-\usepackage{extsizes}
-\usepackage[super,sort&compress,comma]{natbib}
-\usepackage[version=3]{mhchem}
-\usepackage[left=1.5cm, right=1.5cm, top=1.785cm, bottom=2.0cm]{geometry}
-\usepackage{balance}
-\usepackage{times,mathptmx}
-\usepackage{sectsty}
-\usepackage{graphicx}
-\usepackage{lastpage}
-\usepackage[format=plain,justification=justified,singlelinecheck=false,font={stretch=1.125,small,sf},labelfont=bf,labelsep=space]{caption}
-\usepackage{float}
-\usepackage{fancyhdr}
-\usepackage{fnpos}
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\addto{\captionsenglish}{%
-  \renewcommand{\refname}{Notes and references}
-}
-\usepackage{array}
-\usepackage{droidsans}
-\usepackage{charter}
-\usepackage[T1]{fontenc}
-\usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{setspace}
-\usepackage[compact]{titlesec}
-\usepackage{hyperref}
-%%%Please don't disable any packages in the preamble, as this may cause the template to display incorrectly.%%%
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+\usepackage[detect-all]{siunitx}
+\usepackage{hyperref}% add hypertext capabilities
+\usepackage{xr}
+\externaldocument{si}
+%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
 
-\newcommand*{\citen}[1]{%
-	\begingroup
-	\romannumeral-`\x % remove space at the beginning of \setcitestyle
-	\setcitestyle{numbers}%
-	\cite{#1}%
-	\endgroup
-}
-
-\usepackage{epstopdf}%This line makes .eps figures into .pdf - please comment out if not required.
-
-\definecolor{cream}{RGB}{222,217,201}
+%\usepackage[showframe,%Uncomment any one of the following lines to test
+%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
+%%text={7in,10in},centering,
+%%margin=1.5in,
+%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
+%%height=10in,a5paper,hmargin={3cm,0.8in},
+%]{geometry}
 
@@
 
-\pagestyle{fancy}
-\thispagestyle{plain}
-\fancypagestyle{plain}{
+\preprint{APS/123-QED}
 
-%%%HEADER%%%
-\fancyhead[C]{\includegraphics[width=18.5cm]{head_foot/header_bar}}
-\fancyhead[L]{\hspace{0cm}\vspace{1.5cm}\includegraphics[height=30pt]{head_foot/journal_name}}
-\fancyhead[R]{\hspace{0cm}\vspace{1.7cm}\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}
-\renewcommand{\headrulewidth}{0pt}
-}
-%%%END OF HEADER%%%
+\title{Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers}% Force line breaks with \\%
 
-%%%PAGE SETUP - Please do not change any commands within this section%%%
-\makeFNbottom
-\makeatletter
-\renewcommand\LARGE{\@setfontsize\LARGE{15pt}{17}}
-\renewcommand\Large{\@setfontsize\Large{12pt}{14}}
-\renewcommand\large{\@setfontsize\large{10pt}{12}}
-\renewcommand\footnotesize{\@setfontsize\footnotesize{7pt}{10}}
-\makeatother
+\author{A.~R.~McCluskey}
+\email{a.r.mccluskey@bath.ac.uk}
+  \thanks{These authors have contributed equally to the work presented within}
+  \altaffiliation[Also at ]{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
 
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\renewcommand\footnoterule{\vspace*{1pt}%
-\color{cream}\hrule width 3.5in height 0.4pt \color{black}\vspace*{5pt}}
-\setcounter{secnumdepth}{5}
+\author{A.~Sanchez-Fernandez}
+  \thanks{These authors have contributed equally to the work presented within}
+  \altaffiliation[Also at ]{European Spallation Source, SE-211 00 Lund, Sweden}
+  \altaffiliation[Present address ]{Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
 
-\makeatletter
-\renewcommand\@biblabel[1]{#1}
-\renewcommand\@makefntext[1]%
-{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
-\makeatother
-\renewcommand{\figurename}{\small{Fig.}~}
-\sectionfont{\sffamily\Large}
-\subsectionfont{\normalsize}
-\subsubsectionfont{\bf}
-\setstretch{1.125} %In particular, please do not alter this line.
-\setlength{\skip\footins}{0.8cm}
-\setlength{\footnotesep}{0.25cm}
-\setlength{\jot}{10pt}
-\titlespacing*{\section}{0pt}{4pt}{4pt}
-\titlespacing*{\subsection}{0pt}{15pt}{1pt}
-%%%END OF PAGE SETUP%%%
+\author{K.~J.~Edler}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
 
-%%%FOOTER%%%
-\fancyfoot{}
-\fancyfoot[LO,RE]{\vspace{-7.1pt}\includegraphics[height=9pt]{head_foot/LF}}
-\fancyfoot[CO]{\vspace{-7.1pt}\hspace{13.2cm}\includegraphics{head_foot/RF}}
-\fancyfoot[CE]{\vspace{-7.2pt}\hspace{-14.2cm}\includegraphics{head_foot/RF}}
-\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
-\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
-\fancyhead{}
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrulewidth}{0pt}
-\setlength{\arrayrulewidth}{1pt}
-\setlength{\columnsep}{6.5mm}
-\setlength\bibsep{1pt}
-%%%END OF FOOTER%%%
+\author{S.~C.~Parker}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
 
-%%%FIGURE SETUP - please do not change any commands within this section%%%
-\makeatletter
-\newlength{\figrulesep}
-\setlength{\figrulesep}{0.5\textfloatsep}
+\author{A.~J.~Jackson}
+  \altaffiliation[Also at ]{Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden}
+\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
 
-\newcommand{\topfigrule}{\vspace*{-1pt}%
-\noindent{\color{cream}\rule[-\figrulesep]{\columnwidth}{1.5pt}} }
+\author{R.~A.~Campbell}
+  \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France}
+\affiliation{Division of Pharmacy and Optometry, University of Manchester, Manchester, UK}
 
-\newcommand{\botfigrule}{\vspace*{-2pt}%
-\noindent{\color{cream}\rule[\figrulesep]{\columnwidth}{1.5pt}} }
+\author{T.~Arnold}
+\email{tom.arnold@esss.se}
+  \altaffiliation[Also at ]{ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 OQX, UK; Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK; Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
+\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
 
-\newcommand{\dblfigrule}{\vspace*{-1pt}%
-\noindent{\color{cream}\rule[-\figrulesep]{\textwidth}{1.5pt}} }
+\date{\today}% It is always \today, today,
+             %  but any date may be explicitly specified
 
-\makeatother
-%%%END OF FIGURE SETUP%%%
+\begin{abstract}
+  In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous liquid.
+  Deep eutectic solvents are a novel class of environmentally friendly non-aqueous room temperature liquids with tunable properties, that have wide ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
+  We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
+  However, the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leads to an apparent increase in its volume compared to that observed in water.
+  No such change was observed for the phosphocholine head, indicating that such interactions are head, and therefore solvent, specific.
+  This has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
+\begin{description}
+\item[Usage]
+Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and figure files, allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: **some doi**) under an MIT license.
+Reduced experimental datasets are available at \url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
+\end{description}
+\end{abstract}
 
-%%%TITLE, AUTHORS AND ABSTRACT%%%
-\twocolumn[
-  \begin{@twocolumnfalse}
-\vspace{3cm}
-\sffamily
-\begin{tabular}{m{4.5cm} p{13.5cm} }
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+\maketitle
 
-\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
-\vspace{0.3cm} & \vspace{0.3cm} \\
+%\tableofcontents
 
- & \noindent\large{Andrew R.
-McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ Karen J.
-Edler,\textit{$^{a}$}$^{\ast}$ Stephen C.
-Parker,\textit{$^{a}$} Andrew J.
-Jackson,\textit{$^{cd}$} Richard A.
-Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$} \\%Author names go here instead of "Full name", etc.
+Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013}.
+The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
+Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
+Recently DES have also been shown to exhibit a "solvophobic" effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein conformations\cite{Sanchez-Fernandez2017}.
 
-\includegraphics{head_foot/dates} & \noindent\normalsize{Deep eutectic solvents present a novel class of non-aqueous room temperature solvent with tunable properties, that are capable of promoting the self-assembly of surfactant molecules.
-However, the solvation model in these systems still challenges the classic understanding of amphiphilicity.
-In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous solvent.
-Furthermore, we use novel, chemically-consistant Bayesian modelling of X-ray and neutron reflectometry measurements to show the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head component, leading to an apparent increase in the component volume compared to that observed in water.
-No such change was observed for the phosphocholine head component, indicating that the interaction is head component specific.} \\
+Phospholipid monolayers at the air/water interface have been widely studied as simplistic models for biological membranes.
+As such, they have been used to gain insight into many biological processes that are technologically and medically relevant.
+For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
+However, the native environment for lipids in-vivo is far from a simple aqueous solution.
+In fact, it has been suggested\cite{Dai2013,Hammond2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
 
-\end{tabular}
-
-	\end{@twocolumnfalse} \vspace{0.6cm}
-
-  ]
-%%%END OF TITLE, AUTHORS AND ABSTRACT%%%
-
-%%%FONT SETUP - please do not change any commands within this section
-\renewcommand*\rmdefault{bch}\normalfont\upshape
-\rmfamily
-\section*{}
-\vspace{-1cm}
-
-%%%FOOTNOTES%%%
-
-\footnotetext{\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK.}}
-\footnotetext{\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK.}}
-\footnotetext{\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.}}
-\footnotetext{\textit{$^{d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden.}}
-\footnotetext{\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France.}}
-\footnotetext{\textit{$^{f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, M13 9PT, UK.}}
-\footnotetext{\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK.}}
-\footnotetext{\textit{$^{\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}}
-\footnotetext{$^{\ast}$~Corresponding author: k.edler@bath.ac.uk, tom.arnold@esss.se}
-
-%Please use \dag to cite the ESI in the main text of the article.
-%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
-\footnotetext{\dag~Electronic Supplementary Information (ESI) available: All datasets, figure file and analysis/plotting scripts, allowing for a fully reproducible analysis of all work presented herein.
-See DOI: 10.6084/m9.figshare.6661784}
-%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
-
-\footnotetext{$^{\ddag}$~These authors have contributed equally to the work presented within.}
-%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
-Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
-
-%%%END OF FOOTNOTES%%%
-
-%%%MAIN TEXT%%%%
-\section{Introduction}
-Deep eutectic solvents (DES) are green, sustainable solvents obtained through the complexation of naturally occurring compounds, such as sugars, alcohols, amines and carboxylic acids, among others.\cite{Smith2014, Dai2013} An extensive hydrogen-bonding network is present between these precursors, allowing the mixture to remain liquid at room temperature.\cite{Hammond2016, Hammond2017, Araujo2017} Additionally, through different combinations of the precursor materials, it is possible to tune the physicochemical properties of the solvent, such as polarity,\cite{Pandey2014} viscosity and surface tension,\cite{Smith2014} network charge,\cite{Zahn2016} and hydrophobicity.\cite{Ribeiro2015,vanOsch2015}
-
-It has recently been shown that these solvents have the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect.
-The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to the potential application of DES as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES are able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}
-
-The formation of phospholipid monolayers at the air/liquid interface plays a key role in many biological and technological processes.
-The solvent-specific solubility of different components of the phospholipid results in the formation of a stable monolayer of phospholipid at the interface.\cite{Mohwald1990} Phospholipids contain a charged head, either anionic or zwitterionic, and investigations at the air-salt water interface have revealed the importance of the phospholipid-ion interactions on structure, monomer packing, and stability of the monolayer.\cite{Mohwald1990,Kewalramani2010} Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and a non-aqueous media has not been previously reported, to the best of the authors' knowledge.
+This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any non-aqueous media, to the best of the authors' knowledge).
+We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
 
 Recent developments in computational resources and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
-This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework.\cite{Kluyver2016} In the area of neutron and X-ray reflectometry data-analysis, the landscape of open-source software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, motofit,\cite{Nelson2006} Aurore,\cite{Gerelli2016} and GenX.\cite{Bjorck2007} The Python library refnx is particularly powerful due to the ability to implement complete custom models which can contain chemically-relevant information.
+This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework\cite{Kluyver2016}.
+In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Rascal\cite{HughesRascal} Aurore\cite{Gerelli2016}, and GenX\cite{Bjorck2007}.
 
-The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This is a method for sampling a high-dimensionality parameter space, such as that which is relevant in reflectometry fitting, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously.
-The use of Bayesian inference allows the PDF for each fitting variable to be probed, therefore estimations of the inverse uncertainties associated with each parameter can be found, as well as information about the correlations between different variables.
-
-In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemically-consistant modelling of X-ray reflectometry (XRR) measurements.
-Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air.
-This allowed the nature of two, chemically distinct, phospholipid head components to be understood in this non-aqueous solvent, in addition to the effect of the tail chain length.
-The analysis was then extended to model complementary neutron reflectometry measurements for two contrasts of DMPC and DPPC at a single surface pressure.
-
-\section{Experimental}
-
-\subsection{Materials}
-Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) d$_9$-choline chloride (99 \%, 98 \% D, CK Isotopes) and d$_8$-glycerol (99 \%, 98 \% D, CK Isotopes)  were purchased and used without further purification.
-The DES was prepared by mixing the precursors at the appropriate ratio, and heating at 80 $^\circ$C until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at 40 $^\circ$C and subsequently stored under a dry atmosphere.
-Due to the limited availability of the deuterated precursors, a fully protonated subphase (hDES) and a partially deuterated subphase (hdDES) were prepared and used during the neutron reflectometry (NR) experiment.
-The partially deuterated subphase was prepared using the following mixtures of precursors: 1 mole of 0.38 fraction of h-choline chloride/0.62 mole fraction of d-choline chloride; and 2 moles of 0.56 mole fraction of h-glycerol/0.44 mole fraction of d-glycerol.
-The solvent was subsequently prepared following the procedure discussed above.
-
-The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
-Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have to little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}
-
-DPPC (> 99 \%, C$_{16}$ tails), DMPC (> 99 \%, C$_{14}$ tails), and DMPG (> 99 \%, C$_{14}$ tails) were supplied by Avanti Polar Lipids and DLPC (> 99 \%, C$_{12}$ tails) was supplied by Sigma-Aldrich and all were used as received.
-Deuterated versions of DPPC (d$_{62}$-DPPC, > 99 \%, deuterated tails-only) and DMPC (d$_{54}$-DPPC, > 99 \%, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
-These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature.
-PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphatidylglycerol head component, these are shown in Figure \ref{fig:heads}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.30\textwidth]{figures/head_groups}
-	\caption{The two lipid classes with different head components compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol, (b) phosphocholine.}
-	\label{fig:heads}
-\end{figure}
-
-\begin{table*}
-	\small
-	\caption{\ Lipid component volumes extracted from different literature sources.
-$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry.
-$^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
-	\label{tab:water}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l|lll|ll|ll|l|l}
-		\hline
-    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
-    \hline
-    Reference & [\citen{Armen1998}] & [\citen{Sun1994}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Pan2012}] & [\citen{Kucerka2012}] \\
-    \hline
-    $V_l$/\AA$^3$ & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1£$ & $1155.4\pm30.0£$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
-    $V_t$/\AA$^3$ & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0£$ & $815.9\pm15.5£$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
-    $V_h$/\AA$^3$ & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
-    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
-    T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
-    \hline
-	\end{tabular*}
-\end{table*}
-In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
-After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
-Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
-In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
-Instead, small Delrin adsorption troughs were used that did not have controllable barriers.
-So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.
-
-\subsection{Methods}
-XRR measurements were taken on I07 at Diamond Light Source, at 12.5 keV photon energy using the double-crystal-deflector.\cite{Arnold2012} The reflected intensity was measured in a momentum transfer range from 0.018 to 0.7 \AA$^{-1}$.
-The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
-Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
-XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and 35 mNm$^{-1}$, DMPC: 20, 25, 30, and 40 mNm$^{-1}$, DPPC: 15, 20, 25, and 30 mNm$^{-1}$, DMPG: 15, 20, 25, and 30 mNm$^{-1}$), as measured with an aluminium Wilhelmy plate; all measurements were conducted at 22 $^\circ$C.
-The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
-
-The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Data at two incident angles of 0.62$^\circ$ and 3.8$^\circ$ were measured to provide a momentum transfer range from 0.005 to 0.18 \AA$^{-1}$.
-Two surface pressures for each system and contrast was measured (DMPC: 20 and 25 mNm$^{-1}$, DPPC: 15 and 20 mNm$^{-1}$).
-Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours), kept under an inert atmosphere, and all measurements were conducted at 22 $^\circ$C.
-
-\subsection{Data analysis}
-The use of XRR and NR to analyse the structure of phospholipids on the surface of water has a history extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} The models used in the rationalisation of XRR and NR data have varied significantly in number of layers present, use of interfacial roughness, and parameterisation of physical constraints.
-Frequently these physical constraints include the component volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}.
-Additionally, a recent evaluation of the applicability of different models to surfactant and phospholipid monolayers from the NR perspective has been published,\cite{Campbell2018} that suggests possible oversights in the modelling of NR data.
-
-In Table \ref{tab:water}, there appears to be a general consensus that the component volume of the phosphocholine (PC) head is in the range from 320-360 \AA$^3$ while the phosphatidylglycerol (PG) head is in the range 289-291 \AA$^3$.
-However, we do not know whether the head component volumes used in the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
-The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES components.\cite{Sanchez-Fernandez2018} Furthermore, it has been shown that in the liquid expanded and condensed phases, which are often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured from other techniques,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}
-
-In this work we would therefore like to use a model that does not assume the molecular volume while remaining physical meaningful.
-To do this we have allowed the lipid component volumes to vary while constraining the overall system to be self-consistent across multiple different measurements.
-To do this we have used the Python library refnx\cite{Nelson2018}.
-This software allows the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s reflectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}).
-This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under CC-BY.\cite{mccluskey_2018c}
-
-Our chemically-consistent model is made up of two layers to define the lipid monolayer; the head layer at the interface with the solvent and tail layer at the interface with the air.
-The head components have a calculated scattering length, $b_h$, (found as a summation of the X-ray or neutron atomic scattering lengths), and a component volume, $V_h$.
-These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
-The tail components also have a calculated scattering length, $b_t$, roughness, $\sigma_t$, and a component volume, $V_t$.
-We have defined the thickness of the tail layer, $d_t$, in terms of the maximum (all-trans) length of the carbon tail, $t_t$, and the angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
-%
-\begin{equation}
-\label{equ:tl}
-d_t = t_t \cos{\theta_t}.
-\end{equation}
-%
-This was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g.
-it cannot be thicker than the maximum extended length of the lipid tail.
-The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
-%
-\begin{equation}
-\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}(\phi_i),
-\end{equation}
-%
-where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains neither solvent nor air, e.g.
-$\phi_t = 0$.
-To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
-%
-\begin{equation}
-\label{equ:phih}
-\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
-\end{equation}
-%
-Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
-$\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
-Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
-
-In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations.
-In keeping with the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the head thickness was fitted for each lipid across all surface pressures, as the thickness of the head layer was considered to be dependent on molecular dimensions only.
-The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
-The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} since this is the maximum chain length possible and the most likely conformation at the surface pressures studied.\cite{Hollinshead2009} For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
-Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.
+The use of a Python library, such as refnx, enables the implementation custom models that contain chemically-relevant information as well as the application of probability distribution function (PDF) sampling techniques.
+The Python library emcee\cite{Foreman-Mackey2013} offers refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method\cite{Goodman2010}.
+This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously\cite{Sivia2006}.
+Bayesian inference gives an understanding of the PDF for the fitted parameters and therefore estimations of their inverse uncertainties and inter-parameter correlations.
 
 %
-\begin{table}[h]
-	\small
-	\caption{\ The invariant parameters within the chemically-consistent model.
-	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
-	\label{tab:invariant}
-	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
-		\hline
-		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
-		\hline
-		X-ray & & & & \\
-		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
-		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
-		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
-		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
-		Air & -- & -- & -- & 0\\
-		DES & -- & -- & -- & 10.8$^b$ \\
-		\hline
-		Neutron & & & & \\
-		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
-		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
-		h-DES & -- & -- & -- & 0.43$^b$  \\
-		hd-DES & -- & -- & -- & 3.15$^b$ \\
-		\hline
-	\end{tabular*}
-\end{table}
+\begin{figure}[b]
+\includegraphics[width=0.3\textwidth]{figures/head_groups}
+\caption{\label{fig:heads}\small The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
+\end{figure}
 %
-In the second step, the head and tail component volumes, and head layer thickness determined from XRR were fixed for the refinement of the custom model against the NR measurements.
-This approach means that the number of variable parameters to fit the NR data can be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.
-Table \ref{tab:invariant} also gives the details of the scattering lengths and SLDs used as invariant parameters for the NR fitting.
-
-In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data.
-The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
-In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
-The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions (shown in detail in the ESI).
-This allowed asymmetric confidence intervals to be found for each of the variable parameters.
-However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e.
-they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.
+We report on measurements of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-DES (1:2 choline choride:glycerol) interface.
+In contrast to many previous studies\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed a chemically-consistent model (detail in the ESI) that allows for the co-refinement of reflectometry measurements at different surface pressure and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
+Instead these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG and DLPC.
+This model was required because we cannot assume that the electrostatic interactions between lipid head and the solvent are the same in the DES and in water.
+This may therefore influence the effective head volume which means we cannot rely on the literature values (see ESI) derived from measurements on or in water.
+Furthermore, it is known that, on water, increased surface pressure and associated LE-LC phase transitions lead to a compression of the lipid tail volume\cite{Marsh2010,Small1984} and this compaction has not necessarily been accounted for in the literature\cite{Campbell2018}.
+Our approach avoids this issue by making no assumption about the molecular volumes and only considering surface pressures that we believe to be in the same phase.
 
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
-	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up.
-The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.}
+	\caption{\small The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; see legend above each plot.
+The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:lipids}
@@
 %
-\section{Results \& Discussion}
-The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
-The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of all varied parameters for each lipid at the highest surface pressure measured, as well as the details of $d_t$ and $\phi_h$ which are determined from Eqns.
-\ref{equ:tl} and \ref{equ:phih} respectively.
-Each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
+Our model has more variables than we can uniquely fit with limited data.
+In reflectometry the usual approach to this problem is to collect more equivalent dataset with varying deuteration (NR). For reasons of cost and practicality this was not possible in this work.
+The other approach is to constrain the model so that the number of fitted variables are reduced, and is the approach taken here.
+To do this we add the constraint that a single tail volume can be used for all surface pressures.
+To justify this we need to be sure that the lipids remain in the same phase.
+On water this is can be demonstrated with a Langmuir isotherm.
+However, while we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the high viscosity of the DES.
+This inconsistency means that we cannot be confident in the phase of the lipids based on the surface pressure alone.
+Instead we have used grazing incidence X-ray diffraction to confirm the phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
+DPPC was found to be in the LC phase and DMPC in the LE phase at room temperature for the surface pressures measured (see Section \ref{sec:gixd}).
+We assume that DMPG and DLPC are also in the LE phase since there is no reason to believe that the phase behaviour in these systems differs significantly from DMPC at the same temperature.
 
-The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure.
-The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}.
-Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $d_t$ and $\phi_h$, again determined from Eqns.
-\ref{equ:tl} and \ref{equ:phih}.
-These are, once again, given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
+The model, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data.
+The associated SLD profiles are shown in Figure \ref{fig:lipids} while table \ref{tab:liptab} presents the results of the PDF for each of the varying parameters; the tail tilt angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
+In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure.
+The other parameters, $V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface pressures measured for each lipid.
+
 %
 \begin{table}
-	\small
-	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
-The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
-\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
-\ref{equ:phih}}
-	\label{tab:liptab}
-	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
+	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the \SI{30}{\milli\newton\per\meter}.
+The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
+\ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn.
+\ref{equ:phih}.}
+  \begin{ruledtabular}
+	\begin{tabular}{ccccc}
+    Lipid & DLPC & DMPC & DPPC & DMPG \\
     \hline
-		Lipid & DLPC & DMPC & DPPC & DMPG \\
-    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
+    $\theta_t$/\si{\degree} & \input{../output/dlpc/angle30.txt} & \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
+    $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
     \hline
-		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
-		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
+    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+    $V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+    $d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
     \hline
-    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
-		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
-		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
-    \hline
-    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
-		\hline
-	\end{tabular*}
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
+    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
+	\end{tabular}
+  \end{ruledtabular}
 \end{table}
@@
 
-\subsection{Effect of compression on monolayer thickness}
-Table \ref{tab:liptab} gives the best-fit values for each lipid at the highest surface pressure measured.
-From this, we can see that, as expected and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
-Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$ \AA\ at 30 mN/m\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=16.7$ \AA\ at 40 mN/m\cite{Helm1987} in water for DPPC.
+For each lipid, the tail layer thickness, $d_t$, increases with chain length and in general agrees with the literature for monolayers on water\cite{Mohwald1990,Vaknin1991}:
+For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
+In all cases the surface roughness was found to be relatively high compared to water.
+This is expected because the absolute surface tension of the DES is less than water, while a previous XRR measurement of pure choline chloride:glycerol suggests a roughness of 3.3\si{\angstrom}\cite{Sanchez-Fernandez2016}, significantly higher than the capillary wave roughness of water of about 2.8\si{\angstrom}.
 
+Figure \ref{fig:lipresults} shows the tail layer thickness variation with surface pressure.
+For DPPC and DMPC a plateau in thickness is reached at \SI{25}{\milli\newton\per\meter} and \SI{30}{\milli\newton\per\meter} respectively.
+Presumably a similar plateau would be seen for DMPG and DLPC at higher pressures.
+This phenomenon has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
 %
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
-	\caption{The PDFs of the head component volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.}
+	\caption{\small The PDFs of the head volume (left) and variation of $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
+The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
+\ref{equ:tl}.}
 	\label{fig:lipresults}
@@
 %
-The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
-It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateauing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC can be assumed to be at higher pressures than those studied.
-This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
 
-\subsection{Effect of compression on solvent concentration}
-In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer.
-This can be rationalised by considering that when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.
-A similar effect has been observed when increasing the surface pressure from 11 mNm$^{-1}$ to 31 mNm$^{-1)}$ for a DMPC/DMPG monolayer at the air-water interface.\cite{Bayerl1990}
+Figure \ref{fig:lipresults} also shows that for all four lipids there is a decrease in head solvation, $\phi_h$, with surface pressure.
+This is because an increase in the surface pressure means a reduction in the free volume available between the lipid heads, which in turn forces solvent molecules out of the layer, an effect that has also been observed on water\cite{Bayerl1990}.
 
-\subsection{Effect of compression on the lipid tail component volumes}
-It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
-It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
-However, this reduction has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elevated surface pressure.
-In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.
+Our fits suggest lower lipid tail volumes than previous measurements using other techniques (compare Tables \ref{tab:water} and \ref{tab:liptab}).
+It is unlikely that this is a result of the DES subphase since the tails do not directly interact with the solvent.
+However this may be related to the compaction of the monolayer at elevated surface pressures.
+The optimal value of the tail volume for DPPC in the LC phase\cite{Campbell2018} was found to be \SI{772}{\cubic\angstrom} at \SI{35}{\milli\newton\per\meter}, which agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work.
+Similarly the tail volume for DMPS in the LE phase\cite{Campbell2018}, \SI{714}{\cubic\angstrom} at \SI{10}{\milli\newton\per\meter}, broadly agrees with the values for DMPC (\input{../output/dmpc/vt.txt}\si{\cubic\angstrom}) and DMPG (\input{../output/dmpg/vt.txt}\si{\cubic\angstrom}) in this work.
+The literature value\cite{Pan2012} quoted for DMPG (at a lower temperature) is also similar to our result (but slightly smaller).
+We find that the reduction is \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
+In general our results are at least self-consistent while comparisons to the literature are favourable.
 
-In this work, a single tail component volume was fitted to each lipid for all four surface pressures that were measured.
-This is based on the assumption, that at all four surface pressures, the lipids adopt the same phase (as discussed in the ESI) and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the chain tilt angle.
-It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail component volumes are also reduced in the current XRR measurements compared to those determined previously.
-The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
-Notably this value is similar to that found in this work for DMPC, which has the same tail structure and suggests that our results are at least self-consistent.
+Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of the four lipids.
+The three lipids with the PC head are consistent with values of around \SI{330}{\cubic\angstrom}, regardless of hydrocarbon tail.
+This agrees well with the values found for the same head in water (Table \ref{tab:water}).
+Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, which is significantly larger than values quoted in the literature for DMPG\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG\cite{Kucerka2012} (\SI{289}{\cubic\angstrom}).
+This suggests that there may be some effect arising from the solvation in DES.
 
-\subsection{Solvent effect on lipid head component volumes}
-Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids.
-The three lipids with the PC head component are consistent, giving values of $\sim330$ \AA$^3$, regardless of tail component.
-This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
-Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$.
-The PG head component volume in water, from either DMPG using differential vibrating tube densimetry\cite{Pan2012} or POPG using molecular dynamics simulations,\cite{Kucerka2012} is noticeably smaller.
-This indicates that there may be some effect arising from the solvation in choline cloride:glycerol causing an apparent increase in the PG component volume when compared with water.
+The major difference between the two heads is the fact PG head is negatively charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
+It has been shown previously that the PC head is folded in water\cite{Gilliams2016}, while the presence of strong electrostatic interactions in DES is known to effect the structure of surfactants micelles\cite{Sanchez-Fernandez2018}.
+If we infer a similar folded structure for the PG head driven by a weaker interaction between the alcohol and phosphate groups, then we may explain the observed increase in volume to be due to unfolding of the PG head because we expect that the DES provides a greater charge screening effect than water.
+If so then we would also expect an increase in the thickness of the head layer in DES.
+This does seem to be the case: The PG head layer thickness was found to be \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and \SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at \SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements at the air-water interface.
+For the PC head the stronger folding interaction, due to the formal charge on the ammonium group, means that no unfolding effect is observed.
 
-The major difference between the two head components is the fact PG component is negatively charged whereas the PC component is zwitterionic.
-It has been shown previously that the conformation for the PC component is folded in water,\cite{Gilliams2016} due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
-A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
-However, such an interaction would be weaker than that observed in the PC component.
-Therefore, this observed increase found for the PG component volume in DES when compared with water may be due to the unfolding of the PG head.
-This unfolding would be made possible by the charged nature of the solvent providing a greater screening effect for the PG head than are present in water.
-This effect may not be observed for the PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group.
-It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements,\cite{Clifton2012} which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
-
-\subsection{Refinement of neutron reflectometry}
-The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head component volume is consistant between the pair of measurements for the same system.
-It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust enough to be used in the modelling of NR data.
-Futhermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components are consistant with that found in the NR models.
+The volumes determined for the head and tails, and the thickness of the head layers, for DMPC and DPPC were used to constrain the fitting of corresponding NR data (Figure \ref{fig:neutron}).
+This leaves only two variables, $\theta_t$ and $\sigma$ to fit this data.
+The agreement is good and a confirmation that the volumes derived from XRR are consistent with the NR data.
+Furthermore, the observed trends with surface pressure are also consistent which adds some confidence in our conclusions.
 %
@@
 	\includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
-	\caption{The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$, the h-DES contrast is shown in blue while the hd-DES in green; (a) DMPC, (b) DPPC.
-The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity.}
+	\caption{\small The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$ for two contrasts (see legend above each plot); (a) DMPC, (b) DPPC.
+The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:neutron}
@@
 %
+%
 \begin{table}
-	\small
-	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
+  \caption{\label{tab:neutron} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
 The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
@@
 \ref{equ:phih}.}
-	\label{tab:neutron}
-	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}l|ll|ll}
-		\hline
-		Lipid & d$_{54}$-DMPC & & d$_{62}$-DPPC & \\
+  \begin{ruledtabular}
+	\begin{tabular}{ccccc}
+    Lipid & \multicolumn{2}{c}{d$_{54}$-DMPC} & \multicolumn{2}{c}{d$_{62}$-DPPC} \\
     SP/mNm$^{-1}$ & 20 & 25 & 15 & 20 \\
@@
     $d_t$/\AA & \input{../output/dmpc/tail20_neutron.txt} & \input{../output/dmpc/tail25_neutron.txt} & \input{../output/dppc/tail15_neutron.txt} & \input{../output/dppc/tail20_neutron.txt} \\
-		\hline
-	\end{tabular*}
+	\end{tabular}
+  \end{ruledtabular}
 \end{table}
@@
 
-\section{Conclusions}
-
 For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a non-aqueous liquid surface.
-Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of phospholipid monolayers at the air-liquid interface.
+Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of functional phospholipid monolayers at the air-liquid interface.
 
@@
 Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
-However, the PG component did show a significant difference; having a larger head component volume than observed for the same system in water.
-This suggests that the transfer of lipids to a DES is not just a simple substitution of the subphase.
-In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the partially charged solvent.
+However, the fact remains that the PG lipid did show a significant difference; having a larger head volume than observed for the same system in water.
+This shows that the transfer of lipids to a DES is not just a simple substitution of the subphase.
+In this specific case we have proposed an explanation based on unfolding of the PG head that is enabled by electrostatic screening of the head charges by the charged solvent.
 
-The ability to determine the head component volume was facilitated by access to easy to use, open-source software that allowed for the straightforward use of a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
-Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
+The ability to determine the head volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistent model within the analysis of the XRR and NR measurements.
+Furthermore, this work presents the first, to our knowledge, use of chemically-consistent parameterisation to co-refine XRR measurements at different surface concentrations.
 
-\section*{Conflicts of interest}
-There are no conflicts to declare.
+\begin{acknowledgments}
+The authors thank Andrew Nelson for his help with the refnx software.
+A.R.M. is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
+Thanks also to the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
+We also thank Diamond Light Source (Experiment number SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
+\end{acknowledgments}
 
-\section*{Acknowledgements}
-The authors thank the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
-A.R.M.
-is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-We also thank Diamond Light Source (Experiment Number: SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
-
-%%%END OF MAIN TEXT%%%
-
-%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
-
-\balance
-
-%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
-%\renewcommand\refname{Notes and references}
-
-%%%REFERENCES%%%
-\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
-\bibliographystyle{rsc} %the RSC's .bst file
+\bibliography{bibi}% Produces the bibliography via BibTeX.
 
 \end{document}
+%
+% ****** End of file apssamp.tex ******

### 2018-10-17 reports/paper.tex
cleaning things up and updating readme and make
change his to their
add reference to refl1d

@@
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.1 distribution.
-%   Version 4.1r of REVTeX, August 2010
-%
-%   Copyright (c) 2009, 2010 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
 \documentclass[%
@@
  %aps,
- prl,
+ %prl,
 %pra,
@@
 \item[Usage]
-Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and figure files, allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: **some doi**) under an MIT license.
+Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and figure files, allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: **zenodo-doi**) under a CC-BY 4.0 license.
 Reduced experimental datasets are available at \url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
@@
 This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework\cite{Kluyver2016}.
-In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Rascal\cite{HughesRascal} Aurore\cite{Gerelli2016}, and GenX\cite{Bjorck2007}.
+In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Rascal\cite{HughesRascal} Aurore\cite{Gerelli2016}, Refl1D\cite{Kienzle2011}, and GenX\cite{Bjorck2007}.
 
@@
 \begin{acknowledgments}
-The authors thank Andrew Nelson for his help with the refnx software.
+The authors thank Andrew Nelson for their help with the refnx software.
 A.R.M. is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).

### 2018-10-17 reports/paper.tex
get 80 character lines

@@
-\documentclass[%
- reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose,
-%preprint,
-%showpacs,preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- %aps,
- %prl,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
+\documentclass[amsmath,amssymb,twocolumn]{revtex4-1}
 
@@
 
-\title{Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers}% Force line breaks with \\%
+\title{Bayesian determination of the effect of a deep eutectic solvent on the
+structure of lipid monolayers}% Force line breaks with \\%
 
@@
   \thanks{These authors have contributed equally to the work presented within}
-  \altaffiliation[Also at ]{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
+  \altaffiliation[Also at ]{Diamond Light Source, Harwell Campus, Didcot,
+  OX11 0DE, UK}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
 
@@
   \thanks{These authors have contributed equally to the work presented within}
-  \altaffiliation[Also at ]{European Spallation Source, SE-211 00 Lund, Sweden}
-  \altaffiliation[Present address ]{Department of Food Technology, Lund University, SE-211 00 Lund, Sweden}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
+  \altaffiliation[Also at ]{European Spallation Source, SE-211 00 Lund,
+  Sweden}
+  \altaffiliation[Present address ]{Department of Food Technology, Lund
+  University, SE-211 00 Lund, Sweden}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
 
 \author{K.~J.~Edler}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
 
 \author{S.~C.~Parker}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
 
 \author{A.~J.~Jackson}
-  \altaffiliation[Also at ]{Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden}
+  \altaffiliation[Also at ]{Department of Physical Chemistry,
+  Lund University, SE-211 00 Lund, Sweden}
 \affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
@@
 \author{R.~A.~Campbell}
-  \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France}
-\affiliation{Division of Pharmacy and Optometry, University of Manchester, Manchester, UK}
+  \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs,
+  38000, Grenoble, France}
+\affiliation{Division of Pharmacy and Optometry, University of Manchester,
+Manchester, UK}
 
@@
 \email{tom.arnold@esss.se}
-  \altaffiliation[Also at ]{ISIS Neutron and Muon Source, Science and Technology Facilities Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 OQX, UK; Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK; Department of Chemistry, University of Bath, Claverton Down, Bath, BA2 7AY, UK}
+  \altaffiliation[Also at ]{ISIS Neutron and Muon Source, Science and
+  Technology Facilities Council, Rutherford Appleton Laboratory, Harwell
+  Oxford, Didcot OX11 OQX, UK; Diamond Light Source, Harwell Campus, Didcot,
+  OX11 0DE, UK; Department of Chemistry, University of Bath, Claverton Down,
+  Bath, BA2 7AY, UK}
 \affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
@@
 \begin{abstract}
-  In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and a non-aqueous liquid.
-  Deep eutectic solvents are a novel class of environmentally friendly non-aqueous room temperature liquids with tunable properties, that have wide ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
-  We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
-  However, the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leads to an apparent increase in its volume compared to that observed in water.
-  No such change was observed for the phosphocholine head, indicating that such interactions are head, and therefore solvent, specific.
-  This has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
+  In this work, we present the first example of the self-assembly of
+  phospholipid monolayers at the interface between air and a non-aqueous
+  liquid.
+  Deep eutectic solvents are a novel class of environmentally friendly
+  non-aqueous room temperature liquids with tunable properties, that have
+  wide ranging potential applications and are capable of promoting the
+  self-assembly of surfactant molecules.
+  We use a chemically-consistent Bayesian modelling of X-ray and neutron
+  reflectometry measurements to show that these monolayers broadly behave
+  as they do on water.
+  However, the ability of the deep eutectic solvent to interact with the
+  phosphatidylglycerol lipid head, leads to an apparent increase in its
+  volume compared to that observed in water.
+  No such change was observed for the phosphocholine head, indicating that
+  such interactions are head, and therefore solvent, specific.
+  This has important implications for the potential uses of these solvents
+  and for our understanding of how biomolecules behave in the absence of water.
 \begin{description}
 \item[Usage]
-Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and figure files, allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: **zenodo-doi**) under a CC-BY 4.0 license.
-Reduced experimental datasets are available at \url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
+Electronic Supplementary Information (ESI) available: All analysis/plotting
+scripts and figure files, allowing for a fully reproducible, and automated,
+analysis workflow for the work presented is available at
+\url{https://github.com/arm61/lipids_at_airdes} (DOI: **zenodo-doi**) under
+a CC-BY 4.0 license.
+Reduced experimental datasets are available at
+\url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
 \end{description}
@@
 
-Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids\cite{Smith2014,Dai2013}.
-The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
-Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014}, network charge\cite{Zahn2016}, and hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
-Recently DES have also been shown to exhibit a "solvophobic" effect through the promotion of surfactant micelle formation\cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018}, phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein conformations\cite{Sanchez-Fernandez2017}.
+Deep eutectic solvents (DES) are green, sustainable liquids that are obtained
+through the combination of ionic species with compounds that act as hydrogen
+bond donors, such as sugars, alcohols, amines, and carboxylic
+acids\cite{Smith2014,Dai2013}.
+The resulting extensive hydrogen bonding network is able to stabilise the
+ionic species and allows the eutectic mixture to remain liquid at room
+temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
+Through different combinations of the precursor materials, it is possible to
+tune the solvent's physicochemical properties, such as
+polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014},
+network charge\cite{Zahn2016}, and
+hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
+Recently DES have also been shown to exhibit a "solvophobic" effect through
+the promotion of surfactant micelle
+formation\cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018},
+phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and
+the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein
+conformations\cite{Sanchez-Fernandez2017}.
 
-Phospholipid monolayers at the air/water interface have been widely studied as simplistic models for biological membranes.
-As such, they have been used to gain insight into many biological processes that are technologically and medically relevant.
-For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer\cite{Mohwald1990,Kewalramani2010}.
-However, the native environment for lipids in-vivo is far from a simple aqueous solution.
-In fact, it has been suggested\cite{Dai2013,Hammond2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
+Phospholipid monolayers at the air/water interface have been widely studied
+as simplistic models for biological membranes.
+As such, they have been used to gain insight into many biological processes
+that are technologically and medically relevant.
+For example, investigations at the air/salt-water interface have identified
+the importance that interactions between charged phospholipid heads and ions
+present in solution have on the structure, monomer packing and stability of
+the monolayer\cite{Mohwald1990,Kewalramani2010}.
+However, the native environment for lipids in-vivo is far from a simple
+aqueous solution.
+In fact, it has been suggested\cite{Dai2013,Hammond2017} that DES might form
+within the crowded cellular environment and could assist in solubilizing
+biological species in an intermediate environment between that of the
+hydrophobic phospholipid tails and highly polar water rich regions, thereby
+assisting survival under extreme conditions such as freezing temperatures or
+drought where the water content of cells is restricted.
 
-This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any non-aqueous media, to the best of the authors' knowledge).
-We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
+This work presents the first observation of phospholipid monolayers at an
+air-DES interface (or for that matter, any non-aqueous media, to the best of
+the authors' knowledge).
+We have used a chemically-consistent approach to model X-ray (XRR) and
+neutron (NR) reflectometry measurements and thereby evaluate the effect of
+this non-aqueous solvent on the structure of phospholipid monolayers.
 
-Recent developments in computational resources and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
-This has benefitted significantly from open-source software projects such as the Python language\cite{vanRossum1995} and the Jupyter notebooks framework\cite{Kluyver2016}.
-In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Rascal\cite{HughesRascal} Aurore\cite{Gerelli2016}, Refl1D\cite{Kienzle2011}, and GenX\cite{Bjorck2007}.
+Recent developments in computational resources and software have enabled
+powerful methodologies and algorithms to be harnessed by those from
+non-expert backgrounds.
+This has benefitted significantly from open-source software projects such as
+the Python language\cite{vanRossum1995} and the Jupyter notebooks
+framework\cite{Kluyver2016}.
+In the area of NR and XRR, the landscape of data-analysis software is diverse,
+with a range of software packages available from a variety of sources;
+refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Rascal\cite{HughesRascal}
+Aurore\cite{Gerelli2016}, Refl1D\cite{Kienzle2011}, and GenX\cite{Bjorck2007}.
 
-The use of a Python library, such as refnx, enables the implementation custom models that contain chemically-relevant information as well as the application of probability distribution function (PDF) sampling techniques.
-The Python library emcee\cite{Foreman-Mackey2013} offers refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method\cite{Goodman2010}.
-This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously\cite{Sivia2006}.
-Bayesian inference gives an understanding of the PDF for the fitted parameters and therefore estimations of their inverse uncertainties and inter-parameter correlations.
+The use of a Python library, such as refnx, enables the implementation custom
+models that contain chemically-relevant information as well as the
+application of probability distribution function (PDF) sampling techniques.
+The Python library emcee\cite{Foreman-Mackey2013} offers refnx to access the
+Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble
+method\cite{Goodman2010}.
+This allows the sampling of the high-dimensionality parameter space, relevant
+in reflectomety analysis, in a Bayesian fashion, where the new samples are
+generated with consideration of those sampled previously\cite{Sivia2006}.
+Bayesian inference gives an understanding of the PDF for the fitted
+parameters and therefore estimations of their inverse uncertainties and
+inter-parameter correlations.
 
@@
 \includegraphics[width=0.3\textwidth]{figures/head_groups}
-\caption{\label{fig:heads}\small The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
+\caption{\label{fig:heads}\small The two lipid classes with different head
+groups compared in this study, where R indicates the hydrocarbon tail;
+(a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
 \end{figure}
 %
-We report on measurements of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-DES (1:2 choline choride:glycerol) interface.
-In contrast to many previous studies\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed a chemically-consistent model (detail in the ESI) that allows for the co-refinement of reflectometry measurements at different surface pressure and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
-Instead these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG and DLPC.
-This model was required because we cannot assume that the electrostatic interactions between lipid head and the solvent are the same in the DES and in water.
-This may therefore influence the effective head volume which means we cannot rely on the literature values (see ESI) derived from measurements on or in water.
-Furthermore, it is known that, on water, increased surface pressure and associated LE-LC phase transitions lead to a compression of the lipid tail volume\cite{Marsh2010,Small1984} and this compaction has not necessarily been accounted for in the literature\cite{Campbell2018}.
-Our approach avoids this issue by making no assumption about the molecular volumes and only considering surface pressures that we believe to be in the same phase.
+We report on measurements of four phospholipids monolayers, namely
+1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails),
+1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),
+1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and
+1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol)
+(DMPG, C$_{14}$ tails), at the air-DES (1:2 choline choride:glycerol)
+interface.
+In contrast to many previous studies\cite{Mohwald1990,Kewalramani2010,
+Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed
+a chemically-consistent model (detail in the ESI) that allows for the
+co-refinement of reflectometry measurements at different surface pressure
+and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
+Instead these parameters were allowed to vary for each lipid while being
+constrained to be self-consistent over different surface pressures in the
+same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for
+DMPC, DMPG and DLPC.
+This model was required because we cannot assume that the electrostatic
+interactions between lipid head and the solvent are the same in the DES and
+in water. This may therefore influence the effective head volume which means
+we cannot rely on the literature values (see ESI) derived from measurements
+on or in water.
+Furthermore, it is known that, on water, increased surface pressure and
+associated LE-LC phase transitions lead to a compression of the lipid tail
+volume\cite{Marsh2010,Small1984} and this compaction has not necessarily
+been accounted for in the literature\cite{Campbell2018}.
+Our approach avoids this issue by making no assumption about the molecular
+volumes and only considering surface pressures that we believe to be in the
+same phase.
 
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
-	\caption{\small The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; see legend above each plot.
-The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
+	\caption{\small The XRR profiles (left) and SLD profiles (right) for each
+  of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four
+  measured surface pressures; see legend above each plot. The different
+  surface pressure XRR profiles have been offset in the $y$-axis by an order
+  of magnitude and SLD profiles offset in the $y$-axis by
+  \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:lipids}
@@
 Our model has more variables than we can uniquely fit with limited data.
-In reflectometry the usual approach to this problem is to collect more equivalent dataset with varying deuteration (NR). For reasons of cost and practicality this was not possible in this work.
-The other approach is to constrain the model so that the number of fitted variables are reduced, and is the approach taken here.
-To do this we add the constraint that a single tail volume can be used for all surface pressures.
-To justify this we need to be sure that the lipids remain in the same phase.
-On water this is can be demonstrated with a Langmuir isotherm.
-However, while we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the high viscosity of the DES.
-This inconsistency means that we cannot be confident in the phase of the lipids based on the surface pressure alone.
-Instead we have used grazing incidence X-ray diffraction to confirm the phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
-DPPC was found to be in the LC phase and DMPC in the LE phase at room temperature for the surface pressures measured (see Section \ref{sec:gixd}).
-We assume that DMPG and DLPC are also in the LE phase since there is no reason to believe that the phase behaviour in these systems differs significantly from DMPC at the same temperature.
+In reflectometry the usual approach to this problem is to collect more
+equivalent dataset with varying deuteration (NR). For reasons of cost and
+practicality this was not possible in this work.
+The other approach is to constrain the model so that the number of fitted
+variables are reduced, and is the approach taken here.
+To do this we add the constraint that a single tail volume can be used for
+all surface pressures. To justify this we need to be sure that the lipids
+remain in the same phase. On water this is can be demonstrated with a
+Langmuir isotherm.
+However, while we have confidence that the individual surface pressures
+measured were reliable, we were unable to collect consistent Langmuir
+isotherm measurements, due to the high viscosity of the DES.
+This inconsistency means that we cannot be confident in the phase of the
+lipids based on the surface pressure alone.
+Instead we have used grazing incidence X-ray diffraction to confirm the
+phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
+DPPC was found to be in the LC phase and DMPC in the LE phase at room
+temperature for the surface pressures measured (see Section \ref{sec:gixd}).
+We assume that DMPG and DLPC are also in the LE phase since there is no
+reason to believe that the phase behaviour in these systems differs
+significantly from DMPC at the same temperature.
 
-The model, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data.
-The associated SLD profiles are shown in Figure \ref{fig:lipids} while table \ref{tab:liptab} presents the results of the PDF for each of the varying parameters; the tail tilt angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
-In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure.
-The other parameters, $V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface pressures measured for each lipid.
+The model, based on the standard two-layer model widely used for lipids on
+water, was first fitted to the experimental XRR data.
+The associated SLD profiles are shown in Figure \ref{fig:lipids} while
+Table \ref{tab:liptab} presents the results of the PDF for each of the
+varying parameters; the tail tilt angle, $\theta_t$, the interfacial
+roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively,
+and the head layer thickness, $d_h$.
+In order to constrain the fitting process only $\theta_t$ and $\sigma$ were
+allowed to vary independently of surface pressure. The other parameters,
+$V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface
+pressures measured for each lipid.
 
@@
 \begin{table}
-	\caption{\label{tab:liptab} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the \SI{30}{\milli\newton\per\meter}.
-The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn.
-\ref{equ:phih}.}
+	\caption{\label{tab:liptab} The best-fit values, and associated 95 \%
+  confidence intervals for the varying parameters in the XRR models, at the
+  \SI{30}{\milli\newton\per\meter}. The values of $d_t$ were found from the
+  appropriate values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for
+  $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih}.}
   \begin{ruledtabular}
@@
     \hline
-    $\theta_t$/\si{\degree} & \input{../output/dlpc/angle30.txt} & \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
-    $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
+    $\theta_t$/\si{\degree} & \input{../output/dlpc/angle30.txt} &
+    \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle30.txt} &
+    \input{../output/dmpg/angle30.txt} \\
+    $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} &
+    \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} &
+    \input{../output/dmpg/rough30.txt} \\
     \hline
-    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
-    $V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
-    $d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
+    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} &
+    \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} &
+    \input{../output/dmpg/vt.txt} \\
+    $V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} &
+    \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} &
+    \input{../output/dmpg/vh.txt} \\
+    $d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} &
+    \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} &
+    \input{../output/dmpg/head.txt} \\
     \hline
-    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
-    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} &
+    \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} &
+    \input{../output/dmpg/solh30.txt} \\
+    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} &
+    \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} &
+    \input{../output/dmpg/tail30.txt} \\
 	\end{tabular}
@@
 
-For each lipid, the tail layer thickness, $d_t$, increases with chain length and in general agrees with the literature for monolayers on water\cite{Mohwald1990,Vaknin1991}:
-For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
-In all cases the surface roughness was found to be relatively high compared to water.
-This is expected because the absolute surface tension of the DES is less than water, while a previous XRR measurement of pure choline chloride:glycerol suggests a roughness of 3.3\si{\angstrom}\cite{Sanchez-Fernandez2016}, significantly higher than the capillary wave roughness of water of about 2.8\si{\angstrom}.
+For each lipid, the tail layer thickness, $d_t$, increases with chain length
+and in general agrees with the literature for monolayers on
+water\cite{Mohwald1990,Vaknin1991}:
+For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at
+\SI{30}{\milli\newton\per\meter} in DES compared with
+$d_t=\SI{15.8}{\angstrom}$ at
+\SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for
+DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at
+\SI{30}{\milli\newton\per\meter} in DES compared with
+$d_t=\SI{16.7}{\angstrom}$ at
+\SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
+In all cases the surface roughness was found to be relatively high compared
+to water.
+This is expected because the absolute surface tension of the DES is less
+than water, while a previous XRR measurement of pure choline
+chloride:glycerol suggests a roughness of
+3.3\si{\angstrom}\cite{Sanchez-Fernandez2016}, significantly higher than
+the capillary wave roughness of water of about 2.8\si{\angstrom}.
 
-Figure \ref{fig:lipresults} shows the tail layer thickness variation with surface pressure.
-For DPPC and DMPC a plateau in thickness is reached at \SI{25}{\milli\newton\per\meter} and \SI{30}{\milli\newton\per\meter} respectively.
-Presumably a similar plateau would be seen for DMPG and DLPC at higher pressures.
-This phenomenon has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.
+Figure \ref{fig:lipresults} shows the tail layer thickness variation with
+surface pressure. For DPPC and DMPC a plateau in thickness is reached at
+\SI{25}{\milli\newton\per\meter} and \SI{30}{\milli\newton\per\meter}
+respectively. Presumably a similar plateau would be seen for DMPG and DLPC
+at higher pressures.
+This phenomenon has been noted before for DMPC\cite{Bayerl1990} and
+DPPC\cite{Campbell2018} at the air-water interface.
 %
@@
 	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
-	\caption{\small The PDFs of the head volume (left) and variation of $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.
-The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl}.}
+	\caption{\small The PDFs of the head volume (left) and variation of
+  $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of
+  the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG. The values of
+  $d_t$ were found from the appropriate values of $\theta_t$ using
+  Eqn. \ref{equ:tl}.}
 	\label{fig:lipresults}
@@
 
-Figure \ref{fig:lipresults} also shows that for all four lipids there is a decrease in head solvation, $\phi_h$, with surface pressure.
-This is because an increase in the surface pressure means a reduction in the free volume available between the lipid heads, which in turn forces solvent molecules out of the layer, an effect that has also been observed on water\cite{Bayerl1990}.
+Figure \ref{fig:lipresults} also shows that for all four lipids there is a
+decrease in head solvation, $\phi_h$, with surface pressure.
+This is because an increase in the surface pressure means a reduction in the
+free volume available between the lipid heads, which in turn forces solvent
+molecules out of the layer, an effect that has also been observed on
+water\cite{Bayerl1990}.
 
-Our fits suggest lower lipid tail volumes than previous measurements using other techniques (compare Tables \ref{tab:water} and \ref{tab:liptab}).
-It is unlikely that this is a result of the DES subphase since the tails do not directly interact with the solvent.
-However this may be related to the compaction of the monolayer at elevated surface pressures.
-The optimal value of the tail volume for DPPC in the LC phase\cite{Campbell2018} was found to be \SI{772}{\cubic\angstrom} at \SI{35}{\milli\newton\per\meter}, which agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work.
-Similarly the tail volume for DMPS in the LE phase\cite{Campbell2018}, \SI{714}{\cubic\angstrom} at \SI{10}{\milli\newton\per\meter}, broadly agrees with the values for DMPC (\input{../output/dmpc/vt.txt}\si{\cubic\angstrom}) and DMPG (\input{../output/dmpg/vt.txt}\si{\cubic\angstrom}) in this work.
-The literature value\cite{Pan2012} quoted for DMPG (at a lower temperature) is also similar to our result (but slightly smaller).
-We find that the reduction is \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
-In general our results are at least self-consistent while comparisons to the literature are favourable.
+Our fits suggest lower lipid tail volumes than previous measurements using
+other techniques (compare Tables \ref{tab:water} and \ref{tab:liptab}).
+It is unlikely that this is a result of the DES subphase since the tails do
+not directly interact with the solvent.
+However this may be related to the compaction of the monolayer at elevated
+surface pressures.
+The optimal value of the tail volume for DPPC in the LC
+phase\cite{Campbell2018} was found to be \SI{772}{\cubic\angstrom} at
+\SI{35}{\milli\newton\per\meter}, which agrees well with the value of
+\input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work.
+Similarly the tail volume for DMPS in the LE phase\cite{Campbell2018},
+\SI{714}{\cubic\angstrom} at \SI{10}{\milli\newton\per\meter}, broadly
+agrees with the values for
+DMPC (\input{../output/dmpc/vt.txt}\si{\cubic\angstrom}) and DMPG
+(\input{../output/dmpg/vt.txt}\si{\cubic\angstrom}) in this work.
+The literature value\cite{Pan2012} quoted for DMPG (at a lower temperature) is
+also similar to our result (but slightly smaller).
+We find that the reduction is \SIrange{8}{12}{\percent} for DPPC, DMPC and
+DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, in
+good agreement with the maximum compression percentage of \SI{15}{\percent}
+noted by Small \emph{et al.}\cite{Small1984}.
+In general our results are at least self-consistent while comparisons to the
+literature are favourable.
 
-Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of the four lipids.
-The three lipids with the PC head are consistent with values of around \SI{330}{\cubic\angstrom}, regardless of hydrocarbon tail.
-This agrees well with the values found for the same head in water (Table \ref{tab:water}).
-Interestingly, the volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, which is significantly larger than values quoted in the literature for DMPG\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG\cite{Kucerka2012} (\SI{289}{\cubic\angstrom}).
+Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of
+the four lipids.
+The three lipids with the PC head are consistent with values of around
+\SI{330}{\cubic\angstrom}, regardless of hydrocarbon tail.
+This agrees well with the values found for the same head in water
+(Table \ref{tab:water}).
+Interestingly, the volume for the PG head is similar to that for the PC head
+with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, which is
+significantly larger than values quoted in the literature for
+DMPG\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG\cite{Kucerka2012}
+(\SI{289}{\cubic\angstrom}).
 This suggests that there may be some effect arising from the solvation in DES.
 
-The major difference between the two heads is the fact PG head is negatively charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
-It has been shown previously that the PC head is folded in water\cite{Gilliams2016}, while the presence of strong electrostatic interactions in DES is known to effect the structure of surfactants micelles\cite{Sanchez-Fernandez2018}.
-If we infer a similar folded structure for the PG head driven by a weaker interaction between the alcohol and phosphate groups, then we may explain the observed increase in volume to be due to unfolding of the PG head because we expect that the DES provides a greater charge screening effect than water.
-If so then we would also expect an increase in the thickness of the head layer in DES.
-This does seem to be the case: The PG head layer thickness was found to be \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and \SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at \SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements at the air-water interface.
-For the PC head the stronger folding interaction, due to the formal charge on the ammonium group, means that no unfolding effect is observed.
+The major difference between the two heads is the fact PG head is negatively
+charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
+It has been shown previously that the PC head is folded in
+water\cite{Gilliams2016}, while the presence of strong electrostatic
+interactions in DES is known to effect the structure of surfactants
+micelles\cite{Sanchez-Fernandez2018}.
+If we infer a similar folded structure for the PG head driven by a weaker
+interaction between the alcohol and phosphate groups, then we may explain
+the observed increase in volume to be due to unfolding of the PG head
+because we expect that the DES provides a greater charge screening effect
+than water.
+If so then we would also expect an increase in the thickness of the head
+layer in DES. This does seem to be the case: The PG head layer thickness was
+found to be \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at
+\SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and
+\SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at
+\SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements at
+the air-water interface.
+For the PC head the stronger folding interaction, due to the formal charge
+on the ammonium group, means that no unfolding effect is observed.
 
-The volumes determined for the head and tails, and the thickness of the head layers, for DMPC and DPPC were used to constrain the fitting of corresponding NR data (Figure \ref{fig:neutron}).
-This leaves only two variables, $\theta_t$ and $\sigma$ to fit this data.
-The agreement is good and a confirmation that the volumes derived from XRR are consistent with the NR data.
-Furthermore, the observed trends with surface pressure are also consistent which adds some confidence in our conclusions.
+The volumes determined for the head and tails, and the thickness of the head
+layers, for DMPC and DPPC were used to constrain the fitting of corresponding
+NR data (Figure \ref{fig:neutron}). This leaves only two variables,
+$\theta_t$ and $\sigma$ to fit this data.
+The agreement is good and a confirmation that the volumes derived from XRR
+are consistent with the NR data.
+Furthermore, the observed trends with surface pressure are also consistent
+which adds some confidence in our conclusions.
 %
@@
 	\includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
-	\caption{\small The NR and SLD profiles at a surface pressure of 20 mNm$^{-1}$ for two contrasts (see legend above each plot); (a) DMPC, (b) DPPC.
-The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
+	\caption{\small The NR and SLD profiles at a surface pressure of
+  20 mNm$^{-1}$ for two contrasts (see legend above each plot); (a) DMPC,
+  (b) DPPC. The NR profiles have been offset in the $y$-axis by an order of
+  magnitude and SLD profiles offset in the $y$-axis by
+  \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:neutron}
@@
 \begin{table}
-  \caption{\label{tab:neutron} The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the co-refined NR models.
-The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn.
-\ref{equ:tl}, and the values of $\phi_h$ were found using Eqn.
+  \caption{\label{tab:neutron} The best-fit values, and associated 95 \%
+  confidence intervals for the varying parameters in the co-refined NR models.
+  The values of $d_t$ were found from the appropriate values of $\theta_t$
+  using Eqn. \ref{equ:tl}, and the values of $\phi_h$ were found using Eqn.
   \ref{equ:phih}.}
@@
     \hline
-    $\theta_t$/$^\circ$ & \input{../output/dmpc/angle20_neutron.txt} & \input{../output/dmpc/angle25_neutron.txt} & \input{../output/dppc/angle15_neutron.txt} & \input{../output/dppc/angle20_neutron.txt} \\
-    $\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rough20_neutron.txt} & \input{../output/dmpc/rough25_neutron.txt} & \input{../output/dppc/rough15_neutron.txt} & \input{../output/dppc/rough20_neutron.txt} \\
+    $\theta_t$/$^\circ$ & \input{../output/dmpc/angle20_neutron.txt} &
+    \input{../output/dmpc/angle25_neutron.txt} &
+    \input{../output/dppc/angle15_neutron.txt} &
+    \input{../output/dppc/angle20_neutron.txt} \\
+    $\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rough20_neutron.txt} &
+    \input{../output/dmpc/rough25_neutron.txt} &
+    \input{../output/dppc/rough15_neutron.txt} &
+    \input{../output/dppc/rough20_neutron.txt} \\
     \hline
-    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} & \input{../output/dmpc/solh25_neutron.txt} & \input{../output/dppc/solh15_neutron.txt} & \input{../output/dppc/solh20_neutron.txt} \\
-    $d_t$/\AA & \input{../output/dmpc/tail20_neutron.txt} & \input{../output/dmpc/tail25_neutron.txt} & \input{../output/dppc/tail15_neutron.txt} & \input{../output/dppc/tail20_neutron.txt} \\
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} &
+    \input{../output/dmpc/solh25_neutron.txt} &
+    \input{../output/dppc/solh15_neutron.txt} &
+    \input{../output/dppc/solh20_neutron.txt} \\
+    $d_t$/\AA & \input{../output/dmpc/tail20_neutron.txt} &
+    \input{../output/dmpc/tail25_neutron.txt} &
+    \input{../output/dppc/tail15_neutron.txt} &
+    \input{../output/dppc/tail20_neutron.txt} \\
 	\end{tabular}
@@
 
-For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a non-aqueous liquid surface.
-Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of functional phospholipid monolayers at the air-liquid interface.
+For the first time, stable phosphocholine and phosphatidylglycerol lipid
+monolayers have been observed and characterised on a non-aqueous liquid
+surface.
+Until the emergence of ionic liquids and DES, only a limited number of
+molecular solvents exhibited the ability to promote self-assembly and, to
+the best of our knowledge, only water among those had demonstrated the
+formation of functional phospholipid monolayers at the air-liquid interface.
 
-A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
-This has the important implication that DES therefore offer the possibility of performing studies of model membranes in the absence of water.
-Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
-However, the fact remains that the PG lipid did show a significant difference; having a larger head volume than observed for the same system in water.
-This shows that the transfer of lipids to a DES is not just a simple substitution of the subphase.
-In this specific case we have proposed an explanation based on unfolding of the PG head that is enabled by electrostatic screening of the head charges by the charged solvent.
+A physically and chemically constrained modelling approach and Bayesian
+analysis method was used to rationalise these measurements showing that the
+structures are remarkably similar at the air-DES interface to those
+previously observed at the air-water interface.
+This has the important implication that DES therefore offer the possibility
+of performing studies of model membranes in the absence of water.
+Such applications may include fundamental investigations of phospholipid
+monolayers in extreme environments (total or partial absence of water,
+cryogenic temperatures), protein membrane interactions and development of
+new technologies for drug delivery.
+However, the fact remains that the PG lipid did show a significant
+difference; having a larger head volume than observed for the same system
+in water.
+This shows that the transfer of lipids to a DES is not just a simple
+substitution of the subphase. In this specific case we have proposed an
+explanation based on unfolding of the PG head that is enabled by
+electrostatic screening of the head charges by the charged solvent.
 
-The ability to determine the head volume was facilitated by access to easy to use, and open-source software that allowed for the straightforward use a custom, chemically-consistent model within the analysis of the XRR and NR measurements.
-Furthermore, this work presents the first, to our knowledge, use of chemically-consistent parameterisation to co-refine XRR measurements at different surface concentrations.
+The ability to determine the head volume was facilitated by access to easy to
+use, and open-source software that allowed for the straightforward use a
+custom, chemically-consistent model within the analysis of the XRR and NR
+measurements.
+Furthermore, this work presents the first, to our knowledge, use of
+chemically-consistent parameterisation to co-refine XRR measurements at
+different surface concentrations.
 
@@
 The authors thank Andrew Nelson for their help with the refnx software.
-A.R.M. is grateful to the University of Bath and Diamond Light Source for co-funding a studentship (Studentship Number STU0149).
-Thanks also to the European Spallation Source and the University of Bath Alumni Fund for supporting A.S.-F.
-We also thank Diamond Light Source (Experiment number SI10546-1) and Institut Laue-Langevin (DOI: \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612}) for the awarded beamtime.
+A.R.M. is grateful to the University of Bath and Diamond Light Source for
+co-funding a studentship (Studentship Number STU0149).
+Thanks also to the European Spallation Source and the University of Bath
+Alumni Fund for supporting A.S.-F.
+We also thank Diamond Light Source (Experiment number SI10546-1) and
+Institut Laue-Langevin (DOI:
+\href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612})
+for the awarded beamtime.
 \end{acknowledgments}
@@
 \end{document}
-%
-% ****** End of file apssamp.tex ******

### 2018-10-18 reports/paper.tex
update zenodo doi
fix quote marks around solvophobic

@@
 analysis workflow for the work presented is available at
-\url{https://github.com/arm61/lipids_at_airdes} (DOI: **zenodo-doi**) under
-a CC-BY 4.0 license.
+\url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.1464836)
+under a CC-BY 4.0 license.
 Reduced experimental datasets are available at
@@
 hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
-Recently DES have also been shown to exhibit a "solvophobic" effect through
+Recently DES have also been shown to exhibit a ``solvophobic'' effect through
 the promotion of surfactant micelle

### 2018-10-18 reports/si.tex
edit corresponding author in si

@@
 \title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
-\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ \\
+\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag\ast}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$} \\
 S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold \textit{$^{abcg}$}$^{\ast}$}

### 2018-11-04 reports/paper.tex
resolve issues regarding byline endnotes

@@
-\documentclass[amsmath,amssymb,twocolumn]{revtex4-1}
+\documentclass[amsmath,amssymb,twocolumn,superscriptaddress,prl]{revtex4-1}
 
@@
 \author{A.~R.~McCluskey}
+\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
 \email{a.r.mccluskey@bath.ac.uk}
-  \thanks{These authors have contributed equally to the work presented within}
-  \altaffiliation[Also at ]{Diamond Light Source, Harwell Campus, Didcot,
-  OX11 0DE, UK}
 \affiliation{Department of Chemistry, University of Bath, Claverton Down,
 Bath, BA2 7AY, UK}
+\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
 
 \author{A.~Sanchez-Fernandez}
-  \thanks{These authors have contributed equally to the work presented within}
-  \altaffiliation[Also at ]{European Spallation Source, SE-211 00 Lund,
-  Sweden}
+\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
 \altaffiliation[Present address ]{Department of Food Technology, Lund
-  University, SE-211 00 Lund, Sweden}
+University, SE-211 00 Lund, Sweden.}
 \affiliation{Department of Chemistry, University of Bath, Claverton Down,
 Bath, BA2 7AY, UK}
+\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
 
@@
 \author{A.~J.~Jackson}
-  \altaffiliation[Also at ]{Department of Physical Chemistry,
-  Lund University, SE-211 00 Lund, Sweden}
 \affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
+\affiliation{Department of Physical Chemistry, Lund University, SE-211 00
+Lund, Sweden}
 
 \author{R.~A.~Campbell}
-  \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs,
-  38000, Grenoble, France}
 \affiliation{Division of Pharmacy and Optometry, University of Manchester,
 Manchester, UK}
+\affiliation{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble,
+France}
 
@@
 \email{tom.arnold@esss.se}
-  \altaffiliation[Also at ]{ISIS Neutron and Muon Source, Science and
-  Technology Facilities Council, Rutherford Appleton Laboratory, Harwell
-  Oxford, Didcot OX11 OQX, UK; Diamond Light Source, Harwell Campus, Didcot,
-  OX11 0DE, UK; Department of Chemistry, University of Bath, Claverton Down,
+\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
+\affiliation{ISIS Neutron and Muon Source, Science and Technology Facilities
+Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot, OX11 0QX,
+UK}
+\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
 Bath, BA2 7AY, UK}
-\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
 
@@
   and for our understanding of how biomolecules behave in the absence of water.
+\end{abstract}
+
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+\maketitle
+
+%\tableofcontents
 \begin{description}
@@
 \end{description}
-\end{abstract}
-
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-\maketitle
-
-%\tableofcontents
 

### 2018-11-06 reports/paper.tex
toms affiliation ordered numerically
move usage statement to references

@@
-\documentclass[amsmath,amssymb,twocolumn,superscriptaddress,prl]{revtex4-1}
+\documentclass[amsmath,amssymb,twocolumn,superscriptaddress,aps,prl]{revtex4-1}
 
@@
 \email{tom.arnold@esss.se}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
 \affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
+\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
 \affiliation{ISIS Neutron and Muon Source, Science and Technology Facilities
@@
 UK}
-\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
-\affiliation{Department of Chemistry, University of Bath, Claverton Down,
-Bath, BA2 7AY, UK}
 
@@
 %\tableofcontents
-\begin{description}
-\item[Usage]
-Electronic Supplementary Information (ESI) available: All analysis/plotting
-scripts and figure files, allowing for a fully reproducible, and automated,
-analysis workflow for the work presented is available at
-\url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.1464836)
-under a CC-BY 4.0 license.
-Reduced experimental datasets are available at
-\url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
-\end{description}
-
 Deep eutectic solvents (DES) are green, sustainable liquids that are obtained
@@
 Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed
-a chemically-consistent model (detail in the ESI) that allows for the
+a chemically-consistent model that allows for the
 co-refinement of reflectometry measurements at different surface pressure
-and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
+and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$ \cite{SI2018}.
 Instead these parameters were allowed to vary for each lipid while being
@@
 in water. This may therefore influence the effective head volume which means
-we cannot rely on the literature values (see ESI) derived from measurements
-on or in water.
+we cannot rely on the literature values derived from measurements
+on or in water \cite{SI2018}.
 Furthermore, it is known that, on water, increased surface pressure and

### 2018-11-06 reports/paper.tex
add ESI reference to figures

@@
 groups compared in this study, where R indicates the hydrocarbon tail;
-(a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
+(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) \cite{SI2018}.}
 \end{figure}
@@
   of magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity.}
+  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2018}.}
 	\label{fig:lipids}
@@
   $d_t$ were found from the appropriate values of $\theta_t$ using
-  Eqn. \ref{equ:tl}.}
+  Eqn. \ref{equ:tl} \cite{SI2018}.}
 	\label{fig:lipresults}
@@
   magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity.}
+  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2018}.}
 	\label{fig:neutron}

### 2018-11-06 reports/paper.tex
more ESI referencing

@@
 DPPC was found to be in the LC phase and DMPC in the LE phase at room
-temperature for the surface pressures measured (see Section \ref{sec:gixd}).
+temperature for the surface pressures measured (see Section \ref{sec:gixd}) \cite{SI2018}.
 We assume that DMPG and DLPC are also in the LE phase since there is no
@@
   appropriate values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for
-  $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih}.}
+  $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih} \cite{SI2018}.}
   \begin{ruledtabular}
@@
 Our fits suggest lower lipid tail volumes than previous measurements using
-other techniques (compare Tables \ref{tab:water} and \ref{tab:liptab}).
+other techniques (compare Tables \ref{tab:water} and \ref{tab:liptab}) \cite{SI2018}.
 It is unlikely that this is a result of the DES subphase since the tails do
@@
 This agrees well with the values found for the same head in water
-(Table \ref{tab:water}).
+(Table \ref{tab:water}) \cite{SI2018}.
 Interestingly, the volume for the PG head is similar to that for the PC head
@@
   using Eqn. \ref{equ:tl}, and the values of $\phi_h$ were found using Eqn.
-  \ref{equ:phih}.}
+  \ref{equ:phih} \cite{SI2018}.}
   \begin{ruledtabular}

### 2019-01-07 reports/paper.tex
fix ordering of toms references
reformat

@@
-\documentclass[amsmath,amssymb,twocolumn,superscriptaddress,aps,prl]{revtex4-1}
+\documentclass[amsmath,amssymb,twocolumn,superscriptaddress]{revtex4-1}
 
@@
 \author{A.~R.~McCluskey}
-\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
-\email{a.r.mccluskey@bath.ac.uk}
+%\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
+\email{a.r.mccluskey@bath.ac.uk/andrew.mccluskey@diamond.ac.uk}
 \affiliation{Department of Chemistry, University of Bath, Claverton Down,
@@
 \author{A.~Sanchez-Fernandez}
-\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
-\altaffiliation[Present address ]{Department of Food Technology, Lund
+%\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
+\altaffiliation[Present address: ]{Department of Food Technology, Lund
 University, SE-211 00 Lund, Sweden.}
@@
 Bath, BA2 7AY, UK}
+\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
 \affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
-\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
 \affiliation{ISIS Neutron and Muon Source, Science and Technology Facilities
@@
 %\tableofcontents
-Deep eutectic solvents (DES) are green, sustainable liquids that are obtained
-through the combination of ionic species with compounds that act as hydrogen
-bond donors, such as sugars, alcohols, amines, and carboxylic
-acids\cite{Smith2014,Dai2013}.
-The resulting extensive hydrogen bonding network is able to stabilise the
-ionic species and allows the eutectic mixture to remain liquid at room
-temperature\cite{Hammond2016,Hammond2017,Araujo2017}.
-Through different combinations of the precursor materials, it is possible to
-tune the solvent's physicochemical properties, such as
-polarity\cite{Pandey2014}, viscosity and surface tension\cite{Smith2014},
-network charge\cite{Zahn2016}, and
-hydrophobicity\cite{Ribeiro2015,vanOsch2015}.
-Recently DES have also been shown to exhibit a ``solvophobic'' effect through
-the promotion of surfactant micelle
-formation\cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018},
-phospholipid bilayer formation\cite{Bryant2017,Bryant2016,Gutierrez2009}, and
-the ability to stabilise non-ionic polymer\cite{Sapir2016} and protein
-conformations\cite{Sanchez-Fernandez2017}.
+\section{Introduction}
+%
+Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids \cite{Smith2014,Dai2013}.
+The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature \cite{Hammond2016,Hammond2017,Araujo2017}.
+Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity \cite{Pandey2014}, viscosity and surface tension \cite{Smith2014}, network charge \cite{Zahn2016}, and hydrophobicity \cite{Ribeiro2015,vanOsch2015}.
+Recently DES have also been shown to exhibit a ``solvophobic'' effect through the promotion of surfactant micelle formation \cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018}, phospholipid bilayer formation \cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer \cite{Sapir2016} and protein conformations \cite{Sanchez-Fernandez2017}.
 
-Phospholipid monolayers at the air/water interface have been widely studied
-as simplistic models for biological membranes.
-As such, they have been used to gain insight into many biological processes
-that are technologically and medically relevant.
-For example, investigations at the air/salt-water interface have identified
-the importance that interactions between charged phospholipid heads and ions
-present in solution have on the structure, monomer packing and stability of
-the monolayer\cite{Mohwald1990,Kewalramani2010}.
-However, the native environment for lipids in-vivo is far from a simple
-aqueous solution.
-In fact, it has been suggested\cite{Dai2013,Hammond2017} that DES might form
-within the crowded cellular environment and could assist in solubilizing
-biological species in an intermediate environment between that of the
-hydrophobic phospholipid tails and highly polar water rich regions, thereby
-assisting survival under extreme conditions such as freezing temperatures or
-drought where the water content of cells is restricted.
+Phospholipid monolayers at the air/water interface have been widely studied as simplistic models for biological membranes.
+As such, they have been used to gain insight into many biological processes that are technologically and medically relevant.
+For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer \cite{Mohwald1990,Kewalramani2010}.
+However, the native environment for lipids in-vivo is far from a simple aqueous solution.
+In fact, it has been suggested \cite{Dai2013,Hammond2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
 
-This work presents the first observation of phospholipid monolayers at an
-air-DES interface (or for that matter, any non-aqueous media, to the best of
-the authors' knowledge).
-We have used a chemically-consistent approach to model X-ray (XRR) and
-neutron (NR) reflectometry measurements and thereby evaluate the effect of
-this non-aqueous solvent on the structure of phospholipid monolayers.
+This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any non-aqueous media, to the best of the authors' knowledge).
+We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
 
-Recent developments in computational resources and software have enabled
-powerful methodologies and algorithms to be harnessed by those from
-non-expert backgrounds.
-This has benefitted significantly from open-source software projects such as
-the Python language\cite{vanRossum1995} and the Jupyter notebooks
-framework\cite{Kluyver2016}.
-In the area of NR and XRR, the landscape of data-analysis software is diverse,
-with a range of software packages available from a variety of sources;
-refnx\cite{Nelson2018}, MOTOFIT\cite{Nelson2006}, Rascal\cite{HughesRascal}
-Aurore\cite{Gerelli2016}, Refl1D\cite{Kienzle2011}, and GenX\cite{Bjorck2007}.
+Recent developments in computational resources and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
+This has benefitted significantly from open-source software projects such as the Python language \cite{vanRossum1995} and the Jupyter notebooks framework \cite{Kluyver2016}.
+In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx \cite{Nelson2018,Nelson2018a}, MOTOFIT \cite{Nelson2006}, Rascal \cite{HughesRascal} Aurore \cite{Gerelli2016}, Refl1D \cite{Kienzle2011}, and GenX \cite{Bjorck2007}.
 
-The use of a Python library, such as refnx, enables the implementation custom
-models that contain chemically-relevant information as well as the
-application of probability distribution function (PDF) sampling techniques.
-The Python library emcee\cite{Foreman-Mackey2013} offers refnx to access the
-Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble
-method\cite{Goodman2010}.
-This allows the sampling of the high-dimensionality parameter space, relevant
-in reflectomety analysis, in a Bayesian fashion, where the new samples are
-generated with consideration of those sampled previously\cite{Sivia2006}.
-Bayesian inference gives an understanding of the PDF for the fitted
-parameters and therefore estimations of their inverse uncertainties and
-inter-parameter correlations.
+The use of a Python library, such as refnx, enables the implementation custom models that contain chemically-relevant information as well as the application of probability distribution function (PDF) sampling techniques.
+The Python library emcee \cite{Foreman-Mackey2013} offers refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method \cite{Goodman2010}.
+This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously \cite{Sivia2006}.
+Bayesian inference gives an understanding of the PDF for the fitted parameters and therefore estimations of their inverse uncertainties and inter-parameter correlations.
 
+\section{Experimental Section}
 %
-\begin{figure}[b]
+\subsection{Materials}
+%
+Choline chloride (\SI{99}{\percent} \%, Sigma-Aldrich) and glycerol (\SI{99}{\percent}, Sigma-Aldrich) d$_9$-choline chloride (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) and d$_8$-glycerol (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) were purchased and used without further purification.
+The DES was prepared by mixing the precursors at a 1:2 ratio of chloine chlroide:glycerol, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed \cite{Smith2014}.
+The solvent was equilibrated overnight at \SI{40}{\celsius} and subsequently stored under a dry atmosphere.
+Due to the limited availability of the deuterated precursors, a fully protonated subphase (hDES) and a partially deuterated subphase (hdDES) were prepared and used during the neutron reflectometry (NR) experiment.
+The partially deuterated subphase was prepared using the following mixtures of precursors: \SI{1}{\mole} of \SI{0.38}{\mole} fraction of h-choline chloride/\SI{0.62}{\mole} fraction of d-choline chloride; and \SI{2}{\mole} of \SI{0.56}{\mole} fraction of h-glycerol/\SI{0.44}{\mole} fraction of d-glycerol.
+The solvent was subsequently prepared following the procedure discussed above.
+
+The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
+Those measurements showed that the water content of the solvent was kept below \SI{0.3}{wt/\percent} during all the experimental procedures presented here, which we assume to be negligible and have to little impact on the characteristics of the DES \cite{Hammond2016,Hammond2017}.
+
+1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails, \SI{>99}{\percent}), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails, \SI{>99}{\percent}), and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails, \SI{>99}{\percent}) were supplied by Avanti Polar Lipids and, 2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails, \SI{>99}{\percent}) was supplied by Sigma Aldrich and all were used without further purification.
+Deuterated versions of DPPC (d$_{62}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) and DMPC (d$_{54}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
+These phopholipids were dissolved in chloroform (\SI{0.5}{\milli\gram\per\milli\liter}) at room temperature.
+PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphatidylglycerol head component, these are shown in Figure \ref{fig:heads}.
+%
+\begin{figure}
 \includegraphics[width=0.3\textwidth]{figures/head_groups}
@@
 %
-We report on measurements of four phospholipids monolayers, namely
-1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails),
-1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),
-1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and
-1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol)
-(DMPG, C$_{14}$ tails), at the air-DES (1:2 choline choride:glycerol)
-interface.
-In contrast to many previous studies\cite{Mohwald1990,Kewalramani2010,
-Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed
-a chemically-consistent model that allows for the
-co-refinement of reflectometry measurements at different surface pressure
-and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$ \cite{SI2018}.
-Instead these parameters were allowed to vary for each lipid while being
-constrained to be self-consistent over different surface pressures in the
-same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for
-DMPC, DMPG and DLPC.
-This model was required because we cannot assume that the electrostatic
-interactions between lipid head and the solvent are the same in the DES and
-in water. This may therefore influence the effective head volume which means
-we cannot rely on the literature values derived from measurements
-on or in water \cite{SI2018}.
-Furthermore, it is known that, on water, increased surface pressure and
-associated LE-LC phase transitions lead to a compression of the lipid tail
-volume\cite{Marsh2010,Small1984} and this compaction has not necessarily
-been accounted for in the literature\cite{Campbell2018}.
-Our approach avoids this issue by making no assumption about the molecular
-volumes and only considering surface pressures that we believe to be in the
-same phase.
 
+In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
+After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface.
+Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
+In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
+Instead, small Delrin adsorption troughs were used that did not have controllable barriers.
+So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.
+
+\subsection{Methods}
+%
+XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\electronvolt} photon energy using the double-crystal deflector \cite{Arnold2012}.
+The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\per\angstrom}.
+The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
+Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
+XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: \SIlist[list-units = single]{20;25;30;35}{\milli\newton\per\meter}, DMPC: \SIlist[list-units = single]{20;25;30;40}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, DMPG: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, as measured with an aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius}.
+The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
+
+The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method \cite{Campbell2011}.
+Data at two incident angles of \SI{0.62}{\degree} and \SI{3.8}{\degree} were measured to provide a momentum transfer range from \SIrange{0.005}{0.18}{\per\angstrom}.
+Two surface pressures for each system and contrast was measured (DMPC: \SIlist[list-units = single]{20;25}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20}{\milli\newton\per\meter}).
+Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours), kept under an inert atmosphere, and all measurements were conducted at \SI{22}{\celsius}.
+
+\subsection{Data analysis}
+%
+The use of XRR and NR to analyse the structure of phospholipids on the surface of water is well documented \cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}.
+The models used in the rationalisation of XRR and NR data have varied significantly in numbers of layers present, use of interfactial roughness, and the parameterisation of the physical constraints applied.
+Frequently, these physical constraints include the volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}.
+Additionally, a recent evaluation of the applicability of different models for surfactant and phospholipid monolayers from the NR perspective has been published \cite{Campbell2018}, that suggests possible oversights in the modelling of NR data.
+%
+\begin{table*}
+	\caption{\label{tab:water} Lipid component volumes extracted from different literature sources.
+  $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$
+  The values for the head component in Kucerka \emph{et al.} \cite{Kucerka2004}, were taken from Balgav\'{y} \emph{et al} \cite{Balgavy2001}.}
+  \begin{ruledtabular}
+	\begin{tabular*}{\textwidth}{l|lll|ll|ll|l|l}
+    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
+    \hline
+    Reference & \cite{Armen1998} & \cite{Sun1994} &
+    \cite{Kucerka2004,Balgavy2001}$^a$ & \cite{Armen1998}] & \cite{Kucerka2004,Balgavy2001}$^a$ & \cite{Armen1998} & \cite{Kucerka2004,Balgavy2001}$^a$ & \cite{Pan2012} &
+    \cite{Kucerka2012} \\
+    \hline
+    $V_l$/\AA$^3$ & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ &
+    $1172.5\pm25.1£$ & $1155.4\pm30.0£$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ &
+    $1011.4$ & $1203$ \\
+    $V_t$/\AA$^3$ & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ &
+    $851.5\pm5.0£$ & $815.9\pm15.5£$ & $736.8\pm4.6$ & $707.1\pm13.5$ &
+    $720.4$ & $914$ \\
+    $V_h$/\AA$^3$ & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ &
+    $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ &
+    $291.0$ & $289$ \\
+    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
+    T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
+	\end{tabular*}
+  \end{ruledtabular}
+\end{table*}
+%
+
+In Table \ref{tab:water}, there appears to be a general consensus that the component volume for the phosphocholine (PC) head is around \SIrange{320}{360}{\angstrom\cubed}, while the phosphatidylglycerol (PG) head is in the range \SIrange{289}{291}{\angstrom\cubed}.
+However, it is not clear is the head component volumes from the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
+The charged nature of the zwitterionic or anionic lipid heads may have different interactions with the polar, but neutral water as compared to the charged DES components \cite{Sanchez-Fernandez2018}, which will affect the phospholipid head component volume.
+Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure, and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$ \cite{SI2018}.
+Instead, these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG, and DLPC.
+Furthermore, it is known that, on water, increase surface pressure and the associated LE-LC phase transitions lead to a compression of the lipid tail volume \cite{Marsh2010,Small1984}, and this compaction has not necessarily been accounted for in the literature \cite{Campbell2018}.
+This model avoids this issue by making no assumption about the molecular volumes and only considers surface pressures that we believe to be in the same phase.
+
+Our chemically-consistent model has been implemented in the Python library refnx \cite{Nelson2018,Nelson2018a}.
+This software allows for the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s refelectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}).
+This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under a CC BY-SA 4.0 licence \cite{SI2018}.
+
+This model consists of two layers to define the lipid monolayer; the head layer at the interface with the solvent and the tail layer at the interface with the air.
+The head components have a calculated scattering length, $b_h$, (found as a summation of the X-ray or neutron atomic scattering lengths), and a component volume, $V_h$.
+These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
+The tail layer is defined in the same fashion, except that the thickness, $d_t$, is limited such that it may be no greater than the maximum extended length of the lipid tail (the Tanford length, $t_t$ \cite{Tanford1980}), which is given in Table \ref{tab:invariant}, and that no solvent may interacalate into the layer (e.g.
+$\phi_t = 0$).
+The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
+%
+\begin{equation}
+\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}(\phi_i),
+\end{equation}
+%
+where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer.
+To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
+%
+\begin{equation}
+\label{equ:phih}
+\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
+\end{equation}
+%
+Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
+$\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
+Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
+%
+\begin{table}
+	\caption{\label{tab:invariant} The invariant parameters within the chemically-consistent model.
+	$^a$Values obtained from the Tanford formula \cite{Tanford1980}.
+  $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}.}
+  \begin{ruledtabular}
+  \begin{tabular*}{0.48\textwidth}{lllll}
+		Component & $b_t$/\si{\femto\meter} & $b_h$/\si{\femto\meter} & $t_t$/\si{\angstrom} & $\text{SLD}$/$10^{-6}$\si{\per\angstrom\squared} \\
+		\hline
+		X-ray & & & & \\
+		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
+		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
+		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
+		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
+		Air & -- & -- & -- & 0\\
+		DES & -- & -- & -- & 10.8$^b$ \\
+		\hline
+		Neutron & & & & \\
+		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
+		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
+		h-DES & -- & -- & -- & 0.43$^b$  \\
+		hd-DES & -- & -- & -- & 3.15$^b$ \\
+	\end{tabular*}
+  \end{ruledtabular}
+\end{table}
+%
+
+In order to justify the use of a single tail volume accross many surface pressures, it was necessary to ensure that the lipids remain in the same phase.
+On water, this can be demonstrated with a Langmuir isotherm.
+However, while we have confience that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the high viscosity of the DES.
+Instead we have used grazing incidence X-ray diffraction to confirm the
+phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
+DPPC was found to be in the LC phase and DMPC in the LE phase at room
+temperature for the surface pressures measured (see Section \ref{sec:gixd}) \cite{SI2018}.
+We assume that DMPG and DLPC are also in the LE phase since there is no
+reason to believe that the phase behaviour in these systems differs
+significantly from DMPC at the same temperature.
+
+In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations.
+In keeping with the work of Campbell \emph{et al.} \cite{Campbell2018}, a single value for the head thickness was fitted for each lipid across all surface pressures, as the thickness of the head layer was considered to be dependent on molecular dimensions only.
+The following parameters were allowed to vary; $d_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
+For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
+Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.
+
+In the second step, the head and tail component volumes, and head layer thickness determined from XRR were fixed for the refinement of the custom model against the NR measurements.
+This approach means that the number of variable parameters to fit the NR data can be reduced to two, namely the thickness of the tail layer, $d_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.
+Table \ref{tab:invariant} also gives the details of the scattering lengths and SLDs used as invariant parameters for the NR fitting.
+
+In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library \cite{Jones2001}, to find the parameters that gave the best fit to the data.
+The parameter space was then probed using the MCMC method available through emcee \cite{Foreman-Mackey2013}, which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
+In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
+The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions (shown in detail in the ESI).
+This allowed the Shapiro test to be used to assess if each PDF was normally distributed.
+Parameters that were shown to be normally distributed are given with symmetric confidence intervals, while those that failed the Shapiro test are given with asymmetric confidence intervals.
+However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e.
+they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.
+
+\section{Results \& Discussions}
+%
+The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
+The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
+Table \ref{tab:liptab} gives details of all varied parameters for each lipid at \SI{30}{\milli\newton\per\meter}, as well as the details of $\phi_h$ which was determined from Eqn. \ref{equ:phih}.
 %
@@
 %
-Our model has more variables than we can uniquely fit with limited data.
-In reflectometry the usual approach to this problem is to collect more
-equivalent dataset with varying deuteration (NR). For reasons of cost and
-practicality this was not possible in this work.
-The other approach is to constrain the model so that the number of fitted
-variables are reduced, and is the approach taken here.
-To do this we add the constraint that a single tail volume can be used for
-all surface pressures. To justify this we need to be sure that the lipids
-remain in the same phase. On water this is can be demonstrated with a
-Langmuir isotherm.
-However, while we have confidence that the individual surface pressures
-measured were reliable, we were unable to collect consistent Langmuir
-isotherm measurements, due to the high viscosity of the DES.
-This inconsistency means that we cannot be confident in the phase of the
-lipids based on the surface pressure alone.
-Instead we have used grazing incidence X-ray diffraction to confirm the
-phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
-DPPC was found to be in the LC phase and DMPC in the LE phase at room
-temperature for the surface pressures measured (see Section \ref{sec:gixd}) \cite{SI2018}.
-We assume that DMPG and DLPC are also in the LE phase since there is no
-reason to believe that the phase behaviour in these systems differs
-significantly from DMPC at the same temperature.
-
-The model, based on the standard two-layer model widely used for lipids on
-water, was first fitted to the experimental XRR data.
-The associated SLD profiles are shown in Figure \ref{fig:lipids} while
-Table \ref{tab:liptab} presents the results of the PDF for each of the
-varying parameters; the tail tilt angle, $\theta_t$, the interfacial
-roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively,
-and the head layer thickness, $d_h$.
-In order to constrain the fitting process only $\theta_t$ and $\sigma$ were
-allowed to vary independently of surface pressure. The other parameters,
-$V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface
-pressures measured for each lipid.
-
 %
-\begin{table}
-	\caption{\label{tab:liptab} The best-fit values, and associated 95 \%
-  confidence intervals for the varying parameters in the XRR models, at the
-  \SI{30}{\milli\newton\per\meter}. The values of $d_t$ were found from the
-  appropriate values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for
-  $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih} \cite{SI2018}.}
+\begin{table*}
+	\caption{\label{tab:liptab} The best-fit values, and associated \SI{95}{\percent} confidence intervals for the varying parameters in the XRR models, at the \SI{30}{\milli\newton\per\meter}.
+The values for $\phi_h$ was obtained from the appropriate use of Eqn.
+\ref{equ:phih} \cite{SI2018}.}
   \begin{ruledtabular}
-	\begin{tabular}{ccccc}
+	\begin{tabular*}{\textwidth}{ccccc}
     Lipid & DLPC & DMPC & DPPC & DMPG \\
     \hline
-    $\theta_t$/\si{\degree} & \input{../output/dlpc/angle30.txt} &
-    \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle30.txt} &
-    \input{../output/dmpg/angle30.txt} \\
     $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} &
@@
     \input{../output/dmpg/head.txt} \\
+    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} &
+    \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} &
+    \input{../output/dmpg/tail30.txt} \\
     \hline
@@
     \input{../output/dmpg/solh30.txt} \\
-    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} &
-    \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} &
-    \input{../output/dmpg/tail30.txt} \\
-	\end{tabular}
+	\end{tabular*}
   \end{ruledtabular}
-\end{table}
+\end{table*}
 %
 
-For each lipid, the tail layer thickness, $d_t$, increases with chain length
-and in general agrees with the literature for monolayers on
-water\cite{Mohwald1990,Vaknin1991}:
-For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at
-\SI{30}{\milli\newton\per\meter} in DES compared with
-$d_t=\SI{15.8}{\angstrom}$ at
-\SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for
-DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at
-\SI{30}{\milli\newton\per\meter} in DES compared with
-$d_t=\SI{16.7}{\angstrom}$ at
-\SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
-In all cases the surface roughness was found to be relatively high compared
-to water.
-This is expected because the absolute surface tension of the DES is less
-than water, while a previous XRR measurement of pure choline
-chloride:glycerol suggests a roughness of
-3.3\si{\angstrom}\cite{Sanchez-Fernandez2016}, significantly higher than
-the capillary wave roughness of water of about 2.8\si{\angstrom}.
-
-Figure \ref{fig:lipresults} shows the tail layer thickness variation with
-surface pressure. For DPPC and DMPC a plateau in thickness is reached at
-\SI{25}{\milli\newton\per\meter} and \SI{30}{\milli\newton\per\meter}
-respectively. Presumably a similar plateau would be seen for DMPG and DLPC
-at higher pressures.
-This phenomenon has been noted before for DMPC\cite{Bayerl1990} and
-DPPC\cite{Campbell2018} at the air-water interface.
-%
-\begin{figure}
-	\centering
-  \includegraphics[width=0.45\textwidth]{figures/dlpc_vh_dt_phi}
-	\includegraphics[width=0.45\textwidth]{figures/dmpc_vh_dt_phi}
-	\includegraphics[width=0.45\textwidth]{figures/dppc_vh_dt_phi}
-	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
-	\caption{\small The PDFs of the head volume (left) and variation of
-  $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of
-  the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG. The values of
-  $d_t$ were found from the appropriate values of $\theta_t$ using
-  Eqn. \ref{equ:tl} \cite{SI2018}.}
-	\label{fig:lipresults}
-\end{figure}
-%
-
-Figure \ref{fig:lipresults} also shows that for all four lipids there is a
-decrease in head solvation, $\phi_h$, with surface pressure.
-This is because an increase in the surface pressure means a reduction in the
-free volume available between the lipid heads, which in turn forces solvent
-molecules out of the layer, an effect that has also been observed on
-water\cite{Bayerl1990}.
-
-Our fits suggest lower lipid tail volumes than previous measurements using
-other techniques (compare Tables \ref{tab:water} and \ref{tab:liptab}) \cite{SI2018}.
-It is unlikely that this is a result of the DES subphase since the tails do
-not directly interact with the solvent.
-However this may be related to the compaction of the monolayer at elevated
-surface pressures.
-The optimal value of the tail volume for DPPC in the LC
-phase\cite{Campbell2018} was found to be \SI{772}{\cubic\angstrom} at
-\SI{35}{\milli\newton\per\meter}, which agrees well with the value of
-\input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work.
-Similarly the tail volume for DMPS in the LE phase\cite{Campbell2018},
-\SI{714}{\cubic\angstrom} at \SI{10}{\milli\newton\per\meter}, broadly
-agrees with the values for
-DMPC (\input{../output/dmpc/vt.txt}\si{\cubic\angstrom}) and DMPG
-(\input{../output/dmpg/vt.txt}\si{\cubic\angstrom}) in this work.
-The literature value\cite{Pan2012} quoted for DMPG (at a lower temperature) is
-also similar to our result (but slightly smaller).
-We find that the reduction is \SIrange{8}{12}{\percent} for DPPC, DMPC and
-DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, in
-good agreement with the maximum compression percentage of \SI{15}{\percent}
-noted by Small \emph{et al.}\cite{Small1984}.
-In general our results are at least self-consistent while comparisons to the
-literature are favourable.
-
-Figure \ref{fig:lipresults} shows the PDFs for the head volume for each of
-the four lipids.
-The three lipids with the PC head are consistent with values of around
-\SI{330}{\cubic\angstrom}, regardless of hydrocarbon tail.
-This agrees well with the values found for the same head in water
-(Table \ref{tab:water}) \cite{SI2018}.
-Interestingly, the volume for the PG head is similar to that for the PC head
-with a value of \input{../output/dmpg/vh.txt}\si{\cubic\angstrom}, which is
-significantly larger than values quoted in the literature for
-DMPG\cite{Pan2012} (\SI{291}{\cubic\angstrom}) or POPG\cite{Kucerka2012}
-(\SI{289}{\cubic\angstrom}).
-This suggests that there may be some effect arising from the solvation in DES.
-
-The major difference between the two heads is the fact PG head is negatively
-charged whereas the PC head is zwitterionic (Figure \ref{fig:heads}).
-It has been shown previously that the PC head is folded in
-water\cite{Gilliams2016}, while the presence of strong electrostatic
-interactions in DES is known to effect the structure of surfactants
-micelles\cite{Sanchez-Fernandez2018}.
-If we infer a similar folded structure for the PG head driven by a weaker
-interaction between the alcohol and phosphate groups, then we may explain
-the observed increase in volume to be due to unfolding of the PG head
-because we expect that the DES provides a greater charge screening effect
-than water.
-If so then we would also expect an increase in the thickness of the head
-layer in DES. This does seem to be the case: The PG head layer thickness was
-found to be \SI[separate-uncertainty=true]{10.3\pm0.4}{\angstrom} at
-\SI{22}{\milli\newton\per\meter} \cite{Clifton2012} and
-\SI[separate-uncertainty=true]{9.7\pm1.0}{\angstrom} at
-\SI{15}{\milli\newton\per\meter} \cite{Ciumac2017} from NR measurements at
-the air-water interface.
-For the PC head the stronger folding interaction, due to the formal charge
-on the ammonium group, means that no unfolding effect is observed.
-
-The volumes determined for the head and tails, and the thickness of the head
-layers, for DMPC and DPPC were used to constrain the fitting of corresponding
-NR data (Figure \ref{fig:neutron}). This leaves only two variables,
-$\theta_t$ and $\sigma$ to fit this data.
-The agreement is good and a confirmation that the volumes derived from XRR
-are consistent with the NR data.
-Furthermore, the observed trends with surface pressure are also consistent
-which adds some confidence in our conclusions.
+Following the initial structural determination of the monolayer by XRR, NR was used to confirm the structure and show the applicability of the chemically-consistent model for DPPC and DMPC.
+The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}.
+Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $\phi_h$ as determined from NR.
 %
@@
 %
-\begin{table}
+\begin{table*}
   \caption{\label{tab:neutron} The best-fit values, and associated 95 \%
   confidence intervals for the varying parameters in the co-refined NR models.
-  The values of $d_t$ were found from the appropriate values of $\theta_t$
-  using Eqn. \ref{equ:tl}, and the values of $\phi_h$ were found using Eqn.
-  \ref{equ:phih} \cite{SI2018}.}
+  The values of $\phi_h$ were found using Eqn. \ref{equ:phih} \cite{SI2018}.}
   \begin{ruledtabular}
-	\begin{tabular}{ccccc}
+	\begin{tabular*}{\textwidth}{ccccc}
     Lipid & \multicolumn{2}{c}{d$_{54}$-DMPC} & \multicolumn{2}{c}{d$_{62}$-DPPC} \\
@@
     \hline
-    $\theta_t$/$^\circ$ & \input{../output/dmpc/angle20_neutron.txt} &
-    \input{../output/dmpc/angle25_neutron.txt} &
-    \input{../output/dppc/angle15_neutron.txt} &
-    \input{../output/dppc/angle20_neutron.txt} \\
-    $\sigma_{t,h,s}$/\AA & \input{../output/dmpc/rough20_neutron.txt} &
+    $\sigma_{t,h,s}$/\si{\angstrom} & \input{../output/dmpc/rough20_neutron.txt} &
     \input{../output/dmpc/rough25_neutron.txt} &
@@
     \input{../output/dppc/rough20_neutron.txt} \\
+    $d_t$/\si{\angstrom} & \input{../output/dmpc/tail20_neutron.txt} &
+    \input{../output/dmpc/tail25_neutron.txt} &
+    \input{../output/dppc/tail15_neutron.txt} &
+    \input{../output/dppc/tail20_neutron.txt} \\
     \hline
@@
     \input{../output/dppc/solh20_neutron.txt} \\
-    $d_t$/\AA & \input{../output/dmpc/tail20_neutron.txt} &
-    \input{../output/dmpc/tail25_neutron.txt} &
-    \input{../output/dppc/tail15_neutron.txt} &
-    \input{../output/dppc/tail20_neutron.txt} \\
-	\end{tabular}
+	\end{tabular*}
   \end{ruledtabular}
-\end{table}
+\end{table*}
+%
+\subsection{Effect of compression on monolayer thickness}
+%
+From Tables \ref{tab:liptab} and \ref{tab:neutron}, we can see that, as expected and as found in previous work \cite{Mohwald1990,Vaknin1991}, the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
+Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$\si{\angstrom} at \SI{30}{\milli\newton\per\meter} \cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$\si{\angstrom} at \SI{40}{\milli\newton\per\meter} \cite{Helm1987} in water for DPPC.
+
+The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
+It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateauing; for DPPC this occurs at \SI{20}{\milli\newton\per\meter}, DMPC at \SI{30}{\milli\newton\per\meter} and for DMPG and DLPC can be assumed to be at higher pressures than those studied.
+This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC \cite{Bayerl1990} and DPPC \cite{Campbell2018} at the air-water interface.
+%
+\begin{figure}
+	\centering
+  \includegraphics[width=0.45\textwidth]{figures/dlpc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dmpc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dppc_vh_dt_phi}
+	\includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
+	\caption{\small The PDFs of the head volume (left) and variation of
+  $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of
+  the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.}
+	\label{fig:lipresults}
+\end{figure}
 %
 
-For the first time, stable phosphocholine and phosphatidylglycerol lipid
-monolayers have been observed and characterised on a non-aqueous liquid
-surface.
-Until the emergence of ionic liquids and DES, only a limited number of
-molecular solvents exhibited the ability to promote self-assembly and, to
-the best of our knowledge, only water among those had demonstrated the
-formation of functional phospholipid monolayers at the air-liquid interface.
+\subsection{Effect of compression on solvent concentration}
+%
+In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer.
+This can be rationalised by considering that when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.
+A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface \cite{Bayerl1990}.
 
-A physically and chemically constrained modelling approach and Bayesian
-analysis method was used to rationalise these measurements showing that the
-structures are remarkably similar at the air-DES interface to those
-previously observed at the air-water interface.
-This has the important implication that DES therefore offer the possibility
-of performing studies of model membranes in the absence of water.
-Such applications may include fundamental investigations of phospholipid
-monolayers in extreme environments (total or partial absence of water,
-cryogenic temperatures), protein membrane interactions and development of
-new technologies for drug delivery.
-However, the fact remains that the PG lipid did show a significant
-difference; having a larger head volume than observed for the same system
-in water.
-This shows that the transfer of lipids to a DES is not just a simple
-substitution of the subphase. In this specific case we have proposed an
-explanation based on unfolding of the PG head that is enabled by
-electrostatic screening of the head charges by the charged solvent.
+\subsection{Effect of compression on the lipid tail component volumes}
+%
+It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
+It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
+However, this reduction has been shown previously \cite{Campbell2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
+In that work, the optimal value of the tail component volume for DPPC was found to be \SI{772}{\angstrom\cubed} at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\angstrom\cubed} found in this work at surface pressures of \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}.
 
-The ability to determine the head volume was facilitated by access to easy to
-use, and open-source software that allowed for the straightforward use a
-custom, chemically-consistent model within the analysis of the XRR and NR
-measurements.
-Furthermore, this work presents the first, to our knowledge, use of
-chemically-consistent parameterisation to co-refine XRR measurements at
-different surface concentrations.
+In this work, a single tail component volume was fitted to each lipid for all four surface pressures that were measured.
+This is based on the assumption, that at all four surface pressures, the lipids adopt the same phase and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness.
+It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail component volumes are also reduced in the current XRR measurements compared to those determined previously.
+The reduction was found to be between \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small and coworkers \cite{Small1984}.
+DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
+Notably this value is similar to that found in this work for DMPC, which has the same tail structure and suggests that our results are at least self-consistent.
+
+\subsection{Solvent effect on lipid head component volumes}
+%
+Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids.
+The three lipids with the PC head component are consistent, giving values of $\sim330$ \AA$^3$, regardless of tail component.
+This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
+Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\angstrom\cubed} .
+The PG head component volume in water, from either DMPG using differential vibrating tube densimetry \cite{Pan2012} or POPG using molecular dynamics simulations \cite{Kucerka2012}, is noticeably smaller.
+This indicates that there may be some effect arising from the solvation in choline cloride:glycerol causing an apparent increase in the PG component volume when compared with water.
+
+The major difference between the two head components is the fact PG component is negatively charged whereas the PC component is zwitterionic.
+It has been shown previously that the conformation for the PC component is folded in water \cite{Gilliams2016}, due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
+A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
+However, such an interaction would be weaker than that observed in the PC component.
+Therefore, this observed increase found for the PG component volume in DES when compared with water may be due to the unfolding of the PG head.
+This unfolding would be made possible by the charged nature of the solvent providing a greater screening effect for the PG head than are present in water.
+This effect may not be observed for the PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group.
+It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
+Previously, DPPG has been reported to have a head layer thickness of \SI{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements \cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
+
+\subsection{Refinement of neutron reflectometry}
+%
+The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head component volume is consistant between the pair of measurements for the same system.
+It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust enough to be used in the modelling of NR data.
+Futhermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components are consistant with that found in the NR models.
+
+\section{Conclusions}
+%
+For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a non-aqueous liquid surface.
+Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of phospholipid monolayers at the air-liquid interface.
+
+A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
+This has the important implication that DES therefore offer the possibility of performing studies of model membranes in the absence of water.
+Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
+However, the PG component did show a significant difference; having a larger head component volume than observed for the same system in water.
+This suggests that the transfer of lipids to a DES is not just a simple substitution of the subphase.
+In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the partially charged solvent.
+
+The ability to determine the head component volume was facilitated by access to easy to use, open-source software that allowed for the straightforward use of a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
+Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
 

### 2019-01-07 notebooks/lipid_xrr.py

@@ -1,4 +1,4 @@
-
+#!/usr/bin/env python
 # coding: utf-8
 
 # # X-ray reflectometry analysis
@@ -107,8 +107,7 @@ tail_sl = mv.get_scattering_length(tail)
 # In[ ]:
 
 
-thick_heads = 11.057
-chain_tilt = 0.792674
+thick_heads = 12.057
 if lipid == 'dlpc':
     vols = [330., 667.]
 if lipid == 'dmpg':
@@ -136,13 +135,13 @@ tail_length = 1.54 + 1.265 * length
 # In[ ]:
 
 
-lipid1 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid1 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}1'.format(lipid))
-lipid2 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid2 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}2'.format(lipid))
-lipid3 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid3 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}3'.format(lipid))
-lipid4 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid4 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}4'.format(lipid))
 
 
@@ -167,49 +166,48 @@ structure_lipid4 = air(0, 0) | lipid4 | des(0, 3.3)
 
 lipid1.head_mol_vol.setp(vary=True, bounds=(vols[0]*0.8, vols[0]*1.2))
 lipid1.tail_mol_vol.setp(vary=True, bounds=(vols[1]*0.8, vols[1]*1.2))
-lipid1.tail_length.setp(vary=False)
-lipid1.cos_rad_chain_tilt.setp(vary=True, bounds=(0.01, 0.99))
+lipid1.thick_tails.setp(vary=True, bounds=(5, tail_length))
[…]

### 2019-01-07 notebooks/xrr_chain_analysis.py

@@ -1,4 +1,4 @@
-
+#!/usr/bin/env python
 # coding: utf-8
 
 # # X-ray reflectometry analysis
@@ -115,7 +115,6 @@ head_sl = mv.get_scattering_length(head)
 tail_sl = mv.get_scattering_length(tail)
 
 thick_heads = 11.057
-chain_tilt = 0.792674
 if lipid == 'dlpc':
     vols = [330., 667.]
 if lipid == 'dmpg':
@@ -127,13 +126,13 @@ if lipid == 'dppc':
 
 tail_length = 1.54 + 1.265 * length
 
-lipid1 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid1 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}1'.format(lipid))
-lipid2 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid2 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}2'.format(lipid))
-lipid3 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid3 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}3'.format(lipid))
-lipid4 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, chain_tilt, vols, 
+lipid4 = mv.VolMono(head_sl, thick_heads, tail_sl, tail_length, vols, 
                     reverse_monolayer=True, name='{}4'.format(lipid))
 
 air = SLD(0, 'air')
@@ -146,42 +145,41 @@ structure_lipid4 = air(0, 0) | lipid4 | des(0, 3.3)
 
 lipid1.head_mol_vol.setp(vary=True, bounds=(vols[0]*0.8, vols[0]*1.2))
 lipid1.tail_mol_vol.setp(vary=True, bounds=(vols[1]*0.8, vols[1]*1.2))
-lipid1.tail_length.setp(vary=False)
-lipid1.cos_rad_chain_tilt.setp(vary=True, bounds=(0.01, 0.99))
+lipid1.thick_tails.setp(vary=True, bounds=(5, tail_length))
[…]

### 2019-01-07 src/tools/helper.py

@@ -10,3 +10,6 @@ def data_cutoff(dataset, cutoff):
 
 def latex_asym(a, b, c):
     return '$' + str(a) + '^{+' + str(b) + '}_{-' + str(c) + '}$'
+
+def latex_sym(a, b):
+    return '$' + str(a) + '\pm{' + str(b) + '}$'

### 2019-01-08 reports/paper.tex
second version

@@
 \externaldocument{si}
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
-
-%\usepackage[showframe,%Uncomment any one of the following lines to test
-%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
-%%text={7in,10in},centering,
-%%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
-%%height=10in,a5paper,hmargin={3cm,0.8in},
-%]{geometry}
 
 \begin{document}
-
-\preprint{APS/123-QED}
 
@@
 \author{A.~R.~McCluskey}
-%\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
+\thanks{A.R.M. and A.S.-F. contributed equally to this work}
 \email{a.r.mccluskey@bath.ac.uk/andrew.mccluskey@diamond.ac.uk}
@@
 \author{A.~Sanchez-Fernandez}
-%\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
+\thanks{A.R.M. and A.S.-F. contributed equally to this work}
 \altaffiliation[Present address: ]{Department of Food Technology, Lund
@@
 \begin{abstract}
-  In this work, we present the first example of the self-assembly of
-  phospholipid monolayers at the interface between air and a non-aqueous
-  liquid.
-  Deep eutectic solvents are a novel class of environmentally friendly
-  non-aqueous room temperature liquids with tunable properties, that have
-  wide ranging potential applications and are capable of promoting the
-  self-assembly of surfactant molecules.
-  We use a chemically-consistent Bayesian modelling of X-ray and neutron
-  reflectometry measurements to show that these monolayers broadly behave
-  as they do on water.
-  However, the ability of the deep eutectic solvent to interact with the
-  phosphatidylglycerol lipid head, leads to an apparent increase in its
-  volume compared to that observed in water.
-  No such change was observed for the phosphocholine head, indicating that
-  such interactions are head, and therefore solvent, specific.
-  This has important implications for the potential uses of these solvents
-  and for our understanding of how biomolecules behave in the absence of water.
+  In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and an ionic solvent.
+  Deep eutectic solvents are a novel class of environmentally friendly non-aqueous room temperature liquids with tunable properties, that have wide ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
+  We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
+  However, the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leads to an apparent increase in its volume compared to that observed in water.
+  No such change was observed for the phosphocholine head, indicating that such interactions are head, and therefore solvent, specific.
+  This has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
 \end{abstract}
@@
 
-This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any non-aqueous media, to the best of the authors' knowledge).
+This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any ionic solvent, to the best of the authors' knowledge).
+Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide being noted previously \cite{Weinbach1993,Graner1995}.
 We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
@@
 groups compared in this study, where R indicates the hydrocarbon tail;
-(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) \cite{SI2018}.}
+(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) \cite{SI2019}.}
 \end{figure}
@@
 The charged nature of the zwitterionic or anionic lipid heads may have different interactions with the polar, but neutral water as compared to the charged DES components \cite{Sanchez-Fernandez2018}, which will affect the phospholipid head component volume.
-Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure, and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$ \cite{SI2018}.
+Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure, and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$ \cite{SI2019}.
 Instead, these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG, and DLPC.
@@
 This software allows for the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s refelectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}).
-This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under a CC BY-SA 4.0 licence \cite{SI2018}.
+This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under a CC BY-SA 4.0 licence \cite{SI2019}.
 
@@
 DPPC was found to be in the LC phase and DMPC in the LE phase at room
-temperature for the surface pressures measured (see Section \ref{sec:gixd}) \cite{SI2018}.
+temperature for the surface pressures measured (see Section \ref{sec:gixd}) \cite{SI2019}.
 We assume that DMPG and DLPC are also in the LE phase since there is no
@@
 In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations.
-In keeping with the work of Campbell \emph{et al.} \cite{Campbell2018}, a single value for the head thickness was fitted for each lipid across all surface pressures, as the thickness of the head layer was considered to be dependent on molecular dimensions only.
+In keeping with the work of Campbell \emph{et al.} \cite{Campbell2018}, a single value for the head thickness was fitted for each lipid across all surface pressures, as the thickness of the head layer was considered to be dependent on molecular dimensions only, and has been shown to vary little with surface pressure \cite{Kewalramani2010}.
 The following parameters were allowed to vary; $d_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
@@
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
-The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions (shown in detail in the ESI).
+The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions.
 This allowed the Shapiro test to be used to assess if each PDF was normally distributed.
@@
   of magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2018}.}
+  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2019}.}
 	\label{fig:lipids}
@@
 The values for $\phi_h$ was obtained from the appropriate use of Eqn.
-\ref{equ:phih} \cite{SI2018}.}
+\ref{equ:phih} \cite{SI2019}.}
   \begin{ruledtabular}
@@
     \hline
-    $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} &
-    \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} &
-    \input{../output/dmpg/rough30.txt} \\
+    $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
+    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
     \hline
-    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} &
-    \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} &
-    \input{../output/dmpg/vt.txt} \\
-    $V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} &
-    \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} &
-    \input{../output/dmpg/vh.txt} \\
-    $d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} &
-    \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} &
-    \input{../output/dmpg/head.txt} \\
-    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} &
-    \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} &
-    \input{../output/dmpg/tail30.txt} \\
+    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
+    $V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
+    $d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
     \hline
-    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} &
-    \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} &
-    \input{../output/dmpg/solh30.txt} \\
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
 	\end{tabular*}
@@
   magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2018}.}
+  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2019}.}
 	\label{fig:neutron}
@@
   confidence intervals for the varying parameters in the co-refined NR models.
-  The values of $\phi_h$ were found using Eqn. \ref{equ:phih} \cite{SI2018}.}
+  The values of $\phi_h$ were found using Eqn. \ref{equ:phih} \cite{SI2019}.}
   \begin{ruledtabular}
@@
     \hline
-    $\sigma_{t,h,s}$/\si{\angstrom} & \input{../output/dmpc/rough20_neutron.txt} &
-    \input{../output/dmpc/rough25_neutron.txt} &
-    \input{../output/dppc/rough15_neutron.txt} &
-    \input{../output/dppc/rough20_neutron.txt} \\
-    $d_t$/\si{\angstrom} & \input{../output/dmpc/tail20_neutron.txt} &
-    \input{../output/dmpc/tail25_neutron.txt} &
-    \input{../output/dppc/tail15_neutron.txt} &
-    \input{../output/dppc/tail20_neutron.txt} \\
+    $\sigma_{t,h,s}$/\si{\angstrom} & \input{../output/dmpc/rough20_neutron.txt} & \input{../output/dmpc/rough25_neutron.txt} & \input{../output/dppc/rough15_neutron.txt} & \input{../output/dppc/rough20_neutron.txt} \\
+    $d_t$/\si{\angstrom} & \input{../output/dmpc/tail20_neutron.txt} & \input{../output/dmpc/tail25_neutron.txt} & \input{../output/dppc/tail15_neutron.txt} & \input{../output/dppc/tail20_neutron.txt} \\
     \hline
-    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} &
-    \input{../output/dmpc/solh25_neutron.txt} &
-    \input{../output/dppc/solh15_neutron.txt} &
-    \input{../output/dppc/solh20_neutron.txt} \\
+    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} & \input{../output/dmpc/solh25_neutron.txt} & \input{../output/dppc/solh15_neutron.txt} & \input{../output/dppc/solh20_neutron.txt} \\
 	\end{tabular*}
@@
 
+\subsection{Interparameter correlations}
+%
+The use of Bayesian inference and MCMC sampling allowed for the probing of the probability distribution function for each parameter individually.
+However, it also enables the pairwise interparameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (the same plots for each lipid at each surface pressure measured is available in the ESI \cite{SI2019}).
+These two-dimensional PDFs give important information about the correlations that are present between the parameters of the chemically-consistant model.
+The less circular in nature that the 2D PDF is, the greater the correlation that is present between the parameters, e.g.
+a north-east/south-westernly skewed PDF indicates a positive correlation (where an increase in one parameter correlates an increase in the other) while a north-west/south-easternly skewed PDF indicates a negative correlation (an increase in one correlates with a decrease in the other).
+%
+\begin{figure}
+	\centering
+	\includegraphics[width=0.48\textwidth]{figures/dmpc3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPC XRR data at \SI{30}{\milli\newton\per\meter}.}
+	\label{fig:dmpcpdfs}
+\end{figure}
+%
+
+Substantial correlations are present in the parameters fitted to the XRR datasets, indicating important uncertainty that must be considered.
+In particular, as can be seen in Figure \ref{fig:dmpcpdfs}, there is a positive correlation between the lipid head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$.
+This correlation can be rationalised as a result of the SLD of the solvent and the head layer (which is \SI{50}{\percent} solvated) being similar, and therefore the boundary between the two is not easy to define.
+Such a correlations are unavoidable without considering many neutron contrasts of the lipid and solvent, due to the solvophilic nature of the lipid heads.
+Another, important correlation is that between the head thickness and the tail thickness, $d_t$, again this is due to the lack of a well defined boundary between the head and tail layers.
+This is partially driven by the interfacial roughness that is present between the layers, with the correlation being more pronouned for phospholipids with shorted tails (e.g.
+there is a greater correlation for DLPC than DPPC).
+
 \section{Conclusions}
 %
-For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a non-aqueous liquid surface.
-Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water among those had demonstrated the formation of phospholipid monolayers at the air-liquid interface.
+For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a ionic solvent surface.
+Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water and formamide among those had demonstrated the formation of phospholipid monolayers at the air-liquid interface.
 
@@
 In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the partially charged solvent.
+Finally, the use of MCMC sampling of the reflectometry model parameter space give previously unseen insight into the correlations present in XRR data modelling, that should be considered in nature work of this nature.
 

### 2019-01-08 reports/si.tex
second version

--- 2018-10-17 reports/si.tex
@@
-\documentclass[11pt,a4paper]{paper}
+\documentclass[amsmath,amssymb,superscriptaddress]{revtex4-1}
 \usepackage[latin1]{inputenc}
-\usepackage{amsmath}
 \usepackage{amsfonts}
-\usepackage[super,sort&compress,comma]{natbib}
 \usepackage{amssymb}
@@
 \usepackage{xr}
-\externaldocument{preprint}
+\externaldocument{paper}
 \usepackage{rotating}
@@
 \renewcommand{\thetable}{S\Roman{table}}
+
+\begin{document}
+
 \title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
-\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ \\
-S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold \textit{$^{abcg}$}$^{\ast}$}
+\author{A.~R.~McCluskey}
+\thanks{A.R.M. and A.S.-F. contributed equally to this work}
+\email{a.r.mccluskey@bath.ac.uk/andrew.mccluskey@diamond.ac.uk}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
+\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
 
-\institution{${a}$~Department of Chemistry, University of Bath, Claverton Down, Bath, \\
-BA2 7AY, UK. \\
-${b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK. \\
-${c}$~European Spallation Source, SE-211 00 Lund, Sweden. \\
-${d}$~Department of Physical Chemistry, Lund University, SE-211 00 Lund, Sweden. \\
-${e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble, France. \\
-${f}$~Division of Pharmacy and Optometry, University of Manchester, Manchester, \\
-M13 9PT, UK. \\
-${g}$~ISIS Neutron and Muon Source, Science and Technology Facilities Council, \\
-Rutherford Appleton Laboratory, Harwell Oxford, Didcot OX11 0QX, UK. \\
-${\P}$~Present address: Department of Food Technology, Lund University, SE-211 00 \\
-Lund, Sweden. \\
-$\ddag$~These authors have contributed equally to the work presented within. \\
-$\ast$~k.edler@bath.ac.uk; tom.arnold@esss.se}
+\author{A.~Sanchez-Fernandez}
+\thanks{A.R.M. and A.S.-F. contributed equally to this work}
+\altaffiliation[Present address: ]{Department of Food Technology, Lund
+University, SE-211 00 Lund, Sweden.}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
+\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
+
+\author{K.~J.~Edler}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
+
+\author{S.~C.~Parker}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
+
+\author{A.~J.~Jackson}
+\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
+\affiliation{Department of Physical Chemistry, Lund University, SE-211 00
+Lund, Sweden}
+
+\author{R.~A.~Campbell}
+\affiliation{Division of Pharmacy and Optometry, University of Manchester,
+Manchester, UK}
+\affiliation{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble,
+France}
+
+\author{T.~Arnold}
+\email{tom.arnold@esss.se}
+\affiliation{Department of Chemistry, University of Bath, Claverton Down,
+Bath, BA2 7AY, UK}
+\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
+\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
+\affiliation{ISIS Neutron and Muon Source, Science and Technology Facilities
+Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot, OX11 0QX,
+UK}
 
@@
 
-\begin{document}
-
 \maketitle
 
-\section{Materials}
-Choline chloride (99 \%, Sigma-Aldrich) and glycerol (99 \%, Sigma-Aldrich) d$_9$-choline chloride (99 \%, 98 \% D, CK Isotopes) and d$_8$-glycerol (99 \%, 98 \% D, CK Isotopes)  were purchased and used without further purification.
-The DES was prepared by mixing the precursors at the appropriate ratio, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed.\cite{Smith2014} The solvent was equilibrated overnight at \SI{40}{\celsius} and subsequently stored under a dry atmosphere.
-Due to the limited availability of the deuterated precursors, a fully protonated subphase (hDES) and a partially deuterated subphase (hdDES) were prepared and used during the neutron reflectometry (NR) experiment.
-The partially deuterated subphase was prepared using the following mixtures of precursors: \SI{1}{\mole} of 0.38 mole-fraction of h-choline chloride/0.62 mole-fraction of d-choline chloride; and \SI{2}{\mole} of 0.56 mole-fraction of h-glycerol/0.44 mole-fraction of d-glycerol.
-The solvent was subsequently prepared following the procedure discussed above.
-
-The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
-Those measurements showed that the water content of the solvent was kept below \SI{0.3}{wt\percent} during all the experimental procedures presented here, which we assume to be negligible and have little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}
-
-DPPC (\SI{>99}{\percent}, C$_{16}$ tails), DMPC (\SI{>99}{\percent}, C$_{14}$ tails), and DMPG (\SI{>99}{\percent}, C$_{14}$ tails) were supplied by Avanti Polar Lipids and DLPC (\SI{>99}{\percent}, C$_{12}$ tails) was supplied by Sigma-Aldrich and all were used as received.
-Deuterated versions of DPPC (d$_{62}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) and DMPC (d$_{54}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
-These phospholipids were dissolved in chloroform (\SI{0.5}{\milli\gram\per\milli\liter}) at room temperature.
-PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphoditylglycerol head component, these are shown in Figure 1.
-
-In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration.
-After the evaporation of the chloroform, it is assumed that the resulting system is a liquid subphase with a monolayer of phospholipid at the interface.
-The surface concentration was modified by closing and opening the barriers of a Langmuir trough (Nima Custom model: 20cm x 40cm with a total volume of approximately 450 ml).
-In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
-Instead, small Delrin adsorption troughs (5 x 6 cm with a volume of less than 15 ml) were used that did not have controllable barriers.
-In this case a volume of the lipid-chloroform solution, calculated to give the equivalent surface area per molecule, was spread onto the surface.
-So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.
-
-\section{Methods}
-XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\eV} photon energy using the double-crystal-deflector\cite{Arnold2012} and a Pilatus 100k detector.
-The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\AA^{-1}}.
-The data were normalised with respect to the incident beam and the background was measured from off-specular region-of-interest and subsequently subtracted.
-Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
-XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: 20, 25, 30, and \SI{35}{\milli\newton\meter^{-1}}, DMPC: 20, 25, 30, and \SI{40}{\milli\newton\meter^{-1}}, DPPC: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}, DMPG: 15, 20, 25, and \SI{30}{\milli\newton\meter^{-1}}), as measured with an Aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius} under a Helium atmosphere.
-The Aluminium Wilhelmy plate was used over a traditional paper plate because the DES was found to wet Aluminium but not paper, and therefore allowed more reproducible surface pressure measurements.
-It is noted that the known phase transitions of DMPC and DMPG are 24 and \SI{23}{\celsius} respectively, which is very close to our measurement temperature.
-For the sake of our assumptions during analysis it is therefore important that we were able to to determine which phase (LE or LC) the molecules are in.
-This was done directly using Grazing incident X-ray diffraction (see below).
-
-The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method.\cite{Campbell2011} Measurements at two incident angles of \SI{0.62}{\degree} and \SI{3.8}{\degree} were carried out to provide reduced data with a momentum transfer range from \SIrange{0.005}{0.25}{\AA^{-1}}.
-Two surface pressures for each system and contrast were measured (DMPC: 20 and \SI{25}{\milli\newton\meter^{-1}}, DPPC: 15 and \SI{20}{\milli\newton\meter^{-1}}).
-Similar to the X-ray procedure, samples were given enough time to equilibrate (at least two hours), kept under an inert atmosphere, and all measurements were conducted at \SI{22}{\celsius}.
-
-\section{Literature values for head and tail volumes}
-The range of volumes used for phospholipid heads and tails are somewhat inconsistent in the literature.
-There is a general consensus that the volume of the phosphocholine (PC) head is \SIrange{320}{360}{\cubic\angstrom}, while the phosphatidylglycerol (PG) head is \SIrange{289}{291}{\cubic\angstrom} (see Table \ref{tab:water}).
-Tail volumes are also quite variable and, as discussed in the main text, the compaction in chain volumes on a phase transition is often not accounted for\cite{Campbell2018}.
-We are interested in comparing the volumes of the lipid components on a non-aqueous liquid.
-To allow this comparison, Table \ref{tab:water} gives a variety of literature values for the component volumes of the lipids investigated in this work.
-
-\section{Chemically-consistant model}
-Our chemically-consistent model is made up of two layers to define the lipid monolayer; the head layer at the interface with the solvent and tail layer at the interface with the air.
-The head components have a calculated scattering length, $b_h$, (found as a summation of the X-ray or neutron atomic scattering lengths), and a component volume, $V_h$.
-These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
-The tail components also have a calculated scattering length, $b_t$, roughness, $\sigma_t$, and a component volume, $V_t$.
-We have defined the thickness of the tail layer, $d_t$, in terms of the maximum (all-trans) length of the carbon tail, $t_t$, and the angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
-%
-\begin{equation}
-\label{equ:tl}
-d_t = t_t \cos{\theta_t}.
-\end{equation}
-%
-This was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g.
-it cannot be thicker than the maximum extended length of the lipid tail.
-The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
-%
-\begin{equation}
-\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}(\phi_i),
-\end{equation}
-%
-where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains neither solvent nor air, i.e.
-$\phi_t = 0$.
-To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
-%
-\begin{equation}
-\label{equ:phih}
-\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
-\end{equation}
-%
-Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
-$\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
-Therefore, the capillary wave roughness at the air-DES interface is carried equally through the layers.
-As described in the main text, further constraints were applied to the fitting by co-refining the data across different surface pressures and assuming that the tail volume was constant.
-This is based on our assumption that there is no phase transition in the monolayer over the surface pressures measured.
-Thus we have assumed that DPPC is in the LC phase, while DMPC, DMPG and DLPC are all in the LE phase at the measurement temperature.
-
 \section{XRR parameters at each surface pressure}
-Tables \ref{tab:liptab1}-\ref{tab:liptab3} give the best fit values for the custom model that were fitted to each surface pressure, for each lipid.
+Tables \ref{tab:liptab1}-\ref{tab:liptab4} give the best fit values for the custom model that were fitted to each surface pressure, for each lipid.
 These values were used for comparison to assess the effect of the choline chloride:glycerol on the lipid.
@@
 Importantly there is no such peak observed for DMPC at \SI{22}{\celsius} (see \ref{fig:gixd}), indicating that DMPC is in the LE phase at this temperature.
-The position of the (2,0) peak, approx \SI{1.48}{\AA^{-1}}, is similar to that found under the same conditions in water.\cite{Watkins2009}
+The position of the (2,0) peak, approx \SI{1.48}{\per\angstrom}, is similar to that found under the same conditions in water.\cite{Watkins2009}
 We therefore assume that the phase behaviour on the DES is similar to that observed on water and that the phases observed at \SI{30}{\milli\newton\per\meter} are the same at the other surface pressures measured with XRR and NR.
@@
 \section{Probability distribution functions}
-The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc2}-\ref{fig:dmpg5}.
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc}-\ref{fig:dmpg4}.
 The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpcn1}-\ref{fig:dppcn2}.
-
-These incidate the correlations present between the fitted parameters of the chemically-consistant model.
-Particularly noteworthy is the positive correlation between the head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$, which shows a clear interaction between these two variables.
-This can be rationalised as the smoothing of the interface between the head and the solvent, blurring the values of each variable.
-Additionally, it is noted that the correlations present are more substantial for the smaller lipid (particularly DLPC), this is due to the reduced structure presented for such a short tailed lipid and the fact that the length of the tail is closer to the value of the surface roughness for DES (\SI{3.3}{\angstrom}\cite{Sanchez-Fernandez2016}).
 
@@
 
-\begin{sidewaystable}
-  \centering
-	\caption{\ Lipid component volumes extracted from different literature sources.
-$V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry.
-$^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
-  \centering
-	\label{tab:water}
-	\begin{tabular}{l|lll|ll|ll|l|l}
-    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
-    \hline
-    Reference & [\cite{Armen1998}] & [\cite{Sun1994}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Pan2012}] & [\cite{Kucerka2012}] \\
-    \hline
-    $V_l$/\si{\angstrom^3} & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1$ & $1155.4\pm30.0$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
-    $V_t$/\si{\angstrom^3} & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0$ & $815.9\pm15.5$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
-    $V_h$/\si{\angstrom^3} & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
-    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
-    T/\si{\celsius} & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
-	\end{tabular}
-\end{sidewaystable}
-
-%
-\begin{table}[h]
-  \centering
-	\caption{\ The invariant parameters within the chemically-consistent model.
-	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
-	\label{tab:invariant}
-	\begin{tabular}{c|c|c|c|c}
-		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
-		\hline
-		X-ray & & & & \\
-		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
-		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
-		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
-		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
-		Air & -- & -- & -- & 0\\
-		DES & -- & -- & -- & 10.8$^b$ \\
-		\hline
-		Neutron & & & & \\
-		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
-		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
-		h-DES & -- & -- & -- & 0.43$^b$  \\
-		hd-DES & -- & -- & -- & 3.15$^b$ \\
-	\end{tabular}
-\end{table}
-%
 %
@@
 	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured.
-The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
-\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+The values for $\phi_h$ were obtained from the use of Eqn.
 \ref{equ:phih}}
@@
 		\hline
-		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
 		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
+    $d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
     \hline
@@
     $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
 	\end{tabular}
@@
 	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second highest surface pressure (SP) measured.
-The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
-\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+The values for $\phi_h$ were obtained from the use of Eqn.
 \ref{equ:phih}}
-	\label{tab:liptab1}
+	\label{tab:liptab2}
 	\begin{tabular}{l|l|l|l|l}
@@
 		\hline
-		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle30.txt} & \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle25.txt} & \input{../output/dmpg/angle25.txt} \\
 		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough25.txt} & \input{../output/dmpg/rough25.txt} \\
+    $d_t$/\AA & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail25.txt} & \input{../output/dmpg/tail25.txt} \\
     \hline
@@
     $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh25.txt} & \input{../output/dmpg/solh25.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail25.txt} & \input{../output/dmpg/tail25.txt} \\
 	\end{tabular}
@@
 	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second lowest surface pressure (SP) measured.
-The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
-\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+The values for $\phi_h$ were obtained from the use of Eqn.
 \ref{equ:phih}}
-	\label{tab:liptab2}
+	\label{tab:liptab3}
 	\begin{tabular}{l|l|l|l|l}
@@
 		\hline
-		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle25.txt} & \input{../output/dmpc/angle25.txt} & \input{../output/dppc/angle20.txt} & \input{../output/dmpg/angle20.txt} \\
 		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough25.txt} & \input{../output/dmpc/rough25.txt} & \input{../output/dppc/rough20.txt} & \input{../output/dmpg/rough20.txt} \\
+    $d_t$/\AA & \input{../output/dlpc/tail25.txt} & \input{../output/dmpc/tail25.txt} & \input{../output/dppc/tail20.txt} & \input{../output/dmpg/tail20.txt} \\
     \hline
@@
     $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh25.txt} & \input{../output/dmpc/solh25.txt} & \input{../output/dppc/solh20.txt} & \input{../output/dmpg/solh20.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail25.txt} & \input{../output/dmpc/tail25.txt} & \input{../output/dppc/tail20.txt} & \input{../output/dmpg/tail20.txt} \\
 	\end{tabular}
@@
 	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the lowest surface pressure (SP) measured.
-The values of $d_t$ were found from the values of $\theta_t$ using Eqn.
-\ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn.
+The values for $\phi_h$ were obtained from the use of Eqn.
 \ref{equ:phih}}
-	\label{tab:liptab3}
+	\label{tab:liptab4}
 	\begin{tabular}{l|l|l|l|l}
@@
 		\hline
-		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle20.txt} & \input{../output/dmpc/angle20.txt} & \input{../output/dppc/angle15.txt} & \input{../output/dmpg/angle15.txt} \\
 		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough20.txt} & \input{../output/dmpc/rough20.txt} & \input{../output/dppc/rough15.txt} & \input{../output/dmpg/rough15.txt} \\
+    $d_t$/\AA & \input{../output/dlpc/tail20.txt} & \input{../output/dmpc/tail20.txt} & \input{../output/dppc/tail15.txt} & \input{../output/dmpg/tail15.txt} \\
     \hline
@@
     $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh20.txt} & \input{../output/dmpc/solh20.txt} & \input{../output/dppc/solh15.txt} & \input{../output/dmpg/solh15.txt} \\
-		$d_t$/\AA & \input{../output/dlpc/tail20.txt} & \input{../output/dmpc/tail20.txt} & \input{../output/dppc/tail15.txt} & \input{../output/dmpg/tail15.txt} \\
 	\end{tabular}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dlpc1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 20 mNm$^{-1}$.}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DLPC X-ray reflectometry data at \SI{20}{\milli\newton\per\meter}.}
+	\label{fig:dlpc1}
+\end{figure}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.50\textwidth]{figures/dlpc2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DLPC X-ray reflectometry data at \SI{25}{\milli\newton\per\meter}.}
 	\label{fig:dlpc2}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dlpc2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 25 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dlpc3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DLPC X-ray reflectometry data at \SI{30}{\milli\newton\per\meter}.}
 	\label{fig:dlpc3}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dlpc3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 30 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DLPC X-ray reflectometry data at \SI{35}{\milli\newton\per\meter}.}
 	\label{fig:dlpc4}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at 35 mNm$^{-1}$.}
-	\label{fig:dlpc5}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc1_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPC X-ray reflectometry data at \SI{20}{\milli\newton\per\meter}.}
+	\label{fig:dmpc1}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 20 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPC X-ray reflectometry data at \SI{25}{\milli\newton\per\meter}.}
 	\label{fig:dmpc2}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 25 mNm$^{-1}$.}
-	\label{fig:dmpc3}
-\end{figure}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 30 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPC X-ray reflectometry data at \SI{40}{\milli\newton\per\meter}.}
 	\label{fig:dmpc4}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at 40 mNm$^{-1}$.}
-	\label{fig:dmpc5}
+	\includegraphics[width=0.50\textwidth]{figures/dppc1_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DPPC X-ray reflectometry data at \SI{15}{\milli\newton\per\meter}.}
+	\label{fig:dppc1}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 15 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dppc2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DPPC X-ray reflectometry data at \SI{20}{\milli\newton\per\meter}.}
 	\label{fig:dppc2}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 20 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dppc3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DPPC X-ray reflectometry data at \SI{25}{\milli\newton\per\meter}.}
 	\label{fig:dppc3}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 25 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DPPC X-ray reflectometry data at \SI{30}{\milli\newton\per\meter}.}
 	\label{fig:dppc4}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at 30 mNm$^{-1}$.}
-	\label{fig:dppc5}
+	\includegraphics[width=0.50\textwidth]{figures/dmpg1_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPG X-ray reflectometry data at \SI{15}{\milli\newton\per\meter}.}
+	\label{fig:dmpg1}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg1_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 15 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dmpg2_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPG X-ray reflectometry data at \SI{20}{\milli\newton\per\meter}. }
 	\label{fig:dmpg2}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg2_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 20 mNm$^{-1}$. }
+	\includegraphics[width=0.50\textwidth]{figures/dmpg3_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPG X-ray reflectometry data at \SI{25}{\milli\newton\per\meter}.}
 	\label{fig:dmpg3}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg3_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 25 mNm$^{-1}$.}
+	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of DMPG X-ray reflectometry data at \SI{30}{\milli\newton\per\meter}.}
 	\label{fig:dmpg4}
@@
 	\centering
-	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at 30 mNm$^{-1}$.}
-	\label{fig:dmpg5}
-\end{figure}
-\begin{figure}[H]
-	\centering
 	\includegraphics[width=0.50\textwidth]{figures/dmpc_20n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of two contrast DMPC neutron reflectometry data at \SI{20}{\milli\newton\per\meter}.}
 	\label{fig:dmpcn1}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dmpc_25n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 25 mNm$^{-1}$.}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of two contrast DMPC neutron reflectometry data at \SI{25}{\milli\newton\per\meter}.}
 	\label{fig:dmpcn2}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dppc_15n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DPPC neutron reflectometry data at 15 mNm$^{-1}$.}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of two contrast DPPC neutron reflectometry data at \SI{15}{\milli\newton\per\meter}.}
 	\label{fig:dppcn1}
@@
 	\includegraphics[width=0.50\textwidth]{figures/dppc_20n_all_corner}
-	\caption{The multi-parameter PDFs for the chemically-relevant model of two contrast DMPC neutron reflectometry data at 20 mNm$^{-1}$.}
+	\caption{The multi-parameter PDFs for the chemically-consistent model of two contrast DMPC neutron reflectometry data at \SI{20}{\milli\newton\per\meter}.}
 	\label{fig:dppcn2}

### 2019-01-08 notebooks/lipid_nr.py

@@ -153,7 +153,7 @@ lipid_1.rough_preceding_mono.constraint = structure_lipid_1[-1].rough
 lipid_1.phih.constraint = 1 - (lipid_1.head_mol_vol * lipid_1.thick_tails / 
                                (lipid_1.tail_mol_vol * lipid_1.thick_heads))
 lipid_1.thick_heads.setp(get_value('head'), vary=False)
-structure_lipid_1[-1].rough.setp(get_value('rough{}'.format(sp)), vary=True, bounds=(2.5, 6))
+structure_lipid_1[-1].rough.setp(get_value('rough{}'.format(sp)), vary=True, bounds=(3.3, 6))
 
 lipid_2.head_mol_vol.constraint = lipid_1.head_mol_vol
 lipid_2.tail_mol_vol.constraint = lipid_1.tail_mol_vol

### 2019-01-10 reports/paper.tex
add author contribution note and referees comments and responses

@@
 
-\begin{acknowledgments}
+\section{Author Contributions}
+T.A., R.C., A.J.J., and K.J.E. were involved in the experimental design, and conducted the experiments along with A.S.-F. and R.A.C.
+A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, T.A., and R.A.C..
+A.R.M., A.S.-F. and T.A. wrote the manuscript, with input from all authors.
+
+\acknowledgments{
 The authors thank Andrew Nelson for their help with the refnx software.
@@
 \href{http://doi.org/10.5291/ILL-DATA.9-13-612}{10.5291/ILL-DATA.9-13-612})
-for the awarded beamtime.
-\end{acknowledgments}
+for the awarded beamtime.}
 

### 2019-01-10 reports/referees.tex
add author contribution note and referees comments and responses

\documentclass[amsmath,amssymb,twocolumn,superscriptaddress]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[detect-all]{siunitx}
\usepackage{hyperref}% add hypertext capabilities
\usepackage{xr}
\externaldocument{si}

\begin{document}

\title{Referees reports for ``Bayesian determination of the effect of a deep eutectic solvent on the
structure of lipid monolayers''}% Force line breaks with \\%

\author{A.~R.~McCluskey}
\thanks{A.R.M. and A.S.-F. contributed equally to this work}
\email{a.r.mccluskey@bath.ac.uk/andrew.mccluskey@diamond.ac.uk}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}
\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}

\author{A.~Sanchez-Fernandez}
\thanks{A.R.M. and A.S.-F. contributed equally to this work}
\altaffiliation[Present address: ]{Department of Food Technology, Lund
University, SE-211 00 Lund, Sweden.}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}

\author{K.~J.~Edler}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}

\author{S.~C.~Parker}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}

\author{A.~J.~Jackson}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
\affiliation{Department of Physical Chemistry, Lund University, SE-211 00
Lund, Sweden}

\author{R.~A.~Campbell}
\affiliation{Division of Pharmacy and Optometry, University of Manchester,
Manchester, UK}
\affiliation{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble,
France}

\author{T.~Arnold}
\email{tom.arnold@esss.se}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}
\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
\affiliation{ISIS Neutron and Muon Source, Science and Technology Facilities
Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot, OX11 0QX,
UK}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\maketitle

Note that the Journal names have been redected.

\section{Submission to Journal A: Rejection following peer review}

\subsection{Referee 1}
I am afraid I failed to see the special value in this manuscript
required for Journal A.

\subsection{Referee 2}
I don't think this is appropriate for Journal A.
In particular, the new Bayesian method requires more detail that should be included in a full paper.
A full paper in a specialty journal like Journal B would be better.

Full article - I also suggest that Journal C is not the best journal for this paper.
Journal B would be better.

\subsection{Referee 3}
This manuscript describes an examination of the structure of the insoluble monolayers formed by four phospholipids at the air/deep eutectic solvent interface by X-ray and neutron reflectometry.
The work reported examines a novel class of systems and finds some unexpected results, as well as utilizing some novel methodology.
Deep eutectic solvents are an important emerging class of liquids related to ionic liquids, with broad interest across the physical and material sciences.

The work is carefully done and conclusion reliable as far as I can ascertain.
However the authors should consider some minor revisions as follows before proceeding to publication.

\begin{enumerate}
\item It is incorrect to claim that these are the first studies of insoluble monolayers at an air/non-aqueous liquid interface. Lipid monolayers on formamide have been reported previously e.g. 10.1051/jp2:1995131 and 10.1021/jp9805412.

\item I could not find a clear description of the isotopic compositions of the components used for NR. ``hDES'' is unambiguous, but ``hdDES'' could mean many things. It may be detailed in the ESI but should be in the main paper.

\item Consider including the main ESI document (``si'' on GitHub) as a separate link. The extensive supplementary information provided including data files, is excellent, but specifically called-out references to ESI should be more readily accessible without searching GitHub or the Bath University repository dataset.
\end{enumerate}

The major outcomes of this work are the Bayesian methodology development and the unexpected head group volume of PG compared to water. The significance of this is not clear, and perhaps requires more exposition to justify publication in Journal A.

\subsection{Referee 4}
This paper describes a well-executed structural study of lipid monolayers assembled at an air/non-aqueous liquid interface based on x-ray and neutron reflectivity measurements. The results are solid, and there are many positive qualities to this study which will benefit researchers in the relevant field. However, I do not think that this paper merits a publication in Journal A mainly because the generality and robustness of the main scientific result (i.e., increased volume of the DMPG head group in DES relative to that in water) is uncertain, as explained further below. In my opinion, the study falls short of making a compelling case that it meets the ``broad interest'' criterion of the Journal A.

There are three potentially novel aspects to the study described in this paper:

\begin{enumerate}
\item Self-assembly of phospholipid monolayers at the free surface of an non-aqueous liquid, DES in the present work;

\item Application of a Bayesian approach to the analysis of x-ray and neutron reflectivity results;

\item Evidence for an apparent increase in the volume of DMPG head group at the DES interface, presumably due to ``unfolding of the PG head group,'' as compared to that at the water interface.
\end{enumerate}

For 1., the conclusion about the stable formation of the lipid monolayers at the DES surface is very convincing, and the authors’ claim about ``the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any non-aqueous media)'' may be technically correct. But at the same time, the observation is not surprising, given that (i) phospholipids are prime examples of amphiphilic surfactant molecules, and other amphiphilic surfactant molecules have been shown to form stable monolayers at air-DES interfaces (e.g., 10.1021/acs.langmuir.5b02596, 10.1063/1.4952444); and (ii) as noted by the authors, phospholipids in bulk DES have been shown to exhibit qualitatively similar behavior as those in bulk water, such as formation of bilayers and vesicles (10.1021/acs.langmuir.7b01561, 10.1039/C5SM02660A]). Moreover, formation of stable molecular monolayers on non-aqueous liquid surface has previously been observed, as demonstrated for example by a series of previous x-ray reflectivity-based studies of monolayers on mercury surface, by M. Deutsch, B. Ocko, P. Pershan, O. Magnussen, et al. [e.g., Magnussen et al., Nature 384, 250 (1996); Kraack et al., Science 298, 1404 (2002)].

For 2., the application of a Bayesian approach to the reflectivity analysis is well executed, and the authors do a good job of highlighting its utility, especially in illustrating the correlations between fitting parameters. The practitioners of x-ray and neutron reflectivity analysis will greatly benefit from these illustrative results. However, the novelty and potential impact of (ii) is technical rather than scientific.

In my opinion, aspect 3. of this study’s results is the most scientifically interesting. However, the evidence for the increased head-group volume in DES as compared to that in water is obtained for one particular molecule (DMPG) at the surface of one particular DES. Moreover, the interpretation for the physical origin of the increased head volume, i.e., unfolding of the PG group in DES as compared to the conformation in water, remains speculative and unsubstantiated (e.g., either experimentally or through simulation). As such, the conclusion about the increased PG head volume could be system-specific, and its generality and robustness is far from being well established. Demonstration of generality and robustness would require that similar evidence be gained for a series of PG-containing phospholipids and other types of lipid head groups with relatively weak intra-head interactions (like in PG as opposed to the zwitterionic PC’s).

On the basis of the above, I recommend that this paper be submitted elsewhere to a more specialized journal if its content is to remain as it is. Strengthening the generality of the study’s main scientific result and substantiation of the proposed ``unfolding'' mechanism should be a prerequisite before the manuscript is considered further for publication at the Journal A.

Additional specific comments:

\begin{itemize}
\item Use of ``chemically consistent'' constraints used makes sense and is very nice. Although fixing head-layer thickness $d_{h}$ for all surface pressures measured doesn’t have a good physical justification, it may not be such a serious offense given that this parameter usually has large error bars and doesn’t seem to show any trend with surface pressure that goes outside of the error bars (e.g., 10.1021/jz9002873).

\item Given that the LE phase consists of tail chains that are not stretched out as all-trans, it does not make sense to talk about the tail tilt angle $\theta_{t}$ for DLPC, DMPC, and DMPG. It is suggested that the analysis use the tail-layer thickness $d_{t}$, instead of $\theta_{t}$, as the freely varied parameter, with the constraint that $d_{t}$ be less than the upper bound of $t_{t}$, the maximum all-trans length of the tail. The tilt angle $\theta_{t}$ can be extracted and tabulated for DPPC, which is in the LC phase.

\item The NR roughness of 2.5 Angstrom for d54-DMPC at 25 mN/m seems too small, being comparable to the capillary-wave roughness of water at room T. It is suggested that the calculated capillary roughness (which depends on surface tension, temperature, molecular size, and instrumental resolution) be used as the lower-bound constraint for the surface roughness parameter used in the fitting.
\end{itemize}

\subsection{Changes following rejection}
\begin{itemize}
\item Following the comment from Referee 3, all claims that this is the first example of a lipid monolayer on a non-aqueous solvent have been removed. Instead claiming the first example of a lipid monolayer on an ionic solvent. Furthmore, the references mentioned for lipid monolayers on formamide have been included and mentioned in the text.
\item In the analysis process, the use of $\theta_t$ has been replaced simply with the fitting of a tail thickness, $d_t$. This removes the (inaccurate) assumption that the lipid tails are stretched out in an all-trans conformation (Referee 4).
\item The chemically consistent model that is used is detailed fulling in the main text of the paper now (Referee 2).
\item The justification for the constraint of the head thickness is further detailed, specifically that there is little variation noted in previous work (Referee 4).
\item Inclusions of a more detailed discussion of the inter parameter correlations, that are available from the use of Markov chain Monte Carlo sampling (Referee 2).
\item The lower limit for the NR roughness was increased to 3.3, as suggested by Referee 4.
\item A more detailed description of the neutron contrasts is given in the main text (Referee 3).
\item A link has been included on the GitHub page to access the \texttt{si.pdf} document more easily (Referee 3).
\end{itemize}

\end{document}

### 2019-01-10 reports/paper.tex
add adri to analysis
wording

@@
 The use of Bayesian inference and MCMC sampling allowed for the probing of the probability distribution function for each parameter individually.
-However, it also enables the pairwise interparameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (the same plots for each lipid at each surface pressure measured is available in the ESI \cite{SI2019}).
+However, it also enables the pairwise interparameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for each lipid at each surface pressure measured is available in the ESI \cite{SI2019}).
 These two-dimensional PDFs give important information about the correlations that are present between the parameters of the chemically-consistant model.
@@
 \section{Author Contributions}
-T.A., R.C., A.J.J., and K.J.E. were involved in the experimental design, and conducted the experiments along with A.S.-F. and R.A.C.
-A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, T.A., and R.A.C..
+T.A., A.J.J., and K.J.E. were involved in the experimental design, and conducted the experiments along with A.S.-F. and R.A.C.
+A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, A.S.-F., T.A., and R.A.C..
 A.R.M., A.S.-F. and T.A. wrote the manuscript, with input from all authors.

### 2019-01-11 reports/paper.tex
after adris comments

@@
   We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
-  However, the ability of the deep eutectic solvent to interact with the phosphatidylglycerol lipid head, leads to an apparent increase in its volume compared to that observed in water.
-  No such change was observed for the phosphocholine head, indicating that such interactions are head, and therefore solvent, specific.
-  This has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
+  This method allows for the monolayer structure to be determined, alongside the molecular volumes of the individual monolayer components without the need for water-specific constraints to be introduced.
+  Furthermore, using this method we are able to better understand the correlations present between parameters in the analytical model.
+  This example of a non-aqueous phospholipid monolayer has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
 \end{abstract}
@@
 This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any ionic solvent, to the best of the authors' knowledge).
-Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide being noted previously \cite{Weinbach1993,Graner1995}.
+Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide and mercury being noted previously \cite{Weinbach1993,Graner1995, Magnussen1996, Kraack2002}.
 We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
@@
 This indicates that there may be some effect arising from the solvation in choline cloride:glycerol causing an apparent increase in the PG component volume when compared with water.
+However, as this has only been shown for a single PG-lipid at the air-DES interface, the results are not conclusive.
 
@@
 \section{Author Contributions}
-T.A., A.J.J., and K.J.E. were involved in the experimental design, and conducted the experiments along with A.S.-F. and R.A.C.
+T.A., A.J.J., A.S.-F. and K.J.E. were involved in the experimental design, and conducted the experiments along with R.A.C..
 A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, A.S.-F., T.A., and R.A.C..

### 2019-01-11 reports/paper.tex
richards commnet
final draft

@@
 This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any ionic solvent, to the best of the authors' knowledge).
-Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide and mercury being noted previously \cite{Weinbach1993,Graner1995, Magnussen1996, Kraack2002}.
+Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide previously \cite{Graner1995}.
+Langmuir monolayers of non-phospholipid surfactant molecules have also been noted at air-formamide and air-mercury interfaces \cite{Weinbach1993,Magnussen1996,Kraack2002}.
+In these works, the authors noted that the non-aqueous had an effect on the overall structure of the monolayer, however, little was noted about underlaying mechanism.
 We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
@@
 
-The use of a Python library, such as refnx, enables the implementation custom models that contain chemically-relevant information as well as the application of probability distribution function (PDF) sampling techniques.
-The Python library emcee \cite{Foreman-Mackey2013} offers refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method \cite{Goodman2010}.
+The use of a Python library, such as refnx, enables the implementation of custom models that contain chemically-relevant information as well as the application of probability distribution function (PDF) sampling techniques.
+The Python library emcee \cite{Foreman-Mackey2013} allows refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method \cite{Goodman2010}.
 This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously \cite{Sivia2006}.
@@
 Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
-XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: \SIlist[list-units = single]{20;25;30;35}{\milli\newton\per\meter}, DMPC: \SIlist[list-units = single]{20;25;30;40}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, DMPG: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, as measured with an aluminium Wilhelmy plate; all measurements were conducted at \SI{22}{\celsius}.
+XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: \SIlist[list-units = single]{20;25;30;35}{\milli\newton\per\meter}, DMPC: \SIlist[list-units = single]{20;25;30;40}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, DMPG: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, as measured with an aluminium Wilhelmy plate; measurements were conducted at \SIlist{7;22}{\celsius}.
 The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
@@
 In Table \ref{tab:water}, there appears to be a general consensus that the component volume for the phosphocholine (PC) head is around \SIrange{320}{360}{\angstrom\cubed}, while the phosphatidylglycerol (PG) head is in the range \SIrange{289}{291}{\angstrom\cubed}.
-However, it is not clear is the head component volumes from the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
+However, it is not clear that the head component volumes from the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
 The charged nature of the zwitterionic or anionic lipid heads may have different interactions with the polar, but neutral water as compared to the charged DES components \cite{Sanchez-Fernandez2018}, which will affect the phospholipid head component volume.
@@
 Instead, these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG, and DLPC.
-Furthermore, it is known that, on water, increase surface pressure and the associated LE-LC phase transitions lead to a compression of the lipid tail volume \cite{Marsh2010,Small1984}, and this compaction has not necessarily been accounted for in the literature \cite{Campbell2018}.
+Furthermore, it is known that, on water, increased surface pressure and the associated LE-LC phase transitions lead to a compression of the lipid tail volume \cite{Marsh2010,Small1984}, and this compaction has not necessarily been accounted for in the literature \cite{Campbell2018}.
 This model avoids this issue by making no assumption about the molecular volumes and only considers surface pressures that we believe to be in the same phase.
@@
 Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
+The interfacial roughness was constrained to be greater than \SI{3.3}{\angstrom} in agreement with previous work \cite{Sanchez-Fernandez2016}.
 %
@@
 For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
-Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.
+Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background was constrained to the intensity of either the largest or second-largest $q$-value.
 
@@
 This indicates that there may be some effect arising from the solvation in choline cloride:glycerol causing an apparent increase in the PG component volume when compared with water.
-However, as this has only been shown for a single PG-lipid at the air-DES interface, the results are not conclusive.
+However, as this has only been shown for a single PG-lipid at the air-DES interface.
 
@@
 A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
-However, such an interaction would be weaker than that observed in the PC component.
+However, for PG, such an interaction would be weaker than that observed in the PC component.
 Therefore, this observed increase found for the PG component volume in DES when compared with water may be due to the unfolding of the PG head.
@@
 It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of \SI{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements \cite{Clifton2012}, which it slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
+Previously, DPPG has been reported to have a head layer thickness of \SI{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements \cite{Clifton2012}, which is slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
 
@@
 Another, important correlation is that between the head thickness and the tail thickness, $d_t$, again this is due to the lack of a well defined boundary between the head and tail layers.
-This is partially driven by the interfacial roughness that is present between the layers, with the correlation being more pronouned for phospholipids with shorted tails (e.g.
+This is partially driven by the interfacial roughness that is present between the layers, with the correlation being more pronouned for phospholipids with shorter tails (e.g.
 there is a greater correlation for DLPC than DPPC).
@@
 In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the partially charged solvent.
-Finally, the use of MCMC sampling of the reflectometry model parameter space give previously unseen insight into the correlations present in XRR data modelling, that should be considered in nature work of this nature.
+Finally, the use of MCMC sampling of the reflectometry model parameter space gives insight into the correlations present in XRR data modelling, that should be considered in nature work of this nature.
 
 The ability to determine the head component volume was facilitated by access to easy to use, open-source software that allowed for the straightforward use of a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
-Futhermore, this work presents the first, to our knowledge, use of chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
+Futhermore, to our knowledge, this work presents the first use of a chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
 
@@
 \acknowledgments{
-The authors thank Andrew Nelson for their help with the refnx software.
+The authors thank Andrew Nelson for useful discussions & assistance with the refnx software.
 A.R.M. is grateful to the University of Bath and Diamond Light Source for

### 2019-01-11 reports/si.tex
final draft

@@
 
-\title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
 \author{A.~R.~McCluskey}
@@
 \section{Probability distribution functions}
-The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc}-\ref{fig:dmpg4}.
+The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc1}-\ref{fig:dmpg4}.
 The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpcn1}-\ref{fig:dppcn2}.

### 2019-01-11 reports/paper.tex
preprint2

@@
 groups compared in this study, where R indicates the hydrocarbon tail;
-(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) \cite{SI2019}.}
+(a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
 \end{figure}
@@
 The charged nature of the zwitterionic or anionic lipid heads may have different interactions with the polar, but neutral water as compared to the charged DES components \cite{Sanchez-Fernandez2018}, which will affect the phospholipid head component volume.
-Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure, and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$ \cite{SI2019}.
+Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure, and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$.
 Instead, these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG, and DLPC.
@@
 This software allows for the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s refelectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}).
-This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under a CC BY-SA 4.0 licence \cite{SI2019}.
+This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under a CC BY-SA 4.0 licence.
 
@@
 DPPC was found to be in the LC phase and DMPC in the LE phase at room
-temperature for the surface pressures measured (see Section \ref{sec:gixd}) \cite{SI2019}.
+temperature for the surface pressures measured (see Section \ref{sec:gixd} in the ESI).
 We assume that DMPG and DLPC are also in the LE phase since there is no
@@
   of magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2019}.}
+  \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:lipids}
@@
 The values for $\phi_h$ was obtained from the appropriate use of Eqn.
-\ref{equ:phih} \cite{SI2019}.}
+\ref{equ:phih}.}
   \begin{ruledtabular}
@@
   magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity \cite{SI2019}.}
+  \SI{5e-6}{\per\square\angstrom}, for clarity.}
 	\label{fig:neutron}
@@
   confidence intervals for the varying parameters in the co-refined NR models.
-  The values of $\phi_h$ were found using Eqn. \ref{equ:phih} \cite{SI2019}.}
+  The values of $\phi_h$ were found using Eqn. \ref{equ:phih}.}
   \begin{ruledtabular}
@@
 The use of Bayesian inference and MCMC sampling allowed for the probing of the probability distribution function for each parameter individually.
-However, it also enables the pairwise interparameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for each lipid at each surface pressure measured is available in the ESI \cite{SI2019}).
+However, it also enables the pairwise interparameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for each lipid at each surface pressure measured is available in the ESI).
 These two-dimensional PDFs give important information about the correlations that are present between the parameters of the chemically-consistant model.
@@
 \acknowledgments{
-The authors thank Andrew Nelson for useful discussions & assistance with the refnx software.
+The authors thank Andrew Nelson for useful discussions \& assistance with the refnx software.
 A.R.M. is grateful to the University of Bath and Diamond Light Source for

### 2019-01-11 reports/si.tex
preprint2
update doi
si perfect

@@
 \begin{document}
-
+\title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the
+structure of lipid monolayers''}% Force line breaks with \\%
 \author{A.~R.~McCluskey}
@@
 \maketitle
+
+This Supplementary Information document is only part of a fully reproducible analysis workflow.
+The complete workflow, along with all datasets, figure files, and analysis/plotting scripts is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2538002) under a CC BY-SA 4.0 license.
 

### 2019-01-16 reports/paper.tex
move to zotero bib

@@
 %
-Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids \cite{Smith2014,Dai2013}.
-The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature \cite{Hammond2016,Hammond2017,Araujo2017}.
-Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity \cite{Pandey2014}, viscosity and surface tension \cite{Smith2014}, network charge \cite{Zahn2016}, and hydrophobicity \cite{Ribeiro2015,vanOsch2015}.
-Recently DES have also been shown to exhibit a ``solvophobic'' effect through the promotion of surfactant micelle formation \cite{Sanchez-Fernandez2016,Arnold2015,Hsieh2018,Banjare2018}, phospholipid bilayer formation \cite{Bryant2017,Bryant2016,Gutierrez2009}, and the ability to stabilise non-ionic polymer \cite{Sapir2016} and protein conformations \cite{Sanchez-Fernandez2017}.
+Deep eutectic solvents (DES) are green, sustainable liquids that are obtained through the combination of ionic species with compounds that act as hydrogen bond donors, such as sugars, alcohols, amines, and carboxylic acids \cite{smith_deep_2014,dai_natural_2013}.
+The resulting extensive hydrogen bonding network is able to stabilise the ionic species and allows the eutectic mixture to remain liquid at room temperature \cite{hammond_liquid_2016,hammond_resilience_2017,araujo_inelastic_2017}.
+Through different combinations of the precursor materials, it is possible to tune the solvent's physicochemical properties, such as polarity \cite{pandey_how_2014}, viscosity and surface tension \cite{smith_deep_2014}, network charge \cite{zahn_charge_2016}, and hydrophobicity \cite{ribeiro_menthol-based_2015,van_osch_hydrophobic_2015}.
+Recently DES have also been shown to exhibit a ``solvophobic'' effect through the promotion of surfactant micelle formation \cite{sanchez-fernandez_micellization_2016,arnold_surfactant_2015,hsieh_micelle_2018,banjare_self-assembly_2018}, phospholipid bilayer formation \cite{bryant_effect_2017,bryant_spontaneous_2016,gutierrez_freeze-drying_2009}, and the ability to stabilise non-ionic polymer \cite{sapir_properties_2016} and protein conformations \cite{sanchez-fernandez_protein_2017}.
 
@@
 As such, they have been used to gain insight into many biological processes that are technologically and medically relevant.
-For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer \cite{Mohwald1990,Kewalramani2010}.
+For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer \cite{mohwald_phospholipid_1990,kewalramani_effects_2010}.
 However, the native environment for lipids in-vivo is far from a simple aqueous solution.
-In fact, it has been suggested \cite{Dai2013,Hammond2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
+In fact, it has been suggested \cite{dai_natural_2013,hammond_resilience_2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
 
 This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any ionic solvent, to the best of the authors' knowledge).
-Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide previously \cite{Graner1995}.
-Langmuir monolayers of non-phospholipid surfactant molecules have also been noted at air-formamide and air-mercury interfaces \cite{Weinbach1993,Magnussen1996,Kraack2002}.
+Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide previously \cite{graner_phospholipidic_1995}.
+Langmuir monolayers of non-phospholipid surfactant molecules have also been noted at air-formamide and air-mercury interfaces \cite{weinbach_self-assembled_1993,magnussen_self-assembly_1996,kraack_structure_2002}.
 In these works, the authors noted that the non-aqueous had an effect on the overall structure of the monolayer, however, little was noted about underlaying mechanism.
@@
 Recent developments in computational resources and software have enabled powerful methodologies and algorithms to be harnessed by those from non-expert backgrounds.
-This has benefitted significantly from open-source software projects such as the Python language \cite{vanRossum1995} and the Jupyter notebooks framework \cite{Kluyver2016}.
-In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx \cite{Nelson2018,Nelson2018a}, MOTOFIT \cite{Nelson2006}, Rascal \cite{HughesRascal} Aurore \cite{Gerelli2016}, Refl1D \cite{Kienzle2011}, and GenX \cite{Bjorck2007}.
+This has benefitted significantly from open-source software projects such as the Python language \cite{van_rossum_python_1995} and the Jupyter notebooks framework \cite{kluyver_jupyter_2016}.
+In the area of NR and XRR, the landscape of data-analysis software is diverse, with a range of software packages available from a variety of sources; refnx \cite{nelson_refnx_2019,nelson_refnx_2018-1}, MOTOFIT \cite{nelson_co-refinement_2006}, Rascal \cite{hughes_rascal_nodate} Aurore \cite{gerelli_aurore_2016-1}, Refl1D \cite{kienzle_refl1d_2011}, and GenX \cite{bjorck_genx_2007}.
 
 The use of a Python library, such as refnx, enables the implementation of custom models that contain chemically-relevant information as well as the application of probability distribution function (PDF) sampling techniques.
-The Python library emcee \cite{Foreman-Mackey2013} allows refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method \cite{Goodman2010}.
-This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously \cite{Sivia2006}.
+The Python library emcee \cite{foreman-mackey_emcee_2013} allows refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method \cite{goodman_ensemble_2010}.
+This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously \cite{sivia_data_2006}.
 Bayesian inference gives an understanding of the PDF for the fitted parameters and therefore estimations of their inverse uncertainties and inter-parameter correlations.
@@
 Choline chloride (\SI{99}{\percent} \%, Sigma-Aldrich) and glycerol (\SI{99}{\percent}, Sigma-Aldrich) d$_9$-choline chloride (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) and d$_8$-glycerol (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) were purchased and used without further purification.
-The DES was prepared by mixing the precursors at a 1:2 ratio of chloine chlroide:glycerol, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed \cite{Smith2014}.
+The DES was prepared by mixing the precursors at a 1:2 ratio of chloine chlroide:glycerol, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed \cite{smith_deep_2014}.
 The solvent was equilibrated overnight at \SI{40}{\celsius} and subsequently stored under a dry atmosphere.
@@
 The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum.
-Those measurements showed that the water content of the solvent was kept below \SI{0.3}{wt/\percent} during all the experimental procedures presented here, which we assume to be negligible and have to little impact on the characteristics of the DES \cite{Hammond2016,Hammond2017}.
+Those measurements showed that the water content of the solvent was kept below \SI{0.3}{wt/\percent} during all the experimental procedures presented here, which we assume to be negligible and have to little impact on the characteristics of the DES \cite{hammond_liquid_2016,hammond_resilience_2017}.
 
@@
 %
-XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\electronvolt} photon energy using the double-crystal deflector \cite{Arnold2012}.
+XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\electronvolt} photon energy using the double-crystal deflector \cite{arnold_implementation_2012}.
 The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\per\angstrom}.
@@
 
-The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method \cite{Campbell2011}.
+The NR experiments were performed on FIGARO at the Institut Laue-Langevin using the time-of-flight method \cite{campbell_figaro_2011}.
 Data at two incident angles of \SI{0.62}{\degree} and \SI{3.8}{\degree} were measured to provide a momentum transfer range from \SIrange{0.005}{0.18}{\per\angstrom}.
@@
 %
-The use of XRR and NR to analyse the structure of phospholipids on the surface of water is well documented \cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}.
+The use of XRR and NR to analyse the structure of phospholipids on the surface of water is well documented \cite{mohwald_phospholipid_1990,kewalramani_effects_2010,bayerl_specular_1990,johnson_structure_1991,clifton_role_2012,helm_phospholipid_1987,daillant_x-ray_1990}.
 The models used in the rationalisation of XRR and NR data have varied significantly in numbers of layers present, use of interfactial roughness, and the parameterisation of the physical constraints applied.
 Frequently, these physical constraints include the volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}.
-Additionally, a recent evaluation of the applicability of different models for surfactant and phospholipid monolayers from the NR perspective has been published \cite{Campbell2018}, that suggests possible oversights in the modelling of NR data.
+Additionally, a recent evaluation of the applicability of different models for surfactant and phospholipid monolayers from the NR perspective has been published \cite{campbell_structure_2018}, that suggests possible oversights in the modelling of NR data.
 %
@@
   $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$
-  The values for the head component in Kucerka \emph{et al.} \cite{Kucerka2004}, were taken from Balgav\'{y} \emph{et al} \cite{Balgavy2001}.}
+  The values for the head component in Kucerka \emph{et al.} \cite{kucerka_determination_2004}, were taken from Balgav\'{y} \emph{et al} \cite{balgavy_evaluation_2001}.}
   \begin{ruledtabular}
@@
     \hline
-    Reference & \cite{Armen1998} & \cite{Sun1994} &
-    \cite{Kucerka2004,Balgavy2001}$^a$ & \cite{Armen1998}] & \cite{Kucerka2004,Balgavy2001}$^a$ & \cite{Armen1998} & \cite{Kucerka2004,Balgavy2001}$^a$ & \cite{Pan2012} &
-    \cite{Kucerka2012} \\
+    Reference & \cite{armen_phospholipid_1998} & \cite{sun_order_1994} &
+    \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{armen_phospholipid_1998}] & \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{armen_phospholipid_1998} & \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{pan_molecular_2012} &
+    \cite{kucerka_scattering_2012} \\
     \hline
@@
 However, it is not clear that the head component volumes from the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent.
-The charged nature of the zwitterionic or anionic lipid heads may have different interactions with the polar, but neutral water as compared to the charged DES components \cite{Sanchez-Fernandez2018}, which will affect the phospholipid head component volume.
+The charged nature of the zwitterionic or anionic lipid heads may have different interactions with the polar, but neutral water as compared to the charged DES components \cite{sanchez-fernandez_self-assembly_2018}, which will affect the phospholipid head component volume.
 Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure, and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$.
 Instead, these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG, and DLPC.
-Furthermore, it is known that, on water, increased surface pressure and the associated LE-LC phase transitions lead to a compression of the lipid tail volume \cite{Marsh2010,Small1984}, and this compaction has not necessarily been accounted for in the literature \cite{Campbell2018}.
+Furthermore, it is known that, on water, increased surface pressure and the associated LE-LC phase transitions lead to a compression of the lipid tail volume \cite{marsh_molecular_2010,small_lateral_1984}, and this compaction has not necessarily been accounted for in the literature \cite{campbell_structure_2018}.
 This model avoids this issue by making no assumption about the molecular volumes and only considers surface pressures that we believe to be in the same phase.
 
-Our chemically-consistent model has been implemented in the Python library refnx \cite{Nelson2018,Nelson2018a}.
-This software allows for the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s refelectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}).
+Our chemically-consistent model has been implemented in the Python library refnx \cite{nelson_refnx_2019,nelson_refnx_2018-1}.
+This software allows for the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s refelectivity model (a model that is widely used to calculate reflectivity \cite{abeles_sur_1948,parratt_surface_1954}).
 This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under a CC BY-SA 4.0 licence.
@@
 These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
-The tail layer is defined in the same fashion, except that the thickness, $d_t$, is limited such that it may be no greater than the maximum extended length of the lipid tail (the Tanford length, $t_t$ \cite{Tanford1980}), which is given in Table \ref{tab:invariant}, and that no solvent may interacalate into the layer (e.g.
+The tail layer is defined in the same fashion, except that the thickness, $d_t$, is limited such that it may be no greater than the maximum extended length of the lipid tail (the Tanford length, $t_t$ \cite{tanford_hydrophobic_1980}), which is given in Table \ref{tab:invariant}, and that no solvent may interacalate into the layer (e.g.
 $\phi_t = 0$).
@@
 where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer.
-To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
+To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{braun_polymers_2017}
 %
@@
 %
-Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
+Based on the work of Campbell \emph{et al.},\cite{campbell_structure_2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
 $\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
 Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.
-The interfacial roughness was constrained to be greater than \SI{3.3}{\angstrom} in agreement with previous work \cite{Sanchez-Fernandez2016}.
+The interfacial roughness was constrained to be greater than \SI{3.3}{\angstrom} in agreement with previous work \cite{sanchez-fernandez_micellization_2016}.
 %
@@
 	\caption{\label{tab:invariant} The invariant parameters within the chemically-consistent model.
-	$^a$Values obtained from the Tanford formula \cite{Tanford1980}.
-  $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}.}
+	$^a$Values obtained from the Tanford formula \cite{tanford_hydrophobic_1980}.
+  $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{sanchez-fernandez_micellization_2016}.}
   \begin{ruledtabular}
@@
 In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations.
-In keeping with the work of Campbell \emph{et al.} \cite{Campbell2018}, a single value for the head thickness was fitted for each lipid across all surface pressures, as the thickness of the head layer was considered to be dependent on molecular dimensions only, and has been shown to vary little with surface pressure \cite{Kewalramani2010}.
+In keeping with the work of Campbell \emph{et al.} \cite{campbell_structure_2018}, a single value for the head thickness was fitted for each lipid across all surface pressures, as the thickness of the head layer was considered to be dependent on molecular dimensions only, and has been shown to vary little with surface pressure \cite{kewalramani_effects_2010}.
 The following parameters were allowed to vary; $d_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given.
@@
 
-In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library \cite{Jones2001}, to find the parameters that gave the best fit to the data.
-The parameter space was then probed using the MCMC method available through emcee \cite{Foreman-Mackey2013}, which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
+In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library \cite{jones_scipy_2001}, to find the parameters that gave the best fit to the data.
+The parameter space was then probed using the MCMC method available through emcee \cite{foreman-mackey_emcee_2013}, which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
@@
 %
-From Tables \ref{tab:liptab} and \ref{tab:neutron}, we can see that, as expected and as found in previous work \cite{Mohwald1990,Vaknin1991}, the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
-Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$\si{\angstrom} at \SI{30}{\milli\newton\per\meter} \cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$\si{\angstrom} at \SI{40}{\milli\newton\per\meter} \cite{Helm1987} in water for DPPC.
+From Tables \ref{tab:liptab} and \ref{tab:neutron}, we can see that, as expected and as found in previous work \cite{mohwald_phospholipid_1990,vaknin_structural_1991}, the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
+Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$\si{\angstrom} at \SI{30}{\milli\newton\per\meter} \cite{johnson_structure_1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$\si{\angstrom} at \SI{40}{\milli\newton\per\meter} \cite{helm_phospholipid_1987} in water for DPPC.
 
@@
 It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateauing; for DPPC this occurs at \SI{20}{\milli\newton\per\meter}, DMPC at \SI{30}{\milli\newton\per\meter} and for DMPG and DLPC can be assumed to be at higher pressures than those studied.
-This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC \cite{Bayerl1990} and DPPC \cite{Campbell2018} at the air-water interface.
+This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC \cite{bayerl_specular_1990} and DPPC \cite{campbell_structure_2018} at the air-water interface.
 %
@@
 This can be rationalised by considering that when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.
-A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface \cite{Bayerl1990}.
+A similar effect has been observed when increasing the surface pressure from \SI{11}{\milli\newton\per\meter} to \SI{31}{\milli\newton\per\meter} for a DMPC/DMPG monolayer at the air-water interface \cite{bayerl_specular_1990}.
 
@@
 It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
-However, this reduction has been shown previously \cite{Campbell2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
+However, this reduction has been shown previously \cite{campbell_structure_2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
 In that work, the optimal value of the tail component volume for DPPC was found to be \SI{772}{\angstrom\cubed} at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\angstrom\cubed} found in this work at surface pressures of \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}.
@@
 It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail component volumes are also reduced in the current XRR measurements compared to those determined previously.
-The reduction was found to be between \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small and coworkers \cite{Small1984}.
+The reduction was found to be between \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small and coworkers \cite{small_lateral_1984}.
 DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
@@
 Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\angstrom\cubed} .
-The PG head component volume in water, from either DMPG using differential vibrating tube densimetry \cite{Pan2012} or POPG using molecular dynamics simulations \cite{Kucerka2012}, is noticeably smaller.
+The PG head component volume in water, from either DMPG using differential vibrating tube densimetry \cite{pan_molecular_2012} or POPG using molecular dynamics simulations \cite{kucerka_scattering_2012}, is noticeably smaller.
 This indicates that there may be some effect arising from the solvation in choline cloride:glycerol causing an apparent increase in the PG component volume when compared with water.
@@
 The major difference between the two head components is the fact PG component is negatively charged whereas the PC component is zwitterionic.
-It has been shown previously that the conformation for the PC component is folded in water \cite{Gilliams2016}, due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
+It has been shown previously that the conformation for the PC component is folded in water \cite{gillams_comparative_2016}, due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
 A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
@@
 It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of \SI{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements \cite{Clifton2012}, which is slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
+Previously, DPPG has been reported to have a head layer thickness of \SI{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements \cite{clifton_role_2012}, which is slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
 

### 2019-01-16 reports/si.tex
move to zotero bib

@@
 Importantly there is no such peak observed for DMPC at \SI{22}{\celsius} (see \ref{fig:gixd}), indicating that DMPC is in the LE phase at this temperature.
-The position of the (2,0) peak, approx \SI{1.48}{\per\angstrom}, is similar to that found under the same conditions in water.\cite{Watkins2009}
+The position of the (2,0) peak, approx \SI{1.48}{\per\angstrom}, is similar to that found under the same conditions in water.\cite{watkins_structure_2009}
 We therefore assume that the phase behaviour on the DES is similar to that observed on water and that the phases observed at \SI{30}{\milli\newton\per\meter} are the same at the other surface pressures measured with XRR and NR.

### 2019-01-16 reports/paper.tex
add usage statement

@@
   This example of a non-aqueous phospholipid monolayer has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
+  \begin{description}
+  \item[Usage]
+  Electronic Supplementary Information (ESI) available: All analysis/plotting
+  scripts and figure files, allowing for a fully reproducible, and automated,
+  analysis workflow for the work presented is available at
+  \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2538002)
+  under a CC BY-SA 4.0 license.
+  Reduced experimental datasets are available at
+  \url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
+  \end{description}
 \end{abstract}
-
 %\keywords{Suggested keywords}%Use showkeys class option if keyword

### 2019-02-13 reports/paper.tex
after review comments arm

@@
   In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and an ionic solvent.
-  Deep eutectic solvents are a novel class of environmentally friendly non-aqueous room temperature liquids with tunable properties, that have wide ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
+  Deep eutectic solvents are a novel class of environmentally friendly non-aqueous room temperature liquids with tunable properties, that have wide-ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
   We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
@@
 However, the native environment for lipids in-vivo is far from a simple aqueous solution.
-In fact, it has been suggested \cite{dai_natural_2013,hammond_resilience_2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
+In fact, it has been suggested \cite{dai_natural_2013,hammond_resilience_2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water-rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
+Despite the broad interest in these systems, the presence of stable phospholipid monolayers at the interface between air and an ionic solvent media has not been previously reported, to the best of the authors' knowledge.
 
 This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any ionic solvent, to the best of the authors' knowledge).
-Furthermore, this is one of very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide previously \cite{graner_phospholipidic_1995}.
+Furthermore, this is one of the very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide previously \cite{graner_phospholipidic_1995}.
 Langmuir monolayers of non-phospholipid surfactant molecules have also been noted at air-formamide and air-mercury interfaces \cite{weinbach_self-assembled_1993,magnussen_self-assembly_1996,kraack_structure_2002}.
-In these works, the authors noted that the non-aqueous had an effect on the overall structure of the monolayer, however, little was noted about underlaying mechanism.
+In these works, the authors noted that the non-aqueous had an effect on the overall structure of the monolayer, however, little was noted about the underlying mechanism.
 We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
@@
 The Python library emcee \cite{foreman-mackey_emcee_2013} allows refnx to access the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble method \cite{goodman_ensemble_2010}.
-This allows the sampling of the high-dimensionality parameter space, relevant in reflectomety analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously \cite{sivia_data_2006}.
+This allows the sampling of the high-dimensionality parameter space, relevant in reflectometry analysis, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously \cite{sivia_data_2006}.
 Bayesian inference gives an understanding of the PDF for the fitted parameters and therefore estimations of their inverse uncertainties and inter-parameter correlations.
+
+In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemically-consistent modelling of X-ray reflectometry (XRR) measurements at multiple surface pressures.
+Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air.
+This allowed the nature of two, chemically distinct, phospholipid head components to be understood in this ionic solvent, in addition to the effect of the tail chain length.
+The analysis was then extended to model complementary neutron reflectometry measurements for two contrasts of DMPC and DPPC at a single surface pressure [This paragraph was added following the comments of Ref 3].
 
@@
 Choline chloride (\SI{99}{\percent} \%, Sigma-Aldrich) and glycerol (\SI{99}{\percent}, Sigma-Aldrich) d$_9$-choline chloride (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) and d$_8$-glycerol (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) were purchased and used without further purification.
-The DES was prepared by mixing the precursors at a 1:2 ratio of chloine chlroide:glycerol, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed \cite{smith_deep_2014}.
+The DES was prepared by mixing the precursors at a 1:2 ratio of choline chloride:glycerol, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed \cite{smith_deep_2014}.
 The solvent was equilibrated overnight at \SI{40}{\celsius} and subsequently stored under a dry atmosphere.
@@
 
-1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails, \SI{>99}{\percent}), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails, \SI{>99}{\percent}), and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails, \SI{>99}{\percent}) were supplied by Avanti Polar Lipids and, 2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails, \SI{>99}{\percent}) was supplied by Sigma Aldrich and all were used without further purification.
+DPPC (C$_{16}$ tails, \SI{>99}{\percent}), DMPC (C$_{14}$ tails, \SI{>99}{\percent}), and the sodium salt of DMPG (C$_{14}$ tails, \SI{>99}{\percent}) [Added salt information for DMPG following Ref 1 comment] were supplied by Avanti Polar Lipids and, DLPC (C$_{12}$ tails, \SI{>99}{\percent}) was supplied by Sigma Aldrich and all were used without further purification.
 Deuterated versions of DPPC (d$_{62}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) and DMPC (d$_{54}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
-These phopholipids were dissolved in chloroform (\SI{0.5}{\milli\gram\per\milli\liter}) at room temperature.
+These phospholipids were dissolved in chloroform (\SI{0.5}{\milli\gram\per\milli\liter}) at room temperature.
 PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphatidylglycerol head component, these are shown in Figure \ref{fig:heads}.
@@
 Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough.
-In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough.
+In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level), it was not possible to use a Langmuir trough.
 Instead, small Delrin adsorption troughs were used that did not have controllable barriers.
@@
 XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: \SIlist[list-units = single]{20;25;30;35}{\milli\newton\per\meter}, DMPC: \SIlist[list-units = single]{20;25;30;40}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, DMPG: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, as measured with an aluminium Wilhelmy plate; measurements were conducted at \SIlist{7;22}{\celsius}.
-The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wetability of paper by the DES.
+The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wettability of paper by the DES.
 
@@
 The use of XRR and NR to analyse the structure of phospholipids on the surface of water is well documented \cite{mohwald_phospholipid_1990,kewalramani_effects_2010,bayerl_specular_1990,johnson_structure_1991,clifton_role_2012,helm_phospholipid_1987,daillant_x-ray_1990}.
-The models used in the rationalisation of XRR and NR data have varied significantly in numbers of layers present, use of interfactial roughness, and the parameterisation of the physical constraints applied.
+The models used in the rationalisation of XRR and NR data have varied significantly in numbers of layers present, use of interfacial roughness, and the parameterisation of the physical constraints applied.
 Frequently, these physical constraints include the volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}.
@@
 The charged nature of the zwitterionic or anionic lipid heads may have different interactions with the polar, but neutral water as compared to the charged DES components \cite{sanchez-fernandez_self-assembly_2018}, which will affect the phospholipid head component volume.
-Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure, and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$.
+Therefore, herein we apply a chemically-consistent model that allows for the co-refinement of reflectometry measurements at different surface pressure and makes no assumption of the component volume for the lipid head, $V_h$, or tail, $V_t$.
 Instead, these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG, and DLPC.
@@
 Our chemically-consistent model has been implemented in the Python library refnx \cite{nelson_refnx_2019,nelson_refnx_2018-1}.
-This software allows for the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s refelectivity model (a model that is widely used to calculate reflectivity \cite{abeles_sur_1948,parratt_surface_1954}).
+This software allows for the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s reflectivity model (a model that is widely used to calculate reflectivity \cite{abeles_sur_1948,parratt_surface_1954}).
 This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under a CC BY-SA 4.0 licence.
@@
 These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$.
-The tail layer is defined in the same fashion, except that the thickness, $d_t$, is limited such that it may be no greater than the maximum extended length of the lipid tail (the Tanford length, $t_t$ \cite{tanford_hydrophobic_1980}), which is given in Table \ref{tab:invariant}, and that no solvent may interacalate into the layer (e.g.
+The tail layer is defined in the same fashion, except that the thickness, $d_t$, is limited such that it may be no greater than the maximum extended length of the lipid tail (the Tanford length, $t_t$ \cite{tanford_hydrophobic_1980}), which is given in Table \ref{tab:invariant}, and that no solvent may intercalate into the layer (e.g.
 $\phi_t = 0$).
@@
 
-In order to justify the use of a single tail volume accross many surface pressures, it was necessary to ensure that the lipids remain in the same phase.
+In order to justify the use of a single tail volume across many surface pressures, it was necessary to ensure that the lipids remain in the same phase.
 On water, this can be demonstrated with a Langmuir isotherm.
-However, while we have confience that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the high viscosity of the DES.
-Instead we have used grazing incidence X-ray diffraction to confirm the
+However, while we have confidence that the individual surface pressures measured were reliable, we were unable to collect consistent Langmuir isotherm measurements, due to the high viscosity of the DES.
+Instead, we have used grazing incidence X-ray diffraction to confirm the
 phases of DMPC and DPPC at \SI{30}{\milli\newton\per\meter}.
@@
 
-In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library \cite{jones_scipy_2001}, to find the parameters that gave the best fit to the data.
+In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evolution method available to refnx from the scipy library \cite{jones_scipy_2001}, to find the parameters that gave the best fit to the data.
 The parameter space was then probed using the MCMC method available through emcee \cite{foreman-mackey_emcee_2013}, which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
-In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations.
+In the MCMC sampling, 200 walkers were used over 1000 iterations, following equilibration of 200 iterations.
 The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions.
@@
 However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e.
-they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.
+they do not account of systematic uncertainty in the measurement that is underrepresented, or unrepresented, in the experimental dataset.
 
@@
 The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
-Table \ref{tab:liptab} gives details of all varied parameters for each lipid at \SI{30}{\milli\newton\per\meter}, as well as the details of $\phi_h$ which was determined from Eqn. \ref{equ:phih}.
+Table \ref{tab:liptab} gives details of all varied parameters for each lipid at \SI{30}{\milli\newton\per\meter}, as well as the details of $\phi_h$ which was determined from Eqn.
+\ref{equ:phih} (the same details for the other surface pressures are available in the ESI) [Parentheses added following comments from Ref 3].
 %
@@
 Following the initial structural determination of the monolayer by XRR, NR was used to confirm the structure and show the applicability of the chemically-consistent model for DPPC and DMPC.
-The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}.
+The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron} (the other NR and SLD profiles can be found in the ESI) [Parentheses added following comments from Ref 3].
 Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $\phi_h$ as determined from NR.
@@
 %
-\subsection{Effect of compression on monolayer thickness}
+\subsection{Effect of compression on monolayer thickness [Typo removed]}
 %
@@
 The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
-It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateauing; for DPPC this occurs at \SI{20}{\milli\newton\per\meter}, DMPC at \SI{30}{\milli\newton\per\meter} and for DMPG and DLPC can be assumed to be at higher pressures than those studied.
+It can be observed that as the surface pressure increases, the thickness of the tail layer also increases, this rate of increase appears reduces for DPPC and DMPC at higher surface pressure indicating a maximum value is being reached [Sentence changed to reflect Ref 1 comments].
 This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC \cite{bayerl_specular_1990} and DPPC \cite{campbell_structure_2018} at the air-water interface.
@@
 The reduction was found to be between \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small and coworkers \cite{small_lateral_1984}.
-DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
-Notably this value is similar to that found in this work for DMPC, which has the same tail structure and suggests that our results are at least self-consistent.
+DMPG shows a small increase in the tail volume relative to the literature value quoted at a lower temperature.
+Notably, this value is similar to that found in this work for DMPC, which has the same tail structure and suggests that our results are at least self-consistent.
 
@@
 This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
-Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\angstrom\cubed} .
+Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\angstrom\cubed}.
 The PG head component volume in water, from either DMPG using differential vibrating tube densimetry \cite{pan_molecular_2012} or POPG using molecular dynamics simulations \cite{kucerka_scattering_2012}, is noticeably smaller.
-This indicates that there may be some effect arising from the solvation in choline cloride:glycerol causing an apparent increase in the PG component volume when compared with water.
+This indicates that there may be some effect arising from the solvation in choline chloride:glycerol causing an apparent increase in the PG component volume when compared with water.
 However, as this has only been shown for a single PG-lipid at the air-DES interface.
 
-The major difference between the two head components is the fact PG component is negatively charged whereas the PC component is zwitterionic.
-It has been shown previously that the conformation for the PC component is folded in water \cite{gillams_comparative_2016}, due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups.
-A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group.
-However, for PG, such an interaction would be weaker than that observed in the PC component.
-Therefore, this observed increase found for the PG component volume in DES when compared with water may be due to the unfolding of the PG head.
-This unfolding would be made possible by the charged nature of the solvent providing a greater screening effect for the PG head than are present in water.
-This effect may not be observed for the PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group.
-It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer.
-Previously, DPPG has been reported to have a head layer thickness of \SI{10.3\pm0.4}{\angstrom} at \SI{22}{\milli\newton\per\meter} from neutron reflectometry measurements \cite{clifton_role_2012}, which is slightly less than the \input{../output/dmpg/head.txt}\si{\angstrom} determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
+The major difference between the two head components is the fact that the PG component is present as a sodium salt, whereas the PC component is zwitterionic.
+The solvation of the PG salt occurs in the choline chloride:glycerol DES with a high degree of dissociation, whereas the zwitterionic PC salt is less soluble \cite{sanchez-fernandez_self-assembly_2018}.
+This will lead to the PG head component solvation sphere consisting of the larger, by comparison to water, DES molecules contributed to the apparent head component volume increase.
+Additionally, the charged nature of the PG head component following solvation may result in the electrostatic binding of the choline counterion from the DES, such preferential binding has been observed previously in the self-assembly of surfactant micelles \cite{sanchez-fernandez_counterion_2018}.
+The choline molecule offers a larger counterion than the sodium that is replaced, further contributing to the apparent head component volume increase [This paragraph has been adapted significantly following comments from Ref 1].
 
@@
 %
-The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head component volume is consistant between the pair of measurements for the same system.
+The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the value found for the head component volume is consistent between the pair of measurements for the same system.
 It is clear, that again stable monolayers of the lipids are forming at the air-DES interface, and that the component volumes determined from XRR measurements are robust enough to be used in the modelling of NR data.
-Futhermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components are consistant with that found in the NR models.
+Furthermore, the trends observed with increasing surface pressure in the XRR models, pertaining to the increasing tail thickness and decreasing solvent concentration in the head components are consistent with that found in the NR models.
 
@@
 The use of Bayesian inference and MCMC sampling allowed for the probing of the probability distribution function for each parameter individually.
-However, it also enables the pairwise interparameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for each lipid at each surface pressure measured is available in the ESI).
-These two-dimensional PDFs give important information about the correlations that are present between the parameters of the chemically-consistant model.
+However, it also enables the pairwise inter-parameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for the other XRR datasets and the NR datasets are available in the ESI) [Parentheses added following comments from Ref 3].
+These two-dimensional PDFs give important information about the correlations that are present between the parameters of the chemically-consistent model.
 The less circular in nature that the 2D PDF is, the greater the correlation that is present between the parameters, e.g.
-a north-east/south-westernly skewed PDF indicates a positive correlation (where an increase in one parameter correlates an increase in the other) while a north-west/south-easternly skewed PDF indicates a negative correlation (an increase in one correlates with a decrease in the other).
+a north-east/south-westerly skewed PDF indicates a positive correlation (where an increase in one parameter correlates an increase in the other) while a north-west/south-easterly skewed PDF indicates a negative correlation (an increase in one correlates with a decrease in the other).
 %
@@
 This correlation can be rationalised as a result of the SLD of the solvent and the head layer (which is \SI{50}{\percent} solvated) being similar, and therefore the boundary between the two is not easy to define.
-Such a correlations are unavoidable without considering many neutron contrasts of the lipid and solvent, due to the solvophilic nature of the lipid heads.
-Another, important correlation is that between the head thickness and the tail thickness, $d_t$, again this is due to the lack of a well defined boundary between the head and tail layers.
-This is partially driven by the interfacial roughness that is present between the layers, with the correlation being more pronouned for phospholipids with shorter tails (e.g.
+Such correlations are unavoidable without considering many neutron contrasts of the lipid and solvent, due to the solvophilic nature of the lipid heads.
+Another important correlation is that between the head thickness and the tail thickness, $d_t$, again this is due to the lack of a well-defined boundary between the head and tail layers.
+This is partially driven by the interfacial roughness that is present between the layers, with the correlation being more pronounced for phospholipids with shorter tails (e.g.
 there is a greater correlation for DLPC than DPPC).
@@
 %
-For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on a ionic solvent surface.
+For the first time, stable phosphocholine and phosphatidylglycerol lipid monolayers have been observed and characterised on an ionic solvent surface.
 Until the emergence of ionic liquids and DES, only a limited number of molecular solvents exhibited the ability to promote self-assembly and, to the best of our knowledge, only water and formamide among those had demonstrated the formation of phospholipid monolayers at the air-liquid interface.
@@
 A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
-This has the important implication that DES therefore offer the possibility of performing studies of model membranes in the absence of water.
-Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein membrane interactions and development of new technologies for drug delivery.
+This has the important implication that DES, therefore, offer the possibility of performing studies of model membranes in the absence of water.
+Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein-membrane interactions and development of new technologies for drug delivery.
 However, the PG component did show a significant difference; having a larger head component volume than observed for the same system in water.
 This suggests that the transfer of lipids to a DES is not just a simple substitution of the subphase.
-In this specific case we have proposed an explanation based on unfolding of the PG head component that is enabled by electrostatic screening of the component charges by the partially charged solvent.
+In this specific case, we have proposed an explanation based on the dissociation of the PG head component salt and the subsequent interaction with the DES.
 Finally, the use of MCMC sampling of the reflectometry model parameter space gives insight into the correlations present in XRR data modelling, that should be considered in nature work of this nature.
 
-The ability to determine the head component volume was facilitated by access to easy to use, open-source software that allowed for the straightforward use of a custom, chemically-consistant model within the analysis of the XRR and NR measurements.
-Futhermore, to our knowledge, this work presents the first use of a chemically-consistant parameterisation to co-refine XRR measurements at different surface concentrations.
+The ability to determine the head component volume was facilitated by access to easy to use, open-source software that allowed for the straightforward use of a custom, chemically-consistent model within the analysis of the XRR and NR measurements.
+Furthermore, to our knowledge, this work presents the first use of a chemically-consistent parameterisation to co-refine XRR measurements at different surface concentrations.
 
 \section{Author Contributions}
-T.A., A.J.J., A.S.-F. and K.J.E. were involved in the experimental design, and conducted the experiments along with R.A.C..
+T.A., A.J.J., A.S.-F. and K.J.E. were involved in the experimental design and conducted the experiments along with R.A.C..
 A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, A.S.-F., T.A., and R.A.C..
@@
 The authors thank Andrew Nelson for useful discussions \& assistance with the refnx software.
+Additionally, we thank Oliver Hammond for insightful discussions regarding the effect of the DES.
 A.R.M. is grateful to the University of Bath and Diamond Light Source for

### 2019-02-15 reports/paper.tex
after adris comments

@@
 
-This work presents the first observation of phospholipid monolayers at an air-DES interface (or for that matter, any ionic solvent, to the best of the authors' knowledge).
-Furthermore, this is one of the very few examples of a phospholipid monolayer at the interface between air and a non-aqueous solvent, with only formamide previously \cite{graner_phospholipidic_1995}.
-Langmuir monolayers of non-phospholipid surfactant molecules have also been noted at air-formamide and air-mercury interfaces \cite{weinbach_self-assembled_1993,magnussen_self-assembly_1996,kraack_structure_2002}.
-In these works, the authors noted that the non-aqueous had an effect on the overall structure of the monolayer, however, little was noted about the underlying mechanism.
-We have used a chemically-consistent approach to model X-ray (XRR) and neutron (NR) reflectometry measurements and thereby evaluate the effect of this non-aqueous solvent on the structure of phospholipid monolayers.
+The extension of lipid monolayers to non-aqueous systems, like DES, is relevant to increasing their applicability to new scientific and technological challanges.
+Investigations in non-aqueous system are however rather scarce, denoting the complexity of finding alternative solvents to water, where the solvophobic effect drives the self-association of amphphiles.
+In the absence of water, formamide has been reported to support the formation of lipid monolayers, where the amphphiles arrange in distinct phases depending on the surface pressure, as observed in water \cite{graner_phospholipidic_1995,weinbach_self-assembled_1993}.
+Similarly, Langmuir monolayers have been observed at the air-mercury interface, where the intrinsic disordered nature of the subphase dictates the structure of the amphiphilic monolayer \cite{magnussen_self-assembly_1996,kraack_structure_2002}.
+Surfactant monolayers have been reported for DES, showing similarites to those in water (e.g.
+variation in the surface concentration leads to changes in the structure of the monolayer), although specific charge interactions between the solvent and the surface appear to have an effect on the packing of the molecules \cite{arnold_surfactant_2015,sanchez-fernandez_self-assembly_2018}.
+An effort has also been extended to understanding the specific interactions between lipid monolayers and ionic liquids dissolved in water.
+Such an investigation has shown the ability of molten salts to interact with the charged head components of the phospholipids \cite{goncalves_da_silva_interaction_2018}.
+However, these experiments were performed in aqueous solutions of ionic liquids and the extent of ionic interactions in these mixtures cannot be extrapolated to pure systems, as the ionic correlation within the solvent are possibly very different.
+The absence of knowledge in the formation of lipid monolayers in ionic solvents has thus motivated the investigation presented here [This paragraph was adapted significantly to reflect the comments of Ref 3].
 
@@
 
-In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemically-consistent modelling of X-ray reflectometry (XRR) measurements at multiple surface pressures.
-Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air.
-This allowed the nature of two, chemically distinct, phospholipid head components to be understood in this ionic solvent, in addition to the effect of the tail chain length.
-The analysis was then extended to model complementary neutron reflectometry measurements for two contrasts of DMPC and DPPC at a single surface pressure [This paragraph was added following the comments of Ref 3].
+In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemically-consistent modelling of X-ray reflectometry (XRR) and neutron reflectometry (NR) measurements at multiple surface pressures.
+Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air using XRR.
+This allowed the nature of two chemically distinct phospholipid head components, phosphocholine (PC) and phosphoglycerol (PG) to be probed in this ionic solvent.
+In addition, the effect of the tail chain length in the assembly of the Langmuir monolayer was explored by comparing dipalmitoyl (DP), dimyristoyl (DM) and dilauroyl (DL) tails.
+The analysis was then extended to model complementary NR data for two contrasts of DMPC and DPPC at a single surface pressure. Data were analysed using a novel approach developed by the authors.
+This combines the optical matrix for calculating the reflectivity profiles, a traditional approach to fit reflectivity data, and Bayesian inference \cite{abeles_sur_1948,parratt_surface_1954} [This paragraph was added following the comments of Ref 3].
 
@@
 groups compared in this study, where R indicates the hydrocarbon tail;
-(a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
+(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) [Figure modified to include sodium cation].}
 \end{figure}
@@
 The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
+Although lipid monolayers on water often reach values above \SI{50}{\milli\newton\per\meter}, signifying a decrease in surface tension of ca.
+\SI{20}{\milli\newton\per\meter} upon addition of lipid, it was not possible to reach those values for the monolayers on DES \cite{mohwald_phospholipid_1990}.
+The surface tension of pure choline chloride:glycerol has been previously reported to be \SI{63.5\pm0.5}{\milli\newton\per\meter} \cite{sanchez-fernandez_micellization_2016}.
+This means that a surface pressure of ca. \SI{40}{\milli\newton\per\meter} in choline chloride:glycerol will be reached with a reduction of ca. \SI{20}{\milli\newton\per\meter} in the surface tension.
+Interestingly, the absolute values of surface tension reduction in both water and choline chloride:glycerol upon addition of lipid are similar.
+Therefore, surface pressures of up to \SI{40}{\milli\newton\per\meter} were measured for the monolayers on DES, when possible [This section has been added following comments from Refs 1 \& 3].
 The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
@@
     \caption{\small The NR and SLD profiles at a surface pressure of
-  20 mNm$^{-1}$ for two contrasts (see legend above each plot); (a) DMPC,
-  (b) DPPC. The NR profiles have been offset in the $y$-axis by an order of
-  magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity.}
+  20 mNm$^{-1}$ for two contrasts, the solid line identifing the hdDES contrast and the dash line the hDES contrast; (a) DMPC, (b) DPPC.
+The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
     \label{fig:neutron}
@@
 From Tables \ref{tab:liptab} and \ref{tab:neutron}, we can see that, as expected and as found in previous work \cite{mohwald_phospholipid_1990,vaknin_structural_1991}, the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
-Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$\si{\angstrom} at \SI{30}{\milli\newton\per\meter} \cite{johnson_structure_1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$\si{\angstrom} at \SI{40}{\milli\newton\per\meter} \cite{helm_phospholipid_1987} in water for DPPC.
+Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} \cite{johnson_structure_1991} in water for DMPC, and \input{../output/dppc/tail30.txt}~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$~\si{\angstrom} at \SI{40}{\milli\newton\per\meter} \cite{helm_phospholipid_1987} in water for DPPC.
 
 The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
-It can be observed that as the surface pressure increases, the thickness of the tail layer also increases, this rate of increase appears reduces for DPPC and DMPC at higher surface pressure indicating a maximum value is being reached [Sentence changed to reflect Ref 1 comments].
-This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC \cite{bayerl_specular_1990} and DPPC \cite{campbell_structure_2018} at the air-water interface.
+As it is commonly observed for lipid monolayers at the air-water interface, an increase in surface pressure results in an increase in the thickness of the tail layer.
+The variation of this parameter differs for each of the lipids.
+For DLPC and DMPC a gradual increase in the thickness is observed at the surface pressures measured here.
+For DMPC and DPPC however, after a gradual increase in thickness between \SIlist{15;25}{\milli\newton\per\meter}, a plateau is reached.
+this is indicative of the formation of a compacted monolayer where further compresson does not produce further changes in the thicknes of the tail layer.
+This behaviour has been seen for DMPC and DPPC monolayers, where the formation of the condensed phases is reached at high surface concentrations \cite{mohwald_phospholipid_1990} [This description of the plot has been adapted following comments from Ref 1].
 %
@@
     \caption{\small The PDFs of the head volume (left) and variation of
-  $d_t$ (squares) and $\phi_h$ (circles) with surface pressure for each of
-  the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG.}
+  $d_t$ (crosses) and $\phi_h$ (circles) with surface pressure for each of
+  the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG [This figure has been modified slightly to improve clarity].}
     \label{fig:lipresults}
@@
 However, this reduction has been shown previously \cite{campbell_structure_2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
-In that work, the optimal value of the tail component volume for DPPC was found to be \SI{772}{\angstrom\cubed} at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\angstrom\cubed} found in this work at surface pressures of \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}.
+In that work, the optimal value of the tail component volume for DPPC was found to be \SI{772}{\angstrom\cubed} at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt}~\si{\angstrom\cubed} found in this work at surface pressures of \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}.
 
@@
 This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
-Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\si{\angstrom\cubed}.
+Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}~\si{\angstrom\cubed}.
 The PG head component volume in water, from either DMPG using differential vibrating tube densimetry \cite{pan_molecular_2012} or POPG using molecular dynamics simulations \cite{kucerka_scattering_2012}, is noticeably smaller.
@@
 
-The major difference between the two head components is the fact that the PG component is present as a sodium salt, whereas the PC component is zwitterionic.
-The solvation of the PG salt occurs in the choline chloride:glycerol DES with a high degree of dissociation, whereas the zwitterionic PC salt is less soluble \cite{sanchez-fernandez_self-assembly_2018}.
-This will lead to the PG head component solvation sphere consisting of the larger, by comparison to water, DES molecules contributed to the apparent head component volume increase.
-Additionally, the charged nature of the PG head component following solvation may result in the electrostatic binding of the choline counterion from the DES, such preferential binding has been observed previously in the self-assembly of surfactant micelles \cite{sanchez-fernandez_counterion_2018}.
-The choline molecule offers a larger counterion than the sodium that is replaced, further contributing to the apparent head component volume increase [This paragraph has been adapted significantly following comments from Ref 1].
+The major difference between the two head components is the fact that the PG component is present as a sodium salt, whereas the PC component is zwitterionic in nature.
+The anionic PG lipid will thuis be affected by association with cations in solution, complementing the solvation solvation of the headgroup.
+This has been previously reported for water, where the interaction of the PG component with cations depended on a variety of factors, including ionic strength of the subphase \cite{grigoriev_effect_1999}.
+
+We hypothesise that the interaction of the anionic head component with solvated ions in the bulk DES is significantly more complex.
+In choline chloride:glycerol, the anionic head component is capable of binding sodium ions, the native lipid salt, and choline ions, from the solvent, as has been reported previously for sufactant micelles \cite{sanchez-fernandez_counterion_2018}.
+Although it is unclear the extent of interaction for each of the cations, the partial or total binding will screen the lipid charge and allow the backbone of the head component to swell, resulting in the apparent increase of the PG head component volume in comparison ot that in water.
+The zwitterionic moiety has previously been shown to be soluble in choline chloride:glycerol, where the carges in the head component may lead to variations in the solvent structure due to electrostatic interactions with the choline cations of the solvent \cite{bryant_effect_2017,sanchez-fernandez_self-assembly_2018}.
+The extent of the screening effect by choline ions may not be complete, leaving the remnant charges free to interact, allowing the conformation of the lipid head component to resemble that observed in water.
+This would result in a significantly weaker effect of the DES on the PC head component volume, resulting from short range electrostatic attractions between the phosphate and choline moieties of the lipid [These two paragraphs has been adapted significantly following comments from Ref 1].
 

### 2019-02-19 reports/paper.tex
after reference comments and tom fixing

@@
 In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and an ionic solvent.
-  Deep eutectic solvents are a novel class of environmentally friendly non-aqueous room temperature liquids with tunable properties, that have wide-ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
+Deep eutectic solvents are a novel class of environmentally friendly, non-aqueous, room temperature liquids with tunable properties, that have wide-ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
 We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
-  This method allows for the monolayer structure to be determined, alongside the molecular volumes of the individual monolayer components without the need for water-specific constraints to be introduced.
+This method allows for the monolayer structure to be determined, alongside the molecular volumes of the individual monolayer components, without the need for water-specific constraints to be introduced.
 Furthermore, using this method we are able to better understand the correlations present between parameters in the analytical model.
@@
 For example, investigations at the air/salt-water interface have identified the importance that interactions between charged phospholipid heads and ions present in solution have on the structure, monomer packing and stability of the monolayer \cite{mohwald_phospholipid_1990,kewalramani_effects_2010}.
-However, the native environment for lipids in-vivo is far from a simple aqueous solution.
+However, the native environment for lipids \emph{in-vivo} is far from a simple aqueous solution.
 In fact, it has been suggested \cite{dai_natural_2013,hammond_resilience_2017} that DES might form within the crowded cellular environment and could assist in solubilizing biological species in an intermediate environment between that of the hydrophobic phospholipid tails and highly polar water-rich regions, thereby assisting survival under extreme conditions such as freezing temperatures or drought where the water content of cells is restricted.
@@
 
-The extension of lipid monolayers to non-aqueous systems, like DES, is relevant to increasing their applicability to new scientific and technological challanges.
-Investigations in non-aqueous system are however rather scarce, denoting the complexity of finding alternative solvents to water, where the solvophobic effect drives the self-association of amphphiles.
-In the absence of water, formamide has been reported to support the formation of lipid monolayers, where the amphphiles arrange in distinct phases depending on the surface pressure, as observed in water \cite{graner_phospholipidic_1995,weinbach_self-assembled_1993}.
-Similarly, Langmuir monolayers have been observed at the air-mercury interface, where the intrinsic disordered nature of the subphase dictates the structure of the amphiphilic monolayer \cite{magnussen_self-assembly_1996,kraack_structure_2002}.
-Surfactant monolayers have been reported for DES, showing similarites to those in water (e.g.
-variation in the surface concentration leads to changes in the structure of the monolayer), although specific charge interactions between the solvent and the surface appear to have an effect on the packing of the molecules \cite{arnold_surfactant_2015,sanchez-fernandez_self-assembly_2018}.
-An effort has also been extended to understanding the specific interactions between lipid monolayers and ionic liquids dissolved in water.
-Such an investigation has shown the ability of molten salts to interact with the charged head components of the phospholipids \cite{goncalves_da_silva_interaction_2018}.
-However, these experiments were performed in aqueous solutions of ionic liquids and the extent of ionic interactions in these mixtures cannot be extrapolated to pure systems, as the ionic correlation within the solvent are possibly very different.
-The absence of knowledge in the formation of lipid monolayers in ionic solvents has thus motivated the investigation presented here [This paragraph was adapted significantly to reflect the comments of Ref 3].
+The study of lipid monolayers on a non-aqueous solvent like DES is relevant to some potential new scientific areas or technological applications.
+For example, it may be possible to study the interactions of proteins with model membranes in a zero or low water environment, or even at low temperatures where aqueous based model membranes are not practical.
+To enable such experiments we must first understand how lipid monolayers are affected by a non-aqueous environment.
+Published studies covering such non-aqueous systems are, however, rather scarce mirroring the availability of solvents that show a solvophobic effect comparable to water.
+In the absence of water, formamide has been reported to support the formation of lipid monolayers \cite{graner_phospholipidic_1995, weinbach_self-assembled_1993}.
+Monolayers have also been observed at the air-mercury interface \cite{magnussen_self-assembly_1996, kraack_structure_2002}, although in this case, the similarity to water is somewhat limited.
+We have recently shown that self-assembly of surfactant monolayers is possible for DES with behaviour that is much more comparable to that seen in water \cite{arnold_surfactant_2015, sanchez-fernandez_self-assembly_2018} [This paragraph was adapted significantly to reflect the comments of Ref 3].
+
+In this work, we have investigated the structure of phospholipid monolayers at the air-DES interface.
+To do this we have used the combination of both X-ray and neutron reflectometry (XRR \& NR), techniques that allow detailed structures to be determined with near-atomic resolution.
+In order to interpret our results, we have used a novel analysis method which allows us to sufficiently constrain our model while using Bayesian inference \cite{abeles_sur_1948, parratt_surface_1954} to properly quantify the errors and correlations inherent in such models of reflectometry data.
+Specifically, we have constrained the model to ensure that it is chemically self-consistent across multiple measurements at various surface pressures.
+Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (sodium salt) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air.
+This has allowed a comparison of two chemically distinct phospholipid head components, the zwitterionic phosphocholine (PC) and the anionic phosphoglycerol (PG) to be probed in this ionic solvent (Figure \ref{fig:heads}).
+In addition, the effect of the tail chain length in the assembly of the Langmuir monolayer was explored by comparing molecules with progressively increasing tail length (12, 14 and 16 carbon atoms in each of the two hydrocarbon chains in each molecule).
+Our study is inevitably limited in extent due to the limited availability of X-ray and neutron beamtime together with the prohibitive expense of deuterated chemicals.
+However, we believe that this work both hints at interesting differences in behaviour for phospholipids monolayers on DES and demonstrates how our approach to fitting can provide a quantitative understanding of this behaviour [This paragraph was added following the comments of Ref 3].
+%
+\begin{figure}
+\includegraphics[width=0.3\textwidth]{figures/head_groups}
+\caption{\label{fig:heads}\small The two lipid classes with different head
+groups compared in this study, where R indicates the hydrocarbon tail;
+(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) [Figure modified to include sodium cation].}
+\end{figure}
+%
 
@@
 
-In this work, we present the first investigation of the structure of phospholipid monolayers at the air-DES interface, as determined by chemically-consistent modelling of X-ray reflectometry (XRR) and neutron reflectometry (NR) measurements at multiple surface pressures.
-Four different phospholipids; 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG), were studied at the interface between a 1:2 mixture of choline chloride:glycerol and air using XRR.
-This allowed the nature of two chemically distinct phospholipid head components, phosphocholine (PC) and phosphoglycerol (PG) to be probed in this ionic solvent.
-In addition, the effect of the tail chain length in the assembly of the Langmuir monolayer was explored by comparing dipalmitoyl (DP), dimyristoyl (DM) and dilauroyl (DL) tails.
-The analysis was then extended to model complementary NR data for two contrasts of DMPC and DPPC at a single surface pressure. Data were analysed using a novel approach developed by the authors.
-This combines the optical matrix for calculating the reflectivity profiles, a traditional approach to fit reflectivity data, and Bayesian inference \cite{abeles_sur_1948,parratt_surface_1954} [This paragraph was added following the comments of Ref 3].
-
 \section{Experimental Section}
@@
 %
-Choline chloride (\SI{99}{\percent} \%, Sigma-Aldrich) and glycerol (\SI{99}{\percent}, Sigma-Aldrich) d$_9$-choline chloride (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) and d$_8$-glycerol (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) were purchased and used without further purification.
+Choline chloride (\SI{99}{\percent} \%, Sigma-Aldrich) and glycerol (\SI{99}{\percent}, Sigma-Aldrich), and d$_9$-choline chloride (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) and d$_8$-glycerol (\SI{99}{\percent}, \SI{98}{\percent} D, CK Isotopes) were purchased and used without further purification.
 The DES was prepared by mixing the precursors at a 1:2 ratio of choline chloride:glycerol, and heating at \SI{80}{\celsius} until a homogeneous, transparent liquid formed \cite{smith_deep_2014}.
@@
 The partially deuterated subphase was prepared using the following mixtures of precursors: \SI{1}{\mole} of \SI{0.38}{\mole} fraction of h-choline chloride/\SI{0.62}{\mole} fraction of d-choline chloride; and \SI{2}{\mole} of \SI{0.56}{\mole} fraction of h-glycerol/\SI{0.44}{\mole} fraction of d-glycerol.
-The solvent was subsequently prepared following the procedure discussed above.
+The deuterated solvent was prepared following the procedure discussed above.
 
@@
 PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphatidylglycerol head component, these are shown in Figure \ref{fig:heads}.
-%
-\begin{figure}
-\includegraphics[width=0.3\textwidth]{figures/head_groups}
-\caption{\label{fig:heads}\small The two lipid classes with different head
-groups compared in this study, where R indicates the hydrocarbon tail;
-(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) [Figure modified to include sodium cation].}
-\end{figure}
-%
 
@@
   $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$
-  The values for the head component in Kucerka \emph{et al.} \cite{kucerka_determination_2004}, were taken from Balgav\'{y} \emph{et al} \cite{balgavy_evaluation_2001}.}
+  The values for the head component in Kucerka \emph{et al.} \cite{kucerka_determination_2004}, were taken from Balgav\'{y} \emph{et al.} \cite{balgavy_evaluation_2001}.}
   \begin{ruledtabular}
@@
     Reference & \cite{armen_phospholipid_1998} & \cite{sun_order_1994} &
-    \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{armen_phospholipid_1998}] & \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{armen_phospholipid_1998} & \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{pan_molecular_2012} &
+    \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{armen_phospholipid_1998} & \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{armen_phospholipid_1998} & \cite{kucerka_determination_2004,balgavy_evaluation_2001}$^a$ & \cite{pan_molecular_2012} &
     \cite{kucerka_scattering_2012} \\
@@
 where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer.
-To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{braun_polymers_2017}
+To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model \cite{braun_polymers_2017},
 %
@@
 %
-Based on the work of Campbell \emph{et al.},\cite{campbell_structure_2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
+Based on the work of Campbell \emph{et al.} \cite{campbell_structure_2018}, a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e.
 $\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer.
@@
 For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.
-Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background was constrained to the intensity of either the largest or second-largest $q$-value.
+Throughout all of the analyses, the reflectometry scale factor was allowed to vary freely, while the background was constrained to the intensity of either the largest or second-largest $q$-value.
 
@@
 The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions.
-This allowed the Shapiro test to be used to assess if each PDF was normally distributed.
-Parameters that were shown to be normally distributed are given with symmetric confidence intervals, while those that failed the Shapiro test are given with asymmetric confidence intervals.
+The Shapiro test to be used to assess if each PDF was normally distributed.
+Parameters that were shown to be normally distributed are given with symmetric confidence intervals, while those that failed the Shapiro test are given with asymmetric confidence intervals (\SI{95}{\percent} confidence intervals in both cases).
 However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e.
@@
 
+%
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/dlpc_ref_sld}
+    \includegraphics[width=0.45\textwidth]{figures/dmpc_ref_sld}
+    \includegraphics[width=0.45\textwidth]{figures/dppc_ref_sld}
+    \includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
+    \caption{\small The XRR profiles (left) and SLD profiles (right) for each
+  of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, and (d) DMPG, at the four
+  measured surface pressures; see legend above each plot. The different
+  surface pressure XRR profiles have been offset in the $y$-axis by an order
+  of magnitude and SLD profiles offset in the $y$-axis by
+  \SI{5e-6}{\per\square\angstrom}, for clarity.}
+    \label{fig:lipids}
+\end{figure}
+%
 \section{Results \& Discussions}
@@
 Table \ref{tab:liptab} gives details of all varied parameters for each lipid at \SI{30}{\milli\newton\per\meter}, as well as the details of $\phi_h$ which was determined from Eqn.
-\ref{equ:phih} (the same details for the other surface pressures are available in the ESI) [Parentheses added following comments from Ref 3].
-%
-\begin{figure}
-    \centering
-  \includegraphics[width=0.45\textwidth]{figures/dlpc_ref_sld}
-    \includegraphics[width=0.45\textwidth]{figures/dmpc_ref_sld}
-    \includegraphics[width=0.45\textwidth]{figures/dppc_ref_sld}
-    \includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
-    \caption{\small The XRR profiles (left) and SLD profiles (right) for each
-  of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four
-  measured surface pressures; see legend above each plot. The different
-  surface pressure XRR profiles have been offset in the $y$-axis by an order
-  of magnitude and SLD profiles offset in the $y$-axis by
-  \SI{5e-6}{\per\square\angstrom}, for clarity.}
-    \label{fig:lipids}
-\end{figure}
-%
+\ref{equ:phih} (the same details for the other surface pressures are available in Section \ref{sec:xrrpara} of the ESI) [Parentheses added following comments from Ref 3].
 %
@@
 Following the initial structural determination of the monolayer by XRR, NR was used to confirm the structure and show the applicability of the chemically-consistent model for DPPC and DMPC.
-The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron} (the other NR and SLD profiles can be found in the ESI) [Parentheses added following comments from Ref 3].
+The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron} (the other NR and SLD profiles can be found in Figure \ref{fig:sineutron} of the ESI) [Parentheses added following comments from Ref 3].
 Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $\phi_h$ as determined from NR.
@@
     \caption{\small The NR and SLD profiles at a surface pressure of
-  20 mNm$^{-1}$ for two contrasts, the solid line identifing the hdDES contrast and the dash line the hDES contrast; (a) DMPC, (b) DPPC.
+  20 mNm$^{-1}$ for two contrasts, the solid line identifing the hdDES contrast and the dashed line the hDES contrast; (a) DMPC, (b) DPPC.
 The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
@@
 
-The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}.
-As it is commonly observed for lipid monolayers at the air-water interface, an increase in surface pressure results in an increase in the thickness of the tail layer.
+The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}(e).
+As is commonly observed for lipid monolayers at the air-water interface, an increase in surface pressure results in an increase in the thickness of the tail layer.
 The variation of this parameter differs for each of the lipids.
@@
 For DMPC and DPPC however, after a gradual increase in thickness between \SIlist{15;25}{\milli\newton\per\meter}, a plateau is reached.
-this is indicative of the formation of a compacted monolayer where further compresson does not produce further changes in the thicknes of the tail layer.
+This is indicative of the formation of a compacted monolayer where further compression does not produce further changes in the thickness of the tail layer.
 This behaviour has been seen for DMPC and DPPC monolayers, where the formation of the condensed phases is reached at high surface concentrations \cite{mohwald_phospholipid_1990} [This description of the plot has been adapted following comments from Ref 1].
@@
     \centering
-  \includegraphics[width=0.45\textwidth]{figures/dlpc_vh_dt_phi}
-    \includegraphics[width=0.45\textwidth]{figures/dmpc_vh_dt_phi}
-    \includegraphics[width=0.45\textwidth]{figures/dppc_vh_dt_phi}
-    \includegraphics[width=0.45\textwidth]{figures/dmpg_vh_dt_phi}
-    \caption{\small The PDFs of the head volume (left) and variation of
-  $d_t$ (crosses) and $\phi_h$ (circles) with surface pressure for each of
-  the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG [This figure has been modified slightly to improve clarity].}
+    \includegraphics[width=0.45\textwidth]{figures/vh_dt_phih}
+    \caption{\small The PDFs of the head volume for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, and (d) DMPG, and the variation of the tail layer thickness (e) and volume fraction of solvent in the head layer (f); DLPC (circles), DMPC (squares), DPPC (triangles), and DMPG (crosses), trend lines have been added between the points to guide the eye.
+[This figure has been modified slightly to improve clarity].}
     \label{fig:lipresults}
@@
 %
-In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer.
+In Figure \ref{fig:lipresults}(f), it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer.
 This can be rationalised by considering that when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk.
@@
 %
-It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
+It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volumes of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
 It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
@@
 
-The major difference between the two head components is the fact that the PG component is present as a sodium salt, whereas the PC component is zwitterionic in nature.
-The anionic PG lipid will thuis be affected by association with cations in solution, complementing the solvation solvation of the headgroup.
-This has been previously reported for water, where the interaction of the PG component with cations depended on a variety of factors, including ionic strength of the subphase \cite{grigoriev_effect_1999}.
-
-We hypothesise that the interaction of the anionic head component with solvated ions in the bulk DES is significantly more complex.
-In choline chloride:glycerol, the anionic head component is capable of binding sodium ions, the native lipid salt, and choline ions, from the solvent, as has been reported previously for sufactant micelles \cite{sanchez-fernandez_counterion_2018}.
-Although it is unclear the extent of interaction for each of the cations, the partial or total binding will screen the lipid charge and allow the backbone of the head component to swell, resulting in the apparent increase of the PG head component volume in comparison ot that in water.
-The zwitterionic moiety has previously been shown to be soluble in choline chloride:glycerol, where the carges in the head component may lead to variations in the solvent structure due to electrostatic interactions with the choline cations of the solvent \cite{bryant_effect_2017,sanchez-fernandez_self-assembly_2018}.
-The extent of the screening effect by choline ions may not be complete, leaving the remnant charges free to interact, allowing the conformation of the lipid head component to resemble that observed in water.
-This would result in a significantly weaker effect of the DES on the PC head component volume, resulting from short range electrostatic attractions between the phosphate and choline moieties of the lipid [These two paragraphs has been adapted significantly following comments from Ref 1].
+The major difference between the two head groups of the lipids is that the PG is present as a sodium salt, whereas the PC is zwitterionic.
+When in solution the anionic PG head is expected to associate with cations in solution, as it does in water \cite{grigoriev_effect_1999} where such interactions depended on a variety of factors including the ionic strength.
+In the case of a DES, the environment is inherently ionic and therefore the interaction of an anionic lipid head may be more complex.
+As well as interacting with the sodium, the head is likely to interact with the choline cations, similar to behaviour reported previously for surfactant micelles \cite{sanchez-fernandez_counterion_2018}.
+The extent of interaction with each of the cations is unclear, but regardless it seems likely that the solvation of the PG head is improved in the DES relative to water.
+This better solvation would explain the apparent increase in the volume of the PG head since it would result in a swelling of this group through its strong interactions with the solvent.
+In the case of PC, the proximity of a local cation within the molecule results in the same folding of the head group seen in water because this interaction is less transient than the equivalent interactions with the solvent [This paragraph has been adapted significantly following comments from Ref 1].
 
@@
 The use of Bayesian inference and MCMC sampling allowed for the probing of the probability distribution function for each parameter individually.
-However, it also enables the pairwise inter-parameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for the other XRR datasets and the NR datasets are available in the ESI) [Parentheses added following comments from Ref 3].
+However, it also enables the pairwise inter-parameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for the other XRR datasets and the NR datasets are available in Figures \ref{fig:dlpc1} - \ref{fig:dppcn2} of the ESI) [Parentheses added following comments from Ref 3].
 These two-dimensional PDFs give important information about the correlations that are present between the parameters of the chemically-consistent model.
@@
 In particular, as can be seen in Figure \ref{fig:dmpcpdfs}, there is a positive correlation between the lipid head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$.
-This correlation can be rationalised as a result of the SLD of the solvent and the head layer (which is \SI{50}{\percent} solvated) being similar, and therefore the boundary between the two is not easy to define.
+This correlation can be rationalised as a result of the SLD of the solvent and the head layer (which is \SI{\sim50}{\percent} solvated) being similar, and therefore the boundary between the two is not easy to define.
 Such correlations are unavoidable without considering many neutron contrasts of the lipid and solvent, due to the solvophilic nature of the lipid heads.

### 2019-02-19 reports/si.tex
after reference comments and tom fixing

--- 2019-01-11 reports/si.tex
@@
 
-This Supplementary Information document is only part of a fully reproducible analysis workflow.
+This Supplementary Information document is only a part of a fully reproducible analysis workflow.
 The complete workflow, along with all datasets, figure files, and analysis/plotting scripts is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2538002) under a CC BY-SA 4.0 license.
@@
 \section{XRR parameters at each surface pressure}
+\label{sec:xrrpara}
 Tables \ref{tab:liptab1}-\ref{tab:liptab4} give the best fit values for the custom model that were fitted to each surface pressure, for each lipid.
@@
 \label{sec:gixd}
-We have already indicated that the surface pressure was measured using an Aluminium Wilhelmy plate because the standard paper plates did not wet properly.
+The surface pressure was measured using an Aluminium Wilhelmy plate because the standard paper plates did not wet properly.
 This method did allow us to measure Langmuir isotherms, but these were inconsistent and as such, not a reliable method for determining the phase of the lipid monolayers.
@@
 The presence of any diffraction feature indicates the presence of an LC phase at these temperatures.
-Importantly there is no such peak observed for DMPC at \SI{22}{\celsius} (see \ref{fig:gixd}), indicating that DMPC is in the LE phase at this temperature.
-The position of the (2,0) peak, approx \SI{1.48}{\per\angstrom}, is similar to that found under the same conditions in water.\cite{Watkins2009}
+Importantly there is no such peak observed for DMPC at \SI{22}{\celsius} (see Figure \ref{fig:gixd}), indicating that DMPC is in the LE phase at this temperature.
+The position of the (2,0) peak, approx \SI{1.48}{\per\angstrom}, is similar to that found under the same conditions in water \cite{watkins_structure_2009}.
 We therefore assume that the phase behaviour on the DES is similar to that observed on water and that the phases observed at \SI{30}{\milli\newton\per\meter} are the same at the other surface pressures measured with XRR and NR.
@@
 The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpcn1}-\ref{fig:dppcn2}.
-
-\section{Tables and Figures}
 
@@
 The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
-	\label{fig:neutron}
+	\label{fig:sineutron}
 \end{figure}

### 2019-02-19 notebooks/xrr_chain_analysis.py

@@ -7,7 +7,7 @@
 # 
 # It is first necessary to import the necessary modules for the analysis.
 
-# In[1]:
+# In[2]:
 
 
 # Standard libraries to import
@@ -34,7 +34,7 @@ import helper
 
 # These are parameters to make the plots pretty.
 
-# In[2]:
+# In[3]:
 
 
 mpl.rcParams['axes.labelsize']=44
@@ -94,7 +94,7 @@ refnx.version.full_version, scipy.version.version
 # 
 # For details see the `lipid_xrr` notebook.
 
-# In[19]:
+# In[7]:
 
 
 # Reading datasets into refnx format
@@ -209,7 +209,7 @@ global_objective = GlobalObjective([objective1, objective2, objective3, objectiv
 
 # The chain is read in by refnx, and processed to assigned it to the global objective. 
 
-# In[25]:
+# In[8]:
 
 
 chain = refnx.analysis.load_chain('{}/{}/chain.txt'.format(analysis_dir, lipid))
@@ -219,7 +219,7 @@ processed_chain = refnx.analysis.process_chain(global_objective, chain)
 
 # The global objective is printed to check it is accurate.
 
-# In[26]:
+# In[9]:
 
 
 print(global_objective)
@@ -227,7 +227,7 @@ print(global_objective)
 
 # Using the probability distribution functions from the processed chain, the PDFs for the tail layer thickness and the solvent content of the headgroup are defined. 
 
-# In[33]:
+# In[10]:
 
 
 tail1 = processed_chain[2].chain
@@ -247,7 +247,7 @@ solh4 = 1 - (processed_chain[4].chain / processed_chain[3].chain) * (
 
 # The reflectometry and SLD profile are then plotted. 
 
-# In[35]:
+# In[11]:
 
 
 fig = plt.figure(figsize=(20, 7.5))
@@ -286,69 +286,16 @@ plt.close()
 
 # The PDFs for the head volumes of the lipid and the variation of the tail thickness and solvent content with surface pressure are plotted. 
 
-# In[38]:
+# In[23]:
 
 
-fig = plt.figure(figsize=(20, 5.5))
[…]

### 2019-02-19 reports/paper.tex
remove edit comments

@@
 Monolayers have also been observed at the air-mercury interface \cite{magnussen_self-assembly_1996, kraack_structure_2002}, although in this case, the similarity to water is somewhat limited.
-We have recently shown that self-assembly of surfactant monolayers is possible for DES with behaviour that is much more comparable to that seen in water \cite{arnold_surfactant_2015, sanchez-fernandez_self-assembly_2018} [This paragraph was adapted significantly to reflect the comments of Ref 3].
+We have recently shown that self-assembly of surfactant monolayers is possible for DES with behaviour that is much more comparable to that seen in water \cite{arnold_surfactant_2015, sanchez-fernandez_self-assembly_2018}.
 
@@
 Our study is inevitably limited in extent due to the limited availability of X-ray and neutron beamtime together with the prohibitive expense of deuterated chemicals.
-However, we believe that this work both hints at interesting differences in behaviour for phospholipids monolayers on DES and demonstrates how our approach to fitting can provide a quantitative understanding of this behaviour [This paragraph was added following the comments of Ref 3].
+However, we believe that this work both hints at interesting differences in behaviour for phospholipids monolayers on DES and demonstrates how our approach to fitting can provide a quantitative understanding of this behaviour.
 %
@@
 groups compared in this study, where R indicates the hydrocarbon tail;
-(a) phosphatidylglycerol (PG), (b) phosphocholine (PC) [Figure modified to include sodium cation].}
+(a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
 \end{figure}
@@
 
-DPPC (C$_{16}$ tails, \SI{>99}{\percent}), DMPC (C$_{14}$ tails, \SI{>99}{\percent}), and the sodium salt of DMPG (C$_{14}$ tails, \SI{>99}{\percent}) [Added salt information for DMPG following Ref 1 comment] were supplied by Avanti Polar Lipids and, DLPC (C$_{12}$ tails, \SI{>99}{\percent}) was supplied by Sigma Aldrich and all were used without further purification.
+DPPC (C$_{16}$ tails, \SI{>99}{\percent}), DMPC (C$_{14}$ tails, \SI{>99}{\percent}), and the sodium salt of DMPG (C$_{14}$ tails, \SI{>99}{\percent}) were supplied by Avanti Polar Lipids and, DLPC (C$_{12}$ tails, \SI{>99}{\percent}) was supplied by Sigma Aldrich and all were used without further purification.
 Deuterated versions of DPPC (d$_{62}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) and DMPC (d$_{54}$-DPPC, \SI{>99}{\percent}, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification.
@@
 Interestingly, the absolute values of surface tension reduction in both water and choline chloride:glycerol upon addition of lipid are similar.
-Therefore, surface pressures of up to \SI{40}{\milli\newton\per\meter} were measured for the monolayers on DES, when possible [This section has been added following comments from Refs 1 \& 3].
+Therefore, surface pressures of up to \SI{40}{\milli\newton\per\meter} were measured for the monolayers on DES, when possible.
 The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
 Table \ref{tab:liptab} gives details of all varied parameters for each lipid at \SI{30}{\milli\newton\per\meter}, as well as the details of $\phi_h$ which was determined from Eqn.
-\ref{equ:phih} (the same details for the other surface pressures are available in Section \ref{sec:xrrpara} of the ESI) [Parentheses added following comments from Ref 3].
+\ref{equ:phih} (the same details for the other surface pressures are available in Section \ref{sec:xrrpara} of the ESI).
 %
@@
 Following the initial structural determination of the monolayer by XRR, NR was used to confirm the structure and show the applicability of the chemically-consistent model for DPPC and DMPC.
-The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron} (the other NR and SLD profiles can be found in Figure \ref{fig:sineutron} of the ESI) [Parentheses added following comments from Ref 3].
+The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron} (the other NR and SLD profiles can be found in Figure \ref{fig:sineutron} of the ESI).
 Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $\phi_h$ as determined from NR.
@@
 %
-\subsection{Effect of compression on monolayer thickness [Typo removed]}
+\subsection{Effect of compression on monolayer thickness}
 %
@@
 This is indicative of the formation of a compacted monolayer where further compression does not produce further changes in the thickness of the tail layer.
-This behaviour has been seen for DMPC and DPPC monolayers, where the formation of the condensed phases is reached at high surface concentrations \cite{mohwald_phospholipid_1990} [This description of the plot has been adapted following comments from Ref 1].
+This behaviour has been seen for DMPC and DPPC monolayers, where the formation of the condensed phases is reached at high surface concentrations \cite{mohwald_phospholipid_1990}.
 %
@@
     \includegraphics[width=0.45\textwidth]{figures/vh_dt_phih}
-    \caption{\small The PDFs of the head volume for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, and (d) DMPG, and the variation of the tail layer thickness (e) and volume fraction of solvent in the head layer (f); DLPC (circles), DMPC (squares), DPPC (triangles), and DMPG (crosses), trend lines have been added between the points to guide the eye.
-[This figure has been modified slightly to improve clarity].}
+    \caption{\small The PDFs of the head volume for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, and (d) DMPG, and the variation of the tail layer thickness (e) and volume fraction of solvent in the head layer (f); DLPC (circles), DMPC (squares), DPPC (triangles), and DMPG (crosses), trend lines have been added between the points to guide the eye.}
     \label{fig:lipresults}
@@
 This better solvation would explain the apparent increase in the volume of the PG head since it would result in a swelling of this group through its strong interactions with the solvent.
-In the case of PC, the proximity of a local cation within the molecule results in the same folding of the head group seen in water because this interaction is less transient than the equivalent interactions with the solvent [This paragraph has been adapted significantly following comments from Ref 1].
+In the case of PC, the proximity of a local cation within the molecule results in the same folding of the head group seen in water because this interaction is less transient than the equivalent interactions with the solvent.
 
@@
 The use of Bayesian inference and MCMC sampling allowed for the probing of the probability distribution function for each parameter individually.
-However, it also enables the pairwise inter-parameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for the other XRR datasets and the NR datasets are available in Figures \ref{fig:dlpc1} - \ref{fig:dppcn2} of the ESI) [Parentheses added following comments from Ref 3].
+However, it also enables the pairwise inter-parameter PDFs to be investigated, an example for DMPC at \SI{30}{\milli\newton\per\meter} is shown in Figure \ref{fig:dmpcpdfs} (similar plots for the other XRR datasets and the NR datasets are available in Figures \ref{fig:dlpc1} - \ref{fig:dppcn2} of the ESI).
 These two-dimensional PDFs give important information about the correlations that are present between the parameters of the chemically-consistent model.

### 2019-02-25 reports/paper.tex
final of paper

@@
   analysis workflow for the work presented is available at
-  \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2538002)
+  \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2573512)
   under a CC BY-SA 4.0 license.
   Reduced experimental datasets are available at
-  \url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
+  \url{https://doi.org/10.15125/BATH-00548}, under a CC-BY 4.0 license.
   \end{description}
@@
 The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
-Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
+Samples were equilibrated for at least one hour and preserved under an helium atmosphere to minimise the adsorption of water by the subphase.
 XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: \SIlist[list-units = single]{20;25;30;35}{\milli\newton\per\meter}, DMPC: \SIlist[list-units = single]{20;25;30;40}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, DMPG: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, as measured with an aluminium Wilhelmy plate; measurements were conducted at \SIlist{7;22}{\celsius}.
@@
 In the MCMC sampling, 200 walkers were used over 1000 iterations, following equilibration of 200 iterations.
-The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions.
-The Shapiro test to be used to assess if each PDF was normally distributed.
+The use of MCMC sampling allowed for a Bayesian inference of the PDF for each of the variables and their respective interactions and the Shapiro test to be used to assess if each PDF was normally distributed.
 Parameters that were shown to be normally distributed are given with symmetric confidence intervals, while those that failed the Shapiro test are given with asymmetric confidence intervals (\SI{95}{\percent} confidence intervals in both cases).
@@
 The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
-Although lipid monolayers on water often reach values above \SI{50}{\milli\newton\per\meter}, signifying a decrease in surface tension of ca.
+Although lipid monolayers on water often reach values above \SI{50}{\milli\newton\per\meter}, signifying a decrease in surface tension to ca.
 \SI{20}{\milli\newton\per\meter} upon addition of lipid, it was not possible to reach those values for the monolayers on DES \cite{mohwald_phospholipid_1990}.
 The surface tension of pure choline chloride:glycerol has been previously reported to be \SI{63.5\pm0.5}{\milli\newton\per\meter} \cite{sanchez-fernandez_micellization_2016}.
-This means that a surface pressure of ca. \SI{40}{\milli\newton\per\meter} in choline chloride:glycerol will be reached with a reduction of ca. \SI{20}{\milli\newton\per\meter} in the surface tension.
-Interestingly, the absolute values of surface tension reduction in both water and choline chloride:glycerol upon addition of lipid are similar.
+This means that a surface pressure of ca. \SI{40}{\milli\newton\per\meter} iin choline chloride:glycerol will also result in a reduction to ca. \SI{20}{\milli\newton\per\meter} in the surface tension.
+Interestingly, the absolute values of surface tension in both water and choline chloride:glycerol after addition of lipid are similar.
 Therefore, surface pressures of up to \SI{40}{\milli\newton\per\meter} were measured for the monolayers on DES, when possible.
@@
 From Tables \ref{tab:liptab} and \ref{tab:neutron}, we can see that, as expected and as found in previous work \cite{mohwald_phospholipid_1990,vaknin_structural_1991}, the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
-Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} \cite{johnson_structure_1991} in water for DMPC, and \input{../output/dppc/tail30.txt}~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$~\si{\angstrom} at \SI{40}{\milli\newton\per\meter} \cite{helm_phospholipid_1987} in water for DPPC.
+Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in water for DMPC \cite{johnson_structure_1991}, and \input{../output/dppc/tail30.txt}~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$~\si{\angstrom} at \SI{40}{\milli\newton\per\meter} in water for DPPC \cite{helm_phospholipid_1987}.
 
@@
 This indicates that there may be some effect arising from the solvation in choline chloride:glycerol causing an apparent increase in the PG component volume when compared with water.
-However, as this has only been shown for a single PG-lipid at the air-DES interface.
+However, this has only been shown for a single PG-lipid at the air–DES interface.
 
@@
 In this specific case, we have proposed an explanation based on the dissociation of the PG head component salt and the subsequent interaction with the DES.
-Finally, the use of MCMC sampling of the reflectometry model parameter space gives insight into the correlations present in XRR data modelling, that should be considered in nature work of this nature.
+Finally, the use of MCMC sampling of the reflectometry model parameter space gives insight into the correlations present in XRR data modelling, that should be considered in work of this nature.
 
@@
 T.A., A.J.J., A.S.-F. and K.J.E. were involved in the experimental design and conducted the experiments along with R.A.C..
+
 A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, A.S.-F., T.A., and R.A.C..
+
 A.R.M., A.S.-F. and T.A. wrote the manuscript, with input from all authors.

### 2019-02-26 reports/paper.tex
add new zenodo

@@
   analysis workflow for the work presented is available at
-  \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2573512)
+  \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2577796)
   under a CC BY-SA 4.0 license.
   Reduced experimental datasets are available at
-  \url{https://doi.org/10.15125/BATH-00548}, under a CC-BY 4.0 license.
+  DOI: 10.15125/BATH-00548, under a CC-BY 4.0 license.
   \end{description}
